### 2019-01-30 size_differentiated_export.tex
Initial ShareLaTeX Import

%\documentclass[]{article}

%\setlength{\parskip}{.5cm}
%\usepackage{natbib}
%\usepackage[table,xcdraw]{xcolor}
%\usepackage{graphicx}
%\usepackage{hyperref}
%\usepackage{amsmath}
%\usepackage{appendix}
%\usepackage[left=3cm,right=3cm]{geometry}

% Apply watermark to document
%\usepackage{draftwatermark}
%\SetWatermarkLightness{0.9}
%\SetWatermarkScale{5}
%\SetWatermarkText{DRAFT}

\documentclass[draft,linenumbers]{agujournal2018}
\usepackage{apacite}
\usepackage{url} %this package should fix any errors with URLs in refs.

% FIXME command
\newcommand{\fixme}[1]{\color{red}$<$\textbf{FIX ME: #1}$>$\color{black}}

% Trackchanges package
\usepackage{trackchanges}
%% PLEASE USE THE FOLLOWING COMMANDS
%   \note[editor]{The note} 
%   \annote[editor]{Text to annotate}{The note} 
%   \add[editor]{Text to add} 
%   \remove[editor]{Text to remove} 
%   \change[editor]{Text to remove}{Text to add}

\draftfalse

\journalname{Global Biochemical Cycles}

\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%
\title{Size-differentiated Export in different Dynamical Regimes in the Ocean}

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%
\author{M. Dever\affil{1}, D. Nicholson\affil{1}, M. Omand\affil{2}, and A. Mahadevan\affil{1}}
\affiliation{1}{Woods Hole Oceanographic Institution, Woods Hole, MA 02543, USA}
\affiliation{2}{Graduate School of Oceanography, University of Rhode Island, Narragansett, Rhode Island, USA}

\correspondingauthor{M. Dever}{mdever@whoi.edu}
%% ------------------------------------------------------------------------ %%
%
%  KEYPOINTS
%
%% ------------------------------------------------------------------------ %%

\begin{keypoints}
\item = enter point 1 here =
\item = enter point 2 here =
\item = enter point 3 here =
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%
\begin{abstract}
% Mat: I think that even with the submesoscale mechanism, export is mainly driven by gravitational sinking. So I'm moving the "Traditionally" to later. 
Export of particulate organic carbon (POC) is  mainly driven by gravitational sinking. Thus, traditionally, it is thought that  larger, faster-sinking particles make up most of the POC export flux. However, this need not be the case in a dynamic oceanic flow field, where the ocean velocity can influence the descent rate of particles. Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) the particle number size-spectrum slope, and (2) the ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export. The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important. The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles in POC export. A steeper particle size spectrum, also increases the contribution of smaller, slower-sinking particles. Implementing a remineralization scheme generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven. Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export. This study demonstrates that slow-sinking particles are significant contribution, and at times, can even dominate, the export flux. 
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%
%\begin{article}

%\maketitle

%{\color{red} NOTE: Following Roo's suggestion, I looked at the spectrum of biomass per velocity class vs time to see how it evolves. As Melissa suggested, it will be cool to include into a presentation, but I don't think it is worth including in the paper. I believe it would introduce too much additional concepts that would dilute the conclusions: the spectral shape is mostly determine by the pulse of particle crossing the export horizon. A constant reseeding of particles would be necessary to clearly put our point across using biomass spectra.}

\section{Introduction}

A major pathway transferring carbon from the atmosphere to the ocean is through photosynthesis and the production of Particulate Organic Carbon (POC) in the upper ocean. Sinking POC then allows the transfer of organic carbon from the upper ocean to the interior, leading to carbon sequestration over long time scales \citep{Falkowski_1998}. Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.

Traditionally, POC export is thought to be mainly driven by larger, faster-sinking particles. This reasoning relies on the concept of competing timescales between remineralization and the time required to sink below the base of the mixed layer. The physical processes involved in defining the sinking rate are traditionally assumed to be dominated by gravitational sinking. This is a reasonable assumption if one considers that vertical advective velocities in the ocean are generally much weaker than velocities associated with gravitational sinking.

Recent work demonstrates that the presence of mesoscale eddies can enhance carbon export through two main processes: First, by increasing primary productivity through the injection of nutrients into the euphotic layer, therefore increasing the particle concentration, logically leading to a greater export \citep{Levy_1998}. Second, by generating larger vertical velocities along the front located at the eddy perimeter \citep{vanHaren_2006, Waite_2016}. These studies demonstrate that ocean dynamics potentially play an important role in driving the carbon export from the euphotic layer to the ocean interior. This conclusion is further supported by a recent, yet large, body of literature focusing on ocean dynamics at submeso-scales (1-10 km) and the impact on biogeochemical processes \citep[see reviews in][]{Thomas_2008,Klein_2009,Mahadevan_2016}. Submesoscale dynamics are characterized by Rossby numbers of order 1, indicating that relative vorticity associated with ocean currents exceed the planetary vorticity. These regions typically develop in filaments in areas where sharp density fronts exist \citep{McWilliams_2016}. In this dynamical regime, geostrophic balance fails and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}. On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front. The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}. This asymmetry leads to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}. Just like at meso-scales, enhanced vertical velocities can generate either a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2012}, or can significantly increase the export of POC to the ocean interior \citep{Levy_2012, Estapa_2015,Omand_2015}.

The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales therefore provide a physical mechanism capable of exporting particles over a larger portion of the particle size spectrum. Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities. Considering the fact that, although containing less biomass, smaller particles are far more numerous than larger particles, the impact of submesoscale dynamics on the export of POC is potentially significant. Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe. Additionally, and despite recent methodological progress \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and are more often than not inferred from key parameters such as particle type, size, and density.

In this study, we rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale. Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior. Particles are released in two fundamentally different flow fields in terms of dynamics: one simulation is dominated by mesoscale dynamics, characterized by low Rossby numbers and weak vertical advective velocities, while the other is dominated by submesoscale dynamics, with fine-scale frontal structures and local Rossby numbers $\mathcal{O}$(1). Both simulations and the particle-tracking module are described in Section \ref{sec: Methods}. The impact of particles characteristics and ocean dynamics on the export of POC is quantified  in Section \ref{sec: Results}, and discussed in Section \ref{sec: Discussion}. Section \ref{sec: Conclusions} summarizes the key conclusions of the study.

\section{Methods}
\label{sec: Methods}
\subsection{Model setup and domains}

This study uses a non-hydrostatic, three-dimensional, numerical model called PSOM. Only a brief summary of its characteristics is provided here, as the model is exhaustively described in \cite{Mahadevan_1996a,Mahadevan_1996b}. The model domain is set in a channel configuration with periodic boundaries in the west and east, and solid boundaries in the south and north. The domain covers 112 km in the x-direction, 304 km in the y-direction, and 1000 m in the vertical (Figure \ref{fig: model_domain}). The horizontal resolution is set to 500 m, while the vertical resolution is represented by a stretched grid with 32 levels ranging in thickness from 1.25 m near the surface to 70 m at the lowermost level. The model is integrated numerically in time and evolves the temperature, salinity, free-surface height, pressure, and three-dimensional velocity fields from an initial state, subject to momentum and buoyancy fluxes applied through the surface boundary conditions.

% FIG1
\begin{figure}[ht]
	\centering
	\includegraphics[width = .6\linewidth]{figures/Fig1_model_domain}
	\caption{PSOM model setup. (a) Meridional profile of zonal winds scaling coefficient prescribed to PSOM, with a tapering at the north and south boundaries to reduce upwelling and downwelling, respectively. (b) Restoration factor used to dampen internal waves reflection at boundaries, as well as curl-driven upwelling and downwelling. (c) Surface net heat flux anomaly superimposed to the heat fluxes prescribed at $y = 150$ km.}
	\label{fig: model_domain}
\end{figure}

The zonal component of the  wind stress is prescribed at the surface throughout the model domain ($\tau_y =0$). Winds stress magnitude is, however, tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling that could contaminate the middle third of the model domain, where the analysis is focused (Figure \ref{fig: model_domain}a). A restoration time scale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress (Figure \ref{fig: model_domain}b). The restored regions also limit the reflection of internal waves at the solid boundaries back into the domain. Net surface heat fluxes are homogeneously prescribed throughout the domain. A linear meridional heat flux anomaly is superimposed to maintain a north/south gradient in net surface heat fluxes  (Figure \ref{fig: model_domain}c). The flux anomaly is zero in the center of the domain and has a slope of 1/24 W/m$^2$/km, estimated from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}.

Both wind stress and net heat fluxes are allowed to vary in time. Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory\footnote{https://www.pmel.noaa.gov/ocs/Papa}. Climatologies of daily zonal wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long time series. A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability. In all experiments, the simulation is allowed to spin-down, that is with no forcing, for the first 5 days. Forcing is then linearly ramped up between days 5 and 10, to reach realistic values at day 10.% (Figures \ref{fig: Papa_summer} and \ref{fig: Papa_winter}).

Initial background conditions are determined from a three-dimensional gridded field of temperature and salinity from ARGO floats \citep{Gaillard_2009,Gaillard_2016}. ARGO data is averaged monthly over the period 2002-2012 and two different months are used to initialized \textit{Papa\_summer} and \textit{Papa\_winter}. The north-south background density gradient is then intensified into three fronts located at $y = 75$, $y = 150$, and $y = 225$ km (Figure \ref{fig: model_domain}). The amplitude of the density gradient associated with the three fronts are determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \citep{Pelland_2016}. To reduce model spin-up time, density fronts are perturbed by a sinusoidal wave with a wavelength $\lambda = 112/n$, where $n$ is the closest integer to the 1st baroclinic deformation radius (n = 2 in this study). Similar PSOM configurations were successfully used in previous studies \citep{Mahadevan_2012,Omand_2015}.

Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics mimicking conditions int the northeast Pacific in the summertime. Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($<1$). \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region. A different dynamical regime is expected to dominate during wintertime, with submesoscale dynamics playing a more important role. Submesoscale dynamics are characterized by sharper density fronts, filament-like features and high localized Rossby number ($>1$) over spatial scales $\mathcal{O}$(1 km). Such dynamics are more likely to be found in the winter time, where mixed layer depth is deeper and density gradients enhanced \citep{Thompson_2016}. The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.

\subsubsection{\textit{Papa\_summer} Model Experiment}

In \textit{Papa\_summer}, PSOM is initialized based on climatological ARGO data in April. The magnitude of the density gradient across the front (i.e., frontal sharpness) is set to 3.34$\times$10$^{-6}$ kg/m$^3$/m, which corresponds to the 95$^{th}$ percentile of the PDF of density gradients measured in April from glider data collected in the region (Figure \ref{fig: Papa_summer} and Table \ref{tab: meso_vs_submeso}). The model is run with a timestep of 216 s and is allowed to spin-up for 60 days, allowing for the summer stratification to develop. The model is then run for 30 additional days, saving instantaneous model fields every 3 hours for particle tracking. The month of April is chosen for initialization so the experiment would capture the onset of positive net heat fluxes, and the summer restratification that ensues (Figure \ref{fig: Papa_summer}). In this region, the summer restratification is associated with large primary productivity and therefore large particle production and potentially export \citep[e.g., fecal pallets, dead phytoplankter; ][]{Plant_2016}.

%TAB1
\begin{table}[ht]
\caption{Summary of the key characteristics of PSOM experiments \textit{Papa\_summer} and \textit{Papa\_winter}.}
	\label{tab: meso_vs_submeso}
	\centering
 \centering
\begin{tabular}{|l|c|c|}
		\hline
											& \textit{Papa\_summer} & \textit{Papa\_winter} \\
		\hline
		Period 								& April -- July         & January -- March      \\
		Spin-up								& 60 days               & 50 days               \\
		Advective timestep				    & 216 s                 & 108 s                 \\
		Horizontal diffusivity			    & 1 m$^2$/s             & 0.2 m$^2$/s           \\
		Restoration timescale			    & 3 days                & 15 days               \\
		Maximum M$^2$ ($\times$10$^{-8}$)	& 3.20 s$^{-2}$         & 33.9 s$^{-2}$         \\	
		\hline
	\end{tabular}
\end{table}

% \begin{table}
% \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
% \centering
% \begin{tabular}{l c}
% \hline
%  Run  & Time (min)  \\
% \hline
%   $l1$  & 260   \\
%   $l2$  & 300   \\
%   $l3$  & 340   \\
%   $h1$  & 270   \\
%   $h2$  & 250   \\
%   $h3$  & 380   \\
%   $r1$  & 370   \\
%   $r2$  & 390   \\
% \hline
% \multicolumn{2}{l}{$^{a}$Footnote text here.}
% \end{tabular}
% \end{table}

% FIG2
\begin{figure}[ht]
	\includegraphics[width = 1\linewidth]{figures/Fig2_Papa500_summer}
	\caption{PSOM configuration for \textit{Papa\_summer}. (a) Time series of net heat fluxes and wind stress prescribed at the surface. Notice the positive heat fluxes, as well as downfront winds (i.e. eastward) persisting throughout the experiment. (b)-(d) horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 105, 135, and 165. Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$). (e) Vertical profile of the buoyancy frequency $N^2$ at doy 105, 135, 165, and 195, showing the development of summer stratification centered at z = 30 m (solid lines). Monthly-average vertical stratification obtained from glider profiles collected in June and July are superimposed (dashed lines), along with the correlation coefficient between observations and model outputs.}
	\label{fig: Papa_summer}
\end{figure}

\subsubsection{\textit{Papa\_winter} Model Experiment}

In \textit{Papa\_winter}, PSOM is initialized based on climatological ARGO data in January. The frontal sharpness is set to 3.54$\times$10$^{-5}$ kg/m$^3$/m, which corresponds to the 99$^{th}$ percentile of the PDF of density gradients measured in January from glider data collected in the region (Figure \ref{fig: Papa_winter} and Table \ref{tab: meso_vs_submeso}). The model is allowed to spin-up for 50 days allowing for the prescribed fronts to become unstable. To accommodate the larger density gradients, the advective timestep is shortened to 108 s, and the horizontal diffusivity is lowered to 0.2 m$^2$/s. The model is run for 30 additional days, saving instantaneous model fields every 1.5 hours for particle tracking. The month of January is chosen for initialization so the experiment would capture the time of year where the mixed layer is the deepest, and Rossby number of O(1) are more likely to occur. The objective is for this experiment to contrast \textit{Papa\_summer} by capturing the statistics of ocean conditions dominated by submesoscale dynamics.

% FIG3
\begin{figure}[ht]
	\includegraphics[width = 1\linewidth]{figures/Fig3_Papa500_winter}
	\caption{PSOM configuration for \textit{Papa\_winter}. (a) time series of net heat fluxes and wind stress prescribed at the surface. Notice the mostly negative heat fluxes, as well as alternating zonal wind direction. (b)-(d) horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 0, 30, and 50. Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$). (e) Vertical profile of the buoyancy frequency $N^2$ at doy 0, 30, 50, and 80, showing the persistence of the halocline between z = 80 and z =180 m throughout the experiment (solid lines). Monthly-average vertical stratification obtained from glider profiles collected in March is superimposed (dashed line), along with the correlation coefficient between observations and model outputs.}
	\label{fig: Papa_winter}
\end{figure}

\subsubsection{Validation}
\label{sec: glider_validation}

To ensure that PSOM simulations yielded realistic conditions for both \textit{Papa\_summer} and \textit{Papa\_winter}, distributions of horizontal ($M^2$) and vertical ($N^2$) buoyancy gradients are compared with glider observations collected over the period 2008-2009 \citep{Pelland_2016}.

During this period, underwater gliders sampled in a ``bow-tie" pattern centered on Station Papa. Gliders sample the water column following a triangular wave, whose shape is easily affected by currents, due to the slow moving speed of the glider ($\sim$1 km/hr). It is therefore challenging to associate a specific spatial scale with gradients computed between glider profiles, as profile separation distances can be highly variable through depth and time. To circumvent this issue, horizontal buoyancy gradients are computed between each pair of glider profiles available within one branch of the bow-tie. Each along-track buoyancy gradient is then associated with a separation scale and a timestamp.

 Glider-based density gradients are highly affected by internal waves. To filter the impact of internal waves on the PDF of horizontal buoyancy gradients, only gradients computed at a scale of $\pm$ 1 km of twice the Rossby radius are considered. Rossby radii are $\sim 8$ km in winter and $\sim 20$ km in summer.

\subsection{Particle Tracking Experiments}

\subsubsection{Particle Advective Scheme}
To quantify the impact of submesoscale dynamics on the export of Particulate Organic Matter (POC), Lagrangian particle tracking is used in conjunction with the flow field obtained from the two experiments described above. Particles are tracked using the non-divergent velocity field at each face of a grid cell. The velocity field is then linearly interpolated onto the particle's position. For example, the eastward velocity (x-axis) of a particle is given by:

\begin{equation}
u(x) = u_{i-1} + \frac{(x - x_{i-1})}{(x_i - x_{i-1})}(u_{i}-u_{i-1})
\end{equation}
where the subscripts $i-1$ and $i$ denote the western and eastern walls of the grid cell where the particle is located, respectively. This can be re-written as:

\begin{equation}
\frac{\partial x}{\partial t} + \beta x + \delta =  0
\label{eq: eq_diff}
\end{equation}
where $\beta = (u_{i}-u_{i-1})/\Delta x$ and $\delta = -u_{i-1} - \beta x_{i-1}$ \citep{Doos_2013}. This differential equation can be solved analytically for $\beta \neq 0$:

\begin{equation}
x_{t_1} = \left(x_0 + \frac{\delta}{\beta}\right)\exp^{-\beta(t_1 - t_0)} - \frac{\delta}{\beta}
\label{eq: PT_advection}
\end{equation}
The time it will take for the particle to reach the eastern or western face of the grid cell can be computed by taking $x_{t_1} = x_i$ or $x_{t_1} = x_{i-1}$, respectively, and solving for $t_1$. For each advective timestep, the times required for the particle to reach any of the 6 walls of the grid cell are computed using Equation \ref{eq: PT_advection}. If any of those times is shorter than the advective timestep, the particle is advected until it reaches the cell wall. Then the flow field in the adjacent grid cell is considered and the particle is advected over the remaining time. For each particle tracking experiment, four different classes of particles were released. Each particle class is characterized by a different sinking velocity: 0.025, 0.05, 1, and 5 m/day. The slowest-sinking class was essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported through gravitational sinking, a timescale much greater than commonly observed remineralization timescales. The fastest-sinking velocity is chosen as a low end-member representing velocity classes that will be exported in its entirety over the course of our experiment. The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.

In the horizontal, particles are seeded once every 250 m over the entire domain in the x-direction, and for 100 $<y<$ 200 km in the y-direction. The seeding is centered on the position of the middle front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by artificial features developing at the solid north and south boundaries. In the vertical, eleven of those sheets of particles are seeded every 1 m between 75 and 85 m. This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined as the 1\% light level. The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Available Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}. The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.

The particle advective timestep is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for three weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-suspended into the mixed layer. %The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.

\subsubsection{Density and Biomass Spectra}
\label{sec: equations_biomass}
The slope of the size spectrum of particles is traditionally described by the slope of the log-log curve, $\xi$, between particle number $N$ and particle radius $r$ \citep[also know as the Junge slope;][]{White_2015}:

\begin{equation}
N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}
\label{eq: powerlaw_radius}
\end{equation}
where $N_0$ and $r_0$ represent a reference particle number and radius, and are chosen arbitrarily. For small particles ($<400\mu m$) and relatively cold temperature ($<15^oC$), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ tend to follow Stokes law, with $w_s \propto r^2$ \citep{Bach_2012}. \cite{Bach_2012} also demonstrates that Stokes law is generally a lower-bound limit to estimate sinking velocities for a specific particle size. Assuming a Stokes-like relationship, Equation \ref{eq: powerlaw_radius} can thus be re-written in terms of sinking velocities:

\begin{equation}
N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2}
\label{eq: powerlaw_velocity}
\end{equation}
For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can thus be computed using Equation \ref{eq: powerlaw_velocity} (See Figure \ref{fig: sinking_velocity_spectrum}). For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represent 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}). The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$, can be estimated if the biomass is assumed to vary with the particle's volume. The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed using:

% FIG4
\begin{figure}[ht]
	\centering
	\includegraphics[width = .6\linewidth]{figures/Fig4_particle_PDF}
	\caption{Normalized number of particles (solid) and biomass (dashed) to the fastest-sinking particle class. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 0 (black), and 2 (blue).}
	\label{fig: sinking_velocity_spectrum}
\end{figure}

\begin{equation}
	B_p(w_s) = B_p(w_{s_0})\left(\frac{w_s}{w_{s_0}}\right)^{3/2}
	\label{eq: biomass_realparticle}
\end{equation}
where $B_p(w_{s_0})$ is a reference biomass of one particle in the sinking velocity class $w_{s_0}$. The total biomass associated with one simulated particle can be obtained by scaling Equation \ref{eq: biomass_realparticle} by the ratio $N(w_s)/N_0$:

\begin{equation}
	B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
	\label{eq: biomass_simulatedparticle}
\end{equation}
where $B_0 = B_p(w_{s_0})$. Combining Equations \ref{eq: powerlaw_velocity} and \ref{eq: biomass_simulatedparticle} yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
\begin{equation}
	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}
	\label{eq: biomassjungeslope}
\end{equation}
Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (Equations \ref{eq: powerlaw_velocity} and \ref{eq: biomassjungeslope}) presents the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we therefore define a normalized biomass unit as $B_0=$ 1.

\subsubsection{Particle Remineralization Scheme}
\label{sec: remin_scheme}
Remineralization of particles as they sink through the water column evidently impact the export of biomass. Slow-sinking particles therefore are subject to shallower remineralization than fast-sinking particles. In this study, the impact of remineralization is considered through the implementation of a time-dependent sinking velocity. Remineralization processes driving remineralization rates are complex, species-dependent, and generally not well-understood. In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship linking carbon content and time. This implicitly assumes that the biomass content of a particle diminishes in time proportionally to the particle volume. Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}:
\begin{equation}
	B (t) = B^0\exp(-kt)
	\label{eq: remin_scheme}
\end{equation}
where $B^0$ denotes the biomass content at $t = 0$ days, and $k = 0.13$ day$^{-1}$. This remineralization rate determined by \cite{Iversen_2010} is independent of particle sinking velocity, and seems to generally agree with other findings, despite the large uncertainties \citep{Ploug_2008, Iversen_2013}. The change in biomass with time is in turn expected to affect the sinking velocity of the particle. Given that $B \propto w^{3/2}$ (see Equation \ref{eq: biomass_realparticle}),  a time-varying sinking velocity is imposed to particles in all sinking-velocity classes using:

\begin{equation}
w_s (t) = w_s^0\exp(-\frac{2kt}{3})
\label{eq: sinking_velocity_remin}
\end{equation}
where $w_s^0$ is the initial sinking velocity at $t = 0$ days. Particles are classified based on their initial sinking-velocity. However, it is worth noting that over the length of the particle-tracking experiments including remineralization (28 days), particles slow down by more than 90\% of their initial velocity.

\section{Results}
\label{sec: Results}
\subsection{Physical model}

Two model experiments are designed to capture different dynamical conditions observed in the northeast Pacific Ocean in summer and winter. \textit{Papa\_summer} is initialized in early spring (doy 105) when the water column is characterized by a relatively deep mixed layer ($\sim$100 m) and a halocline present between 100 and 150 m (Figure \ref{fig: Papa_summer}). The forcing by a realistic, positive, net heat flux generates the restratification of the water column, with the development of a strong thermocline between 25 and 50 m leading to the shoaling of the mixed layer and a subsurface peak in $N^2$ at about 30 m (see Figure \ref{fig: Papa_summer}). A comparison between model outputs and monthly-averaged density profiles from underwater gliders collected in June and July over the period 2008-2009 yields correlation coefficients of $r = 0.87$ and $r = 0.88$, respectively. These correlation coefficients suggest that \textit{Papa\_summer} captures reasonably well the vertical spring and summer conditions in the northeast Pacific Ocean.

In the horizontal, the prescribed density fronts progressively become unstable within the first 60 days of the experiment (Figure \ref{fig: Papa_summer}). During this time, the Total Kinetic Energy (TKE) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation. The flattening of the TKE curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments. The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=( \partial v/ \partial x - \partial u/ \partial y)/f$; Figure \ref{fig: dynamics}).

%FIG5
\begin{figure}[t]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig5_dynamic_signature_w_valid}
	\caption{Snapshots of $M^2$ (top), $\zeta /f$ (middle), and $w$ (bottom) half-way through the particle tracking experiment for \textit{Papa\_summer} (left and blue) and \textit{Papa\_winter} (right and red), with the Mixed Layer Depth indicated by the solid black line. The corresponding Probability Distribution Functions (PDFs) are shown in the center. Note the changing color scales between \textit{Papa\_summer} and \textit{Papa\_winter}. Histograms of M$^2$ computed from glider data at Station Papa in February (blue line) and July (red line) are superimposed in the top middle panel.}
	\label{fig: dynamics}
\end{figure}

The largest horizontal buoyancy gradients are observed above the thermocline ($z<$50 m) and along the halocline (100-200 m), and range between 0 and 1.2$\times 10^{-7}$ s$^{-2}$ (Figure \ref{fig: dynamics}). These relatively weak density gradients result in low Rossby numbers O(0.1), positive on the denser (north) side of the front, and negative on the lighter (south) side of the front. Corresponding vertical velocities are consistently weaker than 1 m/day ($<$10$^{-5}$ m/s) and are characterized by regions of weak upwelling and downwelling on the order of 10 km, associated with the meandering of the front \citep{Bower_1989}. Alternating bands of upwelling and downwelling at $\mathcal{O}$(1 km) spatial scale are superimposed, likely caused by propagating internal waves. Coherent vertical velocities structures are homogeneous to depths much greater than the mixed layer depth ($\sim$25 m; Figure \ref{fig: Papa_summer}). The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \citep{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ 1/s (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ 1/s, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s. The agreement between the scaling and the model outputs suggest that PSOM is capable of reproducing a realistic vertical flow field.

\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) with the objective to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \citep{Pelland_2016}. At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m. After spin-up, the vertical stratification remains consistent throughout the model run, and compares well to the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}). In the horizontal, prescribed density fronts are much sharper than in \textit{Papa\_summer} (O(1 km ) vs. O(10 km)). Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in \textit{Papa\_summer} (Figure \ref{fig: Papa_winter}). As a result, TKE starts to plateau at doy 48. The experiment is considered spun-up by doy 50 and the particle-tracking experiment is initialized. %Many sharp fronts and filaments on the order of 1 km can be seen in \textit{Papa\_winter}, penetrating to ocean upper layer to the deeper than in the summer, dissipating within the mixed layer at $\sim$100 m (Figure \ref{fig: dynamics}).

The frontal structures visible in the horizontal buoyancy gradient field are logically associated with filaments of relatively high Rossby numbers, regularly exceeding O(1) (Figure \ref{fig: Papa_winter}). The PDF of Rossby numbers reveals a positively-skewed distribution of Rossby numbers ($s = 0.68$). This is in agreement with the fact the relative vorticity is more likely to be cyclonic than anticyclonic, based on conservation of potential vorticity \citep{Hoskins_1972}. Regions with a high Rossby number are localized and located in the mixed layer exclusively. In places where the local Rossby number reaches O(1), geostrophic balance is lost and a vertical secondary ageostrophic circulation develops to slump the isopycnals and return to a more stable geostrophically-driven flow. This ageostrophic secondary circulation therefore generates ``hot spots" of higher vertical velocities. The fine-scale structures in the vertical velocity field corresponding to Rossby numbers O(1) can be seen in Figure \ref{fig: Papa_winter}, with local vertical velocities up to 60 m/day ($\sim 7\times10^{-4}$ m/s; Figure \ref{fig: dynamics}). Contrarily to the PDF of Rossby numbers, the distribution of vertical velocities demonstrate a negative skewness ($s =$ -0.25). This is in agreement with the theory: In fact, positive vertical vorticity is associated with the dense side of a density front, where Rossby numbers are positive and vertical velocities negative \citep{Mahadevan_2016}. Once again, the amplitude of these vertical velocity hot spots is coherent with the scaling $w \propto RofU/N$: using $Ro\sim1$, $N\sim10^{-2}$ 1/s, $f\sim10^{-5}$ 1/s, and $U\sim0.1$ m/s, we obtain $w\sim 10^{-4}$ m/s. This demonstrates the capabilities of PSOM to resolve sharp frontal features at the kilometer scale, as well as the ageostrophic circulation associated with those fronts.

Comparing \textit{Papa\_summer} and \textit{Papa\_winter} highlights the different dynamical regimes in the two experiments. In \textit{Papa\_winter}, density fronts tend to be sharper, meaning larger density gradients over shorter spatial scales. When computed at the kilometer-scale, the PDF of horizontal buoyancy gradients in \textit{Papa\_winter} exhibits a longer tail than in \textit{Papa\_summer} (Figure \ref{fig: dynamics}). When compared to observations, the PDFs of $M^2$ in \textit{Papa\_summer} and \textit{Papa\_winter} demonstrate a correlation with observations of $r = 0.93$ and $r = 0.95$, respectively

The wider PDF of vertical velocities in \textit{Papa\_winter} shows advective velocities that match and exceed typical gravitational sinking velocities, particularly for smaller, and therefore slower-sinking, particulate organic material. The secondary ageostrophic circulation that develops at submeso-scales (i.e., Ro O(1)) therefore generates an export mechanism that directly competes with the traditional paradigm that relies on gravitational sinking leading the export of particulate matter in the ocean.

\subsection{Particle tracking}

Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle export, using Lagrangian particle-tracking. In this study, particles are considered "exported" once located below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa. Choosing the winter mixed layer as the export depth is most appropriate, as it reduces the chances of particles being re-entrained into the mixed layer the following winter. We first consider the case of conservatives particles that do not remineralize in order to better identify the effects of ocean dynamics and spectral slope on export.

The percentage of simulated particles being exported with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of exported particles closely follow the curves derived from considering gravitational sinking only (Figure \ref{fig: particle_export}).

%FIG6
\begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export}
	\caption{Percentage of particles located below 100 m as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Expected percentages of exported particles based on gravitational sinking only are indicated with dashed lines.}
	\label{fig: particle_export}
\end{figure}

Time series of exported particles in \textit{Papa\_winter} present major differences. In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking. This early arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation. Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}. About 5\% of particles sinking at 0.025 m/day are exported. However, more time is now necessary to export 100\% of the simulated particles. This can be seen in the gentler slopes of the export curves observed in \textit{Papa\_winter} than in \textit{Papa\_summer}.

Particles released in \textit{Papa\_winter} are thus exported faster and in greater number than expected from gravitational sinking only. Eventually, all sinking particles would be exported in both \textit{Papa\_summer} and \textit{Papa\_winter}, if particles were tracked for a long enough period of time. Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale. The impacts of remineralization on export are presented and discussed in Sections \ref{sec: results_remin} and \ref{sec: discussion_particle}.

The presence of submesoscale dynamics therefore increases the number of exported slow-sinking simulated particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles are far more numerous than faster-sinking particles, despite containing less biomass (Figure \ref{fig: sinking_velocity_spectrum}). While the number of simulated particles that are exported is only a function of the modeled flow field, the exported biomass also depends on the Junge slope (see Equation \ref{eq: biomassjungeslope}).

The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhance the role played by slower-sinking particles in biomass export, and thus decrease the importance of faster-sinking particles (Figure \ref{fig: biomass_export_remin}). This is a logical results in sight of the increase in the number of particles exported when submesoscales features are present (Figure \ref{fig: particle_export}). The sinking class dominating export, however, is highly dependent on the Junge slope parameter. As the Junge slope parameter increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases, sometimes dominating biomass export. For example, after 28 days, the 1 m/day exports 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.

%FIG7
 \begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export}
	\caption{Amount of biomass exported in normalized units by each sinking velocity class in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for three different Junge slopes: $\xi =$ 4 (top), $\xi =$ 3 (middle), and $\xi =$ 2 (bottom; see Figure \ref{fig: sinking_velocity_spectrum}). Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
	\label{fig: biomass_export_remin}
\end{figure}

 \subsection{Particle Remineralization}
 \label{sec: results_remin}

 Including remineralization of particles (Equation \ref{eq: remin_scheme}) significantly impacts the relative importance of sinking and advection to export for each particle class. In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles slow down as they are remineralized (Equation \ref{eq: sinking_velocity_remin} and Figure \ref{fig: biomass_export_remin}). In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included. The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is considered.

 The total amount of biomass is also reduced compared to the case with no remineralization. The difference between the two cases is time dependent, and increases with the age of the particle, as particles further remineralize. The impact of remineralization on the amount of biomass exported intensifies as the sinking velocity decreases. In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export, with slower-sinking particles contributing significantly less than faster-sinking particles (dash lines in Figure \ref{fig: biomass_export_remin}. Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduces by 5-6 orders of magnitude depending on the slope of the biomass spectra (see Figure \ref{fig: sinking_velocity_spectrum}). Similarly to the case with no remineralization, a change in the Junge slope impacts the contribution of slower-sinking velocity classes. This can be seen in the amount of biomass exported by the 1 m/day sinking-velocity class: A negative slope (i.e., $\xi$ = 4) leads to a maximum biomass of about 6, while a positive slope (i.e., $\xi$ = 2) leads to a maximum biomass of 1. Both of these amount of exported biomass represent less than 1\% of the total exported biomass, making the contribution to export from this sinking-velocity class virtually insignificant.

 In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported more rapidly than in \textit{Papa\_summer} due to stronger vertical velocities. The difference in exported biomass between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already behind exported. As particles age, remineralization has an increasing impact and the difference in total exported biomass increases at a rate controlled by the remineralization rate in Equation \ref{eq: remin_scheme}. Similarly to \textit{Papa\_summer}, the total amount of biomass exported by a specific sinking-velocity class decreases as the Junge slope decreases (i.e., the sinking-velocity spectra flattens). An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the amount of biomass exported from the 0.025 m/day sinking-velocity class exceeds the amount of biomass exported by both the 0.5 and 1 m/day sinking-velocity classes. This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.

\section{Discussion}
\label{sec: Discussion}

\subsection{Physical model}
\label{sec: Discussion_model}
\textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the northeast Pacific Ocean. After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients than observed using underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}). The two experiments, however, show drastically different distributions of $M^2$, where the winter distribution has a much longer tail, suggesting sharper density gradients. The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sample gradients at a maximum resolution of about 10 km, while the model resolution is 500 m and therefore allows sharp submesoscale fronts and filaments to be captured in the distribution.

Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \citep{Dasaro_2011, Thomas_2013}, or at the edge of mesoscale features \citep{vanHaren_2006,Waite_2016}. The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa, and reflected in the model experiments, echoes findings of recent observational studies conducted at a similar latitude in the Atlantic Ocean demonstrating the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}. Despite being sometimes qualified as an "eddy desert" with low kinetic energy \citep{Chelton_2011}, wintertime ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features: strong density gradients, localized Rossby numbers of the order 1 and larger, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.

Strong downward velocities are hypothesized to enhance POC export by advecting slower-sinking particles out of the mixed layer. \textit{Papa\_winter} indeed exhibits vertical velocities more than 20 times larger than in \textit{Papa\_summer}. The vertical currents in \textit{Papa\_winter}, however, tend to be much patchier than the weaker vertical currents observed in \textit{Papa\_summer}. Because both particle production and downward vertical velocities present a high degree of patchiness, it requires a certain level of covariance between the two fields for the export to effectively be enhanced \citep{Mahadevan_2012}. A more realistic seeding strategy for Lagrangian particles, such as one guided by biological tracers, would likely provide important information towards a better understanding of the effects of patchiness on POC export at submeso-scales

The hypothesis tested in this study is that submesoscale activity enhances export of particulate matter at Station Papa. The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion below). However, the seasonal cycle in submesoscale activity is out-of-phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}. Two mechanisms are therefore present to potentially sustain a year-long POC export: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export by advecting the more numerous slower-sinking particles into the ocean interior. In the summer, the production of POC is much larger, but export tends to be dominated by gravitational sinking, which discriminate against slower-sinking particles.

\subsection{Particle export}
\label{sec: discussion_particle}

The analysis of the particle tracking experiments reveals that the role played by slower-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope coefficient $\xi$).

Mixed layer ocean dynamics at station Papa change significantly between the winter and the summer. In the winter, submesoscale dynamics are intensified and sharp fronts and filaments develop in the mixed layer. This change in dynamics has a clear impact on the amount of particles exported for all sinking-velocity classes modeled in this experiment. First, particles in all sinking-velocity class generally reach the export depth faster. This is the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescales (i.e., the time it takes for a particle to reach the export depth), and its remineralization timescales. The former evidently needs to be shorter than the latter to efficiently export POC. Second, particles are exported more gradually. While particles in a sinking-velocity class reach the export depth over shorter timescale, it takes longer to export the same number of particles as in the summer. This is due to the upward vertical current, re-suspending material that would otherwise sink, and thus delaying its export. Keeping in mind the competing timescales mentioned above, it leads to interesting questions: Is it more efficient to export more faster-sinking particles--less numerous but containing more biomass--and no slower-sinking particles, like in \textit{Papa\_summer}? Or is export greater when less faster-sinking particles are exported, but more slower-sinking particles, much more numerous, also contribute to the export, like in \textit{Papa\_winter}?

%% This section answers the questions above in terms of total amount of biomass efficiently exported with and without remineralization 
In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient. Over the course of our simulation, the total amount of biomass exported is consistently enhanced when $\xi = 4$ (10 to 60\% increase) in the presence of submesoscale dynamics. For a flat biomass spectrum ($\xi = 3$), the export enhancement due to submesoscale dynamics is always smaller than 20\%. When $\xi =2$, the amount of biomass exported in the presence of submesoscale dynamics varies between 95 and 110\% of the export observed in the summer, when submesoscale dynamics are not active. Therefore, to address the questions formulated above, export is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales. %Talk about the asymmetry in the vertical velocity PDF (see Figure \ref{fig: dynamics})? Showing stronger, more localized downwelling, and broader and weaker upwelling?

Introducing remineralization processes significantly decreases the total amount of biomass exported. Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export. The increase in exported biomass when comparing summer and winter time is larger when remineralization processes are included, and also increase with larger $\xi$. Total exported biomass almost doubles when $\xi =4$, and increases by 5 to 20\% for $\xi =2$ and $\xi = 3$, respectively. This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to slow these particles down and thus prolongs their export timescales. In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as all classes rely on gravitational sinking for export. In the winter, however, slower-sinking particles are exported through advective processes. Their export timescale is little affected by remineralization processes as it only depend on local ocean dynamics, leading to a greater net export then when remineralization is not considered.

%% this part discusses the respective contributions of the different sinking-velocity classes
The contribution of a particle class to POC export generally increases with the sinking-velocity. That is, faster-sinking particles tend to dominate the export signal and the curve of exported biomass versus sinking-velocity has a positive slope. To have a greater contribution of a slower-sinking velocity class, the following condition must be satisfied:

\begin{equation}
    N_{slow} > N_{fast} \times \left(\frac{w_{s_{fast}}}{w_{s_{slow}}}\right)^{\frac{3 - \xi}{2}}
    \label{eq: condition}
\end{equation}
where $N$ is the number of simulated particles exported, $w_s$ is the sinking velocity and $\xi$ is the Junge slope coefficient (see Equation \ref{eq: powerlaw_radius}).

In a gravitationally-driven system (i.e., weak submesoscale activity), this can only be achieved by having  $N_{slow} \sim N_{fast}$ and $\xi>3$, as there are no mechanism capable of selectively exporting slower-sinking particles (i.e., $N_{slow} \leq N_{fast}$). Junge slope greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}. Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$). Because of the negative slope in the biomass spectrum, any particle class sinking at a faster rate will not contribute as much to the biomass export. The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth. As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation \ref{eq: condition}). A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}). Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon} towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.

%FIG8
 \begin{figure}[ht!]
	\centering
	\includegraphics[width = .6\linewidth]{figures/cartoon_meso}\\[.2cm]
	\includegraphics[width = .6\linewidth]{figures/cartoon_submeso}
	\caption{}
	\label{fig: export_cartoon}
\end{figure}

In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated. This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}). In this regime, slower-sinking particles significantly contribute to POC export. In this study, sinking-velocity classes that did not contributes to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$. Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller in advectively-driven export mechanism, as opposed to gravitationally-driven.

\section{Conclusion}
\label{sec: Conclusions}
The main conclusions of this study are: 
\begin{enumerate}
\item Submesoscale activity at station Papa is enhanced in the wintertime, leading to larger vertical velocities than in the summer. Export processes in the winter are thus driven by advective sinking, as opposed to gravitational sinking in the summertime.
\item Submesoscale dynamics generally enhance export by increasing the contribution of slower-sinking particles to POC export by increasing the number of particle exported through advective sinking. The contribution of slower-sinking particles in ageostrophic flows is at least significant, and can be dominant in specific conditions.
\item Contribution of slower-sinking particles to POC export also depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class. Three cases emerge in this study:
\begin{enumerate}
	\item If the Junge slope is smaller than 3, larger particles contribute most to export independently of flow dynamics, as even exporting 100\% of the particles in all sinking velocity classes would see larger particles dominate. 
	\item If the Junge slope equals 3, the respective contributions of the different size classes depend on the dynamical characteristics of the flow, as it influences the number of particles being exported. If 100\% of the particles is exported in all sinking classes, then each class contributes equally to POC export.
	\item If the Junge slope is greater than 3, ocean dynamics become the determining factor on which classes dominate: in a mostly geostrophic flow with weak vertical velocities, an intermediate sinking-velocity class will dominate POC export. In a flow with ageostrophic circulation leading to larger vertical velocities, slower sinking classes can potentially dominate export.
	\end{enumerate}
\item Remineralization processes reduces the contribution of slower-sinking particles when export dynamics are dominated by gravitational sinking (i.e., in a geostrophic flow). As flow dynamics become ageostrophic, advective sinking leads the export and remineralization processes have a limited impact.
%\item[(5)] Under specific conditions (large Junge slope and strongly ageostrophic flow), remineralization processes counter-intuitively enhance the role of slower-sinking (and non-sinking) particles to the point where export is dominated by these slow-sinking particles, therefore challenging the traditional paradigm of carbon export.
\end{enumerate}

%These conclusions demonstrate the importance of resolving a large portion of the particle size spectrum to properly quantify export, especially in dynamical regimes where strong ageostrophic circulation is present.

\section*{Acknowledgments}

The authors acknowledge support from the National Aeronautics and Space Administration as part of the EXport Processes in the global Ocean from RemoTe Sensing (EXPORTS) program - grant NNX16AR48G. We would like to thank A. Thompson (Caltech) for his useful comments and suggestions, N. Pelland (NOAA) and Charlie Eriksen (University of Washington) for sharing the glider data collected at Ocean Station Papa, as well as Sebastian Essink for his assistance in developing the particle-tracking code. All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website (\url{https://www.pmel.noaa.gov/ocs/Papa}) and gridded ARGO products can be downloaded at \url{http://www.seanoe.org/data/00348/45945}. Glider data, model outputs, and particle trajectories are freely available on request. % Finally, we are grateful to the two anonymous reviewers for their valuable comments and suggestions.

%% ------------------------------------------------------------------------ %%
%%  REFERENCE LIST AND TEXT CITATIONS
%\bibliographystyle{apalike}
\bibliography{sinking_biblio}

%% ------------------------------------------------------------------------ %%
%
%  END ARTICLE
%
%% ------------------------------------------------------------------------ %%

%\end{article}
%\clearpage

%% ------------------------------------------------------------------------ %%
%
%  FIGURES AND TABLES
%
%% ------------------------------------------------------------------------ %%

%TAB2
%\begin{table}[]
%	\caption{Range of contributions (min-max) to the total amount of biomass exported per size class in both \textit{Papa\_summer} and \textit{Papa\_winter}.}
%	\label{tab: biomass_contribution}
%	\centering	
%	\begin{tabular}{|cc|c|c|c|c||c|c|c|c|}
%		\hline
%		&           & \multicolumn{4}{c||}{\textit{Papa\_summer}} & \multicolumn{4}{c|}{\textit{Papa\_winter}} \\
%		\hline
%		\multicolumn{2}{|c|}{sinking speed [m/day]} & 5               & 1             & 0.5          & 0.025     & 5              & 1            & 0.5          & 0.025       \\
%		\hline\hline
%		$\xi = 2$ & Remin OFF & 69-100\%     & 0-30\%     & 0-1\%     & 0\%       & 70-100\%    & 0-24\%    & 0-6\%     & 0\%         \\
%		\rowcolor[HTML]{EFEFEF} 
%		 & Remin ON  & 100\%           & 0\%           & 0\%          & 0\%       & 92-100\%    & 0-6\%     & 0-3\%     & 0-1\%    \\
%		$\xi = 3$ & Remin OFF & 49-100\%     & 0-49\%     & 0-2\%     & 0\%       & 49-100\%    & 0-37\%    & 0-12\%    & 0-3\%    \\
%		\rowcolor[HTML]{EFEFEF} 
%		& Remin ON  & 100\%           & 0\%           & 0\%          & 0\%       & 78-100\%    & 0-11\%    & 0-9\%     & 0-6\%    \\
%		$\xi = 4$ & Remin OFF & 30-100\%     & 0-68\%     & 0-3\%     & 0\%       & 25-99\%     & 0-43\%    & 0-20\%    & 0-25\%   \\
%		\rowcolor[HTML]{EFEFEF} 
%		& Remin ON  & 100\%           & 0\%           & 0\%          & 0\%       & 38-100\%    & 0-16\%    & 0-14\%    & 0-39\%  \\ 
%		\hline
%	\end{tabular}
%\end{table}
\end{document}

%%%%%%%%%%%%%%%%%%%
%%%% OBSOLETE %%%%%
%%%%%%%%%%%%%%%%%%%
The main consequence of this result is that, when the biomass spectrum has a negative slope (i.e., $\xi>3$) ,

It is impossible to obtain $N_{slow} > N_{fast}$

In the absence of remineralization,

In a gravitationally-driven system (i.e., weak submesoscale activity), contribution to export generally increases as sinking-velocity increases. This is true up to the point where the totality of the particles are exported: for an equal number of particle exported, the

Generally, export is dominated by the contribution of faster-sinking particles. For a slower-sinking velocity class to contribute more to the export than a faster-sinking velocity class, the number of particles exported must satisfy:

In the absence of remineralization, where all particles are eventually exported, this condition is only satisfied if $\xi>3$, that is if the biomass spectrum has a negative slope (see Figure \ref{fig: sinking_velocity_spectrum}). \fixme{While export will then always be dominated by faster-sinking particles, the contribution of slower-sinking particles varies greatly with the 
as a function of (1) the biomass spectral slope must be negative (i.e., $\xi>3$), and (2) the number of particles exported must be large enough. The number of particles to be exported for a slower-sinking velocity class to dominate export over a faster-sinking velocity class depend on the Junge slope and is determined by:
Under those conditions, the contribution to export as a function of sinking speed is notc linear: increasingly faster-sinking classes contribute increasingly to export, as they physically export more particles, until the sinking speed above which 100\% of the particles are exported is reached. Above this threshold, the contribution to biomass export by increasingly faster-sinking particles decreasingly contribute to export, due to the negative slope in the biomass spectra. Despite the export being dominated by faster-sinking particles, this study demonstrates that in the presence of submesoscale activity, slower-sinking particles have the potential to significantly contribute to the total export. The slowest sinking-velocity class simulated in this study contributed to up to 13\% of the total biomass export in the presence of submesoscale dynamics, for $\xi = 4$.}

The important threshold in the Junge slope highlighted in this study can be generally defined by the log-log slope between particle size and biomass content. In this study, we assume that biomass varies as the volume of the particle (B $\propto r^3$), thus obtaining a threshold of $\xi=3$. Using other relationships between biomass and particle size will not impact the main conclusions of this study, but will only affect the threshold at which slower-sinking particles contribute significantly to the export.

\subsection{Impacts of  Particle Remineralization}
\label{sec: discuss_remin}

Remineralization processes introduce a time-dependency in the relationship between biomass and sinking-velocity. A simple, yet commonly-used, remineralization scheme was imposed to the particles. As one would expect, the main impacts of implementing a remineralization scheme is a decrease in the exported biomass across all sinking-velocity classes, as well as a prolonged export timescale. This is due to the fact that, as a particle remineralizes, its sinking-velocity decreases. Because the particle now takes more time to be exported, it further remineralizes, which in turn decreases the particle's sinking-velocity. In the summer, this self-reinforcing mechanism affects slower-sinking classes the most, and therefore significantly decreases their contribution to export. In the winter, remineralization also generally reduces the amount of biomass exported, although the impact is far less pronounced and affects all sinking-velocity classes similarly. This is explained by the different mechanism dominating export in the summer and winter: In the summertime, export is dominated by gravitational sinking, which is directly impacted by remineralization processes. In the wintertime, however, export is largely driven by advective sinking through the stronger downward currents observed in the submesoscale flow. Advective sinking being independent from remineralization processes, the biomass export is less affected than in the summertime. In fact, our analysis clearly shows that remineralization processes does not significantly impact the biomass export associated with slower-sinking velocity classes over the first 5 days of the simulations.

Finally, a very interesting feature arose from implementing a remineralization scheme to the Lagrangian particles. In the winter and with $\xi =4$, the biomass exported by the slowest-sinking class (0.025 m/day) consistently exceeds the amount of biomass exported by slightly faster-sinking classes (0.5 and 1 m/day), despite a considerably smaller number of particles exported ($<4$\% vs. 23\% and 73\%, respectively) This non-intuitive result emerges from the exponential characteristic of the remineralization scheme: the impact of remineralization thus increases with the sinking velocity. This result demonstrates that remineralization can, under specific circumstances, increase the role played by slower sinking-velocity classes. The necessary conditions involve a large Junge slope and strong submesoscale activity.

### 2019-01-30 figures/code/Fig1_model_domain.m

@@ -1,0 +1,97 @@
+clear
+
+%% This code plot the model domain with the wind profile and the het flux 
+% meridoinal anomaly in 3 panels
+%%
+ii = 0;
+x = ncread(['/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/full_',num2str(ii,'%05d'),'.cdf'],'xc')*1000;
+y = ncread(['/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/full_',num2str(ii,'%05d'),'.cdf'],'yc')*1000;
+Z = ncread(['/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/full_',num2str(ii,'%05d'),'.cdf'],'zc');
+z = squeeze(Z(1,1,:));
+rho = ncread(['/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/full_',num2str(ii,'%05d'),'.cdf'],'rho');
+rho(1,:,:) = NaN; rho(end,:,:) = NaN;
+
+% Import the scale factor for restauration time scale
+filename = '/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/scalefactor.out';
+delimiter = ','; startRow = 2; formatSpec = '%*s%s%[^\n\r]';
+fileID = fopen(filename,'r');
+dataArray = textscan(fileID, formatSpec, 'Delimiter', delimiter, 'TextType', 'string', 'HeaderLines' ,startRow-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
+fclose(fileID);
+raw = repmat({''},length(dataArray{1}),length(dataArray)-1);
+for col=1:length(dataArray)-1
+    raw(1:length(dataArray{col}),col) = mat2cell(dataArray{col}, ones(length(dataArray{col}), 1));
+end
+numericData = NaN(size(dataArray{1},1),size(dataArray,2));
+rawData = dataArray{1};
+for row=1:size(rawData, 1)
+    % Create a regular expression to detect and remove non-numeric prefixes and
+    % suffixes.
[…]

### 2019-01-30 figures/code/Fig2_Papa500_summer.m

@@ -1,0 +1,189 @@
+clear
+
+% Create a blue-to-red colorbar for line plot
+cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(11,:);cmap(16,:)];
+
+%% this code creates the figures that synthetize the forcing and density
+% field for the Papa500 xperiment
+
+% Load glider data
+load('/Users/mathieudever/Documents/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
+glider.N2 = 9.81./nanmean(glider.density(:))*(glider.density(3:end,:)-glider.density(1:end-2,:))./(glider.depth(3:end,:)-glider.depth(1:end-2,:));
+glider.time = datevec(nanmean(glider.time));
+clearvars -except glider cmap
+
+%% STEP 1 - Compute the TKE vs time. cannot use the full resolution, as it is domain integrated
+thefolder = pwd;
+cd /Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1
+% Surface view
+depth = 50; % depth to plot in m
+lat = 50;   % Latitude of mid-domain (for f)
+f = gsw_f(lat);
+g = 9.81;
+
+jstart = 201;
+jfinish = 402;
+
+%% Step 2 - load the forcing time series
+
+% Heat Fluxes
+fileID = fopen('/Users/mathieudever/Google Drive/Publications/size_differentiated_sinking/figures/code/ini_heatfluxes.in','r');
+dataArray = textscan(fileID, '%f%[^\n\r]');
+fclose(fileID);
+HF = dataArray{:, 1};
+clearvars fileID dataArray ans;
+
+% Windstress
+fileID = fopen('/Users/mathieudever/Google Drive/Publications/size_differentiated_sinking/figures/code/ini_windstress.in','r');
+dataArray = textscan(fileID, '%f%f%[^\n\r]','delimiter',',');
+fclose(fileID);
+WS = [dataArray{1:end-1}];
+clearvars fileID dataArray ans;
+
+% Applies the scaling imposed in the model
+HF(1:5*86400/216) = 0;
+for ii = 5*86400/216:10*86400/216
+    HF(ii) = HF(ii)*(ii-(5*86400/216))/(5*86400/216);
+end
+WS(1:5*86400/216,:) = 0;
[…]

### 2019-01-30 figures/code/Fig3_Papa500_winter.m

@@ -1,0 +1,191 @@
+clear
+% Create a blue-to-red colorbar for line plot
+cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(11,:);cmap(16,:)];
+
+%% this code creates the figures that synthetize the forcing and density
+% field for the Papa500 xperiment
+
+% Load glider data
+load('/Users/mathieudever/Documents/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
+glider.N2 = 9.81./nanmean(glider.density(:))*(glider.density(3:end,:)-glider.density(1:end-2,:))./(glider.depth(3:end,:)-glider.depth(1:end-2,:));
+glider.time = datevec(nanmean(glider.time));
+clearvars -except glider cmap
+
+
+%% STEP 1 - Compute the TKE vs time. cannot use the full resolution, as it is domain integrated
+thefolder = pwd;
+
+cd /Volumes/mathieudever/PSOM_backup/Papa500_steroid
+% Surface view
+depth = 50; % depth to plot in m
+lat = 50;   % Latitude of mid-domain (for f)
+f = gsw_f(lat);
+g = 9.81;
+
+jstart = 201;
+jfinish = 402;
+
+%% Step 2 - load the forcing time series
+
+% Heat Fluxes
+fileID = fopen('/Users/mathieudever/Google Drive/Publications/size_differentiated_sinking/figures/code/Papa500_winter/ini_heatfluxes.in','r');
+dataArray = textscan(fileID, '%f%[^\n\r]');
+fclose(fileID);
+HF = dataArray{:, 1};
+clearvars fileID dataArray ans;
+
+% Windstress
+fileID = fopen('/Users/mathieudever/Google Drive/Publications/size_differentiated_sinking/figures/code/Papa500_winter/ini_windstress.in','r');
+dataArray = textscan(fileID, '%f%f%[^\n\r]','delimiter',',');
+fclose(fileID);
+WS = [dataArray{1:end-1}];
+clearvars fileID dataArray ans;
+
+% Applies the scaling imposed in the model
+HF(1:5*86400/216) = 0;
+for ii = 5*86400/216:10*86400/216
+    HF(ii) = HF(ii)*(ii-(5*86400/216))/(5*86400/216);
+end
+WS(1:5*86400/216,:) = 0;
[…]

### 2019-01-30 figures/code/Fig4_particle_PDF.m

@@ -1,0 +1,138 @@
+clear
+
+%% This code plots the distribution of Particle, given a spectral slope and the number of LARGEST particle
+
+counter = 1;
+for spectral_slope = [2 3 4]
+    
+    % compute for the sinking velocity actually modeled
+    ws = [0.025 0.5 1 5];
+    N0 = 1971717;
+    N = (ws/max(ws)).^-(spectral_slope/2)*N0;
+    B = (ws/max(ws)).^((3-spectral_slope)/2);
+    
+    % Create the theoretical curve
+    thexaxis = [min(ws):0.001:max(ws)];
+    theyaxis = (thexaxis/thexaxis(4976)).^-(spectral_slope/2);
+    theyaxisB = (thexaxis/thexaxis(4976)).^((3-spectral_slope)/2);
+    
+    %%
+    
+    figure(1)
+    % theoretical curve
+    if spectral_slope>3
+        color = 'r';
+    elseif spectral_slope == 3
+        color = 'k';
+    elseif spectral_slope <3
+        color = 'b';
+    end
+
+    % Plot N/N0
+    h(1) = plot(thexaxis,theyaxis,'--','color',color,'linewidth',2);
+    hold on
+    scatter(ws,N./N0,100,'s','markeredgecolor',color,'markerfacecolor',color)
+    
+    % Plot B/B0
+    h(2) = plot(thexaxis,theyaxisB,'-','color',color,'linewidth',2);
+    g(counter) = h(2);
+    scatter(ws,B,100,'s','markeredgecolor',color,'markerfacecolor',color)
+    
+    set(gca,'yscale','log','xscale','log','fontsize',16)
+    grid on; axis tight;    
+    
+    xlabel('Sinking velocity [m/day]')
+    %ylabel('Number of particles')
+    xlim([0.01 10])
+    counter = counter +1;
+end
+H = legend([h(1) h(2)],'N/N_0','B/B_0','location','east');
+set(H,'Position',[0.7554 0.56 0.1321 0.1250])
+
+
+% get the figure smaller to accomodate the 2nd x-axis later
+POS = get(gca,'position');
+set(gca,'position',[POS(1) POS(2) POS(3) POS(4)-0.05])
+
+% create 2 x-axis
+axes('position',get(gca,'position'),...
+    'xlim',get(gca,'xlim'),...
+    'xscale','log',...
[…]

### 2019-01-30 figures/code/Fig5_dynamic_signature_w_valid.m

@@ -1,0 +1,271 @@
+clear
+close all
+
+%% Load gradients computed from glider data for comparison curve
+load('/Users/mathieudever/Documents/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
+glider.M2time = datevec(glider.M2time);
+clearvars -except glider cmap
+
+
+lat = 50;   % Latitude of mid-domain (for f)
+f = gsw_f(lat);
+g = 9.81;
+
+istart = 200;
+ifinish = 400;
+
+%fullfigure
+
+%%
+thefolder = pwd;
+fullfigure
+for plt = 1:2
+    if plt == 1
+        cd /Volumes/mathieudever/PSOM_backup/Papa500/highrez
+        timesteps = 30500;%[0 24000 30000 36000];
+    elseif plt == 2
+        cd /Volumes/mathieudever/PSOM_backup/Papa500_steroid
+        timesteps = 44000;%[0 32000 44000 56000];
+    end
+    counter = 0;
+    for ii = timesteps
+        counter = counter +1;
+        
+        rho = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'rho');
+        rho(1,:,:) = NaN; rho(end,:,:) = NaN;
+        u = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'u');
+        u(1,:,:) = NaN; u(end,:,:) = NaN;
+        v = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'v');
+        v(1,:,:) = NaN; v(end,:,:) = NaN;
+        w = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'w');
+        w(1,:,:) = NaN; w(end,:,:) = NaN;
+        % vor = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'vor');
+        % vor(1,:,:) = NaN; vor(end,:,:) = NaN;
+        
+        x = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'xc')*1000;
+        y = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'yc')*1000;
+        Z2 = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'zc');
+        z = squeeze(Z2(1,1,:));
+        [X,Y] = meshgrid(x,y);
+        [X2,Y2,Z2] = meshgrid(x,y,squeeze(Z2(1,1,:)));
[…]

### 2019-01-30 figures/code/Fig6_particle_export.m

@@ -1,0 +1,203 @@
+clear
+
+% this code import the number of simulated particles located below 100 m in
+% Papa_meso and Papa_submeso
+
+%% Start with Papa_meso
+
+path = '/Volumes/garuda/Mathieu/particle_tracking/MATLAB/Papa500_';
+for ii = 1:5
+    if ii ==1
+        filename = [path,'0mday/exportTS0mday.txt'];
+    elseif ii == 2
+        filename = [path,'0025mday/exportTS0025mday.txt'];
+    elseif ii == 3
+        filename = [path,'05mday/exportTS05mday.txt'];
+    elseif ii == 4
+        filename = [path,'1mday/exportTS1mday.txt'];
+    elseif ii == 5
+        filename = [path,'5mday/exportTS5mday.txt'];
+    end
+    formatSpec = '%f%[^\n\r]';
+    fileID = fopen(filename,'r');
+    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
+    fclose(fileID);
+    
+    export_meso(:,ii) = dataArray{:, 1};
+    
+    clearvars filename delimiter formatSpec fileID dataArray ans
+end; clear ii path
+
+%% Compute export anomaly based on expected export computed from sinking
+% velocity and distance from 100m horizon
+
+N0 = 1971717;
+t0 = 60.5;
+%ws = 5;
+
+time_meso = 60.5:0.125:88.375;
+Nmeso = zeros(size(export_meso));
+
+wscounter = 1;
+for ws = [0 0.025 0.5 1 5]
+    counter = 1;
+    for zz = 15:25
+        if zz == 15
+            Nmeso(time_meso<t0+zz/ws,wscounter) = 0;
+        end
+        if zz == 25
+            Nmeso(time_meso>t0+zz/ws,wscounter) = 1;
+        end
+        Nmeso(time_meso>=t0+zz/ws & time_meso<t0+(zz+1)/ws,wscounter) = counter/11;
+        counter = counter+1;
+    end
+    wscounter = wscounter +1;
+end; clear ws t0 counter wscounter zz
+
+
+%
+%
+% figure(2)
+% plot(time,(data./Ntot-N)*100,'--','LineWidth',2)
[…]

### 2019-01-30 figures/code/Fig7_biomass_export.m

@@ -1,0 +1,217 @@
+clear
+
+% this code import the number of simulated particles located below 100 m in
+% Papa_meso and Papa_submeso
+
+%% Start with Papa_meso
+
+time_meso = 60.5:0.125:88.375;
+
+path = '/Volumes/mathieudever/particle_backup/Papa500/';
+for ii = 3:5
+    if ii ==1
+        filename = [path,'0mday/exportTS0mday.txt'];
+    elseif ii == 2
+        filename = [path,'0025mday_remin/exportTS0025mday_remin.txt'];
+    elseif ii == 3
+        filename = [path,'05mday_remin/exportTS05mday_remin.txt'];
+    elseif ii == 4
+        filename = [path,'1mday_remin/exportTS1mday_remin.txt'];
+    elseif ii == 5
+        filename = [path,'5mday_remin/exportTS5mday_remin.txt'];
+    end
+    formatSpec = '%f%[^\n\r]';
+    fileID = fopen(filename,'r');
+    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
+    fclose(fileID);
+    
+    export_meso_remin(:,ii) = dataArray{:, 1};
+    
+    clearvars filename delimiter formatSpec fileID dataArray ans
+end; clear ii path
+
+time_meso = 60.5:0.125:88.375;
+
+path = '/Volumes/mathieudever/particle_backup/Papa500/';
+for ii = 3:5
+    if ii ==1
+        filename = [path,'0mday/exportTS0mday.txt'];
+    elseif ii == 2
+        filename = [path,'0025mday/exportTS0025mday.txt'];
+    elseif ii == 3
+        filename = [path,'05mday/exportTS05mday.txt'];
+    elseif ii == 4
+        filename = [path,'1mday/exportTS1mday.txt'];
+    elseif ii == 5
+        filename = [path,'5mday/exportTS5mday.txt'];
+    end
+    formatSpec = '%f%[^\n\r]';
+    fileID = fopen(filename,'r');
+    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
+    fclose(fileID);
+    
+    export_meso(:,ii) = dataArray{:, 1};
+    
+    clearvars filename delimiter formatSpec fileID dataArray ans
[…]

### 2019-02-13 size_differentiated_export.tex
Commit to update

@@
 %\usepackage[left=3cm,right=3cm]{geometry}
-
   % Apply watermark to document
@@
 %\SetWatermarkLightness{0.9}
-%\SetWatermarkScale{5}
+%\SetWatermarkScale{15}
 %\SetWatermarkText{DRAFT}
@@
 % Trackchanges package
-\usepackage{trackchanges}
+%\usepackage{trackchanges}
 %% PLEASE USE THE FOLLOWING COMMANDS
@@
 
-\draftfalse
+%\draftfalse
 
@@
 %% ------------------------------------------------------------------------ %%
-\author{M. Dever\affil{1}, D. Nicholson\affil{1}, M. Omand\affil{2}, and A. Mahadevan\affil{1}}
+\authors{M. Dever\affil{1}, D. Nicholson\affil{1}, M. Omand\affil{2}, and A. Mahadevan\affil{1}}
 \affiliation{1}{Woods Hole Oceanographic Institution, Woods Hole, MA 02543, USA}
@@
 
-\begin{keypoints}
-\item = enter point 1 here =
-\item = enter point 2 here =
-\item = enter point 3 here =
-\end{keypoints}
+%\begin{keypoints}
+%\item = enter point 1 here =
+%\item = enter point 2 here =
+%\item = enter point 3 here =
+%\end{keypoints}
 
@@
 After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients than observed using underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}).
-The two experiments, however, show drastically different distributions of $M^2$, where the winter distribution has a much longer tail, suggesting sharper density gradients.
+The two experiments, however, show significantly different distributions of $M^2$, where the winter distribution has a longer tail, suggesting sharper density gradients.
 The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sample gradients at a maximum resolution of about 10 km, while the model resolution is 500 m and therefore allows sharp submesoscale fronts and filaments to be captured in the distribution.
@@
 The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion below).
-However, the seasonal cycle in submesoscale activity is out-of-phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}.
+However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}.
 Two mechanisms are therefore present to potentially sustain a year-long POC export: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export by advecting the more numerous slower-sinking particles into the ocean interior.
@@
 
-The analysis of the particle tracking experiments reveals that the role played by slower-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope coefficient $\xi$).
+Analyses of particle tracking experiments reveal that the role played by slower\-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope coefficient $\xi$).
 
@@
 Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export.
-The increase in exported biomass when comparing summer and winter time is larger when remineralization processes are included, and also increase with larger $\xi$.
-Total exported biomass almost doubles when $\xi =4$, and increases by 5 to 20\% for $\xi =2$ and $\xi = 3$, respectively.
+The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increase with larger $\xi$.
+Total exported biomass almost doubles when $\xi =4$, and increases by 5 and 20\% for $\xi =2$ and $\xi = 3$, respectively.
 This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to slow these particles down and thus prolongs their export timescales.
@@
 In the winter, however, slower-sinking particles are exported through advective processes.
-Their export timescale is little affected by remineralization processes as it only depend on local ocean dynamics, leading to a greater net export then when remineralization is not considered.
+Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics, leading to a greater net export than when remineralization is not considered.
 
@@
 In a gravitationally-driven system (i.e., weak submesoscale activity), this can only be achieved by having  $N_{slow} \sim N_{fast}$ and $\xi>3$, as there are no mechanism capable of selectively exporting slower-sinking particles (i.e., $N_{slow} \leq N_{fast}$).
-Junge slope greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}.
-Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$).
+Junge slopes greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}.
+Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}).
 Because of the negative slope in the biomass spectrum, any particle class sinking at a faster rate will not contribute as much to the biomass export.
@@
 	\centering
-	\includegraphics[width = .6\linewidth]{figures/cartoon_meso}\\[.2cm]
-	\includegraphics[width = .6\linewidth]{figures/cartoon_submeso}
-	\caption{}
+	\includegraphics[width = .65\linewidth]{figures/cartoon_meso}\\[.2cm]
+	\includegraphics[width = .65\linewidth]{figures/cartoon_submeso}
+	\caption{Schematics showing the respective contribution to export of particles with different sinking velocities in (top) a gravitationally-driven system (i.e., weak submesoscale dynamics), and (bottom) an advectively-driven system (i.e., strong submesoscale dynamics).}
 	\label{fig: export_cartoon}
@@
 In this regime, slower-sinking particles significantly contribute to POC export.
-In this study, sinking-velocity classes that did not contributes to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$.
+In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$.
 Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller in advectively-driven export mechanism, as opposed to gravitationally-driven.
@@
 \begin{enumerate}
-\item Submesoscale activity at station Papa is enhanced in the wintertime, leading to larger vertical velocities than in the summer.
-Export processes in the winter are thus driven by advective sinking, as opposed to gravitational sinking in the summertime.
+\item Submesoscale activity at station Papa is enhanced in the wintertime, leading to larger vertical velocities than in the summertime.
+The export mechanism in the winter is thus driven by advective sinking, as opposed to gravitational sinking in the summertime.
 \item Submesoscale dynamics generally enhance export by increasing the contribution of slower-sinking particles to POC export by increasing the number of particle exported through advective sinking.
 The contribution of slower-sinking particles in ageostrophic flows is at least significant, and can be dominant in specific conditions.
-\item Contribution of slower-sinking particles to POC export also depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class.
+\item Contribution of slower-sinking particles to POC export depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class.
 Three cases emerge in this study:
 \begin{enumerate}
-	\item If the Junge slope is smaller than 3, larger particles contribute most to export independently of flow dynamics, as even exporting 100\% of the particles in all sinking velocity classes would see larger particles dominate.
+	\item If the Junge slope is smaller than 3, larger particles contribute most to export independently of flow dynamics, as there are no mechanism capable of selectively exporting slower-sinking particles.
 	\item If the Junge slope equals 3, the respective contributions of the different size classes depend on the dynamical characteristics of the flow, as it influences the number of particles being exported.
@@
 	\end{enumerate}
-\item Remineralization processes reduces the contribution of slower-sinking particles when export dynamics are dominated by gravitational sinking (i.e., in a geostrophic flow).
+\item Remineralization processes reduce the contribution of slower-sinking particles when export dynamics are dominated by gravitational sinking (i.e., in a geostrophic flow).
 As flow dynamics become ageostrophic, advective sinking leads the export and remineralization processes have a limited impact.

### 2019-02-14 size_differentiated_export.tex
Updates from Overleaf

@@
 %% ------------------------------------------------------------------------ %%
-\authors{M. Dever\affil{1}, D. Nicholson\affil{1}, M. Omand\affil{2}, and A. Mahadevan\affil{1}}
+\authors{M. Dever\affil{1}, D. Nicholson\affil{1}, M. M. Omand\affil{2}, and A. Mahadevan\affil{1}}
 \affiliation{1}{Woods Hole Oceanographic Institution, Woods Hole, MA 02543, USA}
@@
 Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export.
-This study demonstrates that slow-sinking particles are significant contribution, and at times, can even dominate, the export flux.
+This study demonstrates that slow-sinking particles are significant contribution, and at times, can even dominate the export flux.
 \end{abstract}
@@
 
-Traditionally, POC export is thought to be mainly driven by larger, faster-sinking particles.
-This reasoning relies on the concept of competing timescales between remineralization and the time required to sink below the base of the mixed layer.
-The physical processes involved in defining the sinking rate are traditionally assumed to be dominated by gravitational sinking.
+Traditionally, POC export is thought to be mainly driven by larger, faster-sinking, particles capable of gravitationally-sinking below the export depth over timescales shorter than remineralization timescales.
 This is a reasonable assumption if one considers that vertical advective velocities in the ocean are generally much weaker than velocities associated with gravitational sinking.
-
-Recent work demonstrates that the presence of mesoscale eddies can enhance carbon export through two main processes: First, by increasing primary productivity through the injection of nutrients into the euphotic layer, therefore increasing the particle concentration, logically leading to a greater export \citep{Levy_1998}.
+However, recent work demonstrates that the presence of mesoscale eddies can enhance carbon export through two main processes: First, by increasing primary productivity through the injection of nutrients into the euphotic layer, therefore increasing the particle concentration, logically leading to a greater export \citep{Levy_1998}.
 Second, by generating larger vertical velocities along the front located at the eddy perimeter \citep{vanHaren_2006, Waite_2016}.
@@
 This conclusion is further supported by a recent, yet large, body of literature focusing on ocean dynamics at submeso-scales (1-10 km) and the impact on biogeochemical processes \citep[see reviews in][]{Thomas_2008,Klein_2009,Mahadevan_2016}.
-Submesoscale dynamics are characterized by Rossby numbers of order 1, indicating that relative vorticity associated with ocean currents exceed the planetary vorticity.
-These regions typically develop in filaments in areas where sharp density fronts exist \citep{McWilliams_2016}.
+Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{McWilliams_2016}.
 In this dynamical regime, geostrophic balance fails and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}.
 On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front.
-The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}.
-This asymmetry leads to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}.
+The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}.
 Just like at meso-scales, enhanced vertical velocities can generate either a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2012}, or can significantly increase the export of POC to the ocean interior \citep{Levy_2012, Estapa_2015,Omand_2015}.
 
-The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales therefore provide a physical mechanism capable of exporting particles over a larger portion of the particle size spectrum.
+The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
 Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities.
 Considering the fact that, although containing less biomass, smaller particles are far more numerous than larger particles, the impact of submesoscale dynamics on the export of POC is potentially significant.
-Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe.
+Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe in-situ.
 Additionally, and despite recent methodological progress \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and are more often than not inferred from key parameters such as particle type, size, and density.
 
-In this study, we rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale.
+In this study, we therefore rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale.
 Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior.
-Particles are released in two fundamentally different flow fields in terms of dynamics: one simulation is dominated by mesoscale dynamics, characterized by low Rossby numbers and weak vertical advective velocities, while the other is dominated by submesoscale dynamics, with fine-scale frontal structures and local Rossby numbers $\mathcal{O}$(1).
+Particles are released in two fundamentally different flow fields in terms of dynamics based on observed conditions in the Northeast Pacific in the summer, where ocean dynamics are characterized by low Rossby numbers and weak vertical advective velocities, and in the winter, where ocean dynamics include submesoscale frontal structures and local Rossby numbers $\mathcal{O}$(1).
 Both simulations and the particle-tracking module are described in Section \ref{sec: Methods}.
@@
 \label{sec: Methods}
-\subsection{Model setup and domains}
+\subsection{Model setup and domain}
 
-This study uses a non-hydrostatic, three-dimensional, numerical model called PSOM.
-Only a brief summary of its characteristics is provided here, as the model is exhaustively described in \cite{Mahadevan_1996a,Mahadevan_1996b}.
-The model domain is set in a channel configuration with periodic boundaries in the west and east, and solid boundaries in the south and north.
+This study uses a non-hydrostatic, three-dimensional, numerical model called PSOM \citep{Mahadevan_1996a,Mahadevan_1996b}.
+To simulate an eddy field that is representative of the Northeast Pacific Ocean, the model domain is set in a channel configuration with periodic east-west boundaries, and solid boundaries in the south and north.
 The domain covers 112 km in the x-direction, 304 km in the y-direction, and 1000 m in the vertical (Figure \ref{fig: model_domain}).
-The horizontal resolution is set to 500 m, while the vertical resolution is represented by a stretched grid with 32 levels ranging in thickness from 1.25 m near the surface to 70 m at the lowermost level.
-The model is integrated numerically in time and evolves the temperature, salinity, free-surface height, pressure, and three-dimensional velocity fields from an initial state, subject to momentum and buoyancy fluxes applied through the surface boundary conditions.
+The horizontal resolution is 500 m, while a stretched grid is used in the vertical with 32 levels ranging in thickness from 1.25 m near the surface to 70 m at the lowermost level.
+The model is integrated numerically in time and evolves the temperature, salinity, free-surface height, pressure, and three-dimensional velocity field from an initial state, subject to momentum and buoyancy fluxes applied through the surface boundary conditions.
 
@@
 	\caption{PSOM model setup.
-(a) Meridional profile of zonal winds scaling coefficient prescribed to PSOM, with a tapering at the north and south boundaries to reduce upwelling and downwelling, respectively.
-(b) Restoration factor used to dampen internal waves reflection at boundaries, as well as curl-driven upwelling and downwelling.
+(a) Meridional profile of zonal wind scaling coefficient that multiplies $\tau_x$, with a tapering at the north and south boundaries to reduce upwelling and downwelling, respectively.
+(b) Restoration factor (color shading) used to dampen internal wave reflection at boundaries as well as curl-driven upwelling and downwelling, along with constant density contours showing the three fronts (black line).
 (c) Surface net heat flux anomaly superimposed to the heat fluxes prescribed at $y = 150$ km.}
@@
 
-The zonal component of the  wind stress is prescribed at the surface throughout the model domain ($\tau_y =0$).
-Winds stress magnitude is, however, tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling that could contaminate the middle third of the model domain, where the analysis is focused (Figure \ref{fig: model_domain}a).
-A restoration time scale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress (Figure \ref{fig: model_domain}b).
-The restored regions also limit the reflection of internal waves at the solid boundaries back into the domain.
-Net surface heat fluxes are homogeneously prescribed throughout the domain.
-A linear meridional heat flux anomaly is superimposed to maintain a north/south gradient in net surface heat fluxes  (Figure \ref{fig: model_domain}c).
-The flux anomaly is zero in the center of the domain and has a slope of 1/24 W/m$^2$/km, estimated from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}.
+Time-varying wind stress and heat flux are prescribed at the surface boundary.
+Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory\footnote{https://www.pmel.noaa.gov/ocs/Papa}.
+Climatologies of daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long time series.
+A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability.
+In all numerical experiments, the simulations are first allowed to spin-down for the first 5 days with no forcing apply at the surface boundary.
+Surface wind stress and heat fluxes are then linearly ramped up between days 5 and 10 of the simulation, to reach realistic values at day 10.
+% (Figures \ref{fig: Papa_summer} and \ref{fig: Papa_winter}).
+While the meriodional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling that could contaminate the middle third of the model domain, where the analysis is focused (Figure \ref{fig: model_domain}a).
+A restoration time scale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress, as well as to limit internal wave reflection at the solid boundaries back into the domain (Figure \ref{fig: model_domain}b).
+Net surface heat fluxes are homogeneously prescribed throughout the domain, over which a linear meridional heat flux anomaly is superimposed to maintain a north-south gradient (Figure \ref{fig: model_domain}c).
+The flux anomaly is zero in the center of the domain, associated with the latitude of Station Papa, and has a meridional slope of 1/24 W/m$^2$/km, which was determined from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}.
 
-Both wind stress and net heat fluxes are allowed to vary in time.
-Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory\footnote{https://www.pmel.noaa.gov/ocs/Papa}.
-Climatologies of daily zonal wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long time series.
-A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability.
-In all experiments, the simulation is allowed to spin-down, that is with no forcing, for the first 5 days.
-Forcing is then linearly ramped up between days 5 and 10, to reach realistic values at day 10.% (Figures \ref{fig: Papa_summer} and \ref{fig: Papa_winter}).
-
-Initial background conditions are determined from a three-dimensional gridded field of temperature and salinity from ARGO floats \citep{Gaillard_2009,Gaillard_2016}.
-ARGO data is averaged monthly over the period 2002-2012 and two different months are used to initialized \textit{Papa\_summer} and \textit{Papa\_winter}.
+Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from ARGO floats \citep{Gaillard_2009,Gaillard_2016}.
+ARGO data is averaged monthly over the period 2002-2012 and two different months are used to initialize the two main numerical experiments for this study: Climatological conditions in April are used to initialize the \textit{Papa\_summer} experiment, while January climatological conditions are used to initialize the \textit{Papa\_winter} experiment (Table \ref{tab: meso_vs_submeso}).
 The north-south background density gradient is then intensified into three fronts located at $y = 75$, $y = 150$, and $y = 225$ km (Figure \ref{fig: model_domain}).
-The amplitude of the density gradient associated with the three fronts are determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \citep{Pelland_2016}.
-To reduce model spin-up time, density fronts are perturbed by a sinusoidal wave with a wavelength $\lambda = 112/n$, where $n$ is the closest integer to the 1st baroclinic deformation radius (n = 2 in this study).
+The amplitude of the density gradient associated with the three fronts is determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \citep{Pelland_2016}.
+To reduce model spin-up time, density fronts are perturbed by a sinusoidal wave with a wavelength close to the 1st baroclinic deformation radius ($\lambda = $ 66 km).
 Similar PSOM configurations were successfully used in previous studies \citep{Mahadevan_2012,Omand_2015}.
@@
 Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics mimicking conditions int the northeast Pacific in the summertime.
-Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($<1$).
+Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll1$).
 \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region.
 A different dynamical regime is expected to dominate during wintertime, with submesoscale dynamics playing a more important role.
-Submesoscale dynamics are characterized by sharper density fronts, filament-like features and high localized Rossby number ($>1$) over spatial scales $\mathcal{O}$(1 km).
-Such dynamics are more likely to be found in the winter time, where mixed layer depth is deeper and density gradients enhanced \citep{Thompson_2016}.
+Submesoscale dynamics are characterized by sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km).
+Such dynamics are more likely to be found in the winter time, where mixed layers are deeper and lateral density gradients enhanced \citep{Thompson_2016}.
 The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.
@@
 The magnitude of the density gradient across the front (i.e., frontal sharpness) is set to 3.34$\times$10$^{-6}$ kg/m$^3$/m, which corresponds to the 95$^{th}$ percentile of the PDF of density gradients measured in April from glider data collected in the region (Figure \ref{fig: Papa_summer} and Table \ref{tab: meso_vs_submeso}).
-The model is run with a timestep of 216 s and is allowed to spin-up for 60 days, allowing for the summer stratification to develop.
+The model is run with a timestep of 216 s and is allowed to spin-up for 60 days, allowing summer stratification to develop.
 The model is then run for 30 additional days, saving instantaneous model fields every 3 hours for particle tracking.
-The month of April is chosen for initialization so the experiment would capture the onset of positive net heat fluxes, and the summer restratification that ensues (Figure \ref{fig: Papa_summer}).
-In this region, the summer restratification is associated with large primary productivity and therefore large particle production and potentially export \citep[e.g., fecal pallets, dead phytoplankter; ][]{Plant_2016}.
+The month of April is chosen for initialization so the experiment would capture the onset of positive net heat fluxes, and the summer restratification that ensues in July-August (Figure \ref{fig: Papa_summer}).
+In this region, the summer stratification is associated with large primary productivity and therefore large particle production and potentially export \citep[e.g., fecal pallets, dead phytoplankter; ][]{Plant_2016}.
 

### 2019-02-14 figures/code/Fig2_Papa500_summer.m
Modified Fig 2 and 3

@@ -1,7 +1,7 @@
 clear
 
 % Create a blue-to-red colorbar for line plot
-cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(11,:);cmap(16,:)];
+cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(12,:);cmap(16,:)];
 
 %% this code creates the figures that synthetize the forcing and density
 % field for the Papa500 xperiment
@@ -14,7 +14,7 @@ clearvars -except glider cmap
 
 %% STEP 1 - Compute the TKE vs time. cannot use the full resolution, as it is domain integrated
 thefolder = pwd;
-cd /Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1
+cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/
 % Surface view
 depth = 50; % depth to plot in m
 lat = 50;   % Latitude of mid-domain (for f)
@@ -27,14 +27,14 @@ jfinish = 402;
 %% Step 2 - load the forcing time series
 
 % Heat Fluxes
-fileID = fopen('/Users/mathieudever/Google Drive/Publications/size_differentiated_sinking/figures/code/ini_heatfluxes.in','r');
+fileID = fopen('/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_configuration/Papa_summer/ini_heatfluxes.in','r');
 dataArray = textscan(fileID, '%f%[^\n\r]');
 fclose(fileID);
 HF = dataArray{:, 1};
 clearvars fileID dataArray ans;
 
 % Windstress
-fileID = fopen('/Users/mathieudever/Google Drive/Publications/size_differentiated_sinking/figures/code/ini_windstress.in','r');
+fileID = fopen('/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_configuration/Papa_summer/ini_windstress.in','r');
 dataArray = textscan(fileID, '%f%f%[^\n\r]','delimiter',',');
 fclose(fileID);
 WS = [dataArray{1:end-1}];
@@ -123,7 +123,7 @@ for ii =  [0 12000 24000 36000]
         hold on
         contour(x/1000,y/1000,rho(:,:,depth_level)',1025:.01:1026,'k');
         set(gca,'clim',CLIM)
-        colorbar; box on
+        box on
         set(gca,'fontsize',30)
[…]

### 2019-02-14 figures/code/Fig3_Papa500_winter.m

@@ -1,6 +1,6 @@
 clear
 % Create a blue-to-red colorbar for line plot
-cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(11,:);cmap(16,:)];
+cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(12,:);cmap(16,:)];
 
 %% this code creates the figures that synthetize the forcing and density
 % field for the Papa500 xperiment
@@ -73,6 +73,8 @@ h2 = plot([0:36000]*216/86400,WS(1:36001,1),'--k','linewidth',3);
 ylabel('Zonal Wind Stress [N/m^2]')
 set(gca,'ytick',-0.2:0.1:0.2,'ylim',[-0.2 0.2],'ycolor','k')
 
+line(get(gca,'xlim'),[0 0],'linestyle',':','color','k','linewidth',2)
+
 H = legend([h1 h2],'Surface Heat Flux','Zonal Wind Stress');
 set(H,'location','northwest','fontsize',32)
 
@@ -124,7 +126,7 @@ for ii =  [0 16000 32000 56000]
         hold on
         contour(x/1000,y/1000,rho(:,:,depth_level)',1025:.01:1026,'k');
         set(gca,'clim',CLIM)
-        colorbar; box on
+        box on
         set(gca,'fontsize',30)
         xlabel('x [km]')
         ylabel('y [km]')
@@ -138,9 +140,17 @@ for ii =  [0 16000 32000 56000]
         elseif loop_counter==2
             text(4,195,'(c)','fontsize',30,'fontweight','b','backgroundcolor','w')
             title(['doy ',num2str((ii-8000)/86400*108 + 20)])
+            set(gca,'yticklabels',{})
+            ylabel('')            
         elseif loop_counter==3
             text(4,195,'(d)','fontsize',30,'fontweight','b','backgroundcolor','w')
             title(['doy ',num2str((ii-8000)/86400*108 + 20)])
+            set(gca,'yticklabels',{})
+            ylabel('')
+            colorbar
+            POS = get(gca,'pos');
+            POS (3) = 0.1566;
+            set(gca,'pos',POS); clear POS
         end
     end
     

### 2019-02-14 figures/code/Fig5_dynamic_signature_w_valid.m
Update Fig5_dynamic_signature_w_valid.m

@@ -21,30 +21,30 @@ thefolder = pwd;
 fullfigure
 for plt = 1:2
     if plt == 1
-        cd /Volumes/mathieudever/PSOM_backup/Papa500/highrez
+        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/highrez
         timesteps = 30500;%[0 24000 30000 36000];
     elseif plt == 2
-        cd /Volumes/mathieudever/PSOM_backup/Papa500_steroid
+        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_winter
         timesteps = 44000;%[0 32000 44000 56000];
     end
     counter = 0;
-    for ii = timesteps
+    for tt = timesteps
         counter = counter +1;
         
-        rho = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'rho');
+        rho = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'rho');
         rho(1,:,:) = NaN; rho(end,:,:) = NaN;
-        u = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'u');
+        u = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'u');
         u(1,:,:) = NaN; u(end,:,:) = NaN;
-        v = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'v');
+        v = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'v');
         v(1,:,:) = NaN; v(end,:,:) = NaN;
-        w = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'w');
+        w = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'w');
         w(1,:,:) = NaN; w(end,:,:) = NaN;
         % vor = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'vor');
         % vor(1,:,:) = NaN; vor(end,:,:) = NaN;
         
-        x = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'xc')*1000;
-        y = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'yc')*1000;
-        Z2 = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'zc');
[…]

### 2019-02-14 size_differentiated_export.tex
Updates from Overleaf

@@
 The month of April is chosen for initialization so the experiment would capture the onset of positive net heat fluxes, and the summer restratification that ensues in July-August (Figure \ref{fig: Papa_summer}).
-In this region, the summer stratification is associated with large primary productivity and therefore large particle production and potentially export \citep[e.g., fecal pallets, dead phytoplankter; ][]{Plant_2016}.
+In this region, the summer stratification is associated with large primary productivity, particle production, and POC export \citep[e.g., fecal pallets, dead phytoplankter; ][]{Plant_2016}.
 
 %TAB1
-\begin{table}[ht]
+\begin{table}[t]
 \caption{Summary of the key characteristics of PSOM experiments \textit{Papa\_summer} and \textit{Papa\_winter}.}
@@
 		\hline
-		Period 								& April -- July         & January -- March      \\
+		Time period 								& April -- July             & January -- March          \\
 		Spin-up								& 60 days                   & 50 days                   \\
 		Advective timestep				    & 216 s                     & 108 s                     \\
-		Horizontal diffusivity			    & 1 m$^2$/s             & 0.2 m$^2$/s           \\
+		Horizontal diffusivity			    & 1 m$^2$/s                 & 0.2 m$^2$ s$^{-1}$        \\
 		Restoration timescale			    & 3 days                    & 15 days                   \\
 		Maximum M$^2$ ($\times$10$^{-8}$)	& 3.20 s$^{-2}$             & 33.9 s$^{-2}$             \\	
+		Maximum N$^2$ ($\times$10$^{-4}$)	& 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\
+		Initial mixed layer depth           & 73 m                      & 85 m                      \\
+		Zonal wind stress                	& 0 -- 0.16 N m$^{-2}$      & -0.05 -- 0.17 N m$^{-2}$  \\	
+		Surface heat flux               	& -46.8 -- 167.5 W m$^{-2}$ & -57.6 -- 15.3 W m$^{-2}$  \\	
 		\hline
@@
 % FIG2
-\begin{figure}[ht]
+\begin{figure}[t]
 	\includegraphics[width = 1\linewidth]{figures/Fig2_Papa500_summer}

### 2019-02-27 size_differentiated_export.tex
Updates from Overleaf

@@
 Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics mimicking conditions int the northeast Pacific in the summertime.
-Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll1$).
+Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1).
 \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region.
@@
 		Advective timestep				            & 216 s                     & 108 s                     \\
-		Horizontal diffusivity			    & 1 m$^2$/s                 & 0.2 m$^2$ s$^{-1}$        \\
+		Horizontal diffusivity			            & 1 m$^2$ s$^{-1}$          & 0.2 m$^2$ s$^{-1}$        \\
 		Restoration timescale			            & 3 days                    & 15 days                   \\
-		Maximum M$^2$ ($\times$10$^{-8}$)	& 3.20 s$^{-2}$             & 33.9 s$^{-2}$             \\	
-		Maximum N$^2$ ($\times$10$^{-4}$)	& 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\
+		Maximum initial M$^2$ ($\times$10$^{-8}$)	& 3.2 s$^{-2}$             & 33.9 s$^{-2}$             \\	
+		Maximum initial N$^2$ ($\times$10$^{-4}$)	& 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\
 		Initial mixed layer depth                   & 73 m                      & 85 m                      \\
@@
 To ensure that PSOM simulations yielded realistic conditions for both \textit{Papa\_summer} and \textit{Papa\_winter}, distributions of horizontal ($M^2$) and vertical ($N^2$) buoyancy gradients are compared with glider observations collected over the period 2008-2009 \citep{Pelland_2016}.
-
 During this period, underwater gliders sampled in a ``bow-tie" pattern centered on Station Papa.
-Gliders sample the water column following a triangular wave, whose shape is easily affected by currents, due to the slow moving speed of the glider ($\sim$1 km/hr).
+Gliders sample the water column in a triangular wave pattern, whose shape is easily affected by currents, due to the slow moving speed of the glider ($\sim$1 km/hr).
 It is therefore challenging to associate a specific spatial scale with gradients computed between glider profiles, as profile separation distances can be highly variable through depth and time.
 To circumvent this issue, horizontal buoyancy gradients are computed between each pair of glider profiles available within one branch of the bow-tie.
-Each along-track buoyancy gradient is then associated with a separation scale and a timestamp.
-
- Glider-based density gradients are highly affected by internal waves.
-To filter the impact of internal waves on the PDF of horizontal buoyancy gradients, only gradients computed at a scale of $\pm$ 1 km of twice the Rossby radius are considered.
+Each along-track buoyancy gradient is thus associated with a specific separation scale and a timestamp.
+Glider-based density gradients can be affected by internal waves.
+To filter the impact of internal waves on the PDF of horizontal buoyancy gradients, only gradients computed at a scale of twice the Rossby radius $\pm$ 1 km are considered.
 Rossby radii are $\sim 8$ km in winter and $\sim 20$ km in summer.
@@
 The time it will take for the particle to reach the eastern or western face of the grid cell can be computed by taking $x_{t_1} = x_i$ or $x_{t_1} = x_{i-1}$, respectively, and solving for $t_1$.
-For each advective timestep, the times required for the particle to reach any of the 6 walls of the grid cell are computed using Equation \ref{eq: PT_advection}.
+For each advective timestep, the times required for the particle to reach any of the 6 walls of the grid cell are computed using (\ref{eq: PT_advection}).
 If any of those times is shorter than the advective timestep, the particle is advected until it reaches the cell wall.
 Then the flow field in the adjacent grid cell is considered and the particle is advected over the remaining time.
-For each particle tracking experiment, four different classes of particles were released.
+
+\subsubsection{Particle Seeding}
+
+For all particle-tracking experiments, a single particle seeding event is prescribed.
+In the horizontal, particles are seeded every 250 m over the entire domain in the x-direction, and for 100 $<y<$ 200 km in the y-direction.
+The seeding is centered over the mean position of the middle front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by undesired effects created by the solid north-south solid boundaries.
+In the vertical, particles are seeded every 1 m between 75 and 85 m.
+This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined by the 1\% light level.
+The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Available Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}.
+The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.
+
+In each particle-tracking experiment, four different classes of particles are released.
 Each particle class is characterized by a different sinking velocity: 0.025, 0.05, 1, and 5 m/day.
-The slowest-sinking class was essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
+The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
 The fastest-sinking velocity is chosen as a low end-member representing velocity classes that will be exported in its entirety over the course of our experiment.
@@
 
-In the horizontal, particles are seeded once every 250 m over the entire domain in the x-direction, and for 100 $<y<$ 200 km in the y-direction.
-The seeding is centered on the position of the middle front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by artificial features developing at the solid north and south boundaries.
-In the vertical, eleven of those sheets of particles are seeded every 1 m between 75 and 85 m.
-This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined as the 1\% light level.
-The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Available Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}.
-The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.
-
-The particle advective timestep is set to 1.5 hours.
+The advective timestep for particles is set to 1.5 hours.
 The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}.
@@
 Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles.
-Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-suspended into the mixed layer.
+Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-suspended into the mixed layer.
 %The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.
@@
 \end{equation}
-where $N_0$ and $r_0$ represent a reference particle number and radius, and are chosen arbitrarily.
-For small particles ($<400\mu m$) and relatively cold temperature ($<15^oC$), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ tend to follow Stokes law, with $w_s \propto r^2$ \citep{Bach_2012}.
-\cite{Bach_2012} also demonstrates that Stokes law is generally a lower-bound limit to estimate sinking velocities for a specific particle size.
-Assuming a Stokes-like relationship, Equation \ref{eq: powerlaw_radius} can thus be re-written in terms of sinking velocities:
+where $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily.
+For small particles ($<$400$\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ tend to follow Stokes law, with $w_s \propto r^2$ \citep{Bach_2012}.
+\cite{Bach_2012} also demonstrate that Stokes law is generally a lower-bound estimate of sinking velocities for a specific particle size.
+Assuming a Stokes-like relationship, (\ref{eq: powerlaw_radius}) can be re-written in terms of sinking velocities as:
 
@@
 \end{equation}
-For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can thus be computed using Equation \ref{eq: powerlaw_velocity} (See Figure \ref{fig: sinking_velocity_spectrum}).
+For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can thus be computed using (\ref{eq: powerlaw_velocity}) (See Figure \ref{fig: sinking_velocity_spectrum}).
 For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represent 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}).
@@
 	\caption{Normalized number of particles (solid) and biomass (dashed) to the fastest-sinking particle class.
-Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 0 (black), and 2 (blue).}
+Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 3 (black), and 2 (blue).}
 	\label{fig: sinking_velocity_spectrum}
@@
 where $B_p(w_{s_0})$ is a reference biomass of one particle in the sinking velocity class $w_{s_0}$.
-The total biomass associated with one simulated particle can be obtained by scaling Equation \ref{eq: biomass_realparticle} by the ratio $N(w_s)/N_0$:
+The total biomass associated with one simulated particle can be obtained by scaling (\ref{eq: biomass_realparticle}) by the ratio $N(w_s)/N_0$:
 
@@
 where $B_0 = B_p(w_{s_0})$.
-Combining Equations \ref{eq: powerlaw_velocity} and \ref{eq: biomass_simulatedparticle} yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
+Combining (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomass_simulatedparticle}) yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
 \begin{equation}
@@
 Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}).
-This normalized formulation of particle number and biomass (Equations \ref{eq: powerlaw_velocity} and \ref{eq: biomassjungeslope}) presents the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments.
+This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) presents the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments.
 For the purpose of this study, only the relative amount of biomass is relevant.
@@
 \label{sec: remin_scheme}
-Remineralization of particles as they sink through the water column evidently impact the export of biomass.
+Remineralization of particles as they sink through the water column evidently impacts the export of biomass.
 Slow-sinking particles therefore are subject to shallower remineralization than fast-sinking particles.
@@
 In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship linking carbon content and time.
-This implicitly assumes that the biomass content of a particle diminishes in time proportionally to the particle volume.
+This implicitly assumes that the biomass content of a particle decreases in time proportionally to the particle volume.
 Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}:
@@
 The change in biomass with time is in turn expected to affect the sinking velocity of the particle.
-Given that $B \propto w^{3/2}$ (see Equation \ref{eq: biomass_realparticle}),  a time-varying sinking velocity is imposed to particles in all sinking-velocity classes using:
+Given that $B \propto w^{3/2}$ (see Equation (\ref{eq: biomass_realparticle})), particles in all sinking-velocity classes undergo a decay in sinking speed according to:
 
@@
 Particles are classified based on their initial sinking-velocity.
-However, it is worth noting that over the length of the particle-tracking experiments including remineralization (28 days), particles slow down by more than 90\% of their initial velocity.
+However, it is worth noting that over the length of the particle-tracking experiments that include remineralization (28 days), particle sinking speeds slow down to 10\% of their initial velocity.
 
@@
 \label{sec: Results}
-\subsection{Physical model}
+\subsection{\fixme{Seasonal change in dynamical regime? or seasonal cycle in submesoscale activity?}}
 
 Two model experiments are designed to capture different dynamical conditions observed in the northeast Pacific Ocean in summer and winter.
-\textit{Papa\_summer} is initialized in early spring (doy 105) when the water column is characterized by a relatively deep mixed layer ($\sim$100 m) and a halocline present between 100 and 150 m (Figure \ref{fig: Papa_summer}).
-The forcing by a realistic, positive, net heat flux generates the restratification of the water column, with the development of a strong thermocline between 25 and 50 m leading to the shoaling of the mixed layer and a subsurface peak in $N^2$ at about 30 m (see Figure \ref{fig: Papa_summer}).
+\textit{Papa\_summer} is initialized in early spring (doy 105) when the water column is characterized by a relatively deep mixed layer ($\sim$100 m) and a halocline located between 100 and 150 m (Figure \ref{fig: Papa_summer}).
+The forcing by a realistic, positive, net heat flux generates the restratification of the water column, with the development of a strong thermocline between 25 and 50~m leading to the shoaling of the mixed layer and a subsurface peak in $N^2$ at about 30 m (see Figure \ref{fig: Papa_summer}).
 A comparison between model outputs and monthly-averaged density profiles from underwater gliders collected in June and July over the period 2008-2009 yields correlation coefficients of $r = 0.87$ and $r = 0.88$, respectively.
-These correlation coefficients suggest that \textit{Papa\_summer} captures reasonably well the vertical spring and summer conditions in the northeast Pacific Ocean.
+These high correlation suggest that \textit{Papa\_summer} numerical experiment captures the vertical spring and summer conditions in the northeast Pacific Ocean.
 
 In the horizontal, the prescribed density fronts progressively become unstable within the first 60 days of the experiment (Figure \ref{fig: Papa_summer}).
-During this time, the Total Kinetic Energy (TKE) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation.
-The flattening of the TKE curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments.
-The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=( \partial v/ \partial x - \partial u/ \partial y)/f$; Figure \ref{fig: dynamics}).
+During this time, the Total Kinetic Energy (KE$_{\text{tot}}$) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation.
+The flattening of the KE$_{\text{tot}}$ curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments.
+The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=(v_x - u_y)/f$ where f = 1.12$\times10^{-4}$; Figure \ref{fig: dynamics}).
 
@@
 	\includegraphics[width = 1\linewidth]{figures/Fig5_dynamic_signature_w_valid}
-	\caption{Snapshots of $M^2$ (top), $\zeta /f$ (middle), and $w$ (bottom) half-way through the particle tracking experiment for \textit{Papa\_summer} (left and blue) and \textit{Papa\_winter} (right and red), with the Mixed Layer Depth indicated by the solid black line.
-The corresponding Probability Distribution Functions (PDFs) are shown in the center.
-Note the changing color scales between \textit{Papa\_summer} and \textit{Papa\_winter}.
+	\caption{Snapshots of $M^2$ (top), $\zeta /f$ (middle), and $w$ (bottom) half-way through the particle tracking experiment for \textit{Papa\_summer} (left) and \textit{Papa\_winter} (right), with the Mixed Layer Depth indicated by the solid black line.
+The corresponding Probability Distribution Functions (PDFs) are shown in the center for both \textit{Papa\_summer} (blue) and \textit{Papa\_winter} (red).
+Note the different colorbars used for \textit{Papa\_summer} and \textit{Papa\_winter}.
 Histograms of M$^2$ computed from glider data at Station Papa in February (blue line) and July (red line) are superimposed in the top middle panel.}
@@
 
-The largest horizontal buoyancy gradients are observed above the thermocline ($z<$50 m) and along the halocline (100-200 m), and range between 0 and 1.2$\times 10^{-7}$ s$^{-2}$ (Figure \ref{fig: dynamics}).
-These relatively weak density gradients result in low Rossby numbers O(0.1), positive on the denser (north) side of the front, and negative on the lighter (south) side of the front.
-Corresponding vertical velocities are consistently weaker than 1 m/day ($<$10$^{-5}$ m/s) and are characterized by regions of weak upwelling and downwelling on the order of 10 km, associated with the meandering of the front \citep{Bower_1989}.
-Alternating bands of upwelling and downwelling at $\mathcal{O}$(1 km) spatial scale are superimposed, likely caused by propagating internal waves.
-Coherent vertical velocities structures are homogeneous to depths much greater than the mixed layer depth ($\sim$25 m; Figure \ref{fig: Papa_summer}).
+%The largest horizontal buoyancy gradients are observed above the thermocline ($z$$<$50 m) and along the halocline (100--200 m), and range between 0 and 1.2$\times 10^{-7}$ s$^{-2}$ (Figure \ref{fig: dynamics}).
+Lateral buoyancy gradients in the summer are relatively weak $\mathcal{O}$(10$^{-8}$ s$^{-2}$) and result in low Rossby numbers $\mathcal{O}$(0.1), with positive relative vorticity on the denser (north) side of the front and negative relative vorticity on the lighter (south) side of the front.
+Corresponding vertical velocities are consistently weaker than 1 m/day ($<$10$^{-5}$ m/s) and are characterized by regions of weak upwelling and downwelling on 10 km scales, associated with the meandering of the front \citep{Bower_1989}.
+Alternating bands of upwelling and downwelling at $\mathcal{O}$(1 km) spatial scale are superimposed, and likely caused by propagating internal waves.
+Coherent vertical velocities structures extend to depths much greater than the mixed layer depth ($\sim$25 m; Figure \ref{fig: dynamics}).
 The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \citep{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ 1/s (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ 1/s, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s.
-The agreement between the scaling and the model outputs suggest that PSOM is capable of reproducing a realistic vertical flow field.
+%The agreement between the scaling and the model outputs suggest that PSOM is capable of reproducing a realistic vertical flow field.
 
-\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) with the objective to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \citep{Pelland_2016}.
-At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m.
+\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \citep{Pelland_2016}.
+At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m \citep[Figure \ref{fig: Papa_winter}][]{Pelland_2016}.
 After spin-up, the vertical stratification remains consistent throughout the model run, and compares well to the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}).
@@
 Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in \textit{Papa\_summer} (Figure \ref{fig: Papa_winter}).
-As a result, TKE starts to plateau at doy 48.
+As a result, KE$_{\text{tot}}$ starts to plateau at doy 48.
 The experiment is considered spun-up by doy 50 and the particle-tracking experiment is initialized.
@@
 
-The frontal structures visible in the horizontal buoyancy gradient field are logically associated with filaments of relatively high Rossby numbers, regularly exceeding O(1) (Figure \ref{fig: Papa_winter}).
-The PDF of Rossby numbers reveals a positively-skewed distribution of Rossby numbers ($s = 0.68$).
+The frontal structures visible in the horizontal buoyancy gradient field are associated with filaments of relatively high Rossby numbers exceeding $\mathcal{O}$(1) (Figure \ref{fig: Papa_winter}).
+The PDF of relative vorticity reveals a positively-skewed distribution ($s = 0.68$).
 This is in agreement with the fact the relative vorticity is more likely to be cyclonic than anticyclonic, based on conservation of potential vorticity \citep{Hoskins_1972}.
 Regions with a high Rossby number are localized and located in the mixed layer exclusively.
-In places where the local Rossby number reaches O(1), geostrophic balance is lost and a vertical secondary ageostrophic circulation develops to slump the isopycnals and return to a more stable geostrophically-driven flow.
+In places where the local Rossby number reaches $\mathcal{O}$(1), geostrophic balance is lost and a vertical secondary ageostrophic circulation begins to slump the isopycnals and restore the flow to a more geostrophically-balanced flow.
 This ageostrophic secondary circulation therefore generates ``hot spots" of higher vertical velocities.
-The fine-scale structures in the vertical velocity field corresponding to Rossby numbers O(1) can be seen in Figure \ref{fig: Papa_winter}, with local vertical velocities up to 60 m/day ($\sim 7\times10^{-4}$ m/s; Figure \ref{fig: dynamics}).
-Contrarily to the PDF of Rossby numbers, the distribution of vertical velocities demonstrate a negative skewness ($s =$ -0.25).
-This is in agreement with the theory: In fact, positive vertical vorticity is associated with the dense side of a density front, where Rossby numbers are positive and vertical velocities negative \citep{Mahadevan_2016}.
+The fine-scale structures in the vertical velocity field corresponding to $\mathcal{O}$(1) Rossby numbers  can be seen in Figure \ref{fig: Papa_winter}, with local vertical velocities up to 60 m/day ($\sim 7\times10^{-4}$ m/s; Figure \ref{fig: dynamics}).
+Contrary to the PDF of relative vorticity, the distribution of vertical velocities demonstrate a negative skewness ($s =$ -0.25).
+This is in agreement with the theory: In fact, positive vertical vorticity is associated with the dense side of a density front, where relative vorticity are positive and vertical velocities negative \citep{Mahadevan_2016}.
 Once again, the amplitude of these vertical velocity hot spots is coherent with the scaling $w \propto RofU/N$: using $Ro\sim1$, $N\sim10^{-2}$ 1/s, $f\sim10^{-5}$ 1/s, and $U\sim0.1$ m/s, we obtain $w\sim 10^{-4}$ m/s.
-This demonstrates the capabilities of PSOM to resolve sharp frontal features at the kilometer scale, as well as the ageostrophic circulation associated with those fronts.
+%This demonstrates the capabilities of PSOM to resolve sharp frontal features at the kilometer scale, as well as the ageostrophic circulation associated with those fronts.
 
@@
 Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle export, using Lagrangian particle-tracking.
-In this study, particles are considered "exported" once located below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa.
+In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa.
 Choosing the winter mixed layer as the export depth is most appropriate, as it reduces the chances of particles being re-entrained into the mixed layer the following winter.
@@
 
-The percentage of simulated particles being exported with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
+The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
 As expected, the faster-sinking particles are exported earlier and in larger proportions.
-For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%).
-In fact, time series of exported particles closely follow the curves derived from considering gravitational sinking only (Figure \ref{fig: particle_export}).
+For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%).
+In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking only (Figure \ref{fig: particle_export}).
 
@@
 	\caption{Percentage of particles located below 100 m as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
-Expected percentages of exported particles based on gravitational sinking only are indicated with dashed lines.}
+Expected percentages of exported particles based on only gravitational sinking are indicated with dashed lines.}
 	\label{fig: particle_export}
@@
 In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking.
-This early arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day.
+This earlier arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day.
 Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation.
@@
 About 5\% of particles sinking at 0.025 m/day are exported.
-However, more time is now necessary to export 100\% of the simulated particles.
+However, particle export is now stretched over longer periods of time due to particle resuspension.
 This can be seen in the gentler slopes of the export curves observed in \textit{Papa\_winter} than in \textit{Papa\_summer}.
 
-Particles released in \textit{Papa\_winter} are thus exported faster and in greater number than expected from gravitational sinking only.
+Particles released in \textit{Papa\_winter} are thus exported faster and in greater numbers than expected from gravitational sinking.
 Eventually, all sinking particles would be exported in both \textit{Papa\_summer} and \textit{Papa\_winter}, if particles were tracked for a long enough period of time.
@@
 The presence of submesoscale dynamics therefore increases the number of exported slow-sinking simulated particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class.
-This has large implications on the amount of biomass exported, as slower-sinking particles are far more numerous than faster-sinking particles, despite containing less biomass (Figure \ref{fig: sinking_velocity_spectrum}).
-While the number of simulated particles that are exported is only a function of the modeled flow field, the exported biomass also depends on the Junge slope (see Equation \ref{eq: biomassjungeslope}).
+This has large implications on the amount of biomass exported, as slower-sinking particles are far more numerous than faster-sinking particles, despite containing less biomass per particle (Figure \ref{fig: sinking_velocity_spectrum}).
+While the percentage of exported particles is a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).
 
-The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhance the role played by slower-sinking particles in biomass export, and thus decrease the importance of faster-sinking particles (Figure \ref{fig: biomass_export_remin}).
-This is a logical results in sight of the increase in the number of particles exported when submesoscales features are present (Figure \ref{fig: particle_export}).
-The sinking class dominating export, however, is highly dependent on the Junge slope parameter.
-As the Junge slope parameter increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases, sometimes dominating biomass export.
-For example, after 28 days, the 1 m/day exports 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.
+The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (Figure \ref{fig: biomass_export_remin}).
+This is a logical result given the observed increase in the number of particles exported when submesoscales features are present (Figure \ref{fig: particle_export}).
+The sinking class dominating export, however, is highly dependent on the Junge slope.
+As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases.
+For example, after 28 days, the 1 m/day particle class exports 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.
 
@@
 	\caption{Amount of biomass exported in normalized units by each sinking velocity class in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for three different Junge slopes: $\xi =$ 4 (top), $\xi =$ 3 (middle), and $\xi =$ 2 (bottom; see Figure \ref{fig: sinking_velocity_spectrum}).
-Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
+Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.
+\fixme{show only 3 ws?}}
 	\label{fig: biomass_export_remin}
@@
 
- Including remineralization of particles (Equation \ref{eq: remin_scheme}) significantly impacts the relative importance of sinking and advection to export for each particle class.
-In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles slow down as they are remineralized (Equation \ref{eq: sinking_velocity_remin} and Figure \ref{fig: biomass_export_remin}).
+ Including remineralization of particles (see Equation (\ref{eq: remin_scheme})) significantly impacts the relative importance of sinking and advection to export for each particle class.
+In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles slow down as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}).
 In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included.
@@
  The total amount of biomass is also reduced compared to the case with no remineralization.
-The difference between the two cases is time dependent, and increases with the age of the particle, as particles further remineralize.
-The impact of remineralization on the amount of biomass exported intensifies as the sinking velocity decreases.
+The difference is time dependent, and increases with the age of the particle, as particles further remineralize.
+In a gravitationally-driven system such as during the summer in the northeast Pacific, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases.
 In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export, with slower-sinking particles contributing significantly less than faster-sinking particles (dash lines in Figure \ref{fig: biomass_export_remin}.
-Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduces by 5-6 orders of magnitude depending on the slope of the biomass spectra (see Figure \ref{fig: sinking_velocity_spectrum}).
-Similarly to the case with no remineralization, a change in the Junge slope impacts the contribution of slower-sinking velocity classes.
-This can be seen in the amount of biomass exported by the 1 m/day sinking-velocity class: A negative slope (i.e., $\xi$ = 4) leads to a maximum biomass of about 6, while a positive slope (i.e., $\xi$ = 2) leads to a maximum biomass of 1.
-Both of these amount of exported biomass represent less than 1\% of the total exported biomass, making the contribution to export from this sinking-velocity class virtually insignificant.
+Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by 5-6 orders of magnitude depending on the slope of the biomass spectra (see Figure \ref{fig: sinking_velocity_spectrum}).
+Similar to the case with no remineralization, a change in the Junge slope impacts the biomass contribution of slower-sinking velocity classes.
+This can be seen in the amount of biomass exported by the 1 m/day sinking-velocity class: A negative slope (i.e., $\xi$ = 4) leads to a maximum biomass of about 6 normalized biomass units \fixme{n.b.u.
+?}, while a positive slope (i.e., $\xi$ = 2) leads to a maximum biomass of 1 normalized biomass unit.
+However, both these contributions to biomass export represent much less than 1\% of the biomass export of the 5 m/day sinking-velocity class, making the contribution to export from the 1 m/day sinking-velocity class virtually insignificant, regardless of the Junge slope.
 
- In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported more rapidly than in \textit{Papa\_summer} due to stronger vertical velocities.
+ In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities.
 The difference in exported biomass between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already behind exported.
-As particles age, remineralization has an increasing impact and the difference in total exported biomass increases at a rate controlled by the remineralization rate in Equation \ref{eq: remin_scheme}.
-Similarly to \textit{Papa\_summer}, the total amount of biomass exported by a specific sinking-velocity class decreases as the Junge slope decreases (i.e., the sinking-velocity spectra flattens).
-An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the amount of biomass exported from the 0.025 m/day sinking-velocity class exceeds the amount of biomass exported by both the 0.5 and 1 m/day sinking-velocity classes.
+As particles age, remineralization has an increasing impact and the difference in total exported biomass increases at a rate controlled by the remineralization rate in (\ref{eq: remin_scheme}).
+Similar to \textit{Papa\_summer}, the total amount of biomass exported by a sinking-velocity class decreases as the Junge slope decreases (i.e., the sinking-velocity spectra flattens).
+%An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the amount of biomass exported from the 0.025 m/day sinking-velocity class exceeds the amount of biomass exported by both the 0.5 and 1 m/day sinking-velocity classes.
 This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.
@@
 \textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the northeast Pacific Ocean.
-After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients than observed using underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}).
-The two experiments, however, show significantly different distributions of $M^2$, where the winter distribution has a longer tail, suggesting sharper density gradients.
+After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients to observations from underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}).
+The two experiments, however, show significantly different distributions of $M^2$, with the winter distribution exhibiting a longer tail, suggesting sharper density gradients.
 The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sample gradients at a maximum resolution of about 10 km, while the model resolution is 500 m and therefore allows sharp submesoscale fronts and filaments to be captured in the distribution.
@@
 The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa, and reflected in the model experiments, echoes findings of recent observational studies conducted at a similar latitude in the Atlantic Ocean demonstrating the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}.
-Despite being sometimes qualified as an "eddy desert" with low kinetic energy \citep{Chelton_2011}, wintertime ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features: strong density gradients, localized Rossby numbers of the order 1 and larger, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.
+Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, wintertime ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.
 
@@
 
-The hypothesis tested in this study is that submesoscale activity enhances export of particulate matter at Station Papa.
+The hypothesis tested in this study is that submesoscale activity enhances export of particulate matter at Station Papa by shortening the export timescale of particulate matter.
 The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion below).
@@
 Two mechanisms are therefore present to potentially sustain a year-long POC export: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export by advecting the more numerous slower-sinking particles into the ocean interior.
-In the summer, the production of POC is much larger, but export tends to be dominated by gravitational sinking, which discriminate against slower-sinking particles.
+In the summer, the production of POC is at its yearly maximum, but export tends to be dominated by gravitational sinking, which favors faster-sinking particles.
 
@@
 Mixed layer ocean dynamics at station Papa change significantly between the winter and the summer.
-In the winter, submesoscale dynamics are intensified and sharp fronts and filaments develop in the mixed layer.
+In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer.
 This change in dynamics has a clear impact on the amount of particles exported for all sinking-velocity classes modeled in this experiment.
-First, particles in all sinking-velocity class generally reach the export depth faster.
-This is the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescales (i.e., the time it takes for a particle to reach the export depth), and its remineralization timescales.
+
+Particles within a sinking-velocity class are exported both more rapidly and over longer timescales.
+In fact, a portion of the particles tend to reach the export depth over shorter timescales than in the absence of submesoscale dynamics.
+This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale.
 The former evidently needs to be shorter than the latter to efficiently export POC.
-Second, particles are exported more gradually.
-While particles in a sinking-velocity class reach the export depth over shorter timescale, it takes longer to export the same number of particles as in the summer.
-This is due to the upward vertical current, re-suspending material that would otherwise sink, and thus delaying its export.
-Keeping in mind the competing timescales mentioned above, it leads to interesting questions: Is it more efficient to export more faster-sinking particles--less numerous but containing more biomass--and no slower-sinking particles, like in \textit{Papa\_summer}?
-Or is export greater when less faster-sinking particles are exported, but more slower-sinking particles, much more numerous, also contribute to the export, like in \textit{Papa\_winter}?
+However, while some particles are exported faster, the rest of the particles within a sinking-velocity class are exported more gradually in time.
+This is due to upward vertical currents, re-suspending material that would otherwise sink, and thus delay its export.
+
+In the summer, the gravitationally-driven export mechanism efficiently exports faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles.
+In the winter, however, the export mechanisms is advectively-driven, which leads to a smaller export of faster-sinking particles than in the summer due to resuspension, but efficiently exports slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: sinking_velocity_spectrum}).
+These two competing mechanisms rise the questions as to which process is most efficient in exporting particulate material below the winter mixed layer.
 
@@
 Over the course of our simulation, the total amount of biomass exported is consistently enhanced when $\xi = 4$ (10 to 60\% increase) in the presence of submesoscale dynamics.
-For a flat biomass spectrum ($\xi = 3$), the export enhancement due to submesoscale dynamics is always smaller than 20\%.
-When $\xi =2$, the amount of biomass exported in the presence of submesoscale dynamics varies between 95 and 110\% of the export observed in the summer, when submesoscale dynamics are not active.
+For a flat biomass spectrum ($\xi = 3$), the export enhancement due to submesoscale dynamics is always smaller than 20\%.\fixme{eventually all is exported...} When $\xi =2$, the amount of biomass exported in the presence of submesoscale dynamics varies between 95 and 110\% of the export observed in the summer, when submesoscale dynamics are not active.
 Therefore, to address the questions formulated above, export is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales.
@@
 
+\fixme{modify when results section is edited}
 Introducing remineralization processes significantly decreases the total amount of biomass exported.
 Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export.
-The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increase with larger $\xi$.
+The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increases with larger $\xi$.
 Total exported biomass almost doubles when $\xi =4$, and increases by 5 and 20\% for $\xi =2$ and $\xi = 3$, respectively.
@@
 \end{equation}
-where $N$ is the number of simulated particles exported, $w_s$ is the sinking velocity and $\xi$ is the Junge slope coefficient (see Equation \ref{eq: powerlaw_radius}).
+where $N$ is the number of simulated particles exported, $w_s$ is the sinking velocity and $\xi$ is the Junge slope coefficient (see Equation (\ref{eq: powerlaw_radius})).
 
@@
 The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth.
-As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation \ref{eq: condition}).
+As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation (\ref{eq: condition})).
 A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}).

### 2019-02-27 figures/code/Fig6_particle_export_flux.m
New figure 6
Now is particle flux instead of export

@@ -1,0 +1,224 @@
+clear
+
+% this code import the number of simulated particles located below 100 m in
+% Papa_meso and Papa_submeso
+
+%% Start with Papa_summer
+
+% total number of particles
+N0 = 1971717;
+% start day
+t0 = 60.5;
+% Time vector.
+time_meso = 60.5:0.125:88.375;
+
+path = '/Volumes/mahadevanlab/mathieudever/particle_backup/Papa_summer/';
+for ii = 1:5
+    if ii ==1
+        continue
+    elseif ii == 2
+        continue
+    elseif ii == 3
+        filenamedown = [path,'05mday/exportTS05mdaydown.txt'];
+        filenameup = [path,'05mday/exportTS05mdayup.txt'];
+    elseif ii == 4
+        filenamedown = [path,'1mday/exportTS1mdaydown.txt'];
+        filenameup = [path,'1mday/exportTS1mdayup.txt'];
+    elseif ii == 5
+        filenamedown = [path,'5mday/exportTS5mdaydown.txt'];
+        filenameup = [path,'5mday/exportTS5mdayup.txt'];
+    end
+    
+    % Get downward flux
+    formatSpec = '%f%[^\n\r]';
+    fileID = fopen(filenamedown,'r');
+    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
+    fclose(fileID);
+    flux_meso_down(:,ii) = dataArray{:, 1};
+    clearvars filenamedown delimiter formatSpec fileID dataArray ans
+    
+    % Get upward flux
+    formatSpec = '%f%[^\n\r]';
+    fileID = fopen(filenameup,'r');
+    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
+    fclose(fileID);
+    flux_meso_up(:,ii) = dataArray{:, 1};
+    
+    clearvars filenameup delimiter formatSpec fileID dataArray ans
+end; clear ii path
+
+flux_meso_down(flux_meso_down==0) = 1e-10;
+flux_meso_up(flux_meso_up==0) = 1e-10;
+%% Compute export anomaly based on expected export computed from sinking
+% velocity and distance from 100m horizon
+
[…]

### 2019-02-28 figures/code/Fig6_particle_export_flux.m
Even newer Fig6
paticle fluxes are normalized by total number of particles to avoid discussion about spectral slope.

@@ -47,8 +47,7 @@ for ii = 1:5
     clearvars filenameup delimiter formatSpec fileID dataArray ans
 end; clear ii path
 
-flux_meso_down(flux_meso_down==0) = 1e-10;
-flux_meso_up(flux_meso_up==0) = 1e-10;
+
 %% Compute export anomaly based on expected export computed from sinking
 % velocity and distance from 100m horizon
 
@@ -59,14 +58,13 @@ for ws = [0.025 0.5 1 5]
         ind = find(t0+zz/ws<=time_meso,1,'first');
         grav_flux_meso(ind,wscounter) = N0./11./0.125;
     end; clear zz ind
-    grav_flux_meso(:,wscounter) = smooth(grav_flux_meso(:,wscounter),8);
-    a =find(grav_flux_meso(:,wscounter)~=0,1,'first');
-    b = find(grav_flux_meso(:,wscounter)~=0,1,'last');
-    grav_flux_meso(a:b,wscounter) = max(grav_flux_meso(a:b,wscounter));
+    %grav_flux_meso(:,wscounter) = smooth(grav_flux_meso(:,wscounter),12);
+    %a =find(grav_flux_meso(:,wscounter)~=0,1,'first');
+    %b = find(grav_flux_meso(:,wscounter)~=0,1,'last');
+    %grav_flux_meso(a:b,wscounter) = max(grav_flux_meso(a:b,wscounter));
     wscounter = wscounter +1;
 end; clear ws wscounter a b
 
-grav_flux_meso(grav_flux_meso==0) = 1e-10;
 
 %% Then do Papa_submeso
 N0 = 1971717;
@@ -140,37 +138,42 @@ cmap = [0    0.4470    0.7410
 fullfigure
 subplot(3,2,1)
 for ii = 1:5
-    plot(time_meso+105,smooth(flux_meso_up(:,ii)./unique(diff(time_meso)),12),'color',cmap(ii,:),'linewidth',1);
+    plot(time_meso+105,flux_meso_up(:,ii)./unique(diff(time_meso))./N0*100,'color',cmap(ii,:),'linewidth',1);
     hold on; grid on
     theh(ii) = line([0 0],[0 0],'color',cmap(ii,:),'linewidth',2);
 end; clear ii
-set(gca,'yscale','log','xticklabel',{},'fontsize',16,'xlim',[min(time_meso)+105 max(time_meso)+105])
[…]

### 2019-02-28 size_differentiated_export.tex
Updates from Overleaf

@@
 
-\subsection{Particle tracking}
+\subsection{Gravitational and Advective Sinking of POC}
 
@@
 In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa.
-Choosing the winter mixed layer as the export depth is most appropriate, as it reduces the chances of particles being re-entrained into the mixed layer the following winter.
-We first consider the case of conservatives particles that do not remineralize in order to better identify the effects of ocean dynamics and spectral slope on export.
+Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2018}.
+We first consider the case of conservatives particles that do not remineralize in order to isolate the effects of ocean dynamics on export.
 
-The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
+The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles, is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
+As expected, the faster-sinking particles are exported earlier and in larger proportions than slower-sinking particles.
+For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\% of total export).
+In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}).
+
+\fixme{mention deviations from dashed line. Mention resuspension (less than 1\%) for slow-sinking particles only due to vertical velocities.}
+%The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
 As expected, the faster-sinking particles are exported earlier and in larger proportions.
@@
 	\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export}
-	\caption{Percentage of particles located below 100 m as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
-Expected percentages of exported particles based on only gravitational sinking are indicated with dashed lines.}
+	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
+	\caption{Upward (top) and downward (bottom) fluxes of particles at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
+Fluxes are  For each sinking-velocity class, the net particle flux is shown by a thick line.
+Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
 	\label{fig: particle_export}

### 2019-03-03 size_differentiated_export.tex
Updates from Overleaf

@@
 eastward) persisting throughout the experiment.
-(b)-(d) horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 105, 135, and 165.
+(b)-(d) surface horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 105, 135, and 165.
 Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$).
@@
 Notice the mostly negative heat fluxes, as well as alternating zonal wind direction.
-(b)-(d) horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 0, 30, and 50.
+(b)-(d) surface horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 0, 30, and 50.
 Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$).
@@
 
-The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles, is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
+The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
 As expected, the faster-sinking particles are exported earlier and in larger proportions than slower-sinking particles.
-For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\% of total export).
-In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}).
+For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%).
+In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}a).
+The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).
 
-\fixme{mention deviations from dashed line. Mention resuspension (less than 1\%) for slow-sinking particles only due to vertical velocities.}
+%\fixme{mention deviations from dashed line. Mention resuspension (less than 1\%) for slow-sinking particles only due to vertical velocities.}
 %The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
@@
 	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
-	\caption{Upward (top) and downward (bottom) fluxes of particles at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
-Fluxes are  For each sinking-velocity class, the net particle flux is shown by a thick line.
+	\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
+Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain.
+For each sinking-velocity class, the net particle flux is shown by a thick line.
 Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
@@
 
-Time series of exported particles in \textit{Papa\_winter} present major differences.
+Time series of particle fluxes in \textit{Papa\_winter} present major differences.
+In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking.
+This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day.
+Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation.
+Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}.
+About 5\% of particles sinking at 0.025 m/day are exported within the first 28 days of the experiment.
+However, particle export is now stretched over longer periods of time due to particle resuspension.
+In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features, such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a).
+These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet).
+However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring at submesoscales.
+
+%Time series of exported particles in \textit{Papa\_winter} present major differences.
 In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking.
@@
 
-The presence of submesoscale dynamics therefore increases the number of exported slow-sinking simulated particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class.
+The presence of submesoscale dynamics therefore hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class.
 This has large implications on the amount of biomass exported, as slower-sinking particles are far more numerous than faster-sinking particles, despite containing less biomass per particle (Figure \ref{fig: sinking_velocity_spectrum}).
-While the percentage of exported particles is a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).
+While the normalized particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).
 
-The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (Figure \ref{fig: biomass_export_remin}).
-This is a logical result given the observed increase in the number of particles exported when submesoscales features are present (Figure \ref{fig: particle_export}).
+The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}).
+This is a logical result given the observed increase in the particle export flux when submesoscales features are present (Figure \ref{fig: particle_export}).
 The sinking class dominating export, however, is highly dependent on the Junge slope.

### 2019-03-04 figures/code/Fig7_biomass_export_flux.m
New figure 7
Shows export fluxes instead of cumulated biomass

@@ -1,0 +1,286 @@
+clear
+
+% this code import the number of simulated particles located below 100 m in
+% Papa_meso and Papa_submeso
+
+%% Start with Papa_summer
+
+% arbitrary biomass unit
+B0 = 1;
+% Sinking-velocity classes
+ws = [0 0.025 0.5 1 5];
+% Reference sinking-velocity
+ws0 = max(ws);
+
+% total number of particles
+N0 = 1971717;
+% start day
+t0 = 60.5;
+% Time vector.
+time_meso = 60.5:0.125:88.375;
+
+path = '/Volumes/mahadevanlab/mathieudever/particle_backup/Papa_summer/';
+for ii = 1:5
+    if ii ==1
+        continue
+    elseif ii == 2
+        continue
+    elseif ii == 3
+        filenamedown = [path,'05mday/exportTS05mdaydown.txt'];
+        filenameup = [path,'05mday/exportTS05mdayup.txt'];
+    elseif ii == 4
+        filenamedown = [path,'1mday/exportTS1mdaydown.txt'];
+        filenameup = [path,'1mday/exportTS1mdayup.txt'];
+    elseif ii == 5
+        filenamedown = [path,'5mday/exportTS5mdaydown.txt'];
+        filenameup = [path,'5mday/exportTS5mdayup.txt'];
+    end
+    
+    % Get downward flux
+    formatSpec = '%f%[^\n\r]';
+    fileID = fopen(filenamedown,'r');
+    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
+    fclose(fileID);
+    flux_meso_down(:,ii) = dataArray{:, 1};
+    clearvars filenamedown delimiter formatSpec fileID dataArray ans
+    
+    % Get upward flux
+    formatSpec = '%f%[^\n\r]';
+    fileID = fopen(filenameup,'r');
+    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
+    fclose(fileID);
+    flux_meso_up(:,ii) = dataArray{:, 1};
+    
+    clearvars filenameup delimiter formatSpec fileID dataArray ans
+end; clear ii
+
+for ii = 1:5
+    if ii ==1
+        continue
+    elseif ii == 2
+        continue
+    elseif ii == 3
+        continue
[…]

### 2019-03-04 figures/code/Fig6b_biomass_export_flux.m
Add a biomass flux figure for different Junge slopes

@@ -217,7 +217,7 @@ for slope = [4 2]
             B_meso_remin([1:find(B_meso_remin(:,ii)>0,1,'first')-1 find(B_meso_remin(:,ii)>0,1,'last')+1:end],ii) = 1e-10;
         else
             B_meso(1:find(B_meso(:,ii)>0,1,'first')-1,ii) = 1e-10;
-            B_meso_remin(1:find(B_meso_remin(:,ii)>1e-9,1,'first')-1,ii) = 1e-10;  
+            B_meso_remin(1:find(B_meso_remin(:,ii)>1e-9,1,'first')-1,ii) = 1e-10;
         end
         
         B_submeso(1:find(B_submeso(:,ii)>0,1,'first')-1,ii) = 1e-10;
@@ -231,31 +231,32 @@ for slope = [4 2]
     
     
     % PAPA WINTER
-    axes
     if counter == 0
-    set(gca,'position',[0.1   0.55   0.4   0.3])
-    elseif counter == 1
-    set(gca,'position',[0.1   0.2   0.4   0.3])
+        ax1 = axes;
+        set(gca,'position',[0.1   0.55   0.4   0.35])
+        POS = get(gca,'position');
+    else
+        axes(ax1)
     end
-    POS = get(gca,'position');
-
+    
     % Plot Curves
     for ii = 5:-1:2
-        h1(5-ii+1) = plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','--');
+        if counter == 0
+            h1(5-ii+1) = plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','-');
+        else
+            plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','--');
+        end
         hold on
-        h2(5-ii+1) = plot(time_meso+105,B_meso_remin(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:));
-        h3(5-ii+1) = plot(time_meso+105,B_meso_remin(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:));
     end; clear ii
-        
+    
     % Make it pretty
     % Legend
-    if counter == 0
-    H = legend(h2,'w_s = 5','w_s = 1','w_s = 0.5','w_s = 0.025');
[…]

### 2019-03-04 size_differentiated_export.tex
Updates from Overleaf

@@
 Eventually, all sinking particles would be exported in both \textit{Papa\_summer} and \textit{Papa\_winter}, if particles were tracked for a long enough period of time.
+
+\fixme{Here Fig6b should be included an described.
+The key points are (1) the large difference between velocity class that have $w_s\ll w_{adv}$, and the one that have $w_s\sim w_{adv}$, (2) despite the large difference in \% of particles exported the biomass fluxes are of the same order of magnitude when $\xi=4$ as it is often reported in the ocean, and (3) the predictible decrease in biomass export flux when changing the slope based on equation (8).
+}
+
+\begin{equation}
+    \frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
+\end{equation}
+
 Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale.

### 2019-03-04 size_differentiated_export.tex
Updates from Overleaf

@@
 
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
+	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum})}
+	\label{fig: biomass_export}
+\end{figure}
+
 Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale.

### 2019-03-04 figures/code/Fig6b_biomass_export_flux.m
update Fig6b

@@ -269,8 +269,8 @@ for slope = [4 2]
     
     % Annotations
     if counter == 1
-        text(0.03,0.95,'(a)','fontsize',28,'HorizontalAlignment','center','edgecolor','w','Units','normalized')
-        text(0.5,1.25,'Papa\_summer','HorizontalAlignment','center','FontWeight','b','FontSize',30,'Units','normalized')
+        h = text(0.03,0.95,'(a)','fontsize',28,'HorizontalAlignment','center','edgecolor','none','Units','normalized','FontWeight','b','BackgroundColor','none')
+        text(0.5,1.22,'Papa\_summer','HorizontalAlignment','center','FontWeight','b','FontSize',40,'Units','normalized')
     end
     
     % Second legend
@@ -325,8 +325,8 @@ for slope = [4 2]
     
     % Annotations
     if counter == 1
-        text(0.03,0.95,'(b)','fontsize',28,'HorizontalAlignment','center','edgecolor','w','Units','normalized')
-        text(0.5,1.25,'Papa\_winter','HorizontalAlignment','center','FontWeight','b','FontSize',30,'Units','normalized')
+        text(0.03,0.95,'(b)','fontsize',28,'HorizontalAlignment','center','edgecolor','none','Units','normalized','FontWeight','b','BackgroundColor','none')
+        text(0.5,1.22,'Papa\_winter','HorizontalAlignment','center','FontWeight','b','FontSize',40,'Units','normalized')
     end
     
     % Second legend

### 2019-03-04 figures/code/Fig7_biomass_export_flux.m
New figure 7 with biomass flux and just remin vs no remin

@@ -196,7 +196,7 @@ cmap = [0    0.4470    0.7410
 %%
 fullfigure
 counter = 0;
-for slope = [4 2]
+for slope = 4%[4 2]
     
     for ii = 1:length(ws)
         B_meso(:,ii) = flux_meso(:,ii).*B0.*(ws(ii)/ws0)^((3-slope)/2);
@@ -263,18 +263,13 @@ for slope = [4 2]
     
     % Labels
     ylabel({'Biomass Flux','[normalized units]'})
-    if counter == 0
-        xlabel('')
-        set(gca,'xticklabel',{})
-    else
         xlabel('Day of Year')
-    end
     
     % Annotations
-     text(0.93,0.9,['\xi = ',num2str(slope)],'fontsize',32,'HorizontalAlignment','center','edgecolor','k','Units','normalized')
+     %text(0.93,0.9,['\xi = ',num2str(slope)],'fontsize',32,'HorizontalAlignment','center','edgecolor','k','Units','normalized')
     if counter == 0
-        text(0.03,0.93,'(a)','fontsize',28,'HorizontalAlignment','center','edgecolor','w','Units','normalized')
-        text(0.5,1.25,'Papa\_summer','HorizontalAlignment','center','FontWeight','b','FontSize',30,'Units','normalized')
+        text(0.03,0.95,'(a)','fontsize',28,'HorizontalAlignment','center','edgecolor','none','Units','normalized','FontWeight','b','BackgroundColor','none')
+        text(0.5,1.22,'Papa\_summer','HorizontalAlignment','center','FontWeight','b','FontSize',40,'Units','normalized')
     end
 
     % second legend
@@ -320,18 +315,13 @@ for slope = [4 2]
     % Labels
     ylabel('')
     set(gca,'yticklabel',{})
-    if counter == 0
-        xlabel('')
-        set(gca,'xticklabel',{})
-    else
         xlabel('Day of Year')
-    end
 
     % Annotations
-    text(0.93,0.9,['\xi = ',num2str(slope)],'fontsize',32,'HorizontalAlignment','center','edgecolor','k','Units','normalized')
+    %text(0.93,0.9,['\xi = ',num2str(slope)],'fontsize',32,'HorizontalAlignment','center','edgecolor','k','Units','normalized')
     if counter == 0
-        text(0.03,0.93,'(b)','fontsize',28,'HorizontalAlignment','center','edgecolor','w','Units','normalized')
[…]

### 2019-03-04 size_differentiated_export.tex
Updates from Overleaf

@@
 	\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export}
-	\caption{Amount of biomass exported in normalized units by each sinking velocity class in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for three different Junge slopes: $\xi =$ 4 (top), $\xi =$ 3 (middle), and $\xi =$ 2 (bottom; see Figure \ref{fig: sinking_velocity_spectrum}).
-Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.
-\fixme{show only 3 ws?}}
+	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
+	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi =4$.
+Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
 	\label{fig: biomass_export_remin}

### 2019-03-08 size_differentiated_export.tex
Updates from Overleaf

@@
 \label{sec: Results}
-\subsection{\fixme{Seasonal change in dynamical regime? or seasonal cycle in submesoscale activity?}}
+\subsection{Seasonal dynamical regimes}
 
@@
 The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
-As expected, the faster-sinking particles are exported earlier and in larger proportions than slower-sinking particles.
+As expected, the faster-sinking particles are exported earlier than slower-sinking particles.
 For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%).
-In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}a).
+In fact, time series of particle export flux closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}a).
 The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).
@@
 
-Time series of particle fluxes in \textit{Papa\_winter} present major differences.
-In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking.
+Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b).
+In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking.
 This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day.
-Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation.
-Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}.
-About 5\% of particles sinking at 0.025 m/day are exported within the first 28 days of the experiment.
+Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward export within the first 15 days of the simulation.
+For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}.
 However, particle export is now stretched over longer periods of time due to particle resuspension.
-In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features, such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a).
+In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a).
 These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet).
 However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring at submesoscales.
+%\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}
 
-%Time series of exported particles in \textit{Papa\_winter} present major differences.
-In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking.
-This earlier arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day.
-Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation.
-Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}.
-About 5\% of particles sinking at 0.025 m/day are exported.
-However, particle export is now stretched over longer periods of time due to particle resuspension.
-This can be seen in the gentler slopes of the export curves observed in \textit{Papa\_winter} than in \textit{Papa\_summer}.
+The biomass export fluxes computed from the particle flux shown in Figure \ref{fig: particle_export} using two different Junge slopes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b).
+The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$).
+However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model (Figure \ref{fig: particle_export}), suggesting that the export for this sinking-velocity class tend to be gravitationally-driven.
 
-Particles released in \textit{Papa\_winter} are thus exported faster and in greater numbers than expected from gravitational sinking.
-Eventually, all sinking particles would be exported in both \textit{Papa\_summer} and \textit{Papa\_winter}, if particles were tracked for a long enough period of time.
-
-\fixme{Here Fig6b should be included an described.
-The key points are (1) the large difference between velocity class that have $w_s\ll w_{adv}$, and the one that have $w_s\sim w_{adv}$, (2) despite the large difference in \% of particles exported the biomass fluxes are of the same order of magnitude when $\xi=4$ as it is often reported in the ocean, and (3) the predictible decrease in biomass export flux when changing the slope based on equation (8).
-}
-
-\begin{equation}
-    \frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
-\end{equation}
-
-\begin{figure}[ht]
+\begin{figure}[t]
 	\centering
 	\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
-	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum})}
+	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}).
+Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
 	\label{fig: biomass_export}
@@
 
-Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale.
-The impacts of remineralization on export are presented and discussed in Sections \ref{sec: results_remin} and \ref{sec: discussion_particle}.
+As anticipated from Figure \ref{fig: sinking_velocity_spectrum}, the Junge slope $\xi$ is a determining parameter that affects the contribution of slower-sinking classes in the presence of submesoscale dynamics.
+Figure \ref{fig: biomass_export} shows the biomass export fluxes in normalized units for two different Junge slopes.
+The contribution from slow-sinking particles to the total biomass export flux expectedly decreases with the Junge slope.
+The decrease in biomass export flux is constant through time and can be predicted using Equation (\ref{eq: biomassjungeslope}):
 
-The presence of submesoscale dynamics therefore hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class.
-This has large implications on the amount of biomass exported, as slower-sinking particles are far more numerous than faster-sinking particles, despite containing less biomass per particle (Figure \ref{fig: sinking_velocity_spectrum}).
+\begin{equation}
+    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_s_0}\right)^{\frac{\xi_2-\xi_1}{2}}
+    %\frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
+\end{equation}
+Using $\xi_1 = 2$ and $\xi_2 = 4$, as depicted in Figure \ref{fig: biomass_export}, the decrease in biomass export is 80\%, 90\%, and 99.5\% for the 1, 0.5 and 0.025 m/day particle classes, respectively.
+%\fixme{The evolution of the biological community through time that would affect the slope of the size spectrum also has direct consequences on the export of the slower-sinking particles.}
+
+The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class.
+This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}).
 While the normalized particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).
@@
 
-%FIG7
- \begin{figure}[ht]
-	\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
-	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi =4$.
-Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
-	\label{fig: biomass_export_remin}
-\end{figure}
+Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale.
+The impacts of remineralization on export are presented and discussed in Sections \ref{sec: results_remin} and \ref{sec: discussion_particle}.
 
@@
 In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included.
-The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is considered.
+The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.
 
- The total amount of biomass is also reduced compared to the case with no remineralization.
-The difference is time dependent, and increases with the age of the particle, as particles further remineralize.
-In a gravitationally-driven system such as during the summer in the northeast Pacific, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases.
-In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export, with slower-sinking particles contributing significantly less than faster-sinking particles (dash lines in Figure \ref{fig: biomass_export_remin}.
-Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by 5-6 orders of magnitude depending on the slope of the biomass spectra (see Figure \ref{fig: sinking_velocity_spectrum}).
-Similar to the case with no remineralization, a change in the Junge slope impacts the biomass contribution of slower-sinking velocity classes.
-This can be seen in the amount of biomass exported by the 1 m/day sinking-velocity class: A negative slope (i.e., $\xi$ = 4) leads to a maximum biomass of about 6 normalized biomass units \fixme{n.b.u.
-?}, while a positive slope (i.e., $\xi$ = 2) leads to a maximum biomass of 1 normalized biomass unit.
-However, both these contributions to biomass export represent much less than 1\% of the biomass export of the 5 m/day sinking-velocity class, making the contribution to export from the 1 m/day sinking-velocity class virtually insignificant, regardless of the Junge slope.
+ %FIG7
+ \begin{figure}[t]
+	\centering
+	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
+	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$.
+Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
+	\label{fig: biomass_export_remin}
+\end{figure}
 
- In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities.
-The difference in exported biomass between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already behind exported.
-As particles age, remineralization has an increasing impact and the difference in total exported biomass increases at a rate controlled by the remineralization rate in (\ref{eq: remin_scheme}).
-Similar to \textit{Papa\_summer}, the total amount of biomass exported by a sinking-velocity class decreases as the Junge slope decreases (i.e., the sinking-velocity spectra flattens).
-%An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the amount of biomass exported from the 0.025 m/day sinking-velocity class exceeds the amount of biomass exported by both the 0.5 and 1 m/day sinking-velocity classes.
+ The biomass export flux is also reduced compared to the case with no remineralization.
+In a gravitationally-driven system such as during the summer in the northeast Pacific, captured in \textit{Papa\_summer}, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases.
+In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export over different timescales (dash lines in Figure \ref{fig: biomass_export_remin}).
+Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by several orders of magnitude.
+
+ In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}.
+The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already behind exported.
+As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}).
+An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the biomass export flux of the 0.025 m/day sinking-velocity class exceeds the biomass export flux from both the 0.5 and 1 m/day sinking-velocity classes.
 This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.
@@
 
-\subsection{Physical model}
+\subsection{Dynamical Regimes}
 \label{sec: Discussion_model}
@@
 The hypothesis tested in this study is that submesoscale activity enhances export of particulate matter at Station Papa by shortening the export timescale of particulate matter.
-The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion below).
+The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion in Section \ref{sec: discussion_particle}).
 However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}.
 Two mechanisms are therefore present to potentially sustain a year-long POC export: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export by advecting the more numerous slower-sinking particles into the ocean interior.
-In the summer, the production of POC is at its yearly maximum, but export tends to be dominated by gravitational sinking, which favors faster-sinking particles.
+In the summer, the production of POC is at its yearly maximum, but export tends to be dominated by gravitational sinking, which favors faster-sinking particles and thus exclude part of the particle spectrum from contributing to the export flux.
 
@@
 
-Analyses of particle tracking experiments reveal that the role played by slower\-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope coefficient $\xi$).
+Analyses of particle tracking experiments reveal that the role played by slower-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope $\xi$).
 
@@
 In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer.
-This change in dynamics has a clear impact on the amount of particles exported for all sinking-velocity classes modeled in this experiment.
-
-Particles within a sinking-velocity class are exported both more rapidly and over longer timescales.
-In fact, a portion of the particles tend to reach the export depth over shorter timescales than in the absence of submesoscale dynamics.
-This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale.
-The former evidently needs to be shorter than the latter to efficiently export POC.
-However, while some particles are exported faster, the rest of the particles within a sinking-velocity class are exported more gradually in time.
-This is due to upward vertical currents, re-suspending material that would otherwise sink, and thus delay its export.
+This change in dynamics has a clear impact on the export flux of all sinking-velocity classes modeled in this experiment.
+Particle export within a sinking-velocity class is hastened and occur over longer timescales.
+In fact, particles tend to reach the export depth over shorter timescales than in the absence of submesoscale dynamics.
+This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale.; The former evidently needing to be shorter than the latter to efficiently export POC.
+However, while some particles are exported faster, the rest of the particles within a sinking-velocity class are exported over longer timescales.
+This is due to upward vertical currents, re-suspending material that would otherwise sink, and thus delay its export (Figure \ref{fig: particle_export}).
 
 In the summer, the gravitationally-driven export mechanism efficiently exports faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles.
-In the winter, however, the export mechanisms is advectively-driven, which leads to a smaller export of faster-sinking particles than in the summer due to resuspension, but efficiently exports slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: sinking_velocity_spectrum}).
-These two competing mechanisms rise the questions as to which process is most efficient in exporting particulate material below the winter mixed layer.
+In the winter, however, the export mechanisms is advectively-driven, which leads to a slightly weaker export flux of faster-sinking particles than in the summer due to resuspension, but a much larger export flux of slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: biomass_export}).
+These two competing mechanisms raise the question as to which process is most efficient in exporting particulate material below the winter mixed layer.
 
 %% This section answers the questions above in terms of total amount of biomass efficiently exported with and without remineralization 
-In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient.
-Over the course of our simulation, the total amount of biomass exported is consistently enhanced when $\xi = 4$ (10 to 60\% increase) in the presence of submesoscale dynamics.
-For a flat biomass spectrum ($\xi = 3$), the export enhancement due to submesoscale dynamics is always smaller than 20\%.\fixme{eventually all is exported...} When $\xi =2$, the amount of biomass exported in the presence of submesoscale dynamics varies between 95 and 110\% of the export observed in the summer, when submesoscale dynamics are not active.
-Therefore, to address the questions formulated above, export is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales.
+In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient (Figure \ref{fig: biomass_export}).
+Over the course of our simulation, the biomass export flux is consistently enhanced when $\xi = 4$ in the presence of submesoscale dynamics.
+Therefore, export flux is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales.
 %Talk about the asymmetry in the vertical velocity PDF (see Figure \ref{fig: dynamics})?
@@
 
-\fixme{modify when results section is edited}
-Introducing remineralization processes significantly decreases the total amount of biomass exported.
+Introducing remineralization processes significantly decreases the biomass export flux.
 Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export.
-The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increases with larger $\xi$.
-Total exported biomass almost doubles when $\xi =4$, and increases by 5 and 20\% for $\xi =2$ and $\xi = 3$, respectively.
+The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increases with larger Junge slopes.
 This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to slow these particles down and thus prolongs their export timescales.
-In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as all classes rely on gravitational sinking for export.
+In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as all modeled classes rely on gravitational sinking for export.
 In the winter, however, slower-sinking particles are exported through advective processes.
-Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics, leading to a greater net export than when remineralization is not considered.
+Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics, leading to a greater net export flux than when remineralization is not considered.
 
@@
 Junge slopes greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}.
-Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}).
+Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}a).
 Because of the negative slope in the biomass spectrum, any particle class sinking at a faster rate will not contribute as much to the biomass export.
@@
 As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation (\ref{eq: condition})).
-A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}).
-Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon} towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.
+A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}a).
+Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon}a towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.
 
@@
 In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated.
-This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}).
+This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b).
 In this regime, slower-sinking particles significantly contribute to POC export.
 In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$.
-Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller in advectively-driven export mechanism, as opposed to gravitationally-driven.
+Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller when export flux is advectively-driven, as opposed to gravitationally-driven.
 

### 2019-03-09 figures/code/Fig7_biomass_export_flux.m
Re-did Figure 9 - diagram
Made modifications to Fig 9 (diagram), plus renamed some routines

@@ -196,7 +196,7 @@ cmap = [0    0.4470    0.7410
 %%
 fullfigure
 counter = 0;
-for slope = 4%[4 2]
+for slope = [4 2]
     
     for ii = 1:length(ws)
         B_meso(:,ii) = flux_meso(:,ii).*B0.*(ws(ii)/ws0)^((3-slope)/2);
@@ -217,7 +217,7 @@ for slope = 4%[4 2]
             B_meso_remin([1:find(B_meso_remin(:,ii)>0,1,'first')-1 find(B_meso_remin(:,ii)>0,1,'last')+1:end],ii) = 1e-10;
         else
             B_meso(1:find(B_meso(:,ii)>0,1,'first')-1,ii) = 1e-10;
-            B_meso_remin(1:find(B_meso_remin(:,ii)>1e-9,1,'first')-1,ii) = 1e-10;  
+            B_meso_remin(1:find(B_meso_remin(:,ii)>1e-9,1,'first')-1,ii) = 1e-10;
         end
         
         B_submeso(1:find(B_submeso(:,ii)>0,1,'first')-1,ii) = 1e-10;
@@ -231,31 +231,32 @@ for slope = 4%[4 2]
     
     
     % PAPA WINTER
-    axes
     if counter == 0
-    set(gca,'position',[0.1   0.55   0.4   0.3])
-    elseif counter == 1
-    set(gca,'position',[0.1   0.2   0.4   0.3])
+        ax1 = axes;
+        set(gca,'position',[0.1   0.55   0.4   0.35])
+        POS = get(gca,'position');
+    else
+        axes(ax1)
     end
-    POS = get(gca,'position');
-
+    
     % Plot Curves
     for ii = 5:-1:2
-        h1(5-ii+1) = plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','--');
+        if counter == 0
+            h1(5-ii+1) = plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','-');
+        else
+            plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','--');
+        end
         hold on
-        h2(5-ii+1) = plot(time_meso+105,B_meso_remin(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:));
[…]

### 2019-03-09 figures/code/Fig8_biomass_export_flux_remin.m

@@ -196,7 +196,7 @@ cmap = [0    0.4470    0.7410
 %%
 fullfigure
 counter = 0;
-for slope = [4 2]
+for slope = 4%[4 2]
     
     for ii = 1:length(ws)
         B_meso(:,ii) = flux_meso(:,ii).*B0.*(ws(ii)/ws0)^((3-slope)/2);
@@ -217,7 +217,7 @@ for slope = [4 2]
             B_meso_remin([1:find(B_meso_remin(:,ii)>0,1,'first')-1 find(B_meso_remin(:,ii)>0,1,'last')+1:end],ii) = 1e-10;
         else
             B_meso(1:find(B_meso(:,ii)>0,1,'first')-1,ii) = 1e-10;
-            B_meso_remin(1:find(B_meso_remin(:,ii)>1e-9,1,'first')-1,ii) = 1e-10;
+            B_meso_remin(1:find(B_meso_remin(:,ii)>1e-9,1,'first')-1,ii) = 1e-10;  
         end
         
         B_submeso(1:find(B_submeso(:,ii)>0,1,'first')-1,ii) = 1e-10;
@@ -231,32 +231,31 @@ for slope = [4 2]
     
     
     % PAPA WINTER
+    axes
     if counter == 0
-        ax1 = axes;
-        set(gca,'position',[0.1   0.55   0.4   0.35])
-        POS = get(gca,'position');
-    else
-        axes(ax1)
+    set(gca,'position',[0.1   0.55   0.4   0.3])
+    elseif counter == 1
+    set(gca,'position',[0.1   0.2   0.4   0.3])
     end
-    
+    POS = get(gca,'position');
+
     % Plot Curves
     for ii = 5:-1:2
-        if counter == 0
-            h1(5-ii+1) = plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','-');
-        else
-            plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','--');
-        end
+        h1(5-ii+1) = plot(time_meso+105,B_meso(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:),'linestyle','--');
         hold on
+        h2(5-ii+1) = plot(time_meso+105,B_meso_remin(:,ii)./unique(diff(time_meso)),'LineWidth',2,'Color',cmap(ii,:));
[…]

### 2019-03-09 size_differentiated_export.tex

@@
 Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2018}.
-We first consider the case of conservatives particles that do not remineralize in order to isolate the effects of ocean dynamics on export.
+We first consider the case of conservative particles that do not remineralize in order to isolate the effects of ocean dynamics on export.
 
@@
 For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%).
-In fact, time series of particle export flux closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}a).
+In fact, time series of particle export flux closely follow the curves derived from considering gravitational sinking only (Figure \ref{fig: particle_export}a).
 The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).
@@
 This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day.
-Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward export within the first 15 days of the simulation.
+Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward flux within the first 15 days of the simulation.
 For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}.
@@
 These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet).
-However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring at submesoscales.
+However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring in the presence of submesoscale dynamics.
 %\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}
 
-The biomass export fluxes computed from the particle flux shown in Figure \ref{fig: particle_export} using two different Junge slopes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b).
+The corresponding biomass export fluxes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b).
 The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$).
-However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model (Figure \ref{fig: particle_export}), suggesting that the export for this sinking-velocity class tend to be gravitationally-driven.
+However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model, suggesting that the export for this sinking-velocity class remains mostly gravitationally-driven.
 
@@
 This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}).
-While the normalized particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).
+%While the particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).
 
 The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}).
-This is a logical result given the observed increase in the particle export flux when submesoscales features are present (Figure \ref{fig: particle_export}).
+This is a logical result given the observed increase in the particle export flux when submesoscale features are present (Figure \ref{fig: particle_export}).
 The sinking class dominating export, however, is highly dependent on the Junge slope.
 As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases.
-For example, after 28 days, the 1 m/day particle class exports 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.
-
-Particles, and specifically slow-sinking ones, are however expected to remineralize on timescales shorter than their export timescale.
-The impacts of remineralization on export are presented and discussed in Sections \ref{sec: results_remin} and \ref{sec: discussion_particle}.
+For example, after 28 days, the 1 m/day particle class cumulatively exported 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.
+However, slow-sinking particles are generally expected to remineralize on timescales shorter than their export timescale.
+The impacts of remineralization on export are considered in hthe following section.
 
@@
 
- Including remineralization of particles (see Equation (\ref{eq: remin_scheme})) significantly impacts the relative importance of sinking and advection to export for each particle class.
-In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles slow down as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}).
+ Including remineralization of particles significantly impacts the relative importance of sinking and advection to export for each particle class.
+In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles decelerate as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}).
 In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included.
@@
 
- In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}.
-The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already behind exported.
+ In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}).
+The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already being exported.
 As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}).
@@
 The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa, and reflected in the model experiments, echoes findings of recent observational studies conducted at a similar latitude in the Atlantic Ocean demonstrating the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}.
-Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, wintertime ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.
+Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.
 
@@
 However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}.
-Two mechanisms are therefore present to potentially sustain a year-long POC export: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export by advecting the more numerous slower-sinking particles into the ocean interior.
+Two mechanisms are therefore present to potentially sustain a year-long POC export flux: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export flux by advecting the more numerous slower-sinking particles into the ocean interior.
 In the summer, the production of POC is at its yearly maximum, but export tends to be dominated by gravitational sinking, which favors faster-sinking particles and thus exclude part of the particle spectrum from contributing to the export flux.
@@
 Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export.
-The increase in exported biomass when comparing summertime and wintertime is larger when remineralization processes are included, and also increases with larger Junge slopes.
-This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to slow these particles down and thus prolongs their export timescales.
-In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as all modeled classes rely on gravitational sinking for export.
+The difference between summertime and wintertime biomass fluxes is even larger when remineralization processes are included.
+This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to decelrate these particles and thus prolongs their export timescales.
+In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as export is gravitationally-driven.
 In the winter, however, slower-sinking particles are exported through advective processes.
-Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics, leading to a greater net export flux than when remineralization is not considered.
+Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics.
 
@@
 The contribution of a particle class to POC export generally increases with the sinking-velocity.
-That is, faster-sinking particles tend to dominate the export signal and the curve of exported biomass versus sinking-velocity has a positive slope.
-To have a greater contribution of a slower-sinking velocity class, the following condition must be satisfied:
+That is, faster-sinking particles tend to dominate the export signal.
+However, this tendency can be reversed if the following condition is satisfied:
 
@@
 where $N$ is the number of simulated particles exported, $w_s$ is the sinking velocity and $\xi$ is the Junge slope coefficient (see Equation (\ref{eq: powerlaw_radius})).
+The number of exported slower-sinking particles must therefore be large enough to compensate for the smaller biomass content than faster-sinking particles.
 
@@
 Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}a).
-Because of the negative slope in the biomass spectrum, any particle class sinking at a faster rate will not contribute as much to the biomass export.
+Because of the negative slope in the biomass spectrum, the contribution to export of any particle class sinking at a faster rate will be smaller.
 The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth.
@@
 A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}a).
-Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon}a towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.
+%Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon}a towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.
 
@@
 In this regime, slower-sinking particles significantly contribute to POC export.
-In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$.
-Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller when export flux is advectively-driven, as opposed to gravitationally-driven.
+\fixme{In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$ Also talk about te fct that it is what we see in Fig 8 with the reveral fo the order.} %Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller when export flux is advectively-driven, as opposed to gravitationally-driven.
 

### 2019-03-09 size_differentiated_export.tex
Updates from Overleaf

@@
 
-%FIG8
+%FIG9
  \begin{figure}[ht!]
 	\centering
-	\includegraphics[width = .65\linewidth]{figures/cartoon_meso}\\[.2cm]
-	\includegraphics[width = .65\linewidth]{figures/cartoon_submeso}
-	\caption{Schematics showing the respective contribution to export of particles with different sinking velocities in (top) a gravitationally-driven system (i.e., weak submesoscale dynamics), and (bottom) an advectively-driven system (i.e., strong submesoscale dynamics).}
+	\includegraphics[width = .65\linewidth]{figures/Fig9_cartoon_meso}\\[.2cm]
+	\includegraphics[width = .65\linewidth]{figures/Fig9_cartoon_submeso}
+	\caption{Schematics illustrating the respective contribution to export of particles with different sinking velocities for $\xi > 3$ in (a) a gravitationally-driven system (i.e., weak submesoscale dynamics), and (b) an advectively-driven system (i.e., strong submesoscale dynamics).}
 	\label{fig: export_cartoon}
@@
 This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b).
-In this regime, slower-sinking particles significantly contribute to POC export.
-\fixme{In this study, sinking-velocity classes that did not contribute to POC export in a mesoscale regime, are found to contribute up to 30\% of POC export in the most extreme case, where $\xi =4$ Also talk about te fct that it is what we see in Fig 8 with the reveral fo the order.} %Implementing remineralization process has little to no impact on the respective contributions of the different sinking-velocity classes as the impact of remineralization is smaller when export flux is advectively-driven, as opposed to gravitationally-driven.
+In this regime, slower-sinking particles significantly contribute to POC export, and can even dominate the export signal for large $\xi$.
+This scenario is captured in one of the Lagrangian experiment and shown in Figure \ref{fig: biomass_export}b, where the contribution to biomass export from the 0.025 m/day sinking class exceeds the one from the 0.5 m/day sinking class.
+This surprising result further emphasizes the key role played by slow-sinking particles in POC export, especially in the presence of submesoscale dynamics and large $\xi$.
 
@@
 \begin{enumerate}
-\item Submesoscale activity at station Papa is enhanced in the wintertime, leading to larger vertical velocities than in the summertime.
-The export mechanism in the winter is thus driven by advective sinking, as opposed to gravitational sinking in the summertime.
+\item Ocean dynamics in the subpolar Pacific northeast exhibit a seasonal cycle with low submesoscale activity in the summertime, and more submesoscale features in the wintertime.
+Submesoscale dynamics generate larger, and asymmetrical, vertical currents leading to an export mechanisms dominated by advective processes, as opposed to gravitationally-driven in the summertime.
+
 \item Submesoscale dynamics generally enhance export by increasing the contribution of slower-sinking particles to POC export by increasing the number of particle exported through advective sinking.
-The contribution of slower-sinking particles in ageostrophic flows is at least significant, and can be dominant in specific conditions.
+The contribution of slower-sinking particles subducted through irreversible ageostrophic processes to particle export is at least significant, and can be dominant in specific conditions.
 \item Contribution of slower-sinking particles to POC export depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class.
@@
 	\item If the Junge slope equals 3, the respective contributions of the different size classes depend on the dynamical characteristics of the flow, as it influences the number of particles being exported.
-If 100\% of the particles is exported in all sinking classes, then each class contributes equally to POC export.
-	\item If the Junge slope is greater than 3, ocean dynamics become the determining factor on which classes dominate: in a mostly geostrophic flow with weak vertical velocities, an intermediate sinking-velocity class will dominate POC export.
+If 100\% of particles is exported in all sinking classes, then each class contributes equally to POC export.
+	\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become the determining factor on which classes dominate: in a mostly geostrophic flow with weak vertical velocities, an intermediate sinking-velocity class will dominate POC export.
 In a flow with ageostrophic circulation leading to larger vertical velocities, slower sinking classes can potentially dominate export.
@@
 As flow dynamics become ageostrophic, advective sinking leads the export and remineralization processes have a limited impact.
-%\item[(5)] Under specific conditions (large Junge slope and strongly ageostrophic flow), remineralization processes counter-intuitively enhance the role of slower-sinking (and non-sinking) particles to the point where export is dominated by these slow-sinking particles, therefore challenging the traditional paradigm of carbon export.
 \end{enumerate}

### 2019-06-11 size_differentiated_export.tex

@@
 However, this need not be the case in a dynamic oceanic flow field, where the ocean velocity can influence the descent rate of particles.
-Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) the particle number size-spectrum slope, and (2) the ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export.
+Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) the ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
 The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important.
-The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles in POC export.
+The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export.
 A steeper particle size spectrum, also increases the contribution of smaller, slower-sinking particles.
@@
 Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export.
-This study demonstrates that slow-sinking particles are significant contribution, and at times, can even dominate the export flux.
+This study demonstrates that slow-sinking particles can be a significant contribution, and at times, even dominate the export flux.
 \end{abstract}
@@
 Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities.
-Considering the fact that, although containing less biomass, smaller particles are far more numerous than larger particles, the impact of submesoscale dynamics on the export of POC is potentially significant.
+Considering the fact that, although containing less biomass per particle, smaller particles are far more numerous than larger particles, the impact of submesoscale dynamics on the export of POC is potentially significant.
 Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe in-situ.
@@
 Time-varying wind stress and heat flux are prescribed at the surface boundary.
-Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory\footnote{https://www.pmel.noaa.gov/ocs/Papa}.
-Climatologies of daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long time series.
+Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory.
+Daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long climatology.
 A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability.
-In all numerical experiments, the simulations are first allowed to spin-down for the first 5 days with no forcing apply at the surface boundary.
+In all numerical experiments, the simulations are first allowed to spin-down for the first 5 days with no forcing applied at the surface boundary.
 Surface wind stress and heat fluxes are then linearly ramped up between days 5 and 10 of the simulation, to reach realistic values at day 10.
 % (Figures \ref{fig: Papa_summer} and \ref{fig: Papa_winter}).
-While the meriodional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling that could contaminate the middle third of the model domain, where the analysis is focused (Figure \ref{fig: model_domain}a).
-A restoration time scale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress, as well as to limit internal wave reflection at the solid boundaries back into the domain (Figure \ref{fig: model_domain}b).
-Net surface heat fluxes are homogeneously prescribed throughout the domain, over which a linear meridional heat flux anomaly is superimposed to maintain a north-south gradient (Figure \ref{fig: model_domain}c).
-The flux anomaly is zero in the center of the domain, associated with the latitude of Station Papa, and has a meridional slope of 1/24 W/m$^2$/km, which was determined from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}.
+While the meriodional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling %that could contaminate the middle third of the model domain, where the analysis is focused
+(Figure \ref{fig: model_domain}a).
+A restoration timescale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress, as well as to limit internal wave reflection at the solid boundaries back into the domain (Figure \ref{fig: model_domain}b).
+While net surface heat fluxes are homogeneous in the zonal direction, a meridional gradient is maintained throughout the simulation.
+The meridional gradient was determined from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}, and set to 1/24 W/m$^2$/km (Figure \ref{fig: model_domain}c).
 
-Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from ARGO floats \citep{Gaillard_2009,Gaillard_2016}.
-ARGO data is averaged monthly over the period 2002-2012 and two different months are used to initialize the two main numerical experiments for this study: Climatological conditions in April are used to initialize the \textit{Papa\_summer} experiment, while January climatological conditions are used to initialize the \textit{Papa\_winter} experiment (Table \ref{tab: meso_vs_submeso}).
+Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from Argo floats \citep{Gaillard_2009,Gaillard_2016}.
+Argo data is averaged monthly over the period 2002-2012 and two different months are used to initialize the two main numerical experiments for this study: Climatological conditions in April are used to initialize the \textit{Papa\_summer} experiment, while January climatological conditions are used to initialize the \textit{Papa\_winter} experiment (Table \ref{tab: meso_vs_submeso}).
 The north-south background density gradient is then intensified into three fronts located at $y = 75$, $y = 150$, and $y = 225$ km (Figure \ref{fig: model_domain}).
@@
 
-Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics mimicking conditions int the northeast Pacific in the summertime.
+Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics representing conditions in the northeast Pacific in the summertime.
 Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1).
 \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region.
-A different dynamical regime is expected to dominate during wintertime, with submesoscale dynamics playing a more important role.
-Submesoscale dynamics are characterized by sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km).
-Such dynamics are more likely to be found in the winter time, where mixed layers are deeper and lateral density gradients enhanced \citep{Thompson_2016}.
+A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \citep{Mensa_2013,Callies_2015,Thompson_2016}.
 The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.
@@
 
-In \textit{Papa\_summer}, PSOM is initialized based on climatological ARGO data in April.
-The magnitude of the density gradient across the front (i.e., frontal sharpness) is set to 3.34$\times$10$^{-6}$ kg/m$^3$/m, which corresponds to the 95$^{th}$ percentile of the PDF of density gradients measured in April from glider data collected in the region (Figure \ref{fig: Papa_summer} and Table \ref{tab: meso_vs_submeso}).
+In \textit{Papa\_summer}, PSOM is initialized based on climatological Argo data in April.
+The magnitude of the density gradient across the front is set to 3.34$\times$10$^{-6}$ kg/m$^3$/m, which corresponds to the 95$^{th}$ percentile of the PDF of density gradients measured in April from glider data collected in the region (Figure \ref{fig: Papa_summer} and Table \ref{tab: meso_vs_submeso}).
 The model is run with a timestep of 216 s and is allowed to spin-up for 60 days, allowing summer stratification to develop.
@@
 The month of April is chosen for initialization so the experiment would capture the onset of positive net heat fluxes, and the summer restratification that ensues in July-August (Figure \ref{fig: Papa_summer}).
-In this region, the summer stratification is associated with large primary productivity, particle production, and POC export \citep[e.g., fecal pallets, dead phytoplankter; ][]{Plant_2016}.
+In this region, the summer stratification is associated with large primary productivity, particle production, and POC export \citep[e.g., fecal pellets, dead phytoplankter; ][]{Plant_2016}.
 
@@
 		Restoration timescale			            & 3 days                    & 15 days                   \\
-		Maximum initial M$^2$ ($\times$10$^{-8}$)	& 3.2 s$^{-2}$             & 33.9 s$^{-2}$             \\	
-		Maximum initial N$^2$ ($\times$10$^{-4}$)	& 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\
-		Initial mixed layer depth                   & 73 m                      & 85 m                      \\
-		Zonal wind stress                	        & 0 -- 0.16 N m$^{-2}$      & -0.05 -- 0.17 N m$^{-2}$  \\	
-		Surface heat flux               	        & -46.8 -- 167.5 W m$^{-2}$ & -57.6 -- 15.3 W m$^{-2}$  \\	
+		Zonal wind stress                	        & 0 -- +0.16 N m$^{-2}$      & -0.05 -- +0.17 N m$^{-2}$  \\	
+		Surface heat flux               	        & -46.8 -- +167.5 W m$^{-2}$ & -57.6 -- +15.3 W m$^{-2}$  \\
+		Maximum M$^2$ ($\times$10$^{-8}$)	        &                           &                           \\[-.25cm]
+		\multicolumn{1}{|r|}{initial}	            & 3.2 s$^{-2}$              & 33.9 s$^{-2}$             \\[-.25cm]
+		\multicolumn{1}{|r|}{spun-up}	            & 12.0 s$^{-2}$             & 50.0 s$^{-2}$             \\	
+		Maximum N$^2$ ($\times$10$^{-4}$)	        &                           &                           \\[-.25cm]
+		\multicolumn{1}{|r|}{initial}	            & 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\[-.25cm]
+		\multicolumn{1}{|r|}{spun-up}	            & 3.1 s$^{-2}$              & 1.1 s$^{-2}$              \\	
+		Averaged mixed layer depth                  &                           &                           \\[-.25cm]
+		\multicolumn{1}{|r|}{initial}	            & 73 m                      & 85 m                      \\[-.25cm]
+		\multicolumn{1}{|r|}{spun-up}	            & 11 m                      & 93 m                      \\	
 		\hline
@@
 Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$).
-(e) Vertical profile of the buoyancy frequency $N^2$ at doy 105, 135, 165, and 195, showing the development of summer stratification centered at z = 30 m (solid lines).
+(e) Vertical profile of the buoyancy frequency $N^2$ at day of year 105, 135, 165, and 195, showing the development of summer stratification centered at z = 30 m (solid lines).
 Monthly-average vertical stratification obtained from glider profiles collected in June and July are superimposed (dashed lines), along with the correlation coefficient between observations and model outputs.}
@@
 
-In \textit{Papa\_winter}, PSOM is initialized based on climatological ARGO data in January.
-The frontal sharpness is set to 3.54$\times$10$^{-5}$ kg/m$^3$/m, which corresponds to the 99$^{th}$ percentile of the PDF of density gradients measured in January from glider data collected in the region (Figure \ref{fig: Papa_winter} and Table \ref{tab: meso_vs_submeso}).
+In \textit{Papa\_winter}, PSOM is initialized based on climatological Argo data in January.
+The frontal gradient is set to 3.54$\times$10$^{-5}$ kg/m$^3$/m, which corresponds to the 99$^{th}$ percentile of the PDF of density gradients measured in January from glider data collected in the region (Figure \ref{fig: Papa_winter} and Table \ref{tab: meso_vs_submeso}).
 The model is allowed to spin-up for 50 days allowing for the prescribed fronts to become unstable.
-To accommodate the larger density gradients, the advective timestep is shortened to 108 s, and the horizontal diffusivity is lowered to 0.2 m$^2$/s.
+To accommodate for the larger density gradients and stronger velocities, the advective timestep is shortened to 108 s and the horizontal diffusivity is lowered to 0.2 m$^2$/s throughout the experiment.
 The model is run for 30 additional days, saving instantaneous model fields every 1.5 hours for particle tracking.
-The month of January is chosen for initialization so the experiment would capture the time of year where the mixed layer is the deepest, and Rossby number of O(1) are more likely to occur.
+The month of January is chosen for initialization so the experiment would capture the time of year where the mixed layer is the deepest, and Rossby number O(1) occur more frequently.
 The objective is for this experiment to contrast \textit{Papa\_summer} by capturing the statistics of ocean conditions dominated by submesoscale dynamics.
@@
 To circumvent this issue, horizontal buoyancy gradients are computed between each pair of glider profiles available within one branch of the bow-tie.
-Each along-track buoyancy gradient is thus associated with a specific separation scale and a timestamp.
+Each along-track lateral buoyancy gradient is thus associated with a specific separation scale and a timestamp.
 Glider-based density gradients can be affected by internal waves.
 To filter the impact of internal waves on the PDF of horizontal buoyancy gradients, only gradients computed at a scale of twice the Rossby radius $\pm$ 1 km are considered.
-Rossby radii are $\sim 8$ km in winter and $\sim 20$ km in summer.
+Rossby radii are estimated from the glider data and are $\sim8$ km in winter and $\sim20$ km in summer.
 
@@
 Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles.
-Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-suspended into the mixed layer.
+Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.
 %The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.
@@
 where $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily.
-For small particles ($<$400$\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ tend to follow Stokes law, with $w_s \propto r^2$ \citep{Bach_2012}.
-\cite{Bach_2012} also demonstrate that Stokes law is generally a lower-bound estimate of sinking velocities for a specific particle size.
-Assuming a Stokes-like relationship, (\ref{eq: powerlaw_radius}) can be re-written in terms of sinking velocities as:
+For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically.
+Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \citep{Bach_2012}.
+%\cite{Bach_2012} also demonstrate that Stokes law is generally a lower-bound estimate of sinking velocities for a specific particle size.
+Assuming a Stokes-like relationship, we can construct a particle sinking velocity spectrum $N(w_s)$ based on (\ref{eq: powerlaw_radius}), where $w_{s_0}$ is the sinking speed of particles with a radius $r_0$:
 
@@
 For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represent 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}).
-The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$, can be estimated if the biomass is assumed to vary with the particle's volume.
+The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$, can be estimated if the biomass is assumed to scale with the particle's volume.
 The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed using:
@@
 	\includegraphics[width = .6\linewidth]{figures/Fig4_particle_PDF}
-	\caption{Normalized number of particles (solid) and biomass (dashed) to the fastest-sinking particle class.
+	\caption{Number of particles (solid) and biomass (dashed) normalized to the fastest-sinking particle class as a function of sinking velocity $w_s$.
 Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 3 (black), and 2 (blue).}
@@
 \end{equation}
-where $B_p(w_{s_0})$ is a reference biomass of one particle in the sinking velocity class $w_{s_0}$.
+where $B_p(w_{s_0})$ is the biomass of a particle in the sinking velocity class $w_{s_0}$.
 The total biomass associated with one simulated particle can be obtained by scaling (\ref{eq: biomass_realparticle}) by the ratio $N(w_s)/N_0$:
@@
 Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}).
-This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) presents the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments.
+This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) has the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments, where the number of seeded particles would vary to account for the different spectral slopes.
 For the purpose of this study, only the relative amount of biomass is relevant.
@@
 \label{sec: remin_scheme}
-Remineralization of particles as they sink through the water column evidently impacts the export of biomass.
-Slow-sinking particles therefore are subject to shallower remineralization than fast-sinking particles.
-In this study, the impact of remineralization is considered through the implementation of a time-dependent sinking velocity.
-Remineralization processes driving remineralization rates are complex, species-dependent, and generally not well-understood.
-In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship linking carbon content and time.
-This implicitly assumes that the biomass content of a particle decreases in time proportionally to the particle volume.
+Remineralization of particles as they sink through the water column impacts the amount of biomass exported.
+Slow-sinking particles generally contains less biomass and spends more time in the mixed layer, which means that they are remineralized at a shallower depth than faster sinking particles.
+Remineralization processes are complex, species-dependent, and generally not well-understood.
+In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship which assumes that the biomass content of a particle decreases in time proportionally to the particle volume.
 Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}:
@@
 \end{equation}
-where $B^0$ denotes the biomass content at $t = 0$ days, and $k = 0.13$ day$^{-1}$.
-This remineralization rate determined by \cite{Iversen_2010} is independent of particle sinking velocity, and seems to generally agree with other findings, despite the large uncertainties \citep{Ploug_2008, Iversen_2013}.
+where $B^0$ denotes the biomass content at $t = 0$ days, and the remineralization rate is taken to be $k = 0.13$ day$^{-1}$ in this study \citep{Iversen_2010}.
+This remineralization rate is independent of particle sinking velocity, and seems to lie within the range of other estimates \citep{Ploug_2008, Iversen_2010, Iversen_2013}.
 The change in biomass with time is in turn expected to affect the sinking velocity of the particle.
@@
 where $w_s^0$ is the initial sinking velocity at $t = 0$ days.
-Particles are classified based on their initial sinking-velocity.
-However, it is worth noting that over the length of the particle-tracking experiments that include remineralization (28 days), particle sinking speeds slow down to 10\% of their initial velocity.
+In this study, the impact of remineralization is thus considered through the implementation of a time-dependent sinking velocity (Equation \ref{eq: sinking_velocity_remin}).
+While particles classes are classified based on their initial sinking-velocity, it is worth noting that over the length of the particle-tracking experiments that include remineralization (28 days), particle sinking speeds slow down to 10\% of their initial velocity, which correspond to 3.1\5.
 
@@
 \label{sec: Results}
-\subsection{Seasonal dynamical regimes}
+\subsection{Seasonally varying dynamical regimes}
 
@@
 Note the different colorbars used for \textit{Papa\_summer} and \textit{Papa\_winter}.
-Histograms of M$^2$ computed from glider data at Station Papa in February (blue line) and July (red line) are superimposed in the top middle panel.}
+Histograms of $M^2$ computed from glider data at Station Papa in February (blue line) and July (red line) are superimposed in the top middle panel.}
 	\label{fig: dynamics}
@@
 Coherent vertical velocities structures extend to depths much greater than the mixed layer depth ($\sim$25 m; Figure \ref{fig: dynamics}).
-The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \citep{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ 1/s (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ 1/s, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s.
+The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \citep{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ s$^{-1}$ (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ s$^{-1}$, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s, or $\sim 10^{-1}$ m/day.
 %The agreement between the scaling and the model outputs suggest that PSOM is capable of reproducing a realistic vertical flow field.
@@
 At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m \citep[Figure \ref{fig: Papa_winter}][]{Pelland_2016}.
-After spin-up, the vertical stratification remains consistent throughout the model run, and compares well to the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}).
-In the horizontal, prescribed density fronts are much sharper than in \textit{Papa\_summer} (O(1 km ) vs.
+After spin-up, the vertical stratification remains consistent throughout the model run, and compares well with the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}).
+In the horizontal, prescribed density fronts are much sharper than in summer (i.e., over smaller spatial scales O(1 km ) vs.
 O(10 km)).
-Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in \textit{Papa\_summer} (Figure \ref{fig: Papa_winter}).
+Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in summer (Figure \ref{fig: Papa_winter}).
 As a result, KE$_{\text{tot}}$ starts to plateau at doy 48.
@@
 
-The frontal structures visible in the horizontal buoyancy gradient field are associated with filaments of relatively high Rossby numbers exceeding $\mathcal{O}$(1) (Figure \ref{fig: Papa_winter}).
+The frontal structures visible in the horizontal buoyancy gradient field are associated with filaments of relatively high Rossby number of $\mathcal{O}$(1) (Figure \ref{fig: dynamics}).
 The PDF of relative vorticity reveals a positively-skewed distribution ($s = 0.68$).
@@
 This ageostrophic secondary circulation therefore generates ``hot spots" of higher vertical velocities.
-The fine-scale structures in the vertical velocity field corresponding to $\mathcal{O}$(1) Rossby numbers  can be seen in Figure \ref{fig: Papa_winter}, with local vertical velocities up to 60 m/day ($\sim 7\times10^{-4}$ m/s; Figure \ref{fig: dynamics}).
+The fine-scale structures in the vertical velocity field corresponding to $\mathcal{O}$(1) Rossby numbers  can be seen in Figure \ref{fig: dynamics}, with local vertical velocities up to 60 m/day ($\sim 7\times10^{-4}$ m/s).
 Contrary to the PDF of relative vorticity, the distribution of vertical velocities demonstrate a negative skewness ($s =$ -0.25).
-This is in agreement with the theory: In fact, positive vertical vorticity is associated with the dense side of a density front, where relative vorticity are positive and vertical velocities negative \citep{Mahadevan_2016}.
-Once again, the amplitude of these vertical velocity hot spots is coherent with the scaling $w \propto RofU/N$: using $Ro\sim1$, $N\sim10^{-2}$ 1/s, $f\sim10^{-5}$ 1/s, and $U\sim0.1$ m/s, we obtain $w\sim 10^{-4}$ m/s.
+This is in agreement with the theory: In fact, positive relative vorticity is associated with the dense side of a density front, where vertical velocities are negative \citep{Mahadevan_2016}.
+Once again, the amplitude of these vertical velocity hot spots is coherent with the scaling $w \propto RofU/N$: using $Ro\sim1$, $N\sim10^{-2}$ 1/s, $f\sim10^{-5}$ 1/s, and $U\sim0.1$ m/s, we obtain $w\sim 10^{-4}$ m/s, or $\sim 10^{1}$ m/day.
 %This demonstrates the capabilities of PSOM to resolve sharp frontal features at the kilometer scale, as well as the ageostrophic circulation associated with those fronts.
@@
 In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa.
-Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2018}.
+Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2016,Palevsky_2018}.
 We first consider the case of conservative particles that do not remineralize in order to isolate the effects of ocean dynamics on export.
@@
 \begin{equation}
-    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_s_0}\right)^{\frac{\xi_2-\xi_1}{2}}
+    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_{s_0}}\right)^{\frac{\xi_2-\xi_1}{2}}
     %\frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
@@
 
-The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class.
+The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, between a few percent and tens of percents, depending on the sinking-velocity class.
 This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}).
@@
 
-The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}).
+The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role of slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}).
 This is a logical result given the observed increase in the particle export flux when submesoscale features are present (Figure \ref{fig: particle_export}).
@@
 However, slow-sinking particles are generally expected to remineralize on timescales shorter than their export timescale.
-The impacts of remineralization on export are considered in hthe following section.
+The impacts of remineralization on export are considered in the following section.
 
@@
 In fact, particles tend to reach the export depth over shorter timescales than in the absence of submesoscale dynamics.
-This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale.; The former evidently needing to be shorter than the latter to efficiently export POC.
+This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale; The former evidently needing to be shorter than the latter to efficiently export POC.
 However, while some particles are exported faster, the rest of the particles within a sinking-velocity class are exported over longer timescales.
@@
 The difference between summertime and wintertime biomass fluxes is even larger when remineralization processes are included.
-This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to decelrate these particles and thus prolongs their export timescales.
+This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to decelerate these particles and thus prolongs their export timescales.
 In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as export is gravitationally-driven.
@@
 \item Remineralization processes reduce the contribution of slower-sinking particles when export dynamics are dominated by gravitational sinking (i.e., in a geostrophic flow).
-As flow dynamics become ageostrophic, advective sinking leads the export and remineralization processes have a limited impact.
+As flow dynamics become ageostrophic, advective downward transport leads the export and remineralization processes have a limited impact.
 \end{enumerate}
@@
 Pelland (NOAA) and Charlie Eriksen (University of Washington) for sharing the glider data collected at Ocean Station Papa, as well as Sebastian Essink for his assistance in developing the particle-tracking code.
-All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website (\url{https://www.pmel.noaa.gov/ocs/Papa}) and gridded ARGO products can be downloaded at \url{http://www.seanoe.org/data/00348/45945}.
-Glider data, model outputs, and particle trajectories are freely available on request.
+All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website (\url{https://www.pmel.noaa.gov/ocs/Papa}) and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945}.
+Glider data is archived at NCEI: https://data.nodc.noaa.gov/cgi-bin/iso?id=gov.noaa.nodc:0155879.
+Model outputs, and particle trajectories are freely available on request.
 % Finally, we are grateful to the two anonymous reviewers for their valuable comments and suggestions.

### 2019-06-11 size_differentiated_export.tex

@@
 	\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
-	\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
+	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
+	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
 Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain.
@@
 Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
+	\includegraphics[width = 1\linewidth]{figures/Fig6.png}
+	\caption{[left] Gridded depth anomaly in the median particle depth 25 days after particle release, in the Winter experiment.
+Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model.
+[right]  Depth profile of the PDF of the number of particle for each velocity class.
+The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions.
+Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies.
+Release depth is indicated by the thick dashed line.}
 	\label{fig: particle_export}
@@
 	\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
-	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}).
+	%\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
+	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}).
 Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
+	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
+	\caption{PDF of biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
+Inserts show the total downward biomass flux associated with each sinking-velocity class.
+Both winter dynamics and steeper June slope tend to increase the relative contribution of slower-sinking particles.}
 	\label{fig: biomass_export}
@@
 	\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
-	\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$.
+	%\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
+	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$.
 Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
+	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
+	\caption{Snapshot of the biomass PDF versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
+Inserts show the total downward biomass flux associated with each sinking-velocity class.
+Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}
 	\label{fig: biomass_export_remin}

### 2019-06-21 size_differentiated_export.tex
Updates from Overleaf

@@
 
-Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle export, using Lagrangian particle-tracking.
-In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa.
+Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle downward flux, using Lagrangian particle-tracking.
+Downward particle flux is expected to be a combination of their sinking velocity and the vertical advective currents affecting the particle along its pathway.
+The deviation in particle depths from the traditional one-dimensional gravitationally driven model is shown in Figure \ref{fig: particle_depth_distribution}d for both summer and winter cases.
+In the summer, the PDF of particle density versus depth remains relatively narrow through time, and is centered on a depth level that can be predicted using a simple 1D gravitational model (see shaded curves in Figure \ref{fig: particle_depth_distribution}).
+PDFs of particle density also vary little among particles classes with different sinking velocities, suggesting that downward fluxes of particles is greatly dominated by gravitational settling and is not subject to significant vertical ocean currents.
+
+%FIG6
+\begin{figure}[ht!]
+	\centering
+	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
+	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
+Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain.
+For each sinking-velocity class, the net particle flux is shown by a thick line.
+Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
+	\includegraphics[width = 1\linewidth]{figures/Fig6.png}
+	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release, in the Winter experiment.
+Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model where $z = w_s\timest$.
+[right] Probability Distribution Function (PDF) of particles as a function of depth for each velocity class.
+The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions.
+Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies.
+Release depth is indicated by the thick dashed line.\fixme{Add a)-d) symbols} \fixme{smaller fontsize}}
+	\label{fig: particle_depth_distribution}
+\end{figure}
+
+In the winter, however, the PDF of particle density versus depth is wider, in agreement with the stronger vertical ocean currents occurring in the winter (see Figure \ref{fig: dynamics}).
+The deviation in the downward particle flux from the traditionally considered 1D gravitational model can be seen in Figure \ref{fig: particle_depth_distribution} (panels (a)-(c)).
+Slower-sinking particles deviate more than faster-sinking particles, exhibiting median depth anomalies up to 50 m.
+This is due to the fact that slower-sinking particles spend more time in the mixed layer, where most of the stronger vertical currents tend to occur (Figure \ref{fig: dynamics}).
+An interesting result emerges from the spatial distribution of the depth-anomaly: both positive (where particles are shallower than expected) and negative (particles are deeper than expected) anomalies are organized into features with a length-scale $\mathcal{O}$(1-10 km).
+This further highlights the importance of winter submesoscale circulation for vertical fluxes of particles and their associated .%, which is explicitly shown in Figure \ref{fig: biomass_export}.
+
+A relative amount of biomass is associated to the particles using equation \ref{eq: biomassjungeslope}.
+The PDF of relative biomass as a function of the vertical velocity is shown in Figure \ref{fig: biomass_export}.
+Following the traditional paradigm derived from the simple 1D gravitational model, the downward flux of biomass in the summer is dominated by faster-sinking particle classes capable of carrying particulate material downwards more efficiently.
+The contribution of slower-sinking particles, however, critically depends on the slope of the size spectrum (see Figure \ref{fig: sinking_velocity_spectrum}).
+As the Junge slope increases, the spectrum of biomass steepens, and the relative contribution of slower-sinking particles to the downward biomass flux significantly increases.
+In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.1\% to 10\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$.
+While significant, the impact of a change in the Junge slope in summer conditions does not challenge the dominant role played by faster-sinking particles.
+This result can be explained by the fact that, in the summer, vertical velocities are weak and vertical biomass fluxes are therefore gravitationally-driven.
+
+%FIG7
+\begin{figure}[t]
+	\centering
+	%\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
+	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}).
+Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
+	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
+	\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class.
+Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.\fixme{bigger fontsize}}
+	\label{fig: biomass_export}
+\end{figure}
+
+In the winter, the PDFs of relative biomass as a function of vertical velocities present a much larger spread, with velocity magnitudes exceeding 50 m/day.
+For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.1\% in the summer to about 4\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes.
+Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass.
+When winter ocean dynamics are coupled with a steeper Junge slope, however, slower-sinking particles largely dominate the downward biomass flux.
+In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 80\% of the biomass flux.
+
+ %In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa.
 Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2016,Palevsky_2018}.
@@
 
-The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
+%The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
 As expected, the faster-sinking particles are exported earlier than slower-sinking particles.
@@
 
-%FIG6
-\begin{figure}[ht]
-	\centering
-	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
-	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
-Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain.
-For each sinking-velocity class, the net particle flux is shown by a thick line.
-Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
-	\includegraphics[width = 1\linewidth]{figures/Fig6.png}
-	\caption{[left] Gridded depth anomaly in the median particle depth 25 days after particle release, in the Winter experiment.
-Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model.
-[right]  Depth profile of the PDF of the number of particle for each velocity class.
-The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions.
-Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies.
-Release depth is indicated by the thick dashed line.}
-	\label{fig: particle_export}
-\end{figure}
-
-Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b).
+%Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b).
 In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking.
@@
 
-The corresponding biomass export fluxes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b).
+%The corresponding biomass export fluxes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b).
 The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$).
@@
 
-\begin{figure}[t]
-	\centering
-	%\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
-	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}).
-Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
-	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
-	\caption{PDF of biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
-Inserts show the total downward biomass flux associated with each sinking-velocity class.
-Both winter dynamics and steeper June slope tend to increase the relative contribution of slower-sinking particles.}
-	\label{fig: biomass_export}
-\end{figure}
-
-As anticipated from Figure \ref{fig: sinking_velocity_spectrum}, the Junge slope $\xi$ is a determining parameter that affects the contribution of slower-sinking classes in the presence of submesoscale dynamics.
+%As anticipated from Figure \ref{fig: sinking_velocity_spectrum}, the Junge slope $\xi$ is a determining parameter that affects the contribution of slower-sinking classes in the presence of submesoscale dynamics.
 Figure \ref{fig: biomass_export} shows the biomass export fluxes in normalized units for two different Junge slopes.
@@
 
-\begin{equation}
-    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_{s_0}}\right)^{\frac{\xi_2-\xi_1}{2}}
+%\begin{equation}
+%    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_{s_0}}\right)^{\frac{\xi_2-\xi_1}{2}}
     %\frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
-\end{equation}
-Using $\xi_1 = 2$ and $\xi_2 = 4$, as depicted in Figure \ref{fig: biomass_export}, the decrease in biomass export is 80\%, 90\%, and 99.5\% for the 1, 0.5 and 0.025 m/day particle classes, respectively.
+%\end{equation}
+%Using $\xi_1 = 2$ and $\xi_2 = 4$, as depicted in Figure \ref{fig: biomass_export}, the decrease in biomass export is 80\%, 90\%, and 99.5\% for the 1, 0.5 and 0.025 m/day particle classes, respectively.
 %\fixme{The evolution of the biological community through time that would affect the slope of the size spectrum also has direct consequences on the export of the slower-sinking particles.}
 
-The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, between a few percent and tens of percents, depending on the sinking-velocity class.
+%The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, between a few percent and tens of percents, depending on the sinking-velocity class.
 This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}).
@@
 
- Including remineralization of particles significantly impacts the relative importance of sinking and advection to export for each particle class.
-In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles decelerate as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}).
-In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included.
-The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.
+ Both ocean dynamics at submeso-scales and the Junge slope were identified as key factors impacting the respective role played by different particle classes in driving downward biomass fluxes.
+Simple Lagrangian particles were used to isolate the effects of these two factors.
+In reality, however, sinking velocities of particulate matter varies in time as the particles slowly remineralize.
+A remineralizing behavior was therefore implemented for the Lagrangian particles, using Equation \ref{eq: sinking_velocity_remin}, to investigate the impact that remineralization processes have on our findings.
+The traditional paradigm relies on the fact that slow-sinking particles tend to fully remineralize over shorter timescales, further enhancing the importance of faster-sinking particles classes in driving downward biomass fluxes.
+While this paradigm holds for flatter Junge slope, where the biomass content is dominated by faster-sinking particles, it becomes inadequate at steeper slopes.
 
- %FIG7
+ Figure \ref{fig: biomass_export_remin} shows the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without remineralization processes.
+As expected, the main impact of implementing particle remineralization is a decrease in the total amount of biomass through time \fixme{refer to Fig 9?}.
+
+ During summertime and in the absence of remineralization, downward fluxes of biomass are dominated by faster-sinking particles, even for steeper Junge slope.
+This is due to the fact that the flux of biomass $\left<wB\right> = \left<w_sB\right> + \left<w_aB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content.
+This is characteristics of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes.
+Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize.
+This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where the PDFs of relative biomass per particle class are centered over lower vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}.
+As a result, the gravitationally-driven term $\left<w_sB\right>$ becomes small, and the downward flux of biomass is generally advectively-driven.
+The advectively-driven component of the biomass fluxes is uniform across particle classes, as it only depends on ocean currents.
+Thus, in a advectively-driven system where $\left<w_sB\right> << \left<w_aB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
+This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a).
+When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c).
+As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics.
+Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes.
+
+ These results highlight the importance in considering slower-sinking particle classes when considering downward biomass fluxes.
+It also demonstrates that, contrarily to the traditional paradigm, remineralization processes enhance the role played by slower-sinking particles in biomass fluxes, in cases where the biomass spectrum slope is negative.
+
+ The timescales over which the system transitioned from an gravitationally-driven to an advectively-driven system depends on the remineralization model used.
+
+  %FIG8
  \begin{figure}[t]
@@
 	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
-	\caption{Snapshot of the biomass PDF versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
-Inserts show the total downward biomass flux associated with each sinking-velocity class.
+	\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class.
 Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}
@@
 
- The biomass export flux is also reduced compared to the case with no remineralization.
+ \fixme{main points of new figure 8:
+\begin{itemize}
+    \item The impact of remineralization is three-fold: (1) it affects the total amount of biomass, as biomass is slowly remineralized - as illustrated by the decrease in area below the curves.
+(2) It shifts the PDFs of relative biomass as a function of vertical velocity towards slower vertical velocities.
+that is because, as they remineralize, the particles slow down.
+This has less of an impact on slower-sinking particles, as they are already sinking slowly anyway, so their PDFs don't change much, and the resulting downward biomass flux remains relatively large.
+faster-sinking particles, however, are more affected by the remineralization process, as their total vertical velocity shifts from gravitationally driven to advectively driven.
+as a result, their associated downward relative biomass flux is greatly decreased.
+Slow-sinking particles dominate the downward relative flux of biomass in both the summer and winter in the presence of remineralzation, as opposed to just the summer when remineralization is not included.
+\end{itemize}
+}
+
+ %Including remineralization of particles significantly impacts the relative importance of sinking and advection to export for each particle class.
+In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles decelerate as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}).
+In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included.
+The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.
+
+ %The biomass export flux is also reduced compared to the case with no remineralization.
 In a gravitationally-driven system such as during the summer in the northeast Pacific, captured in \textit{Papa\_summer}, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases.
@@
 
- In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}).
+ %In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}).
 The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already being exported.

### 2019-06-21 figures/code/Fig2_Papa500_summer.m
another commit

@@ -193,5 +193,5 @@ set(gca,'position',[POS(1)+0.05 POS(2) POS(3) POS(4)])
 cd(thefolder)
 
 set(gcf,'color','w')
-export_fig('Fig2_Papa500_summer.png','-r200')
-close all
+%export_fig('Fig2_Papa500_summer.png','-r200')
+%close all

### 2019-06-21 figures/code/Fig3_Papa500_winter.m

@@ -15,7 +15,7 @@ clearvars -except glider cmap
 %% STEP 1 - Compute the TKE vs time. cannot use the full resolution, as it is domain integrated
 thefolder = pwd;
 
-cd /Volumes/mathieudever/PSOM_backup/Papa500_steroid
+cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_winter
 % Surface view
 depth = 50; % depth to plot in m
 lat = 50;   % Latitude of mid-domain (for f)
@@ -197,5 +197,5 @@ set(gca,'position',[POS(1)+0.05 POS(2) POS(3) POS(4)])
 
 cd(thefolder)
 set(gcf,'color','w')
-export_fig('Fig3_Papa500_winter.png','-r200')
-close all
+%export_fig('Fig3_Papa500_winter.png','-r200')
+%close all

### 2019-06-21 figures/code/Fig4.m

@@ -1,0 +1,193 @@
+clear
+% Set of marameters
+wmax = 5; wmin = 0.025;
+slope = 3; B0 = 1;
+
+% Compute total biomass based on the paramters
+Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0 = B0/Btot;
+B0025_3 = B0*(0.025/wmax).^((3-slope)/2);
+B1_3 = B0*(1/wmax).^((3-slope)/2);
+B5_3 = B0*(5/wmax).^((3-slope)/2);
+
+% For Junge slope = 2
+slope = 2;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_2 = B0*(0.025/wmax).^((3-slope)/2);
+B1_2 = B0*(1/wmax).^((3-slope)/2);
+B5_2 = B0*(5/wmax).^((3-slope)/2);
+
+% For Junge slope = 4
+slope = 4;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_4 = B0*(0.025/wmax).^((3-slope)/2);
+B1_4 = B0*(1/wmax).^((3-slope)/2);
+B5_4 = B0*(5/wmax).^((3-slope)/2);
+
+%%
+
+% Set colors for each class
+color0025 = [215,48,39]/256;
+color1 = [39,100,25]/256;
+color5 = [49,54,149]/256;
+
+figure(2)
+thew = [0.025 1 5];
+h1 = loglog(thew,[B0025_3 B1_3 B5_3]./sum([B0025_3 B1_3 B5_3])*100,'-k','linewidth',2);
+hold on
+h2 = loglog(thew,[B0025_2 B1_2 B5_2]./sum([B0025_2 B1_2 B5_2])*100,'--k','linewidth',2);
+h3 = loglog(thew,[B0025_4 B1_4 B5_4]./sum([B0025_4 B1_4 B5_4])*100,':k','linewidth',2);
+
+
[…]

### 2019-06-21 figures/code/Fig6_v3.m

@@ -1,0 +1,88 @@
+clear
+close all
+
+istart = 200;
+ifinish = 400;
+
+%fullfigure
+
+%%
+thefolder = pwd;
+for plt = 2:-1:1
+    if plt == 1
+        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/highrez
+        timesteps = 24000:1000:36000;
+    elseif plt == 2
+        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_winter/highrez
+        timesteps = 32000:1000:56000;
+    end
+    counter = 0;
+    thew = [];
+    for tt = timesteps
+        counter = counter +1;
+        
+        
+        w = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'w');
+        w(1,:,:) = NaN; w(end,:,:) = NaN;
+        
+        x = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'xc')*1000;
+        y = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'yc')*1000;
+        Z2 = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'zc');
+        z = squeeze(Z2(1,1,:));
+        [X,Y] = meshgrid(x,y);
+        [X2,Y2,Z2] = meshgrid(x,y,squeeze(Z2(1,1,:)));
+        X2 = permute(X2,[2 1 3]);
+        Y2 = permute(Y2,[2 1 3]);
+        Z2 = permute(Z2,[2 1 3]);
+        
+        w = permute(w,[2 1 3]);
+        
+        %% PLOT HISTOGRAMS
+        
+        blop = w(istart:ifinish,:,16:end)*86400;
+        thew = cat(1,thew,blop(:));
+        if tt == 36000 && plt == 1
+            %histogram(thew,-10:.5:10,'Normalization','probability')
+            yyaxis right
+            [N,EDGES] = histcounts(thew,-10:.1:10,'Normalization','probability');
+            h2 = plot((EDGES(2:end)+EDGES(1:end-1))/2,N*100,'color',[0.8500    0.3250    0.0980],'linewidth',3);
+            set(gca,'ycolor',[0.8500    0.3250    0.0980])
+            ylabel('PDF [%]')
+        elseif tt == 56000 && plt == 2
+            fullfigure
[…]

### 2019-06-21 figures/code/Fig6_v4.m

@@ -1,0 +1,238 @@
+clear
+
+%speed = {'0025','05','1','5'};
+speed = {'0025','1','5'};
+fullfigure
+for ii = 1:length(speed)
+    subplot(2,1,1)
+    
+    %% SUMMER
+    % Get data
+    filename = ['/Volumes/home/mdever/allparticles/wtotal',num2str(speed{ii}),'mday_summer.csv'];
+    M = csvread(filename);
+    %M(M(:,2)==max(M(:,2)),2) = NaN;
+    
+    % Plots data
+    plot(M(:,1)*86400,M(:,2)./sum(M(:,2))*100,'r')
+    hold on
+    set(gca,'fontsize',18)
+    xlabel('Vertical velocity [m/day]')
+    ylabel('Particles PDF [%]')
+    
+    % computes stats
+    mu = sum(M(:,1).*M(:,2))/sum(M(:,2));
+    std = sqrt(sum(M(:,2).*(M(:,1)-mu).^2)/(sum(M(:,2))-1));
+    s = (sum(M(:,2).*(M(:,1)-mu).^3)/sum(M(:,2)))/(std^3);
+    k = (sum(M(:,2).*(M(:,1)-mu).^4)/sum(M(:,2)))/(std^4) - 3;
+    
+    xlim([-20 20])
+    %ylim([0 60])
+    
+    % display stats
+    %YLIM = get(gca,'ylim');
+    %text(-28,0.85*(YLIM(2)-YLIM(1))+YLIM(1),{['\mu = ',num2str(mu*86400,'%2.2f')],...
+    %    ['\sigma = ',num2str(std*86400,'%2.2f')],...
+    %    ['s = ',num2str(s*86400,'%2.2e')],...
+    %    ['\kappa = ',num2str(k*86400,'%2.2e')]},...
+    %    'fontsize',21,'color','r')
+    
+    
+end
+
+%% GET MODEL PDF
+istart = 200;
+ifinish = 400;
+
+thefolder = pwd;
+cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/highrez
+timesteps = 24000:1000:36000;
+counter = 0;
+thew = [];
+for tt = timesteps
+    counter = counter +1;
+    
+    w = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'w');
+    w(1,:,:) = NaN; w(end,:,:) = NaN;
+    
[…]

### 2019-06-21 figures/code/Fig6_v5.m

@@ -1,0 +1,157 @@
+clear
+
+%% Import (x,y,z) for each size class in winter and summer
+[x0025s,y0025s,z0025s] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal0025mday_summer.csv');
+[x1s,y1s,z1s] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal1mday_summer.csv');
+[x5s,y5s,z5s] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal5mday_summer.csv');
+
+[x0025,y0025,z0025] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal0025mday_winter.csv');
+[x1,y1,z1] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal1mday_winter.csv');
+[x5,y5,z5] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal5mday_winter.csv');
+
+color0025 = [215,48,39]/256;
+color1 = [39,100,25]/256;
+color5 = [49,54,149]/256;
+
+%% Bin the data into 1x1 km and compute the median vertical displacement
+% with respect to the gravitational model
+thedoy = 25;
+countx = 1;
+rez = 1;
+for x = 0:rez:111
+    county = 1;
+    for y = 100:rez:200
+        
+        %% 0025 m/day
+        ind = find(x0025>=x & x0025<=x+rez & y0025>=y & y0025<=y+rez);
+        if isempty(ind)
+            medi0025(countx,county) = NaN;
+        else
+            medi0025(countx,county) = median(z0025(ind)-(80+0.025*thedoy));
+        end
+        
+        %% 1 m/day
+        ind = find(x1>=x & x1<=x+rez & y1>=y & y1<=y+rez);
+        if isempty(ind)
+            medi1(countx,county) = NaN;
+        else
+            medi1(countx,county) = median(z1(ind)-(80+1*thedoy));
+        end
+        
+        %% 5 m/day
+        ind = find(x5>=x & x5<=x+rez & y5>=y & y5<=y+rez);
+        if isempty(ind)
+            medi5(countx,county) = NaN;
+        else
+            medi5(countx,county) = median(z5(ind)-(80+5*thedoy));
+        end
[…]

### 2019-06-21 figures/code/Fig7.m

@@ -1,0 +1,222 @@
+clear
+
+%% This figure plots the histogram of the relative biomass vs vertical velocity at 
+% DOY 25 in Summer/Winter for xi = 2 and xi = 4
+
+%% Import w for each size class in winter and summer
+tt = 25;
+[~,~,wt0025s] = importw('/Volumes/home/mdever/particlespeed/doy25/w0025mday_summer.csv');
+[~,~,wt1s] = importw('/Volumes/home/mdever/particlespeed/doy25/w1mday_summer.csv');
+[~,~,wt5s] = importw('/Volumes/home/mdever/particlespeed/doy25/w5mday_summer.csv');
+
+[~,~,wt0025w] = importw('/Volumes/home/mdever/particlespeed/doy25/w0025mday_winter.csv');
+[~,~,wt1w] = importw('/Volumes/home/mdever/particlespeed/doy25/w1mday_winter.csv');
+[~,~,wt5w] = importw('/Volumes/home/mdever/particlespeed/doy25/w5mday_winter.csv');
+
+%% Set colors for each class
+color0025 = [215,48,39]/256;
+color1 = [39,100,25]/256;
+color5 = [49,54,149]/256;
+
+%% compute biomass per simulated particle
+
+% Set of marameters
+wmax = 5; wmin = 0.025;
+slope = 3; B0 = 1;
+% Compute total biomass based on the paramters
+Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+
+% For Junge slope = 2
+slope = 2;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_2 = B0*(0.025/wmax)^((3-slope)/2);
+B1_2 = B0*(1/wmax)^((3-slope)/2);
+B5_2 = B0*(5/wmax)^((3-slope)/2);
+
+% For Junge slope = 4
+slope = 4;
[…]

### 2019-06-21 figures/code/Fig7_biomass_spectra.m

@@ -1,0 +1,133 @@
+clear
+
+cmap = get(gca,'ColorOrder');
+%close all
+
+%speed = {'0025','05','1','5'};
+speed = {'0025','1','5'};
+%numspeed = [0.025,0.5,1,5];
+numspeed = [0.025,1,5];
+fullfigure
+for ii = 1:length(speed)
+    subplot(2,1,1)
+    
+    %% SUMMER
+    % Get data
+    filename = ['/Volumes/home/mdever/sousML/wtotal',num2str(speed{ii}),'mday_summer.csv'];
+    M = csvread(filename);
+    %M(M(:,2)==max(M(:,2)),2) = NaN;
+    
+    % convert Particles to biomass
+    wmax = 5; wmin = 0.025;
+    slope = 3; B0 = 1;
+    Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+
+    slope = 2;
+    B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+    B2 = B0*(numspeed(ii)/wmax)^((3-slope)/2);
+    
+    slope = 3;
+    B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+    B3 = B0*(numspeed(ii)/wmax)^((3-slope)/2);
+    
+    slope = 4;
+    B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+    B4 = B0*(numspeed(ii)/wmax)^((3-slope)/2);
+    
+    % Plots data
+    h1(ii)=plot(M(:,1)*86400,M(:,2)*B2,'-','linewidth',2,'color',cmap(ii,:));
+    disp(['Total biomass for speed ',speed{ii},'is ',num2str(sum(M(:,2)*B2)),' and xi = 2'])
+    disp(['Total biomass for speed ',speed{ii},'is ',num2str(sum(M(:,2)*B4)),' and xi = 4'])
+    hold on
[…]

### 2019-06-21 figures/code/Fig7_biomass_spectra_remin.m

@@ -1,0 +1,92 @@
+clear
+
+cmap = get(gca,'ColorOrder');
+close all
+
+%speed = {'0025','05','1','5'};
+speed = {'0025','1','5'};
+%numspeed = [0.025,0.5,1,5];
+numspeed = [0.025,1,5];
+styles = {'-',':'};
+fullfigure
+for ii = 2:length(speed)
+    subplot(2,1,1)
+    
+    for xi = [2 4]
+        %% SUMMER
+        % Get data
+        filename = ['/Volumes/home/mdever/sousML/wtotal',speed{ii},'mday_remin_summer_xi',num2str(xi),'.csv'];
+        M = csvread(filename);
+        %M(M(:,2)==max(M(:,2)),2) = NaN;
+        
+        % Plots data
+        h1(xi/2)=plot(M(:,1)*86400,M(:,2),styles{xi/2},'linewidth',2,'color',cmap(ii,:));
+        hold on
+        set(gca,'fontsize',18,'yscale','log')
+        xlabel('Vertical velocity [m/day]')
+        ylabel('Biomass [arbitrary unit]')
+        grid on
+        
+        % computes stats
+        mu = sum(M(:,1).*M(:,2))/sum(M(:,2));
+        std = sqrt(sum(M(:,2).*(M(:,1)-mu).^2)/(sum(M(:,2))-1));
+        s = (sum(M(:,2).*(M(:,1)-mu).^3)/sum(M(:,2)))/(std^3);
+        k = (sum(M(:,2).*(M(:,1)-mu).^4)/sum(M(:,2)))/(std^4) - 3;
+    end
+    xlim([-20 20])
+    %ylim([0 60])
+    
+    % display stats
+    %YLIM = get(gca,'ylim');
+    %text(-28,0.85*(YLIM(2)-YLIM(1))+YLIM(1),{['\mu = ',num2str(mu*86400,'%2.2f')],...
+    %    ['\sigma = ',num2str(std*86400,'%2.2f')],...
+    %    ['s = ',num2str(s*86400,'%2.2e')],...
+    %    ['\kappa = ',num2str(k*86400,'%2.2e')]},...
+    %    'fontsize',21,'color','r')
+end
+title('Summer','fontsize',21)
+legend([h1],'\xi = 2','\xi = 4')
+
+%% WINTER
+for ii = 1:length(speed)
+    subplot(2,1,2)
+    
+    for xi = [2 4]
+        
+        %% SUMMER
[…]

### 2019-06-21 figures/code/Fig8.m

@@ -1,0 +1,261 @@
+clear
+
+%% This figure plots the histogram of the biomass vs vertical velocity at 
+% DOY 25 in Summer/Winter with and without remineralization for slope = 4
+
+%% Import w for each size class in winter and summer
+tt = 25;
+[~,~,wt0025s] = importw('/Volumes/home/mdever/particlespeed/doy25/w0025mday_summer.csv');
+[~,~,wt1s] = importw('/Volumes/home/mdever/particlespeed/doy25/w1mday_summer.csv');
+[~,~,wt5s] = importw('/Volumes/home/mdever/particlespeed/doy25/w5mday_summer.csv');
+
+[~,~,wt0025w] = importw('/Volumes/home/mdever/particlespeed/doy25/w0025mday_winter.csv');
+[~,~,wt1w] = importw('/Volumes/home/mdever/particlespeed/doy25/w1mday_winter.csv');
+[~,~,wt5w] = importw('/Volumes/home/mdever/particlespeed/doy25/w5mday_winter.csv');
+
+%% Set colors for each class
+color0025 = [215,48,39]/256;
+color1 = [39,100,25]/256;
+color5 = [49,54,149]/256;
+
+%% compute biomass per simulated particle
+
+% Set of marameters
+wmax = 5; wmin = 0.025;
+slope = 3; B0 = 1;
+% Compute total biomass based on the paramters
+Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+
+% For Junge slope = 4
+slope = 4;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_4 = B0*(0.025/wmax)^((3-slope)/2);
+B1_4 = B0*(1/wmax)^((3-slope)/2);
+B5_4 = B0*(5/wmax)^((3-slope)/2);
+
+% Compute histograms in summer
[…]

### 2019-06-21 figures/code/Fig6_v5.m
update Fig6

@@ -1,13 +1,13 @@
 clear
 
 %% Import (x,y,z) for each size class in winter and summer
-[x0025s,y0025s,z0025s] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal0025mday_summer.csv');
-[x1s,y1s,z1s] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal1mday_summer.csv');
-[x5s,y5s,z5s] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal5mday_summer.csv');
+[x0025s,y0025s,z0025s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal0025mday_summer.csv');
+[x1s,y1s,z1s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal1mday_summer.csv');
+[x5s,y5s,z5s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal5mday_summer.csv');
 
-[x0025,y0025,z0025] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal0025mday_winter.csv');
-[x1,y1,z1] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal1mday_winter.csv');
-[x5,y5,z5] = importxyz('/Volumes/home/mdever/particleposition/doy25/wtotal5mday_winter.csv');
+[x0025,y0025,z0025] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal0025mday_winter.csv');
+[x1,y1,z1] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal1mday_winter.csv');
+[x5,y5,z5] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal5mday_winter.csv');
 
 color0025 = [215,48,39]/256;
 color1 = [39,100,25]/256;
@@ -58,7 +58,7 @@ figure
 subplot(3,2,1)
 pcolor(0:rez:111,100:rez:200,medi0025'); shading interp
 cmocean('balance'); caxis([-50 50])
-set(gca,'fontsize',16,'xticklabels',{},'tickdir','out')
+set(gca,'fontsize',14,'xticklabels',{},'tickdir','out')
 H = colorbar; set(H,'location','northoutside','TickLength',0.04)
 hold on
 contour(0:rez:111,100:rez:200,medi0025',[0 0],'k')
[…]

### 2019-06-21 size_differentiated_export.tex
Updates from Overleaf

@@
 	\centering
-	\includegraphics[width = .6\linewidth]{figures/Fig4_particle_PDF}
-	\caption{Number of particles (solid) and biomass (dashed) normalized to the fastest-sinking particle class as a function of sinking velocity $w_s$.
-Sinking velocity spectrum are shown for three different Junge slope $\xi$: 4 (red), 3 (black), and 2 (blue).}
+	\includegraphics[width = .49\linewidth]{figures/Fig4b.png}
+	\includegraphics[width = .49\linewidth]{figures/Fig4a.png}
+	\caption{Relative number of particles (left) and biomass (right) as a function of sinking velocity $w_s$.
+Sinking velocity spectrum are shown for three different Junge slope $\xi$: 2 (dotted), 3 (solid), and 2 (dashed).
+Colored squares indicate the sinking velocities of the three particle classes modeled: 0.025 m/day (red), 1 m/day (green), and 5 m/day (blue).}
 	\label{fig: sinking_velocity_spectrum}

### 2019-06-21 figures/code/Fig6_v5.m
update Fig6

@@ -58,7 +58,7 @@ figure
 subplot(3,2,1)
 pcolor(0:rez:111,100:rez:200,medi0025'); shading interp
 cmocean('balance'); caxis([-50 50])
-set(gca,'fontsize',14,'xticklabels',{},'tickdir','out')
+set(gca,'fontsize',12,'xticklabels',{},'tickdir','out')
 H = colorbar; set(H,'location','northoutside','TickLength',0.04)
 hold on
 contour(0:rez:111,100:rez:200,medi0025',[0 0],'k')
@@ -66,26 +66,29 @@ axis tight; ylabel('y [km]')
 set(gca,'position',[0.1 .66 .33 .25])
 set(H,'position',[.12 .92 .3 .015])
 text(109,188,'0.025 m/day','BackgroundColor','w','EdgeColor','k','fontsize',14,'HorizontalAlignment','right','color',color0025)
+text(3,188,'(a)','BackgroundColor','w','EdgeColor','k','fontsize',14,'HorizontalAlignment','left','fontweight','b')
 
 subplot(3,2,3)
 pcolor(0:rez:111,100:rez:200,medi1'); shading interp
 cmocean('balance'); caxis([-50 50])
-set(gca,'fontsize',14,'xticklabels',{},'tickdir','out')
+set(gca,'fontsize',12,'xticklabels',{},'tickdir','out')
 hold on
 contour(0:rez:111,100:rez:200,medi1',[0 0],'k')
 axis tight; ylabel('y [km]')
 set(gca,'position',[0.1 .365 .33 .25])
 text(109,188,'1 m/day','BackgroundColor','w','EdgeColor','k','fontsize',14,'HorizontalAlignment','right','color',color1);
+text(3,188,'(b)','BackgroundColor','w','EdgeColor','k','fontsize',14,'HorizontalAlignment','left','fontweight','b')
 
 subplot(3,2,5)
 pcolor(0:rez:111,100:rez:200,medi5'); shading interp
 cmocean('balance'); caxis([-50 50])
-set(gca,'fontsize',14,'tickdir','out')
+set(gca,'fontsize',12,'tickdir','out')
 hold on
 contour(0:rez:111,100:rez:200,medi5',[0 0],'k')
 axis tight; ylabel('y [km]')
 set(gca,'position',[0.1 .07 .33 .25])
[…]

### 2019-06-21 figures/code/Fig7.m
Update Fig 7

@@ -5,13 +5,13 @@ clear
 
 %% Import w for each size class in winter and summer
 tt = 25;
-[~,~,wt0025s] = importw('/Volumes/home/mdever/particlespeed/doy25/w0025mday_summer.csv');
-[~,~,wt1s] = importw('/Volumes/home/mdever/particlespeed/doy25/w1mday_summer.csv');
-[~,~,wt5s] = importw('/Volumes/home/mdever/particlespeed/doy25/w5mday_summer.csv');
+[~,~,wt0025s] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_summer.csv');
+[~,~,wt1s] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_summer.csv');
+[~,~,wt5s] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_summer.csv');
 
-[~,~,wt0025w] = importw('/Volumes/home/mdever/particlespeed/doy25/w0025mday_winter.csv');
-[~,~,wt1w] = importw('/Volumes/home/mdever/particlespeed/doy25/w1mday_winter.csv');
-[~,~,wt5w] = importw('/Volumes/home/mdever/particlespeed/doy25/w5mday_winter.csv');
+[~,~,wt0025w] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_winter.csv');
+[~,~,wt1w] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_winter.csv');
+[~,~,wt5w] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_winter.csv');
 
 %% Set colors for each class
 color0025 = [215,48,39]/256;
@@ -72,7 +72,7 @@ totalF4 = sum(N0025s(E<=0).*B0025_4.*E(E<=0))+sum(N1s(E<=0).*B1_4.*E(E<=0))+sum(
 totalFw = sum(N0025w(Ew<=0).*B0025_2.*Ew(Ew<=0))+sum(N1w(Ew<=0).*B1_2.*Ew(Ew<=0))+sum(N5w(Ew<=0).*B5_2.*Ew(Ew<=0));
 totalF4w = sum(N0025w(Ew<=0).*B0025_4.*Ew(Ew<=0))+sum(N1w(Ew<=0).*B1_4.*Ew(Ew<=0))+sum(N5w(Ew<=0).*B5_4.*Ew(Ew<=0));
 
[…]

### 2019-06-21 figures/code/Fig7.m
Update Fig7.m

@@ -84,13 +84,13 @@ patch([E(E<=0) 0 min(E(E<=0)) min(E(E<=0))],[N0025s(E<=0).*B0025_2/totalB*100 1e
 patch([E(E<=0) 0 min(E(E<=0)) min(E(E<=0))],[N1s(E<=0).*B1_2/totalB*100 1e-2 1e-2 N1s(1).*B1_2/totalB*100],color1,'edgecolor','none','facealpha',.3)
 patch([E(E<=0) 0 min(E(E<=0)) min(E(E<=0))],[N5s(E<=0).*B5_2/totalB*100 1e-2 1e-2 N5s(1).*B5_2/totalB*100],color5,'edgecolor','none','facealpha',.3)
 
-set(gca,'Yscale','log','FontSize',30)
+set(gca,'Yscale','log','FontSize',40)
 %xlabel('w [m/day]')
 ylabel('Relative Biomass [%]')
 grid on; axis tight; xlim([-10 10])
 ylim([1e-2 100])
 title('Summer','fontsize',50,'position',[-6 11e+01 0]);
-text(-9.5,6e1,'(a)   \xi = 2','fontweight','b','fontsize',30)
+text(-9.5,6e1,'(a)   \xi = 2','fontweight','b','fontsize',40)
 HH = legend([h1 h2 h3],'0.025 m/day','1 m/day','5 m/day','location','southeast');
 set(HH,'fontsize',25)
 
@@ -99,10 +99,10 @@ bar(1,sum(N0025s(E<=0).*B0025_2.*E(E<=0)/totalF*100),'facecolor',color0025,'edge
 hold on
 bar(2,sum(N1s(E<=0).*B1_2.*E(E<=0)/totalF*100),'facecolor',color1,'edgecolor',color1);
 bar(3,sum(N5s(E<=0).*B5_2.*E(E<=0)/totalF*100),'facecolor',color5,'edgecolor',color5);
-set(gca,'YScale','log','fontsize',30,'xtick',[1:3],'XTickLabel',{},'yaxislocation','right')
+set(gca,'YScale','log','fontsize',40,'xtick',[1:3],'XTickLabel',{},'yaxislocation','right')
 grid on; box on
 ylim([1e-2 100])
-title('Relative Downward Biomass Flux','fontsize',30,'position',[2 180 0])
[…]

### 2019-06-22 figures/code/Fig7.m
Update Fig7

@@ -192,7 +192,7 @@ ylim([1e-2 100])
 title('Relative Downward Flux','fontsize',40,'position',[2 200 0])
 
 set(gcf,'color','w')
-%export_fig -r300 Fig7.png
+export_fig -r300 Fig7.png
 %%
 function [w,wsink,wtotal] = importw(filename)
 

### 2019-06-22 figures/code/Fig6_v5.m
update figs

@@ -58,26 +58,26 @@ figure
 subplot(3,2,1)
 pcolor(0:rez:111,100:rez:200,medi0025'); shading interp
 cmocean('balance'); caxis([-50 50])
-set(gca,'fontsize',12,'xticklabels',{},'tickdir','out')
+set(gca,'fontsize',9,'xticklabels',{},'tickdir','out')
 H = colorbar; set(H,'location','northoutside','TickLength',0.04)
 hold on
 contour(0:rez:111,100:rez:200,medi0025',[0 0],'k')
 axis tight; ylabel('y [km]')
 set(gca,'position',[0.1 .66 .33 .25])
 set(H,'position',[.12 .92 .3 .015])
-text(109,188,'0.025 m/day','BackgroundColor','w','EdgeColor','k','fontsize',14,'HorizontalAlignment','right','color',color0025)
-text(3,188,'(a)','BackgroundColor','w','EdgeColor','k','fontsize',14,'HorizontalAlignment','left','fontweight','b')
+text(109,188,'0.025 m/day','BackgroundColor','w','EdgeColor','k','fontsize',12,'HorizontalAlignment','right','color',color0025)
+text(3,188,'(a)','BackgroundColor','w','EdgeColor','k','fontsize',12,'HorizontalAlignment','left','fontweight','b')
 
 subplot(3,2,3)
 pcolor(0:rez:111,100:rez:200,medi1'); shading interp
 cmocean('balance'); caxis([-50 50])
-set(gca,'fontsize',12,'xticklabels',{},'tickdir','out')
+set(gca,'fontsize',9,'xticklabels',{},'tickdir','out')
 hold on
 contour(0:rez:111,100:rez:200,medi1',[0 0],'k')
 axis tight; ylabel('y [km]')
 set(gca,'position',[0.1 .365 .33 .25])
-text(109,188,'1 m/day','BackgroundColor','w','EdgeColor','k','fontsize',14,'HorizontalAlignment','right','color',color1);
-text(3,188,'(b)','BackgroundColor','w','EdgeColor','k','fontsize',14,'HorizontalAlignment','left','fontweight','b')
+text(109,188,'1 m/day','BackgroundColor','w','EdgeColor','k','fontsize',12,'HorizontalAlignment','right','color',color1);
[…]

### 2019-06-22 figures/code/Fig7.m

@@ -189,10 +189,10 @@ bar(3,sum(N5w(Ew<=0).*B5_4.*Ew(Ew<=0))/totalF4w*100,'facecolor',color5,'edgecolo
 set(gca,'YScale','log','fontsize',40,'xtick',[1:3],'XTickLabel',{},'yaxislocation','right')
 grid on; box on
 ylim([1e-2 100])
-title('Relative Downward Flux','fontsize',40,'position',[2 200 0])
+title('Relative Downward Flux','fontsize',40,'position',[2 400 0])
 
 set(gcf,'color','w')
-export_fig -r300 Fig7.png
+%export_fig -r300 Fig7.png
 %%
 function [w,wsink,wtotal] = importw(filename)
 

### 2019-06-22 size_differentiated_export.tex

@@
 Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies.
-Release depth is indicated by the thick dashed line.\fixme{Add a)-d) symbols} \fixme{smaller fontsize}}
+Release depth is indicated by the thick dashed line.}
 	\label{fig: particle_depth_distribution}
@@
 Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class.
-Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.\fixme{bigger fontsize}}
+Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.}
 	\label{fig: biomass_export}

### 2019-06-22 figures/code/Fig6_v5.m
yet another figure tweaking

@@ -58,37 +58,37 @@ figure
 subplot(3,2,1)
 pcolor(0:rez:111,100:rez:200,medi0025'); shading interp
 cmocean('balance'); caxis([-50 50])
-set(gca,'fontsize',9,'xticklabels',{},'tickdir','out')
-H = colorbar; set(H,'location','northoutside','TickLength',0.04)
+set(gca,'fontsize',11,'xticklabels',{},'tickdir','out')
+H = colorbar; set(H,'location','northoutside','TickLength',0.04,'fontsize',12)
 hold on
 contour(0:rez:111,100:rez:200,medi0025',[0 0],'k')
 axis tight; ylabel('y [km]')
 set(gca,'position',[0.1 .66 .33 .25])
 set(H,'position',[.12 .92 .3 .015])
-text(109,188,'0.025 m/day','BackgroundColor','w','EdgeColor','k','fontsize',12,'HorizontalAlignment','right','color',color0025)
-text(3,188,'(a)','BackgroundColor','w','EdgeColor','k','fontsize',12,'HorizontalAlignment','left','fontweight','b')
+text(109,188,'0.025 m/day','BackgroundColor','w','EdgeColor','k','fontsize',13,'HorizontalAlignment','right','color',color0025)
+text(3,188,'(a)','BackgroundColor','w','EdgeColor','k','fontsize',13,'HorizontalAlignment','left','fontweight','b')
 
 subplot(3,2,3)
 pcolor(0:rez:111,100:rez:200,medi1'); shading interp
 cmocean('balance'); caxis([-50 50])
-set(gca,'fontsize',9,'xticklabels',{},'tickdir','out')
+set(gca,'fontsize',11,'xticklabels',{},'tickdir','out')
 hold on
 contour(0:rez:111,100:rez:200,medi1',[0 0],'k')
 axis tight; ylabel('y [km]')
 set(gca,'position',[0.1 .365 .33 .25])
-text(109,188,'1 m/day','BackgroundColor','w','EdgeColor','k','fontsize',12,'HorizontalAlignment','right','color',color1);
-text(3,188,'(b)','BackgroundColor','w','EdgeColor','k','fontsize',12,'HorizontalAlignment','left','fontweight','b')
[…]

### 2019-06-22 figures/code/Fig8.m
Fig 8 tweak

@@ -5,13 +5,13 @@ clear
 
 %% Import w for each size class in winter and summer
 tt = 25;
-[~,~,wt0025s] = importw('/Volumes/home/mdever/particlespeed/doy25/w0025mday_summer.csv');
-[~,~,wt1s] = importw('/Volumes/home/mdever/particlespeed/doy25/w1mday_summer.csv');
-[~,~,wt5s] = importw('/Volumes/home/mdever/particlespeed/doy25/w5mday_summer.csv');
+[~,~,wt0025s] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_summer.csv');
+[~,~,wt1s] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_summer.csv');
+[~,~,wt5s] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_summer.csv');
 
-[~,~,wt0025w] = importw('/Volumes/home/mdever/particlespeed/doy25/w0025mday_winter.csv');
-[~,~,wt1w] = importw('/Volumes/home/mdever/particlespeed/doy25/w1mday_winter.csv');
-[~,~,wt5w] = importw('/Volumes/home/mdever/particlespeed/doy25/w5mday_winter.csv');
+[~,~,wt0025w] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_winter.csv');
+[~,~,wt1w] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_winter.csv');
+[~,~,wt5w] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_winter.csv');
 
 %% Set colors for each class
 color0025 = [215,48,39]/256;
@@ -62,7 +62,7 @@ totalBw = sum(N0025w.*B0025_4)+sum(N1w.*B1_4)+sum(N5w.*B5_4);
 totalF = sum(N0025s(E<=0).*B0025_4.*E(E<=0))+sum(N1s(E<=0).*B1_4.*E(E<=0))+sum(N5s(E<=0).*B5_4.*E(E<=0));
 totalFw = sum(N0025w(Ew<=0).*B0025_4.*Ew(Ew<=0))+sum(N1w(Ew<=0).*B1_4.*Ew(Ew<=0))+sum(N5w(Ew<=0).*B5_4.*Ew(Ew<=0));
 
-figure('position',[15 150 2119 1000])
+figure('position',[15 150 2119 1361])
[…]

### 2019-06-22 size_differentiated_export.tex
Updates from Overleaf

@@
 Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
-	\includegraphics[width = 1\linewidth]{figures/Fig6.png}
+	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
 	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release, in the Winter experiment.
@@
 \end{figure}
-
- \fixme{main points of new figure 8:
-\begin{itemize}
-    \item The impact of remineralization is three-fold: (1) it affects the total amount of biomass, as biomass is slowly remineralized - as illustrated by the decrease in area below the curves.
-(2) It shifts the PDFs of relative biomass as a function of vertical velocity towards slower vertical velocities.
-that is because, as they remineralize, the particles slow down.
-This has less of an impact on slower-sinking particles, as they are already sinking slowly anyway, so their PDFs don't change much, and the resulting downward biomass flux remains relatively large.
-faster-sinking particles, however, are more affected by the remineralization process, as their total vertical velocity shifts from gravitationally driven to advectively driven.
-as a result, their associated downward relative biomass flux is greatly decreased.
-Slow-sinking particles dominate the downward relative flux of biomass in both the summer and winter in the presence of remineralzation, as opposed to just the summer when remineralization is not included.
-\end{itemize}
-}
 

### 2019-06-25 size_differentiated_export.tex
Updates from Overleaf

@@
 For the purpose of this study, only the relative amount of biomass is relevant.
-For simplicity, we therefore define a normalized biomass unit as $B_0=$ 1.
+For simplicity, we define a normalized biomass unit for $\xi =3$ as $B_0=$ 1.
+The values taken by $B_0$ for other Junge slopes $\xi$ are computed under the condition that the total amount of biomass is kept constant (Figure \ref{fig: sinking_velocity_spectrum}b).
 
@@
 Both model experiments described above were then used to investigate the relationship between ocean dynamics and particle downward flux, using Lagrangian particle-tracking.
-Downward particle flux is expected to be a combination of their sinking velocity and the vertical advective currents affecting the particle along its pathway.
+Domain-averaged, downward particle flux is expected to be a combination of the flux driving by gravitational sinking ($\left<w_sB\right>$), and by the vertical advective currents affecting the particle along its pathway ($\left<wB\right>$).
 The deviation in particle depths from the traditional one-dimensional gravitationally driven model is shown in Figure \ref{fig: particle_depth_distribution}d for both summer and winter cases.
 In the summer, the PDF of particle density versus depth remains relatively narrow through time, and is centered on a depth level that can be predicted using a simple 1D gravitational model (see shaded curves in Figure \ref{fig: particle_depth_distribution}).
-PDFs of particle density also vary little among particles classes with different sinking velocities, suggesting that downward fluxes of particles is greatly dominated by gravitational settling and is not subject to significant vertical ocean currents.
+The spread in the particle density also vary little among particle classes with different sinking velocities, suggesting that downward fluxes of particles is greatly dominated by gravitational settling and is not subject to significant vertical ocean currents.
 
@@
 
-In the winter, however, the PDF of particle density versus depth is wider, in agreement with the stronger vertical ocean currents occurring in the winter (see Figure \ref{fig: dynamics}).
-The deviation in the downward particle flux from the traditionally considered 1D gravitational model can be seen in Figure \ref{fig: particle_depth_distribution} (panels (a)-(c)).
+In the winter, however, PDFs of particle density versus depth is wider, in agreement with the stronger vertical ocean currents occurring in the winter (see Figure \ref{fig: dynamics}).
+A top-view of the deviation in the downward particle flux from the traditionally considered 1D gravitational model can be seen in Figure \ref{fig: particle_depth_distribution} (panels (a)-(c)).
 Slower-sinking particles deviate more than faster-sinking particles, exhibiting median depth anomalies up to 50 m.
 This is due to the fact that slower-sinking particles spend more time in the mixed layer, where most of the stronger vertical currents tend to occur (Figure \ref{fig: dynamics}).
-An interesting result emerges from the spatial distribution of the depth-anomaly: both positive (where particles are shallower than expected) and negative (particles are deeper than expected) anomalies are organized into features with a length-scale $\mathcal{O}$(1-10 km).
-This further highlights the importance of winter submesoscale circulation for vertical fluxes of particles and their associated .%, which is explicitly shown in Figure \ref{fig: biomass_export}.
+An interesting result emerges from the spatial distribution of the depth-anomaly: both positive (i.e., particles are shallower than expected) and negative (i.e., particles are deeper than expected) anomalies are organized into features with a length-scale $\mathcal{O}$(1-10 km).
+This further highlights the importance of winter submesoscale circulation for vertical fluxes of particles.%, which is explicitly shown in Figure \ref{fig: biomass_export}.
 
-A relative amount of biomass is associated to the particles using equation \ref{eq: biomassjungeslope}.
-The PDF of relative biomass as a function of the vertical velocity is shown in Figure \ref{fig: biomass_export}.
+A relative amount of biomass is associated to the particles using Equation \ref{eq: biomassjungeslope}.
+PDFs of relative biomass as a function of the vertical velocity is shown in Figure \ref{fig: biomass_export}.
 Following the traditional paradigm derived from the simple 1D gravitational model, the downward flux of biomass in the summer is dominated by faster-sinking particle classes capable of carrying particulate material downwards more efficiently.
@@
 While significant, the impact of a change in the Junge slope in summer conditions does not challenge the dominant role played by faster-sinking particles.
-This result can be explained by the fact that, in the summer, vertical velocities are weak and vertical biomass fluxes are therefore gravitationally-driven.
+This result can be explained by the fact that, in the summer, vertical velocities are weak and vertical biomass fluxes are therefore gravitationally-driven ($\left<w_sB\right> > \left<wB\right>$).
 
@@
 
-In the winter, the PDFs of relative biomass as a function of vertical velocities present a much larger spread, with velocity magnitudes exceeding 50 m/day.
+In the winter, PDFs of relative biomass as a function of vertical velocities present a much larger spread, with velocity magnitudes exceeding 50 m/day.
 For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.1\% in the summer to about 4\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes.
-Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass.
+Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass (Figure \ref{fig: biomass_export}b).
 When winter ocean dynamics are coupled with a steeper Junge slope, however, slower-sinking particles largely dominate the downward biomass flux.
 In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 80\% of the biomass flux.
+
+Our results show that both a steepening of the particle size spectra and the presence of submesoscale dynamics can enhance the contribution of slower-sinking particles to the downward biomass flux.
+While the former is simply due to an increase in particle density in slower-sinking particle classes, the latter is attributed to the larger vertical velocity generated by submesoscale instabilities.
+When both are combined, as expected in the wintertime, slower-sinking particles then become the leading contributor to the downward biomass transport.
+However, slower-sinking particles are generally expected to remineralize on timescales shorter than their export timescale, fueling the argument that the focus should be upon faster-sinking particle classes.
+The impacts of remineralization on export are thus considered in the following section to test the robustness of the findings.
 
@@
 
-The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role of slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}).
+% The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role of slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}).
 This is a logical result given the observed increase in the particle export flux when submesoscale features are present (Figure \ref{fig: particle_export}).
@@
 
- Both ocean dynamics at submeso-scales and the Junge slope were identified as key factors impacting the respective role played by different particle classes in driving downward biomass fluxes.
+ Both submesoscale dynamics and the Junge slope were identified as key factors impacting the respective role played by different particle classes in driving downward biomass fluxes.
 Simple Lagrangian particles were used to isolate the effects of these two factors.
@@
 A remineralizing behavior was therefore implemented for the Lagrangian particles, using Equation \ref{eq: sinking_velocity_remin}, to investigate the impact that remineralization processes have on our findings.
-The traditional paradigm relies on the fact that slow-sinking particles tend to fully remineralize over shorter timescales, further enhancing the importance of faster-sinking particles classes in driving downward biomass fluxes.
-While this paradigm holds for flatter Junge slope, where the biomass content is dominated by faster-sinking particles, it becomes inadequate at steeper slopes.
+The traditional paradigm relies on the fact that slow-sinking particles tend to fully remineralize over short timescales, further enhancing the importance of faster-sinking particles classes in driving downward biomass fluxes.
+While this paradigm holds for flatter Junge slope, where the biomass content is dominated by faster-sinking particles, it becomes unfit at steeper slopes.
 
- Figure \ref{fig: biomass_export_remin} shows the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without remineralization processes.
-As expected, the main impact of implementing particle remineralization is a decrease in the total amount of biomass through time \fixme{refer to Fig 9?}.
-
- During summertime and in the absence of remineralization, downward fluxes of biomass are dominated by faster-sinking particles, even for steeper Junge slope.
-This is due to the fact that the flux of biomass $\left<wB\right> = \left<w_sB\right> + \left<w_aB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content.
-This is characteristics of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes.
-Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize.
-This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where the PDFs of relative biomass per particle class are centered over lower vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}.
-As a result, the gravitationally-driven term $\left<w_sB\right>$ becomes small, and the downward flux of biomass is generally advectively-driven.
-The advectively-driven component of the biomass fluxes is uniform across particle classes, as it only depends on ocean currents.
-Thus, in a advectively-driven system where $\left<w_sB\right> << \left<w_aB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
-This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a).
-When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c).
-As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics.
-Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes.
-
- These results highlight the importance in considering slower-sinking particle classes when considering downward biomass fluxes.
-It also demonstrates that, contrarily to the traditional paradigm, remineralization processes enhance the role played by slower-sinking particles in biomass fluxes, in cases where the biomass spectrum slope is negative.
-
- The timescales over which the system transitioned from an gravitationally-driven to an advectively-driven system depends on the remineralization model used.
+ Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without the remineralization scheme.
+\fixme{As expected, the main impact of implementing particle remineralization is a decrease in the total amount of biomass through time} \fixme{refer to Fig 9?}.
 
@@
 \end{figure}
+
+ As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization.
+This is due to the fact that the flux of biomass $\left<w_{tot}B\right> = \left<w_sB\right> + \left<wB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content per particle.
+This is characteristic of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes.
+Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize.
+This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}.
+As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}).
+In a advectively-driven system where $\left<w_sB\right> < \left<w_B\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
+This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a).
+When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c).
+As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics (82\%; see Figure \ref{fig: biomass_export_remin}b).
+Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (87\%; see Figure \ref{fig: biomass_export_remin}d).
+
+ These results highlight the importance in considering slower-sinking particle classes when considering downward biomass fluxes.
+It also demonstrates that, contrarily to the traditional paradigm, remineralization processes enhance the role played by slower-sinking particles in biomass fluxes, in cases where the biomass spectrum slope is negative.
+
+ The timescales over which the system transitioned from an gravitationally-driven to an advectively-driven system depends on the remineralization model used.
 
@@
 
-\subsection{Particle export}
+\subsection{Downward Fluxes}
 \label{sec: discussion_particle}
 
-Analyses of particle tracking experiments reveal that the role played by slower-sinking particles in POC export depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope $\xi$).
+Analyses of particle tracking experiments reveal that the role played by slower-sinking particles in downward particulate fluxes depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope $\xi$).
 
@@
 In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer.
-This change in dynamics has a clear impact on the export flux of all sinking-velocity classes modeled in this experiment.
-Particle export within a sinking-velocity class is hastened and occur over longer timescales.
-In fact, particles tend to reach the export depth over shorter timescales than in the absence of submesoscale dynamics.
-This is maybe the most significant result, as export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale; The former evidently needing to be shorter than the latter to efficiently export POC.
-However, while some particles are exported faster, the rest of the particles within a sinking-velocity class are exported over longer timescales.
-This is due to upward vertical currents, re-suspending material that would otherwise sink, and thus delay its export (Figure \ref{fig: particle_export}).
+This seasonal change in dynamics is consistent with recent observations \citep{Thompson_2016, Buckingham_2016}, and models \citep{Brannigan_2015, Callies_2015, Rocha_2016}, characterizing the seasonal cycle of submesoscale dynamics.
+The winter intensification in submesoscale dynamics was proven to have an important impact on the downward flux of all sinking-velocity classes modeled in this experiment.
+\fixme{export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale; The former evidently needing to be shorter than the latter to efficiently export POC.
+Not sure I should talk about timescales anymore}
 
-In the summer, the gravitationally-driven export mechanism efficiently exports faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles.
-In the winter, however, the export mechanisms is advectively-driven, which leads to a slightly weaker export flux of faster-sinking particles than in the summer due to resuspension, but a much larger export flux of slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: biomass_export}).
-These two competing mechanisms raise the question as to which process is most efficient in exporting particulate material below the winter mixed layer.
+In the summer, the gravitationally-driven dynamics efficiently drives a downward flux dominated by faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles.
+In the winter, however, vertical fluxes tend to be advectively-driven, which leads to a slightly weaker downward flux of faster-sinking particles than in the summer due to resuspension, but a much larger flux of slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: biomass_export}).
+These two seasonal mechanisms raise the question as to which process is most efficient in driving a downward flux of particulate material.
+
+In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesocale dynamics increase the contribution of slower-sinking particle classes to the downward biomass flux.
+This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}).
+This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \citep{Kostadinov_2009, White_2015}.
+The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations describing the relationships between particle size, sinking velocity, and biomass content used in this study.
+Nevertheless, our results demonstrate that
 
@@
 In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient (Figure \ref{fig: biomass_export}).
+
 Over the course of our simulation, the biomass export flux is consistently enhanced when $\xi = 4$ in the presence of submesoscale dynamics.

### 2019-06-25 size_differentiated_export.tex
Updates from Overleaf

@@
 
-Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics representing conditions in the northeast Pacific in the summertime.
+Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics representing conditions in the Northeast Pacific in the summertime.
 Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1).
@@
 \end{table}
-
-% \begin{table}
-% \caption{Time of the Transition Between Phase 1 and Phase 2$^{a}$}
-% \centering
-% \begin{tabular}{l c}
-% \hline
-%  Run  & Time (min)  \\
-% \hline
-%   $l1$  & 260   \\
-%   $l2$  & 300   \\
-%   $l3$  & 340   \\
-%   $h1$  & 270   \\
-%   $h2$  & 250   \\
-%   $h3$  & 380   \\
-%   $r1$  & 370   \\
-%   $r2$  & 390   \\
-% \hline
-% \multicolumn{2}{l}{$^{a}$Footnote text here.}
-% \end{tabular}
-% \end{table}
 
@@
 In this study, the impact of remineralization is thus considered through the implementation of a time-dependent sinking velocity (Equation \ref{eq: sinking_velocity_remin}).
-While particles classes are classified based on their initial sinking-velocity, it is worth noting that over the length of the particle-tracking experiments that include remineralization (28 days), particle sinking speeds slow down to 10\% of their initial velocity, which correspond to 3.1\5.
+While particles classes are classified based on their initial sinking-velocity, it is worth noting that over the length of the particle-tracking experiments that include remineralization (28 days), particle sinking speeds slow down to 10\% of their initial velocity.
 
@@
 
-Two model experiments are designed to capture different dynamical conditions observed in the northeast Pacific Ocean in summer and winter.
+Two model experiments are designed to capture different dynamical conditions observed in the Northeast Pacific Ocean in summer and winter.
 \textit{Papa\_summer} is initialized in early spring (doy 105) when the water column is characterized by a relatively deep mixed layer ($\sim$100 m) and a halocline located between 100 and 150 m (Figure \ref{fig: Papa_summer}).
@@
 A comparison between model outputs and monthly-averaged density profiles from underwater gliders collected in June and July over the period 2008-2009 yields correlation coefficients of $r = 0.87$ and $r = 0.88$, respectively.
-These high correlation suggest that \textit{Papa\_summer} numerical experiment captures the vertical spring and summer conditions in the northeast Pacific Ocean.
+These high correlation suggest that \textit{Papa\_summer} numerical experiment captures the vertical spring and summer conditions in the Northeast Pacific Ocean.
 
@@
 	\centering
-	%\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
-	%\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right).
-Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain.
-For each sinking-velocity class, the net particle flux is shown by a thick line.
-Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
 	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
@@
 	\centering
-	%\includegraphics[width = 1\linewidth]{figures/Fig6b_biomass_export_flux.png}
-	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for two different Junge slopes: $\xi =$ 4 (solid lines) and $\xi =$ 2 (dashed lines; see Figure \ref{fig: sinking_velocity_spectrum}).
-Biomass export flux for the 5 m/day sinking-velocity class remains unchanged, as it is used as a reference class in Equation (\ref{eq: biomassjungeslope}) ($w_{s_0} = 5$ m/day).}
 	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
@@
 
- %In this study, particles are considered ``exported" once transported below the depth of the winter mixed layer, which roughly corresponds to the 100 m depth horizon at Station Papa.
-Choosing the winter mixed layer as the export depth is most appropriate compared to other commonly chosen depth horizons (e.g., compensation depth, euphotic depth, etc.), as it reduces the chances of particles being re-entrained into the mixed layer the following winter \citep{Palevsky_2016,Palevsky_2018}.
-We first consider the case of conservative particles that do not remineralize in order to isolate the effects of ocean dynamics on export.
-
-%The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
-As expected, the faster-sinking particles are exported earlier than slower-sinking particles.
-For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%).
-In fact, time series of particle export flux closely follow the curves derived from considering gravitational sinking only (Figure \ref{fig: particle_export}a).
-The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).
-
-%\fixme{mention deviations from dashed line. Mention resuspension (less than 1\%) for slow-sinking particles only due to vertical velocities.}
-%The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}.
-As expected, the faster-sinking particles are exported earlier and in larger proportions.
-For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%).
-In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking only (Figure \ref{fig: particle_export}).
-
-%Time series of particle fluxes in \textit{Papa\_winter} present major differences (Figure \ref{fig: particle_export}b).
-In every sinking-velocity class, particles reach the export horizon faster than expected from gravitational sinking.
-This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day.
-Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now exhibit a significant net downward flux within the first 15 days of the simulation.
-For example, over 20\% of particles sinking at 0.5 m/day is cumulatively exported within the first 28 days in \textit{Papa\_winter}, versus less than 5\% in \textit{Papa\_summer}.
-However, particle export is now stretched over longer periods of time due to particle resuspension.
-In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a).
-These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet).
-However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring in the presence of submesoscale dynamics.
-%\fixme{do those irreversible pathways due to sinking out of the reversible pathway, or due to irreversible mechanisms?}
-
-%The corresponding biomass export fluxes demonstrate that, in the presence of submesoscale dynamics, slow-sinking particles significantly contribute to the total export flux over timescales of days (Figure \ref{fig: biomass_export}b).
-The quasi steady-state reached in the biomass export flux of the three slowest sinking-velocity classes suggests that biomass export is driven by advective processes rather than gravitational sinking ($w_s<w_{flow}$).
-However, the 5 m/day particle class still exhibits a peak in the biomass export flux coinciding with the peak expected from a simple one-dimensional gravitational sinking model, suggesting that the export for this sinking-velocity class remains mostly gravitationally-driven.
-
-%As anticipated from Figure \ref{fig: sinking_velocity_spectrum}, the Junge slope $\xi$ is a determining parameter that affects the contribution of slower-sinking classes in the presence of submesoscale dynamics.
-Figure \ref{fig: biomass_export} shows the biomass export fluxes in normalized units for two different Junge slopes.
-The contribution from slow-sinking particles to the total biomass export flux expectedly decreases with the Junge slope.
-The decrease in biomass export flux is constant through time and can be predicted using Equation (\ref{eq: biomassjungeslope}):
-
-%\begin{equation}
-%    \frac{B_{\xi_1}(w_s)}{B_{\xi_2}(w_s)} = \left(\frac{w_s}{w_{s_0}}\right)^{\frac{\xi_2-\xi_1}{2}}
-    %\frac{Flux\times B_{\xi_1}}{Flux\times B_{\xi_2}} = \frac{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_1/2}}{Flux \times B_0 \times \left(\frac{w_s}{w_s_0}\right)^{3-\xi_2/2}} = \left(\frac{w_s}{w_s_0}\right)^{(\xi_2-\xi_1)/2}
-%\end{equation}
-%Using $\xi_1 = 2$ and $\xi_2 = 4$, as depicted in Figure \ref{fig: biomass_export}, the decrease in biomass export is 80\%, 90\%, and 99.5\% for the 1, 0.5 and 0.025 m/day particle classes, respectively.
-%\fixme{The evolution of the biological community through time that would affect the slope of the size spectrum also has direct consequences on the export of the slower-sinking particles.}
-
-%The presence of submesoscale dynamics therefore both hastens particle export, and increases the number of exported slow-sinking particles, between a few percent and tens of percents, depending on the sinking-velocity class.
-This has large implications on the amount of biomass exported, as slower-sinking particles tend to be far more numerous than faster-sinking particles, despite containing less biomass per particle (i.e., $\xi >3$; see Figure \ref{fig: sinking_velocity_spectrum}).
-%While the particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).
-
-% The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role of slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}).
-This is a logical result given the observed increase in the particle export flux when submesoscale features are present (Figure \ref{fig: particle_export}).
-The sinking class dominating export, however, is highly dependent on the Junge slope.
-As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases.
-For example, after 28 days, the 1 m/day particle class cumulatively exported 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.
-However, slow-sinking particles are generally expected to remineralize on timescales shorter than their export timescale.
-The impacts of remineralization on export are considered in the following section.
-
  \subsection{Particle Remineralization}
@@
  Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without the remineralization scheme.
-\fixme{As expected, the main impact of implementing particle remineralization is a decrease in the total amount of biomass through time} \fixme{refer to Fig 9?}.
-
+As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization.
+This is due to the fact that the flux of biomass $\left<w_{tot}B\right> = \left<w_sB\right> + \left<wB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content per particle.
+This is characteristic of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes.
+Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize.
+This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}.
+As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}).
    %FIG8
- \begin{figure}[t]
+ \begin{figure}[t!]
 	\centering
-	%\includegraphics[width = 1\linewidth]{figures/Fig7_biomass_export_flux_remin.png}
-	%\caption{Net biomass flux in normalized units in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right), for $\xi=4$.
-Dashed lines represent the case without remineralization, while solid lines include the remineralization scheme described in Section \ref{sec: remin_scheme}.}
 	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
@@
 \end{figure}
-
- As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization.
-This is due to the fact that the flux of biomass $\left<w_{tot}B\right> = \left<w_sB\right> + \left<wB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content per particle.
-This is characteristic of a gravitationally-driven system, where settling velocity dictates the contribution to downward fluxes.
-Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize.
-This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}.
-As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}).
 In a advectively-driven system where $\left<w_sB\right> < \left<w_B\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
@@
 
- %Including remineralization of particles significantly impacts the relative importance of sinking and advection to export for each particle class.
-In \textit{Papa\_summer}, particle export associated with a specific sinking-velocity class is delayed when remineralization is implemented, because particles decelerate as they are remineralized (see Equation (\ref{eq: sinking_velocity_remin}) and Figure \ref{fig: biomass_export_remin}).
-In our simulations, particles sinking at 5 m/day reach the export horizon about 3 hours later when remineralization is included.
-The impact of remineralization intensifies as the sinking velocity weakens: particles sinking at 1 m/day reach the export horizon 9.5 days later when remineralization is implemented.
-
- %The biomass export flux is also reduced compared to the case with no remineralization.
-In a gravitationally-driven system such as during the summer in the northeast Pacific, captured in \textit{Papa\_summer}, the impact of remineralization on the amount of biomass exported grows as the sinking velocity decreases.
-In fact, in \textit{Papa\_summer} with no remineralization, several sinking-velocity classes contribute to the biomass export over different timescales (dash lines in Figure \ref{fig: biomass_export_remin}).
-Once remineralization is implemented, no particles in the slowest sinking class (0.5 m/day) reach the export horizon and the contribution of the 1 m/day class is reduced by several orders of magnitude.
-
- %In \textit{Papa\_winter}, particles of all sinking-velocity classes tend to be exported over shorter timescales than in \textit{Papa\_summer} due to stronger vertical velocities (Figure \ref{fig: particle_export}).
-The difference in the biomass export flux between the cases with and without remineralization is therefore relatively small for the first 5 days of the time series, as particles have not had time to significantly remineralize yet but are already being exported.
-As particles age, remineralization has an increasing impact and the difference in the biomass export flux increases at a rate controlled by the remineralization rate defined in (\ref{eq: remin_scheme}).
-An interesting result to be noticed is the fact that, when $\xi = 4$ and remineralization is implemented, the biomass export flux of the 0.025 m/day sinking-velocity class exceeds the biomass export flux from both the 0.5 and 1 m/day sinking-velocity classes.
-This result only occurs when a negative slope of the biomass spectrum is combined with remineralization.
-
 \section{Discussion}
@@
 \label{sec: Discussion_model}
-\textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the northeast Pacific Ocean.
+\textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the Northeast Pacific Ocean.
 After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients to observations from underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}).
@@
 The winter intensification in submesoscale dynamics was proven to have an important impact on the downward flux of all sinking-velocity classes modeled in this experiment.
-\fixme{export from any sinking-velocity class is characterized by two competing timescales: its export timescale and its remineralization timescale; The former evidently needing to be shorter than the latter to efficiently export POC.
-Not sure I should talk about timescales anymore}
 
@@
 
-In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesocale dynamics increase the contribution of slower-sinking particle classes to the downward biomass flux.
+In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesoscale dynamics increase the contribution of slower-sinking particle classes to the downward biomass flux.
 This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}).
 This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \citep{Kostadinov_2009, White_2015}.
-The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations describing the relationships between particle size, sinking velocity, and biomass content used in this study.
-Nevertheless, our results demonstrate that
+The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content.
+Nevertheless, our results demonstrate the importance of resolving the lower range of the particle spectrum when measuring vertical fluxes, especially when submesoscale dynamics are active.
+It also highlights the importance of better constraining the relationships linking particle size, sinking velocity, and biomass content.
 
-%% This section answers the questions above in terms of total amount of biomass efficiently exported with and without remineralization 
-In the absence of remineralization, the net effect of submesoscale dynamics on biomass export depends on the Junge slope coefficient (Figure \ref{fig: biomass_export}).
-
-Over the course of our simulation, the biomass export flux is consistently enhanced when $\xi = 4$ in the presence of submesoscale dynamics.
-Therefore, export flux is only enhanced in the presence of submesoscale dynamics if the slope of the size spectrum is steep enough to compensate for the re-suspension of faster-sinking particles by upwards vertical currents at submesoscales.
-%Talk about the asymmetry in the vertical velocity PDF (see Figure \ref{fig: dynamics})?
-Showing stronger, more localized downwelling, and broader and weaker upwelling?
-
-Introducing remineralization processes significantly decreases the biomass export flux.
-Counter-intuitively, however, remineralization processes further strengthen the impact of submesoscale dynamics on export.
-The difference between summertime and wintertime biomass fluxes is even larger when remineralization processes are included.
-This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as remineralization tends to decelerate these particles and thus prolongs their export timescales.
-In the summer, almost the entirety of the sinking velocity spectrum is therefore affected as export is gravitationally-driven.
+Introducing remineralization processes significantly decreases the biomass flux.
+Counter-intuitively, however, the implementation of a remineralization scheme further strengthen the role played by slower-sinking particles in the biomass flux (Figure \ref{fig: biomass_export_remin}.
+This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as these particles decelerate as they remineralize.
+In the summer, all particle classes are similarly affected by the remineralization scheme as downward fluxes are gravitationally-driven.
 In the winter, however, slower-sinking particles are exported through advective processes.
@@
 
-%% this part discusses the respective contributions of the different sinking-velocity classes
-The contribution of a particle class to POC export generally increases with the sinking-velocity.
-That is, faster-sinking particles tend to dominate the export signal.
-However, this tendency can be reversed if the following condition is satisfied:
-
-\begin{equation}
-    N_{slow} > N_{fast} \times \left(\frac{w_{s_{fast}}}{w_{s_{slow}}}\right)^{\frac{3 - \xi}{2}}
-    \label{eq: condition}
-\end{equation}
-where $N$ is the number of simulated particles exported, $w_s$ is the sinking velocity and $\xi$ is the Junge slope coefficient (see Equation (\ref{eq: powerlaw_radius})).
-The number of exported slower-sinking particles must therefore be large enough to compensate for the smaller biomass content than faster-sinking particles.
-
-In a gravitationally-driven system (i.e., weak submesoscale activity), this can only be achieved by having  $N_{slow} \sim N_{fast}$ and $\xi>3$, as there are no mechanism capable of selectively exporting slower-sinking particles (i.e., $N_{slow} \leq N_{fast}$).
-Junge slopes greater than 3 are regularly observed in the ocean \citep{Kostadinov_2009, White_2015}.
-Our results suggest that, in these conditions, the export of biomass is dominated by an intermediate sinking-velocity class that sinks fast enough to be 100\% exported ($N_{slow} = N_{fast}$; see Figure \ref{fig: export_cartoon}a).
-Because of the negative slope in the biomass spectrum, the contribution to export of any particle class sinking at a faster rate will be smaller.
-The intermediate class responsible for the largest part of the export signal will vary with time and space as it depends on the parameter $\xi$, as well as on the export depth.
-As $\xi$ increases, the sinking-velocity of the dominant class decreases (see Equation (\ref{eq: condition})).
-A deeper export depth would have the opposite effect and increase sinking-velocity of the dominant class (Figure \ref{fig: export_cartoon}a).
-%Implementing remineralization processes only shifts the curve shown in Figure \ref{fig: export_cartoon}a towards faster-sinking classes: as particle remineralize, a larger portion of the sinking-velocity spectrum will not contribute to POC export, and a faster initial sinking-velocity is required for the export timescale to be shorter than the remineralization timescale.
-
-%FIG9
- \begin{figure}[ht!]
-	\centering
-	\includegraphics[width = .65\linewidth]{figures/Fig9_cartoon_meso}\\[.2cm]
-	\includegraphics[width = .65\linewidth]{figures/Fig9_cartoon_submeso}
-	\caption{Schematics illustrating the respective contribution to export of particles with different sinking velocities for $\xi > 3$ in (a) a gravitationally-driven system (i.e., weak submesoscale dynamics), and (b) an advectively-driven system (i.e., strong submesoscale dynamics).}
-	\label{fig: export_cartoon}
-\end{figure}
-
-In a system affected by submesoscale dynamics, localized strong downwelling vertical currents are generated.
-This effectively shortens the export timescale of slower-sinking particles, entering a regime where export timescales are shorter than remineralization timescales (Figure \ref{fig: export_cartoon}b).
-In this regime, slower-sinking particles significantly contribute to POC export, and can even dominate the export signal for large $\xi$.
-This scenario is captured in one of the Lagrangian experiment and shown in Figure \ref{fig: biomass_export}b, where the contribution to biomass export from the 0.025 m/day sinking class exceeds the one from the 0.5 m/day sinking class.
-This surprising result further emphasizes the key role played by slow-sinking particles in POC export, especially in the presence of submesoscale dynamics and large $\xi$.
+The result of this study suggest that slow- and non-sinking particles must be considered when studying the downward flux of particulate matter in the upper ocean.
+The patchiness associated with both particle production and submesoscale features poses a real observational challenge to properly resolve vertical fluxes.
+Based on our findings, subsequent studies should focus on testing the impact of patchiness on vertical fluxes: In the wintertime, when size spectral slope is steep and submesoscale dynamics most active, vertical fluxes could be grossly underestimated depending on the level of co-occurrence between particle production and stronger vertical currents.
 
@@
 \begin{enumerate}
-\item Ocean dynamics in the subpolar Pacific northeast exhibit a seasonal cycle with low submesoscale activity in the summertime, and more submesoscale features in the wintertime.
-Submesoscale dynamics generate larger, and asymmetrical, vertical currents leading to an export mechanisms dominated by advective processes, as opposed to gravitationally-driven in the summertime.
+\item Ocean dynamics in the subpolar Northeast Pacific exhibit a seasonal cycle with low submesoscale activity in the summertime, and more submesoscale features present in the wintertime.
+Submesoscale dynamics generate larger, and asymmetrical, vertical currents leading to a vertical biomass flux driven by advective processes, as opposed to gravitationally-driven in the summertime.
 
-\item Submesoscale dynamics generally enhance export by increasing the contribution of slower-sinking particles to POC export by increasing the number of particle exported through advective sinking.
-The contribution of slower-sinking particles subducted through irreversible ageostrophic processes to particle export is at least significant, and can be dominant in specific conditions.
-\item Contribution of slower-sinking particles to POC export depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class.
-Three cases emerge in this study:
+\item Submesoscale dynamics generally enhance downward fluxes by increasing the contribution of slower-sinking particles to the total flux by increasing the number of particle advected downward by ocean currents.
+The contribution of slower-sinking particles to the total flux is found to be at least significant, and can be dominant in certain conditions.
+\item Contribution of slower-sinking particles to downward biomass fluxes export depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class.
+Two cases emerge from this study:
 \begin{enumerate}
-	\item If the Junge slope is smaller than 3, larger particles contribute most to export independently of flow dynamics, as there are no mechanism capable of selectively exporting slower-sinking particles.
-	\item If the Junge slope equals 3, the respective contributions of the different size classes depend on the dynamical characteristics of the flow, as it influences the number of particles being exported.
-If 100\% of particles is exported in all sinking classes, then each class contributes equally to POC export.
-	\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become the determining factor on which classes dominate: in a mostly geostrophic flow with weak vertical velocities, an intermediate sinking-velocity class will dominate POC export.
-In a flow with ageostrophic circulation leading to larger vertical velocities, slower sinking classes can potentially dominate export.
+	\item If the Junge slope is smaller than 3, larger particles contribute most to vertical biomass fluxes independently of flow dynamics, as there are no mechanism capable of selectively advecting slower-sinking particles.
+The system is described as gravitationally-driven.
+	\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become the determining factor on which particle classes dominate the downward fluxes: as submesoscale dynamics become more active, an ageostrophic circulation leading to larger vertical velocities develops.
+In these conditions, downward biomass fluxes are largely driven by the slower-sinking particle classes.
 	\end{enumerate}
-\item Remineralization processes reduce the contribution of slower-sinking particles when export dynamics are dominated by gravitational sinking (i.e., in a geostrophic flow).
-As flow dynamics become ageostrophic, advective downward transport leads the export and remineralization processes have a limited impact.
+\item Remineralization processes logically reduce the amplitude of biomass fluxes.
+However, it unexpectedly enhances the role played by slower-sinking particles as the impact of remineralization is larger on faster-sinking particles by affecting both biomass content and sinking velocity.
 \end{enumerate}
-
-%These conclusions demonstrate the importance of resolving a large portion of the particle size spectrum to properly quantify export, especially in dynamical regimes where strong ageostrophic circulation is present.
 
@@
 
-%TAB2
-%\begin{table}[]
-%	\caption{Range of contributions (min-max) to the total amount of biomass exported per size class in both \textit{Papa\_summer} and \textit{Papa\_winter}.}
-%	\label{tab: biomass_contribution}
-%	\centering	
-%	\begin{tabular}{|cc|c|c|c|c||c|c|c|c|}
-%		\hline
-%		&           & \multicolumn{4}{c||}{\textit{Papa\_summer}} & \multicolumn{4}{c|}{\textit{Papa\_winter}} \\
-%		\hline
-%		\multicolumn{2}{|c|}{sinking speed [m/day]} & 5               & 1             & 0.5          & 0.025     & 5              & 1            & 0.5          & 0.025       \\
-%		\hline\hline
-%		$\xi = 2$ & Remin OFF & 69-100\%     & 0-30\%     & 0-1\%     & 0\%       & 70-100\%    & 0-24\%    & 0-6\%     & 0\%         \\
-%		\rowcolor[HTML]{EFEFEF} 
-%		 & Remin ON  & 100\%           & 0\%           & 0\%          & 0\%       & 92-100\%    & 0-6\%     & 0-3\%     & 0-1\%    \\
-%		$\xi = 3$ & Remin OFF & 49-100\%     & 0-49\%     & 0-2\%     & 0\%       & 49-100\%    & 0-37\%    & 0-12\%    & 0-3\%    \\
-%		\rowcolor[HTML]{EFEFEF} 
-%		& Remin ON  & 100\%           & 0\%           & 0\%          & 0\%       & 78-100\%    & 0-11\%    & 0-9\%     & 0-6\%    \\
-%		$\xi = 4$ & Remin OFF & 30-100\%     & 0-68\%     & 0-3\%     & 0\%       & 25-99\%     & 0-43\%    & 0-20\%    & 0-25\%   \\
-%		\rowcolor[HTML]{EFEFEF} 
-%		& Remin ON  & 100\%           & 0\%           & 0\%          & 0\%       & 38-100\%    & 0-16\%    & 0-14\%    & 0-39\%  \\ 
-%		\hline
-%	\end{tabular}
-%\end{table}
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%
-%%%% OBSOLETE %%%%%
-%%%%%%%%%%%%%%%%%%%
-The main consequence of this result is that, when the biomass spectrum has a negative slope (i.e., $\xi>3$) ,
-
-It is impossible to obtain $N_{slow} > N_{fast}$
-
-In the absence of remineralization,
-
-In a gravitationally-driven system (i.e., weak submesoscale activity), contribution to export generally increases as sinking-velocity increases.
-This is true up to the point where the totality of the particles are exported: for an equal number of particle exported, the
-
-Generally, export is dominated by the contribution of faster-sinking particles.
-For a slower-sinking velocity class to contribute more to the export than a faster-sinking velocity class, the number of particles exported must satisfy:
-
-In the absence of remineralization, where all particles are eventually exported, this condition is only satisfied if $\xi>3$, that is if the biomass spectrum has a negative slope (see Figure \ref{fig: sinking_velocity_spectrum}).
-\fixme{While export will then always be dominated by faster-sinking particles, the contribution of slower-sinking particles varies greatly with the
-as a function of (1) the biomass spectral slope must be negative (i.e., $\xi>3$), and (2) the number of particles exported must be large enough.
-The number of particles to be exported for a slower-sinking velocity class to dominate export over a faster-sinking velocity class depend on the Junge slope and is determined by:
-Under those conditions, the contribution to export as a function of sinking speed is notc linear: increasingly faster-sinking classes contribute increasingly to export, as they physically export more particles, until the sinking speed above which 100\% of the particles are exported is reached.
-Above this threshold, the contribution to biomass export by increasingly faster-sinking particles decreasingly contribute to export, due to the negative slope in the biomass spectra.
-Despite the export being dominated by faster-sinking particles, this study demonstrates that in the presence of submesoscale activity, slower-sinking particles have the potential to significantly contribute to the total export.
-The slowest sinking-velocity class simulated in this study contributed to up to 13\% of the total biomass export in the presence of submesoscale dynamics, for $\xi = 4$.}
-
-The important threshold in the Junge slope highlighted in this study can be generally defined by the log-log slope between particle size and biomass content.
-In this study, we assume that biomass varies as the volume of the particle (B $\propto r^3$), thus obtaining a threshold of $\xi=3$.
-Using other relationships between biomass and particle size will not impact the main conclusions of this study, but will only affect the threshold at which slower-sinking particles contribute significantly to the export.
-
-\subsection{Impacts of  Particle Remineralization}
-\label{sec: discuss_remin}
-
-Remineralization processes introduce a time-dependency in the relationship between biomass and sinking-velocity.
-A simple, yet commonly-used, remineralization scheme was imposed to the particles.
-As one would expect, the main impacts of implementing a remineralization scheme is a decrease in the exported biomass across all sinking-velocity classes, as well as a prolonged export timescale.
-This is due to the fact that, as a particle remineralizes, its sinking-velocity decreases.
-Because the particle now takes more time to be exported, it further remineralizes, which in turn decreases the particle's sinking-velocity.
-In the summer, this self-reinforcing mechanism affects slower-sinking classes the most, and therefore significantly decreases their contribution to export.
-In the winter, remineralization also generally reduces the amount of biomass exported, although the impact is far less pronounced and affects all sinking-velocity classes similarly.
-This is explained by the different mechanism dominating export in the summer and winter: In the summertime, export is dominated by gravitational sinking, which is directly impacted by remineralization processes.
-In the wintertime, however, export is largely driven by advective sinking through the stronger downward currents observed in the submesoscale flow.
-Advective sinking being independent from remineralization processes, the biomass export is less affected than in the summertime.
-In fact, our analysis clearly shows that remineralization processes does not significantly impact the biomass export associated with slower-sinking velocity classes over the first 5 days of the simulations.
-
-Finally, a very interesting feature arose from implementing a remineralization scheme to the Lagrangian particles.
-In the winter and with $\xi =4$, the biomass exported by the slowest-sinking class (0.025 m/day) consistently exceeds the amount of biomass exported by slightly faster-sinking classes (0.5 and 1 m/day), despite a considerably smaller number of particles exported ($<4$\% vs.
-23\% and 73\%, respectively) This non-intuitive result emerges from the exponential characteristic of the remineralization scheme: the impact of remineralization thus increases with the sinking velocity.
-This result demonstrates that remineralization can, under specific circumstances, increase the role played by slower sinking-velocity classes.
-The necessary conditions involve a large Junge slope and strong submesoscale activity.

### 2019-08-26 size_differentiated_export.tex
Updates from Overleaf

@@
 
-\documentclass[draft,linenumbers]{agujournal2018}
+\documentclass[article,linenumbers]{agujournal2018}
 \usepackage{apacite}
@@
 %% ------------------------------------------------------------------------ %%
-\title{Size-differentiated Export in different Dynamical Regimes in the Ocean}
+\title{Size-differentiated Export in Different Dynamical Regimes in the Ocean}
 
@@
 
-%\begin{keypoints}
-%\item = enter point 1 here =
-%\item = enter point 2 here =
-%\item = enter point 3 here =
-%\end{keypoints}
+\begin{keypoints}
+\item Submesoscale dynamics enhance the contribution of slow-sinking particles to POC export, especially for steep particle size-spectrum slopes
+\item Remineralization processes intensify the role of slow-sinking particles, to the point where these particle sometime dominate POC export
+\end{keypoints}
 
@@
 \begin{abstract}
-% Mat: I think that even with the submesoscale mechanism, export is mainly driven by gravitational sinking. So I'm moving the "Traditionally" to later. 
-Export of particulate organic carbon (POC) is  mainly driven by gravitational sinking.
+Export of Particulate Organic Carbon (POC) is  mainly driven by gravitational sinking.
 Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux.
@@
 The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export.
-A steeper particle size spectrum, also increases the contribution of smaller, slower-sinking particles.
+A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles.
 Implementing a remineralization scheme generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven.
@@
 
-%{\color{red} NOTE: Following Roo's suggestion, I looked at the spectrum of biomass per velocity class vs time to see how it evolves.
-As Melissa suggested, it will be cool to include into a presentation, but I don't think it is worth including in the paper.
-I believe it would introduce too much additional concepts that would dilute the conclusions: the spectral shape is mostly determine by the pulse of particle crossing the export horizon.
-A constant reseeding of particles would be necessary to clearly put our point across using biomass spectra.}
-
 \section{Introduction}
 
-A major pathway transferring carbon from the atmosphere to the ocean is through photosynthesis and the production of Particulate Organic Carbon (POC) in the upper ocean.
+Photosynthesis in the sunlit upper ocean and the production of Particulate Organic Carbon (POC) takes up dissolved inorganic carbon and facilitates the uptake of CO$_2$ from the atmosphere.
+The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.
+%???
+Removed 'long time scales', or define it
+Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.
+
+Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth.
+Particles produced through primary and secondary production in the surface layer that are relatively large and fast-sinking, tend to sink out of the upper surface layer
+%below the export depth   ?? remove this because we have not defined 'export depth'?? 
+on timescales shorter than the timescale on which the particles get remineralized.
+It is reasonable to treat POC export as sinking-dominated if the vertical advective velocities in the ocean are weaker than the velocities associated with gravitational sinking.
+However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day.
+The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, which indicates $\mathcal{O}(10^8)$ greater abundance of small  particles than large particles.
+The biomass size spectrum, which indicates the distribution of biomass vs.
+particle size, tends to be flatter and variable in shape \citep{Sheldon72} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and varies, for example, between 2 and 3 depending on shape and porosity).
+Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction.
+Even though the sinking velocity $w_s$ of particles does not perfectly relate to particle size $l$, it is fair to assume  that  $w_s \sim l^n$ (with $n=2$ according to Stokes law, and $1<n<2$ for complex particle shapes).
+Due to this, as well as the fact that particles of organic matter are not very much greater in their densities than seawater, a significant fraction of the biomass sinks very slowly (at velocities less than tens of meters per day).
+When the gravitational sinking velocity of particles is comparable to (or smaller than) the vertical velocities in the flow field, the dynamics of the flow field can impact the trajectories and fate of the POC.
+Thus, depending on the flow dynamics, and the fraction of slow-sinking particulate biomass, the sinking of organic matter can be affected by the fluid flow in the ocean.
+
+Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior.
+For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \citep{vanHaren_2006, Waite_2016}.
+\cite{Omand_2015}  found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic.
+Advectively subducting plumes or filaments of high oxygen, chlorophyll and small POC (evidenced through backscatter) were detected from a suite of gliders during the North Atlantic Bloom experiment \citep{Briggs_2011, Alkire_2012}.
+Using model simulations to capture the process of eddy-driven subduction, \cite{Omand_2015} estimated the downward advective flux of non-sinking POC and parameterized it.
+The flux of fast-sinking particles consisting largely of diatoms was observed from backscatter and quantified separately \citep{Briggs_2011}.
+But, the estimates did not simultaneously account for a range of sinking particle velocities.
+Typically, particulate organic matter (POM) has a spectrum of sinking velocities and in order to understand its fate and export, we need to consider the biomass distribution as a function of the particle sinking velocity spectrum and its interaction with dynamics of the flow field in the ocean.
+
+A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012,Mahadevan_2016}.
+Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2008,Klein_2009,McWilliams_2016}.
+In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}.
+On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front.
+The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}.
+Enhanced vertical velocities can generate a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2000,Levy_2001}, or can significantly increase the export of POC to the ocean interior through downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.
+Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe these processes in-situ.
+
+The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
+Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities.
+However, despite progress on sampling and viewing particles in the ocean \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density.
+Depending on the fraction of  biomass in smaller particles (i.e., with slow sinking velocities), the impact of submesoscale dynamics on the export of POC is potentially significant.
+
+%The impact of submesoscale dynamics on the net biomass flux depends on the sinking velocity spectrum (or size spectrum if we assume that sinking velocities are related to size).
+A relatively large fraction of the biomass at slow sinking velocities leads to a greater dependence of the biomass flux on the flow field, whereas the converse, leads to less dependence on the flow dynamics.
+
+In this study, we account for a range of particle sinking velocities in a dynamic flow field. 
+We  rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale.
+Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior.
+Particles are released in two fundamentally different flow fields in terms of dynamics based on observed conditions in the Northeast Pacific: In the summer, where ocean dynamics are characterized by low Rossby numbers and weak vertical advective velocities, and in the winter, where ocean dynamics include submesoscale frontal structures and local Rossby numbers $\mathcal{O}$(1).
+Both simulations and the particle-tracking module are described in Section \ref{sec: Methods}.
+The impact of particles characteristics and ocean dynamics on the export of POC is quantified in Section \ref{sec: Results}, and discussed in Section \ref{sec: Discussion}.
+Section \ref{sec: Conclusions} summarizes the key conclusions of the study.
+
+%A major pathway transferring carbon from the atmosphere to the ocean is through photosynthesis and the production of Particulate Organic Carbon (POC) in the upper ocean.
 Sinking POC then allows the transfer of organic carbon from the upper ocean to the interior, leading to carbon sequestration over long time scales \citep{Falkowski_1998}.
@@
 
-Traditionally, POC export is thought to be mainly driven by larger, faster-sinking, particles capable of gravitationally-sinking below the export depth over timescales shorter than remineralization timescales.
+%Traditionally, POC export is thought to be mainly driven by larger, faster-sinking, particles capable of gravitationally-sinking below the export depth on timescales shorter than the time scale on which the particles get remineralized.
 This is a reasonable assumption if one considers that vertical advective velocities in the ocean are generally much weaker than velocities associated with gravitational sinking.
@@
 
-The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
+%The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
 Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities.
@@
 Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe in-situ.
-Additionally, and despite recent methodological progress \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and are more often than not inferred from key parameters such as particle type, size, and density.
+Additionally, and despite recent methodological progress \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density.
 
-In this study, we therefore rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale.
+%In this study, we therefore rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale.
 Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior.
@@
 
-This study uses a non-hydrostatic, three-dimensional, numerical model called PSOM \citep{Mahadevan_1996a,Mahadevan_1996b}.
-To simulate an eddy field that is representative of the Northeast Pacific Ocean, the model domain is set in a channel configuration with periodic east-west boundaries, and solid boundaries in the south and north.
+This study uses a non-hydrostatic, three-dimensional, Process Study Ocean Model \citep[PSOM;][]{Mahadevan_1996a,Mahadevan_1996b} to simulate an eddy field that is representative of the Northeast Pacific Ocean.
+The model is set in a channel configuration with periodic east-west boundaries, and solid boundaries in the south and north.
 The domain covers 112 km in the x-direction, 304 km in the y-direction, and 1000 m in the vertical (Figure \ref{fig: model_domain}).
 The horizontal resolution is 500 m, while a stretched grid is used in the vertical with 32 levels ranging in thickness from 1.25 m near the surface to 70 m at the lowermost level.
-The model is integrated numerically in time and evolves the temperature, salinity, free-surface height, pressure, and three-dimensional velocity field from an initial state, subject to momentum and buoyancy fluxes applied through the surface boundary conditions.
+The model is integrated numerically in time and evolves the temperature, salinity, free-surface height, pressure, and three-dimensional velocity field from an initial state, subject to momentum and buoyancy fluxes applied through the surface boundary.
 
@@
 	\caption{PSOM model setup.
-(a) Meridional profile of zonal wind scaling coefficient that multiplies $\tau_x$, with a tapering at the north and south boundaries to reduce upwelling and downwelling, respectively.
-(b) Restoration factor (color shading) used to dampen internal wave reflection at boundaries as well as curl-driven upwelling and downwelling, along with constant density contours showing the three fronts (black line).
-(c) Surface net heat flux anomaly superimposed to the heat fluxes prescribed at $y = 150$ km.}
+(a) Meridional profile of scaling coefficient that multiplies the time-varying zonal wind stress $\tau_x$ shown in Fig.~3a.
+The taper at north and south boundaries prevents `coastal' up-/down-welling being entirely concentrated in the boundary grid cell.
+(b) Restoration factor (color shading) used to dampen internal wave reflection at boundaries as well as up-/down-welling due to the windstress curl.
+Surface density contours (black) show the three fronts used to initialize the model.
+(c) Meridional variation of the time-dependent surface  heat flux (Fig.~3a) prescribed over the domain.}
 	\label{fig: model_domain}
@@
 Time-varying wind stress and heat flux are prescribed at the surface boundary.
-Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory.
+Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory \citep{PMEL_data}.
 Daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long climatology.
 A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability.
-In all numerical experiments, the simulations are first allowed to spin-down for the first 5 days with no forcing applied at the surface boundary.
+In all numerical experiments, simulations are
+run for the first 5 days without any forcing applied to the surface boundary.
 Surface wind stress and heat fluxes are then linearly ramped up between days 5 and 10 of the simulation, to reach realistic values at day 10.
@@
 
-Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from Argo floats \citep{Gaillard_2009,Gaillard_2016}.
+Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from Argo floats \citep{Gaillard_2015,Gaillard_2016}.
 Argo data is averaged monthly over the period 2002-2012 and two different months are used to initialize the two main numerical experiments for this study: Climatological conditions in April are used to initialize the \textit{Papa\_summer} experiment, while January climatological conditions are used to initialize the \textit{Papa\_winter} experiment (Table \ref{tab: meso_vs_submeso}).
 The north-south background density gradient is then intensified into three fronts located at $y = 75$, $y = 150$, and $y = 225$ km (Figure \ref{fig: model_domain}).
-The amplitude of the density gradient associated with the three fronts is determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \citep{Pelland_2016}.
+The amplitude of the density gradient associated with the three fronts is determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \citep{Pelland_2016,Pelland_2018_data}.
 To reduce model spin-up time, density fronts are perturbed by a sinusoidal wave with a wavelength close to the 1st baroclinic deformation radius ($\lambda = $ 66 km).
@@
 A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \citep{Mensa_2013,Callies_2015,Thompson_2016}.
-The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.
+The individual characteristics of each of \linebreak \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.
 
@@
 
-\subsection{Gravitational and Advective Sinking of POC}
+\subsection{Gravitational and Advective Export of POC}
 
@@
 Domain-averaged, downward particle flux is expected to be a combination of the flux driving by gravitational sinking ($\left<w_sB\right>$), and by the vertical advective currents affecting the particle along its pathway ($\left<wB\right>$).
-The deviation in particle depths from the traditional one-dimensional gravitationally driven model is shown in Figure \ref{fig: particle_depth_distribution}d for both summer and winter cases.
+The deviation in particle depths from the traditional one-dimensional gravitationally driven model is shown in Figure \ref{fig: particle_depth_distribution} for both summer and winter cases.
 In the summer, the PDF of particle density versus depth remains relatively narrow through time, and is centered on a depth level that can be predicted using a simple 1D gravitational model (see shaded curves in Figure \ref{fig: particle_depth_distribution}).
@@
 	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
-	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release, in the Winter experiment.
-Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected based on a 1D gravitational model where $z = w_s\timest$.
+	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release in the Winter experiment, with sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d.
+Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\timest$.
 [right] Probability Distribution Function (PDF) of particles as a function of depth for each velocity class.
@@
 
-A relative amount of biomass is associated to the particles using Equation \ref{eq: biomassjungeslope}.
+A relative amount of biomass is associated to the particles using Equation (\ref{eq: biomassjungeslope}).
 PDFs of relative biomass as a function of the vertical velocity is shown in Figure \ref{fig: biomass_export}.
 Following the traditional paradigm derived from the simple 1D gravitational model, the downward flux of biomass in the summer is dominated by faster-sinking particle classes capable of carrying particulate material downwards more efficiently.
-The contribution of slower-sinking particles, however, critically depends on the slope of the size spectrum (see Figure \ref{fig: sinking_velocity_spectrum}).
-As the Junge slope increases, the spectrum of biomass steepens, and the relative contribution of slower-sinking particles to the downward biomass flux significantly increases.
+The contribution of slower-sinking particles, however, depends critically on the slope of the size spectrum (see Figure \ref{fig: sinking_velocity_spectrum}).
+As the Junge slope increases, the spectrum of biomass steepens, and the relative contribution of slower-sinking particles to the downward biomass flux significantly increases (Figure \ref{fig: biomass_export}c).
 In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.1\% to 10\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$.
@@
 In the winter, PDFs of relative biomass as a function of vertical velocities present a much larger spread, with velocity magnitudes exceeding 50 m/day.
-For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.1\% in the summer to about 4\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes.
-Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass (Figure \ref{fig: biomass_export}b).
+For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.1\% in the summer to about 4\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes (Figure \ref{fig: biomass_export}b).
+Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass.
 When winter ocean dynamics are coupled with a steeper Junge slope, however, slower-sinking particles largely dominate the downward biomass flux.
-In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 80\% of the biomass flux.
+In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 80\% of the biomass flux (Figure \ref{fig: biomass_export}d).
 
-Our results show that both a steepening of the particle size spectra and the presence of submesoscale dynamics can enhance the contribution of slower-sinking particles to the downward biomass flux.
+Our results show that both a steepening of the particle size spectrum and the presence of submesoscale dynamics can enhance the contribution of slower-sinking particles to the downward biomass flux.
 While the former is simply due to an increase in particle density in slower-sinking particle classes, the latter is attributed to the larger vertical velocity generated by submesoscale instabilities.
@@
 In reality, however, sinking velocities of particulate matter varies in time as the particles slowly remineralize.
-A remineralizing behavior was therefore implemented for the Lagrangian particles, using Equation \ref{eq: sinking_velocity_remin}, to investigate the impact that remineralization processes have on our findings.
+A remineralizing behavior was therefore implemented for the Lagrangian particles, using Equation (\ref{eq: sinking_velocity_remin}), to investigate the impact that remineralization processes have on our findings.
 The traditional paradigm relies on the fact that slow-sinking particles tend to fully remineralize over short timescales, further enhancing the importance of faster-sinking particles classes in driving downward biomass fluxes.
@@
 Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize.
-This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation \ref{eq: sinking_velocity_remin}.
+This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation (\ref{eq: sinking_velocity_remin}).
 As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}).
@@
 \end{figure}
-In a advectively-driven system where $\left<w_sB\right> < \left<w_B\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
+In a advectively-driven system where $\left<w_sB\right> < \left<wB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
 This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a).
-When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see Figure \ref{fig: biomass_export_remin}c).
-As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics (82\%; see Figure \ref{fig: biomass_export_remin}b).
+When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see inset in Figure \ref{fig: biomass_export_remin}c).
+As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics.
+Biomass fluxes are dominated by the slower-sinking particles, representing 82\% of the downward biomass flux (Figure \ref{fig: biomass_export_remin}b).
 Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (87\%; see Figure \ref{fig: biomass_export_remin}d).
@@
 Introducing remineralization processes significantly decreases the biomass flux.
-Counter-intuitively, however, the implementation of a remineralization scheme further strengthen the role played by slower-sinking particles in the biomass flux (Figure \ref{fig: biomass_export_remin}.
+Counter-intuitively, however, the implementation of a remineralization scheme further strengthen the role played by slower-sinking particles in the biomass flux (Figure \ref{fig: biomass_export_remin}).
 This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as these particles decelerate as they remineralize.
@@
 \item Ocean dynamics in the subpolar Northeast Pacific exhibit a seasonal cycle with low submesoscale activity in the summertime, and more submesoscale features present in the wintertime.
-Submesoscale dynamics generate larger, and asymmetrical, vertical currents leading to a vertical biomass flux driven by advective processes, as opposed to gravitationally-driven in the summertime.
+Submesoscale dynamics generate larger, and asymmetric, vertical currents leading to a vertical biomass flux driven by advective processes, as opposed to gravitational sinking in the summertime.
 
@@
 Pelland (NOAA) and Charlie Eriksen (University of Washington) for sharing the glider data collected at Ocean Station Papa, as well as Sebastian Essink for his assistance in developing the particle-tracking code.
-All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website (\url{https://www.pmel.noaa.gov/ocs/Papa}) and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945}.
-Glider data is archived at NCEI: https://data.nodc.noaa.gov/cgi-bin/iso?id=gov.noaa.nodc:0155879.
+All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website \citep[\url{https://www.pmel.noaa.gov/ocs/Papa};][]{PMEL_data} and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945} \citep{Gaillard_2015}.
+Glider data is archived at the University of Washington's Library \citep[\url{https://digital.lib.washington.edu/researchworks/handle/1773/41656};][]{Pelland_2018_data}.
 Model outputs, and particle trajectories are freely available on request.

### 2019-08-26 GBC_Dever_cover_letter.tex
Adds cover letter and m file
Adds the cover letter for submission to GBC

\documentclass[11pt]{article}

\usepackage{kantlipsum}   %% only for demo
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{marvosym}
\usepackage{graphicx}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{ragged2e}

\pagestyle{empty}

\usepackage[scale=0.775, top = 1.5cm, bottom = 1cm]{geometry}
\setlength{\parindent}{0pt}
\addtolength{\parskip}{6pt}

\def\firstname{Mathieu }
\def\familyname{Dever}
\def\FileAuthor{\firstname \familyname}
\def\FileTitle{\firstname \familyname's cover letter}
\def\FileSubject{Cover letter}
\def\FileKeyWords{\firstname \familyname, Cover letter}

\renewcommand{\ttdefault}{pcr}

\usepackage{url}
\urlstyle{tt}
\ifpdf
  \usepackage[pdftex,pdfborder=0,breaklinks,baseurl=http://,pdfpagemode=None,pdfstartview=XYZ,pdfstartpage=1]{hyperref}
  \hypersetup{
    pdfauthor   = \FileAuthor,%
    pdftitle    = \FileTitle,%
    pdfsubject  = \FileSubject,%
    pdfkeywords = \FileKeyWords,%
    pdfcreator  = \LaTeX,%
    pdfproducer = \LaTeX}
\else
  \usepackage[dvips]{hyperref}
\fi

\begin{document}
\sffamily   % for use with a résumé using sans serif fonts;

%____________________
%% HEADER
%____________________

% My information
%\begin{minipage}[t]{.6\textwidth}
%	\vspace{-0.5cm}
%\raggedright
%\includegraphics[width = 0.8\linewidth]{WHOImarkBLUE.eps}
%\end{minipage}	
\hfill
\begin{minipage}[t]{.4\textwidth}
\raggedleft%
{\bfseries \firstname\familyname}\\[.35ex]
\small\itshape%
266 Woods Hole Rd., MS \#29\\
Woods Hole, MA 02543-1050, U.S.A.\\[.35ex]
\Letter~\href{mailto:mdever@whoi.edu}{mdever@whoi.edu}
%\Mundus~\href{https://www2.whoi.edu/staff/mdever/}{www2.whoi.edu/staff/mdever/}
\end{minipage}\\[0.5em]

% The recipient's information
\begin{minipage}[t]{.65\textwidth}
\raggedright%
{\bfseries Global Biogeochemical Cycles}\\[-.2cm]
\end{minipage}
\hfill
\begin{minipage}[t]{.3\textwidth}
\raggedleft
\today
\end{minipage}\\[-.3cm]
\raggedright

\justifying
%____________________
%% OPENING
%____________________
\noindent Dear editor,\\
%

%____________________
%% CONTENT
%____________________
Please find enclosed the a manuscript titled ``\textbf{Size-differentiated Export in Different Dynamical Regimes in the Ocean}". This study addresses the impacts of ocean dynamics at submeso-scales ($<$10 km) on the vertical fluxes of particulate organic matter. Due to the challenges associated with resolving submeso-scales observationally, in both space and time, we rely on a process-oriented numerical model and particle-tracking to quantify the changes in fluxes of particulate matter. The model is initialized to statistically represent ocean conditions at Station Papa, in the Subpolar Northeastern Pacific, as this is a site where the NASA-funded EXPORTS program will be focusing a large part of its observational effort. A key aspect of our work is to consider the interactions between vertical currents at submeso-scales, and the sinking velocities spectrum for particulate matter.

The main conclusion of this work is that the traditional one-dimensional paradigm of a vertical flux driven exclusively by fast-sinking particles does not hold when submeso-scales dynamics are present. Our findings can be summarized in three key points:

\begin{itemize}
	\item[(1)] Ocean dynamics in the subpolar Northeast Pacific, often described as an ``eddy desert", indeed exhibit submesoscale activity in the wintertime.
	\item[(2)] Submesoscale dynamics generally enhance downward fluxes by increasing the contribution of slower-sinking particles to the total flux. The contribution of slower-sinking particles to the total flux is found to be at least significant, and can be dominant in certain conditions.
	\item[(3)] Remineralization unexpectedly enhances the role played by slower-sinking particles in vertical fluxes of particulate matter.
\end{itemize}

We confirm that this work is original and has not been published elsewhere nor is it currently under consideration for publication elsewhere. We have no conflicts of interest to disclose.

Thank you for your consideration of our work. Please address all correspondence concerning this manuscript to mdever@whoi.edu.\\[.5cm]

%____________________
%% CLOSING
%____________________
\noindent Cordially,\\[.2cm]
%
%\vfill
%\noindent \includegraphics[scale=0.7]{/Users/mathieudever/Dropbox/signature.pdf}\\
{\bfseries \firstname \familyname}
\end{document}

### 2019-08-26 figures/code/Fig7.m

@@ -160,7 +160,7 @@ bar(3,sum(N5w(Ew<=0).*B5_2.*Ew(Ew<=0))/totalFw*100,'facecolor',color5,'edgecolor
 set(gca,'YScale','log','fontsize',40,'xtick',[1:3],'XTickLabel',{},'yaxislocation','right')
 grid on; box on
 ylim([1e-2 100])
-title('Relative Downward Flux','fontsize',40,'position',[2 200 0])
+title('Percentage Downward Flux','fontsize',40,'position',[2 200 0])
 
 subplot(2,2,4)
 h1 = plot(Ew,N0025w.*B0025_4/totalB4w*100,'-','color',color0025,'linewidth',2);

### 2019-08-28 size_differentiated_export.tex
Updates from Overleaf

@@
-%\documentclass[]{article}
-
-%\setlength{\parskip}{.5cm}
-%\usepackage{natbib}
-%\usepackage[table,xcdraw]{xcolor}
-%\usepackage{graphicx}
-%\usepackage{hyperref}
-%\usepackage{amsmath}
-%\usepackage{appendix}
-%\usepackage[left=3cm,right=3cm]{geometry}
-  % Apply watermark to document
-%\usepackage{draftwatermark}
-%\SetWatermarkLightness{0.9}
-%\SetWatermarkScale{15}
-%\SetWatermarkText{DRAFT}
-
 \documentclass[article,linenumbers]{agujournal2018}
@@
 \begin{keypoints}
-\item Submesoscale dynamics enhance the contribution of slow-sinking particles to POC export, especially for steep particle size-spectrum slopes
-\item Remineralization processes intensify the role of slow-sinking particles, to the point where these particle sometime dominate POC export
+\item Submesoscale dynamics enhance the contribution of slow-sinking particles to POC export, depending on their intensity and on the fraction of biomass in the slow sinking particle classes.
+\item Remineralization processes can enhance the contribution of slow-sinking particles to the point where these particles sometimes dominate POC export
 \end{keypoints}
@@
 However, this need not be the case in a dynamic oceanic flow field, where the ocean velocity can influence the descent rate of particles.
-Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) the ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
+Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
 The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important.
@@
 %% ------------------------------------------------------------------------ %%
-%\begin{article}
-
-%\maketitle
-
 \section{Introduction}
@@
 The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.
-%???
-Removed 'long time scales', or define it
 Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.
@@
 Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth.
-Particles produced through primary and secondary production in the surface layer that are relatively large and fast-sinking, tend to sink out of the upper surface layer
-%below the export depth   ?? remove this because we have not defined 'export depth'?? 
-on timescales shorter than the timescale on which the particles get remineralized.
+Particles produced through primary and secondary production in the surface layer that are relatively large and fast-sinking, tend to sink out of the upper surface layer on timescales shorter than the timescale on which the particles get remineralized.
 It is reasonable to treat POC export as sinking-dominated if the vertical advective velocities in the ocean are weaker than the velocities associated with gravitational sinking.
-However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day.
-The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, which indicates $\mathcal{O}(10^8)$ greater abundance of small  particles than large particles.
+However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type, that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day.
+The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, for which the abundance of small particles is $\mathcal{O}(10^4 - 10^8)$ greater than large particles.
 The biomass size spectrum, which indicates the distribution of biomass vs.
-particle size, tends to be flatter and variable in shape \citep{Sheldon72} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and varies, for example, between 2 and 3 depending on shape and porosity).
+particle size, tends to be flatter and variable in shape \citep{Sheldon_1972} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and typically varies between 2 and 3 depending on shape and porosity).
 Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction.
@@
 \cite{Omand_2015}  found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic.
-Advectively subducting plumes or filaments of high oxygen, chlorophyll and small POC (evidenced through backscatter) were detected from a suite of gliders during the North Atlantic Bloom experiment \citep{Briggs_2011, Alkire_2012}.
+Advectively subducting plumes or filaments of high oxygen, chlorophyll and small POC (evidenced through backscatter) were detected from a suite of gliders during the North Atlantic Bloom experiment \citep{Alkire_2012}.
 Using model simulations to capture the process of eddy-driven subduction, \cite{Omand_2015} estimated the downward advective flux of non-sinking POC and parameterized it.
-The flux of fast-sinking particles consisting largely of diatoms was observed from backscatter and quantified separately \citep{Briggs_2011}.
-But, the estimates did not simultaneously account for a range of sinking particle velocities.
-Typically, particulate organic matter (POM) has a spectrum of sinking velocities and in order to understand its fate and export, we need to consider the biomass distribution as a function of the particle sinking velocity spectrum and its interaction with dynamics of the flow field in the ocean.
+\cite{Briggs_2011} quantified the flux of fast-sinking particles consisting largely of diatoms from observations of optical backscatter.
+But, these estimates did not account for a range of sinking particle velocities.
+Typically, particulate organic matter (POM) has a wide spectrum of sinking velocities and in order to understand its fate and export, we need to consider the biomass distribution as a function of the particle sinking velocity spectrum and its interaction with the dynamics of the flow field in the ocean.
 
@@
 Enhanced vertical velocities can generate a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2000,Levy_2001}, or can significantly increase the export of POC to the ocean interior through downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.
-Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe these processes in-situ.
 
 The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
-Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities.
-However, despite progress on sampling and viewing particles in the ocean \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density.
+Through this mechanism, smaller particles can be exported on timescales shorter than their remineralization timescales, despite their slower sinking velocities.
 Depending on the fraction of  biomass in smaller particles (i.e., with slow sinking velocities), the impact of submesoscale dynamics on the export of POC is potentially significant.
 
-%The impact of submesoscale dynamics on the net biomass flux depends on the sinking velocity spectrum (or size spectrum if we assume that sinking velocities are related to size).
-A relatively large fraction of the biomass at slow sinking velocities leads to a greater dependence of the biomass flux on the flow field, whereas the converse, leads to less dependence on the flow dynamics.
+In this study, we account for a range of particle sinking velocities in a dynamic flow field.
+Despite progress on sampling and viewing particles in the ocean \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density.
+Though we acknowledge a large variability in these relationships, we assume a relationship between particle size, biomass, and particle sinking velocity in order to assess the impact of the flow dynamics and particle size spectrum on the export flux.
 
-In this study, we account for a range of particle sinking velocities in a dynamic flow field. 
-We  rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale.
+We  rely on a submesoscale-resolving, non-hydrostatic ocean model to simulate the dynamics in the upper few hundred meters of the ocean.
+The model does not represent surface waves or boundary layer turbulence, but rather, examines the fate of particulate organic matter beneath the turbulent surface boundary layer.
+The dynamical model is coupled with a particle-tracking module to model the advection of particles by fluid flow, while neglecting the effects of particle inertia and drag on their advection.
+In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$).
+
+The model is used to quantify the contribution of slow-sinking particles to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale.
 Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior.
 Particles are released in two fundamentally different flow fields in terms of dynamics based on observed conditions in the Northeast Pacific: In the summer, where ocean dynamics are characterized by low Rossby numbers and weak vertical advective velocities, and in the winter, where ocean dynamics include submesoscale frontal structures and local Rossby numbers $\mathcal{O}$(1).
-Both simulations and the particle-tracking module are described in Section \ref{sec: Methods}.
-The impact of particles characteristics and ocean dynamics on the export of POC is quantified in Section \ref{sec: Results}, and discussed in Section \ref{sec: Discussion}.
-Section \ref{sec: Conclusions} summarizes the key conclusions of the study.
-
-%A major pathway transferring carbon from the atmosphere to the ocean is through photosynthesis and the production of Particulate Organic Carbon (POC) in the upper ocean.
-Sinking POC then allows the transfer of organic carbon from the upper ocean to the interior, leading to carbon sequestration over long time scales \citep{Falkowski_1998}.
-Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.
-
-%Traditionally, POC export is thought to be mainly driven by larger, faster-sinking, particles capable of gravitationally-sinking below the export depth on timescales shorter than the time scale on which the particles get remineralized.
-This is a reasonable assumption if one considers that vertical advective velocities in the ocean are generally much weaker than velocities associated with gravitational sinking.
-However, recent work demonstrates that the presence of mesoscale eddies can enhance carbon export through two main processes: First, by increasing primary productivity through the injection of nutrients into the euphotic layer, therefore increasing the particle concentration, logically leading to a greater export \citep{Levy_1998}.
-Second, by generating larger vertical velocities along the front located at the eddy perimeter \citep{vanHaren_2006, Waite_2016}.
-These studies demonstrate that ocean dynamics potentially play an important role in driving the carbon export from the euphotic layer to the ocean interior.
-This conclusion is further supported by a recent, yet large, body of literature focusing on ocean dynamics at submeso-scales (1-10 km) and the impact on biogeochemical processes \citep[see reviews in][]{Thomas_2008,Klein_2009,Mahadevan_2016}.
-Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{McWilliams_2016}.
-In this dynamical regime, geostrophic balance fails and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}.
-On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front.
-The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}.
-Just like at meso-scales, enhanced vertical velocities can generate either a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2012}, or can significantly increase the export of POC to the ocean interior \citep{Levy_2012, Estapa_2015,Omand_2015}.
-
-%The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
-Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities.
-Considering the fact that, although containing less biomass per particle, smaller particles are far more numerous than larger particles, the impact of submesoscale dynamics on the export of POC is potentially significant.
-Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe in-situ.
-Additionally, and despite recent methodological progress \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density.
-
-%In this study, we therefore rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale.
-Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior.
-Particles are released in two fundamentally different flow fields in terms of dynamics based on observed conditions in the Northeast Pacific in the summer, where ocean dynamics are characterized by low Rossby numbers and weak vertical advective velocities, and in the winter, where ocean dynamics include submesoscale frontal structures and local Rossby numbers $\mathcal{O}$(1).
 Both simulations and the particle-tracking module are described in Section \ref{sec: Methods}.
@@
 Surface wind stress and heat fluxes are then linearly ramped up between days 5 and 10 of the simulation, to reach realistic values at day 10.
-% (Figures \ref{fig: Papa_summer} and \ref{fig: Papa_winter}).
-While the meriodional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling %that could contaminate the middle third of the model domain, where the analysis is focused
-(Figure \ref{fig: model_domain}a).
+
+While the meridional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling (Figure \ref{fig: model_domain}a).
 A restoration timescale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress, as well as to limit internal wave reflection at the solid boundaries back into the domain (Figure \ref{fig: model_domain}b).
@@
 \subsubsection{Particle Advective Scheme}
-To quantify the impact of submesoscale dynamics on the export of Particulate Organic Matter (POC), Lagrangian particle tracking is used in conjunction with the flow field obtained from the two experiments described above.
-Particles are tracked using the non-divergent velocity field at each face of a grid cell.
-The velocity field is then linearly interpolated onto the particle's position.
-For example, the eastward velocity (x-axis) of a particle is given by:
-
+To quantify the impact of submesoscale dynamics on the export of Particulate Organic Matter (POC), Lagrangian particle trajectories are computed using the same scheme as in ``TRACMASS'' \citep{Doos_2013} with the flow fields from the two experiments described above.
+The three-dimensional, non-divergent velocity components from the faces of each ``C" grid cell are linearly interpolated onto the particle's position within the grid cell.
+For example, the eastward (along the x-axis) velocity  of a particle is given by
 \begin{equation}
-u(x) = u_{i-1} + \frac{(x - x_{i-1})}{(x_i - x_{i-1})}(u_{i}-u_{i-1})
+u(x) = u_{i-1} + \frac{(x - x_{i-1})}{(x_i - x_{i-1})}(u_{i}-u_{i-1}),
 \end{equation}
-where the subscripts $i-1$ and $i$ denote the western and eastern walls of the grid cell where the particle is located, respectively. This can be re-written as:
-
+where the subscripts $i-1$ and $i$ denote the western and eastern walls of the grid cell where the particle is located, respectively. This can be re-written as
 \begin{equation}
-\frac{\partial x}{\partial t} + \beta x + \delta =  0
+\frac{\partial x}{\partial t} + \beta x + \delta =  0,
 \label{eq: eq_diff}
 \end{equation}
-where $\beta = (u_{i}-u_{i-1})/\Delta x$ and $\delta = -u_{i-1} - \beta x_{i-1}$ \citep{Doos_2013}. This differential equation can be solved analytically for $\beta \neq 0$:
-
+where $\beta = (u_{i}-u_{i-1})/\Delta x$ and $\delta = -u_{i-1} - \beta x_{i-1}$ \citep{Doos_2013}. This differential equation can be solved analytically for $\beta \neq 0$ as
 \begin{equation}
@@
 In the horizontal, particles are seeded every 250 m over the entire domain in the x-direction, and for 100 $<y<$ 200 km in the y-direction.
-The seeding is centered over the mean position of the middle front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by undesired effects created by the solid north-south solid boundaries.
+The seeding is centered over the mean position of the central front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by undesired effects created by the solid north-south solid boundaries.
 In the vertical, particles are seeded every 1 m between 75 and 85 m.
@@
 The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
-The fastest-sinking velocity is chosen as a low end-member representing velocity classes that will be exported in its entirety over the course of our experiment.
-The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.
+The fastest-sinking velocity is chosen as an end-member velocity class of particle that will be exported in its entirety over the course of our experiment.
+%The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.
 
@@
 Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles.
-Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.
-%The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.
+Particles located deeper than the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.
 
@@
 \label{sec: equations_biomass}
-The slope of the size spectrum of particles is traditionally described by the slope of the log-log curve, $\xi$, between particle number $N$ and particle radius $r$ \citep[also know as the Junge slope;][]{White_2015}:
-
+The slope $\xi$ of the size spectrum of particles \citep[also know as the Junge slope;][]{White_2015} is the slope of the log-log curve of particle number $N$ vs. particle radius $r$, where
 \begin{equation}
-N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}
+N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}.
 \label{eq: powerlaw_radius}
 \end{equation}
-where $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily.
+Here, $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily.
 For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically.
 Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \citep{Bach_2012}.
-%\cite{Bach_2012} also demonstrate that Stokes law is generally a lower-bound estimate of sinking velocities for a specific particle size.
-Assuming a Stokes-like relationship, we can construct a particle sinking velocity spectrum $N(w_s)$ based on (\ref{eq: powerlaw_radius}), where $w_{s_0}$ is the sinking speed of particles with a radius $r_0$:
 
+Assuming a Stokes-like relationship, we can construct a particle sinking velocity spectrum $N(w_s)$ based on (\ref{eq: powerlaw_radius}), as
 \begin{equation}
-N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2}
+N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2},
 \label{eq: powerlaw_velocity}
 \end{equation}
-For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can thus be computed using (\ref{eq: powerlaw_velocity}) (See Figure \ref{fig: sinking_velocity_spectrum}).
-For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represent 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}).
-The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$, can be estimated if the biomass is assumed to scale with the particle's volume.
-The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed using:
-
+where $w_{s_0}$ is the sinking speed of particles with radius $r_0$.
+For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can be computed using (\ref{eq: powerlaw_velocity}) (See Figure \ref{fig: sinking_velocity_spectrum}).
+For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represents 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}).
+The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$ can be estimated if the biomass is assumed to scale with the particle's volume.
+The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed as
 % FIG4
@@
 \end{figure}
-
 \begin{equation}
@@
 The total biomass associated with one simulated particle can be obtained by scaling (\ref{eq: biomass_realparticle}) by the ratio $N(w_s)/N_0$:
-
 \begin{equation}
@@
 \begin{equation}
-	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}
+	B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}.
 	\label{eq: biomassjungeslope}
@@
 Remineralization of particles as they sink through the water column impacts the amount of biomass exported.
-Slow-sinking particles generally contains less biomass and spends more time in the mixed layer, which means that they are remineralized at a shallower depth than faster sinking particles.
+Slow-sinking particles generally contain less biomass and spend more time in the mixed layer, which means that they are remineralized at a shallower depth than faster sinking particles.
 Remineralization processes are complex, species-dependent, and generally not well-understood.
 In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship which assumes that the biomass content of a particle decreases in time proportionally to the particle volume.
-Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}:
+Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}
 \begin{equation}
-	B (t) = B^0\exp(-kt)
+	B (t) = B^0\exp(-kt),
 	\label{eq: remin_scheme}
@@
 The change in biomass with time is in turn expected to affect the sinking velocity of the particle.
-Given that $B \propto w^{3/2}$ (see Equation (\ref{eq: biomass_realparticle})), particles in all sinking-velocity classes undergo a decay in sinking speed according to:
-
+Given that $B \propto w^{3/2}$ (see Equation (\ref{eq: biomass_realparticle})), particles in all sinking-velocity classes undergo a decay in sinking speed according to
 \begin{equation}
-w_s (t) = w_s^0\exp(-\frac{2kt}{3})
+w_s (t) = w_s^0\exp(-\frac{2kt}{3}),
 \label{eq: sinking_velocity_remin}
@@
 The flattening of the KE$_{\text{tot}}$ curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments.
-The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=(v_x - u_y)/f$ where f = 1.12$\times10^{-4}$; Figure \ref{fig: dynamics}).
+The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=(v_x - u_y)/f$ where $f$ = 1.12$\times10^{-4}$; Figure \ref{fig: dynamics}).
 
@@
 
-%The largest horizontal buoyancy gradients are observed above the thermocline ($z$$<$50 m) and along the halocline (100--200 m), and range between 0 and 1.2$\times 10^{-7}$ s$^{-2}$ (Figure \ref{fig: dynamics}).
 Lateral buoyancy gradients in the summer are relatively weak $\mathcal{O}$(10$^{-8}$ s$^{-2}$) and result in low Rossby numbers $\mathcal{O}$(0.1), with positive relative vorticity on the denser (north) side of the front and negative relative vorticity on the lighter (south) side of the front.
@@
 The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \citep{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ s$^{-1}$ (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ s$^{-1}$, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s, or $\sim 10^{-1}$ m/day.
-%The agreement between the scaling and the model outputs suggest that PSOM is capable of reproducing a realistic vertical flow field.
 
@@
 The experiment is considered spun-up by doy 50 and the particle-tracking experiment is initialized.
-%Many sharp fronts and filaments on the order of 1 km can be seen in \textit{Papa\_winter}, penetrating to ocean upper layer to the deeper than in the summer, dissipating within the mixed layer at $\sim$100 m (Figure \ref{fig: dynamics}).
 
@@
 The PDF of relative vorticity reveals a positively-skewed distribution ($s = 0.68$).
-This is in agreement with the fact the relative vorticity is more likely to be cyclonic than anticyclonic, based on conservation of potential vorticity \citep{Hoskins_1972}.
-Regions with a high Rossby number are localized and located in the mixed layer exclusively.
+This is in agreement with the fact that the relative vorticity is more likely to be cyclonic than anticyclonic, based on conservation of potential vorticity \citep{Hoskins_1972}.
+Regions with  high Rossby number are localized and located in the mixed layer exclusively.
 In places where the local Rossby number reaches $\mathcal{O}$(1), geostrophic balance is lost and a vertical secondary ageostrophic circulation begins to slump the isopycnals and restore the flow to a more geostrophically-balanced flow.
@@
 Once again, the amplitude of these vertical velocity hot spots is coherent with the scaling $w \propto RofU/N$: using $Ro\sim1$, $N\sim10^{-2}$ 1/s, $f\sim10^{-5}$ 1/s, and $U\sim0.1$ m/s, we obtain $w\sim 10^{-4}$ m/s, or $\sim 10^{1}$ m/day.
-%This demonstrates the capabilities of PSOM to resolve sharp frontal features at the kilometer scale, as well as the ageostrophic circulation associated with those fronts.
 
@@
 When computed at the kilometer-scale, the PDF of horizontal buoyancy gradients in \textit{Papa\_winter} exhibits a longer tail than in \textit{Papa\_summer} (Figure \ref{fig: dynamics}).
-When compared to observations, the PDFs of $M^2$ in \textit{Papa\_summer} and \textit{Papa\_winter} demonstrate a correlation with observations of $r = 0.93$ and $r = 0.95$, respectively
+When compared to observations, the PDFs of $M^2$ in \textit{Papa\_summer} and \textit{Papa\_winter} demonstrate a correlation with observations of $r = 0.93$ and $r = 0.95$, respectively.
 
@@
 	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
-	\caption{[left] Gridded anomaly in the median depth of particles 25 days after particle release in the Winter experiment, with sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d.
+	\caption{[left] 
+	The median depth anomaly of particles with a sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d within each grid cell for the winter case 25 days after particles are released.
+The `depth anomaly' is with respect to the `expected' sinking depth (= sinking speed $\times$ time since release).
+	%Gridded anomaly in the median depth of particles 25 days after particle release in the Winter experiment, with 
+	%sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d. 
 	Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\timest$.
-[right] Probability Distribution Function (PDF) of particles as a function of depth for each velocity class.
+[right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class.
 The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions.
@@
 An interesting result emerges from the spatial distribution of the depth-anomaly: both positive (i.e., particles are shallower than expected) and negative (i.e., particles are deeper than expected) anomalies are organized into features with a length-scale $\mathcal{O}$(1-10 km).
-This further highlights the importance of winter submesoscale circulation for vertical fluxes of particles.%, which is explicitly shown in Figure \ref{fig: biomass_export}.
+This further highlights the importance of winter submesoscale circulation for vertical fluxes of particles.
 
@@
 \textit{Papa\_summer} and \textit{Papa\_winter} experiments were designed to statistically capture the ocean dynamics at Station Papa (145$^o$W, 50$^o$N) in the Northeast Pacific Ocean.
-After spin-up, the model demonstrated similar distribution of both horizontal ($M^2$) and vertical ($N^2$) density gradients to observations from underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}).
-The two experiments, however, show significantly different distributions of $M^2$, with the winter distribution exhibiting a longer tail, suggesting sharper density gradients.
-The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sample gradients at a maximum resolution of about 10 km, while the model resolution is 500 m and therefore allows sharp submesoscale fronts and filaments to be captured in the distribution.
+After spin-up, the model demonstrated similar distributions of both horizontal ($M^2$) and vertical ($N^2$) density gradients to observational estimates from underwater gliders (see Figures \ref{fig: Papa_summer}, \ref{fig: Papa_winter}, and \ref{fig: dynamics}).
+The two experiments, however, show significantly different distributions of $M^2$, with the winter distribution exhibiting a longer tail, due to sharper density gradients.
+The tail of the wintertime distribution is only partially captured by the glider data, due to the fact that underwater gliders sampled gradients at spatial scales of 10 km and greater, while the model has a horizontal resolution of 500~m, allowing sharper submesoscale fronts and filaments to be formed.
 
-Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \citep{Dasaro_2011, Thomas_2013}, or at the edge of mesoscale features \citep{vanHaren_2006,Waite_2016}.
-The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa, and reflected in the model experiments, echoes findings of recent observational studies conducted at a similar latitude in the Atlantic Ocean demonstrating the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}.
+Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \citep{Dasaro_2011, Thomas_2013}, or the edge of mesoscale features \citep{vanHaren_2006,Waite_2016}.
+The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}.
 Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.
@@
 
-Analyses of particle tracking experiments reveal that the role played by slower-sinking particles in downward particulate fluxes depends on two main characteristics: (1) the dynamics of the ocean flow field, and (2) the slope of the size spectrum (i.e., the Junge slope $\xi$).
+Analyses of particle tracking experiments reveal that the contribution of slower-sinking particles to the downward particulate flux depends on two main factors: (1) the dynamics of the oceanic flow field, and (2) the slope of the size spectrum (i.e., the Junge slope $\xi$).
 
@@
 In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer.
-This seasonal change in dynamics is consistent with recent observations \citep{Thompson_2016, Buckingham_2016}, and models \citep{Brannigan_2015, Callies_2015, Rocha_2016}, characterizing the seasonal cycle of submesoscale dynamics.
+This seasonal change in dynamics is consistent with recent observations \citep{Thompson_2016, Buckingham_2016}, and models \citep{Brannigan_2015, Callies_2015, Rocha_2016} characterizing the seasonal cycle of submesoscale dynamics.
 The winter intensification in submesoscale dynamics was proven to have an important impact on the downward flux of all sinking-velocity classes modeled in this experiment.
 
-In the summer, the gravitationally-driven dynamics efficiently drives a downward flux dominated by faster-sinking particles, less numerous but generally richer in POC, and little to no slower-sinking particles.
+In the summer,  gravitational sinking governs a downward particulate flux, which is dominated by faster-sinking particles, with little to no contribution from slower-sinking particles.
 In the winter, however, vertical fluxes tend to be advectively-driven, which leads to a slightly weaker downward flux of faster-sinking particles than in the summer due to resuspension, but a much larger flux of slower-sinking particles, which are present in far greater numbers (Figure \ref{fig: biomass_export}).
-These two seasonal mechanisms raise the question as to which process is most efficient in driving a downward flux of particulate material.
+The gravitationally-driven flux in the summer is mechanistically different from the advectively-driven winter flux, which raises the question as to which process is most efficient in driving a downward flux of particulate material.
 
-In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesoscale dynamics increase the contribution of slower-sinking particle classes to the downward biomass flux.
+In the absence of remineralization, both a steeper size spectrum slope ($\xi>3$ in this case) and enhanced submesoscale dynamics, increase the contribution of slower-sinking particle classes to the downward biomass flux.
 This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}).
@@
 The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content.
-Nevertheless, our results demonstrate the importance of resolving the lower range of the particle spectrum when measuring vertical fluxes, especially when submesoscale dynamics are active.
+Nevertheless, our results demonstrate the importance of including the smaller particle size range of the particle spectrum,  in the estimation or measurement of vertical fluxes, especially when submesoscale dynamics are active.
 It also highlights the importance of better constraining the relationships linking particle size, sinking velocity, and biomass content.
@@
 Introducing remineralization processes significantly decreases the biomass flux.
-Counter-intuitively, however, the implementation of a remineralization scheme further strengthen the role played by slower-sinking particles in the biomass flux (Figure \ref{fig: biomass_export_remin}).
+Counter-intuitively, however, the implementation of a remineralization scheme further strengthens the contribution of slower-sinking particles to the biomass flux (Figure \ref{fig: biomass_export_remin}).
 This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as these particles decelerate as they remineralize.
-In the summer, all particle classes are similarly affected by the remineralization scheme as downward fluxes are gravitationally-driven.
+In the summer, all particle classes are similarly affected by remineralization, as downward fluxes are gravitationally-driven.
 In the winter, however, slower-sinking particles are exported through advective processes.
-Their export timescale is little affected by remineralization processes as it only depends on local ocean dynamics.
+Their export timescale is barely affected by remineralization processes as it only depends on local ocean dynamics.
 
-The result of this study suggest that slow- and non-sinking particles must be considered when studying the downward flux of particulate matter in the upper ocean.
+The results of this study suggest that slow- and non-sinking particles must be considered when studying the downward flux of particulate matter in the upper ocean.
 The patchiness associated with both particle production and submesoscale features poses a real observational challenge to properly resolve vertical fluxes.
-Based on our findings, subsequent studies should focus on testing the impact of patchiness on vertical fluxes: In the wintertime, when size spectral slope is steep and submesoscale dynamics most active, vertical fluxes could be grossly underestimated depending on the level of co-occurrence between particle production and stronger vertical currents.
+Based on our findings, subsequent studies should focus on testing the impact of patchiness on vertical fluxes.
+In the wintertime, when size spectral slope is steep and submesoscale dynamics most active, vertical fluxes could be grossly underestimated depending on the level of co-occurrence between particle production and stronger vertical currents.
 
@@
 
-\item Submesoscale dynamics generally enhance downward fluxes by increasing the contribution of slower-sinking particles to the total flux by increasing the number of particle advected downward by ocean currents.
-The contribution of slower-sinking particles to the total flux is found to be at least significant, and can be dominant in certain conditions.
-\item Contribution of slower-sinking particles to downward biomass fluxes export depends on the slope of the particle size spectra (i.e., Junge Slope), that controls the relative number of particles per size class.
+\item Submesoscale dynamics generally enhance the downward particulate flux by increasing the contribution of slower-sinking particles to the total flux through advective transport.
+The  slower-sinking particles are found to be significant for export, and can be even make the dominant contribution under certain conditions.
+\item The contribution of slower-sinking particles to the downward biomass flux depends on the slope of the particle size spectra (i.e., the Junge Slope), that controls the relative number of particles per size class.
 Two cases emerge from this study:
 \begin{enumerate}
-	\item If the Junge slope is smaller than 3, larger particles contribute most to vertical biomass fluxes independently of flow dynamics, as there are no mechanism capable of selectively advecting slower-sinking particles.
+	\item If the Junge slope is smaller than 3, larger particles contribute most to vertical biomass fluxes independently of flow dynamics, as there are no mechanisms capable of selectively advecting slower-sinking particles.
 The system is described as gravitationally-driven.
-	\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become the determining factor on which particle classes dominate the downward fluxes: as submesoscale dynamics become more active, an ageostrophic circulation leading to larger vertical velocities develops.
+	\item If the Junge slope is greater than 3, as most commonly observed, ocean dynamics become key for determining which particle classes dominate the downward flux.
+As submesoscale dynamics become more active, ageostrophic circulations leading to larger vertical velocities develop.
 In these conditions, downward biomass fluxes are largely driven by the slower-sinking particle classes.
 	\end{enumerate}
-\item Remineralization processes logically reduce the amplitude of biomass fluxes.
-However, it unexpectedly enhances the role played by slower-sinking particles as the impact of remineralization is larger on faster-sinking particles by affecting both biomass content and sinking velocity.
+\item Remineralization processes logically reduce the amount of biomass flux.
+However, it unexpectedly enhances the role of slower-sinking particles, which are are advectively transported.
+The impact of remineralization is greater on faster-sinking particles since it affects both the biomass content and their sinking velocity.
 \end{enumerate}
@@
 \section*{Acknowledgments}
-
-The authors acknowledge support from the National Aeronautics and Space Administration as part of the EXport Processes in the global Ocean from RemoTe Sensing (EXPORTS) program - grant NNX16AR48G.
+The work was funded by NASA grant NNX16AR48G, to complement the EXport Processes in the global Ocean from RemoTe Sensing (EXPORTS) program.
 We would like to thank A.
@@
 Glider data is archived at the University of Washington's Library \citep[\url{https://digital.lib.washington.edu/researchworks/handle/1773/41656};][]{Pelland_2018_data}.
-Model outputs, and particle trajectories are freely available on request.
+%Model outputs, and particle trajectories are available on request.
 % Finally, we are grateful to the two anonymous reviewers for their valuable comments and suggestions.

### 2019-08-28 size_differentiated_export.tex
Updates from Overleaf

@@
 A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012,Mahadevan_2016}.
-Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2008,Klein_2009,McWilliams_2016}.
+Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2013b,Klein_2009,McWilliams_2016}.
 In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}.
@@
 The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}.
-Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2008,Rudnick_2001, Buckingham_2016}.
+Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2013b,Rudnick_2001, Buckingham_2016}.
 

### 2019-08-28 size_differentiated_export.tex
attempt to fix an issue

--- 2019-08-28 size_differentiated_export.tex
@@
 In the horizontal, the prescribed density fronts progressively become unstable within the first 60 days of the experiment (Figure \ref{fig: Papa_summer}).
-During this time, the Total Kinetic Energy (KE$_{\text{tot}}$) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation.
-The flattening of the KE$_{\text{tot}}$ curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments.
+During this time, the Total Kinetic Energy (KE$_$tot) contained in the model domain slowly increases before reaching a maximum at doy 162, where it remains relatively constant for the rest of the simulation.
+The flattening of the KE$_$tot curve is used to determine the time necessary for the simulation to spin-up, hence determining the start day of the particle-tracking experiments.
 The ocean dynamics associated with \textit{Papa\_summer} are characterized using PDFs of horizontal buoyancy gradients ($M^2 = |\nabla_Hb|^2$), vertical velocities ($w$), and Rossby numbers computed from the normalized vertical component of the relative vorticity (Ro $=(v_x - u_y)/f$ where $f$ = 1.12$\times10^{-4}$; Figure \ref{fig: dynamics}).
@@
 Because of these stronger density gradients, combined with the alternating zonal winds and constantly negative surface heat flux, the fronts become unstable more rapidly than in summer (Figure \ref{fig: Papa_winter}).
-As a result, KE$_{\text{tot}}$ starts to plateau at doy 48.
+As a result, KE$_$tot starts to plateau at doy 48.
 The experiment is considered spun-up by doy 50 and the particle-tracking experiment is initialized.

### 2019-08-28 size_differentiated_export.tex

--- 2019-08-28 size_differentiated_export.tex
@@
 \usepackage{url} %this package should fix any errors with URLs in refs.
+\usepackage{amsmath}
 
@@
 The `depth anomaly' is with respect to the `expected' sinking depth (= sinking speed $\times$ time since release).
-	%Gridded anomaly in the median depth of particles 25 days after particle release in the Winter experiment, with 
-	%sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d. 
-	Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\timest$.
+Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\times t$.
 [right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class.

### 2019-08-28 size_differentiated_export.tex
Final version submited to GBC

@@
 \usepackage{amsmath}
-
-% FIXME command
-\newcommand{\fixme}[1]{\color{red}$<$\textbf{FIX ME: #1}$>$\color{black}}
 
@@
 	\begin{keypoints}
-\item Submesoscale dynamics enhance the contribution of slow-sinking particles to POC export, depending on their intensity and on the fraction of biomass in the slow sinking particle classes.
-\item Remineralization processes can enhance the contribution of slow-sinking particles to the point where these particles sometimes dominate POC export
+		\item Submesoscale dynamics enhance the contribution of slow-sinking particles to POC export, especially for steep particle size-spectrum slopes
+		\item Remineralization processes intensify the role of slow-sinking particles, to the point where these particle sometime dominate POC export
 	\end{keypoints}
@@
 		\centering
-	\includegraphics[width = .6\linewidth]{figures/Fig1_model_domain}
+		\includegraphics[width = .6\linewidth]{Fig1_model_domain}
 		\caption{PSOM model setup.
@@
 			Surface heat flux               	        & -46.8 -- +167.5 W m$^{-2}$ & -57.6 -- +15.3 W m$^{-2}$  \\
-		Maximum M$^2$ ($\times$10$^{-8}$)	        &                           &                           \\[-.25cm]
-		\multicolumn{1}{|r|}{initial}	            & 3.2 s$^{-2}$              & 33.9 s$^{-2}$             \\[-.25cm]
+			Maximum M$^2$ ($\times$10$^{-8}$)	        &                           &                           \\
+			\multicolumn{1}{|r|}{initial}	            & 3.2 s$^{-2}$              & 33.9 s$^{-2}$             \\
 			\multicolumn{1}{|r|}{spun-up}	            & 12.0 s$^{-2}$             & 50.0 s$^{-2}$             \\	
-		Maximum N$^2$ ($\times$10$^{-4}$)	        &                           &                           \\[-.25cm]
-		\multicolumn{1}{|r|}{initial}	            & 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\[-.25cm]
+			Maximum N$^2$ ($\times$10$^{-4}$)	        &                           &                           \\
+			\multicolumn{1}{|r|}{initial}	            & 1.5 s$^{-2}$              & 1.6 s$^{-2}$              \\
 			\multicolumn{1}{|r|}{spun-up}	            & 3.1 s$^{-2}$              & 1.1 s$^{-2}$              \\	
-		Averaged mixed layer depth                  &                           &                           \\[-.25cm]
-		\multicolumn{1}{|r|}{initial}	            & 73 m                      & 85 m                      \\[-.25cm]
+			Averaged mixed layer depth                  &                           &                           \\
+			\multicolumn{1}{|r|}{initial}	            & 73 m                      & 85 m                      \\
 			\multicolumn{1}{|r|}{spun-up}	            & 11 m                      & 93 m                      \\	
@@
 	\begin{figure}[t]
-	\includegraphics[width = 1\linewidth]{figures/Fig2_Papa500_summer}
+		\includegraphics[width = 1\linewidth]{Fig2_Papa500_summer}
 		\caption{PSOM configuration for \textit{Papa\_summer}.
@@
 	\begin{figure}[ht]
-	\includegraphics[width = 1\linewidth]{figures/Fig3_Papa500_winter}
+		\includegraphics[width = 1\linewidth]{Fig3_Papa500_winter}
 		\caption{PSOM configuration for \textit{Papa\_winter}.
@@
 		\centering
-	\includegraphics[width = .49\linewidth]{figures/Fig4b.png}
-	\includegraphics[width = .49\linewidth]{figures/Fig4a.png}
+		\includegraphics[width = .49\linewidth]{Fig4b.png}
+		\includegraphics[width = .49\linewidth]{Fig4a.png}
 		\caption{Relative number of particles (left) and biomass (right) as a function of sinking velocity $w_s$.
@@
 		\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig5_dynamic_signature_w_valid}
+		\includegraphics[width = 1\linewidth]{Fig5_dynamic_signature_w_valid}
 		\caption{Snapshots of $M^2$ (top), $\zeta /f$ (middle), and $w$ (bottom) half-way through the particle tracking experiment for \textit{Papa\_summer} (left) and \textit{Papa\_winter} (right), with the Mixed Layer Depth indicated by the solid black line.
@@
 		\centering
-	\includegraphics[width = .8\linewidth]{figures/Fig6.png}
+		\includegraphics[width = .8\linewidth]{Fig6.png}
 		\caption{[left] 
@@
 		\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig7.png}
+		\includegraphics[width = 1\linewidth]{Fig7.png}
 		\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
@@
 As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}).
+
 	%FIG8
@@
 		\centering
-	\includegraphics[width = 1\linewidth]{figures/Fig8.png}
+		\includegraphics[width = 1\linewidth]{Fig8.png}
 		\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
@@
 All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website \citep[\url{https://www.pmel.noaa.gov/ocs/Papa};][]{PMEL_data} and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945} \citep{Gaillard_2015}.
-Glider data is archived at the University of Washington's Library \citep[\url{https://digital.lib.washington.edu/researchworks/handle/1773/41656};][]{Pelland_2018_data}.
+Glider data is archived at the University of Washington's Library \citep[\url{http://hdl.handle.net/1773/41656};][]{Pelland_2018_data}.
 %Model outputs, and particle trajectories are available on request.

### 2019-12-25 size_differentiated_export.tex
Reviews
Include the reviewers' comments and addresses some of them

@@
 \usepackage{amsmath}
+\usepackage{ulem}
 
@@
 %   \change[editor]{Text to remove}{Text to add}
+
+% The FIXME macro
+\newcommand{\fixme}[1]{\color{red}$<$\textbf{#1}$>$\color{black}}
+% The AUTHOR response macro
+\newcommand{\rep}[1]{\color{blue}$<$\textbf{AUTHORS}: \textit{#1}$>$\color{black}\\}
 
@@
 
-	\correspondingauthor{M. Dever}{mdever@whoi.edu}
+	\correspondingauthor{Mathieu Dever}{mdever@whoi.edu}
 	%% ------------------------------------------------------------------------ %%
@@
 	%% ------------------------------------------------------------------------ %%
+	\pagebreak
+
+	\begin{itemize}
+	{\footnotesize
+	\item \fixme{First, it is not clear why the authors have chosen to release particles only at the base of the euphotic zone between 75-85, which is within 20m of the horizon defined as the export depth (100m).
+In fact, particles are produce throughout the entire euphotic zone, and the production rate (i.e.
+NPP) is generally highest within the first 10-20m where light is ample.
+Distributing the particles through the euphotic zone in this way would almost certainly diminish the contribution of small particles to export, as they would spend significantly longer remineralizing within the mixed layer before passing the export horizon.
+I suggest a new simulation with particles initially distributed between 0-80m, or a clearer reasoning for selecting 75-85m as the release depth.}
+	\rep{We were actually careful to never use the words ``depth horizon", for the same reason that we focus on vertical fluxes as opposed to ``export".
+Nevertheless, The base of the euphotic zone is preferred in our study for three main reasons:
+		\begin{enumerate}
+			\item A series of non-trivia important transformations occur in the euphotic zone (e.g., grazing, material packaging, and many others; see Denman and Pena 1999 for example) that are not captured in our idealized setup, and are far beyond the scope of our study.
+By seeding particles at the base of the euphotic layer, we focus on the particulate material available to export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than advection.
+as demonstrated in this study).
+			\item The main results are expressed in terms of vertical fluxes.
+Vertical fluxes of particulate matter in the ML are not necessarily relevant to particle export, for the reasons detailed above.
+Including fluxes in the ML would introduce a bias into our results that is not relevant to our objectives.
+			\item Seeding over 80 m instead of 10 m would require 8 times as many particles, as it is important to preserve particle density to adequately capture the physical dynamics as small scale (i.e., if particle seeding is too sparse, the presence of submesoscale dynamics would have little impact as no particles would be moving through these features).
+This would bring the total amount of particles tracked from $\sim$6 millions to $\sim$48 millions, largely limiting the number of experiments we could conduct in a reasonable time frame.
+		\end{enumerate}
+
+	\item \fixme{Second, it is unclear why 5m/day is selected for the largest particle class.
+Studies using Underwater Vision Profilers reveal that a large portion of the particle flux is contributed by large aggregates of 0.1-5mm, which can have sinking speeds above 100m/day (see Guidi et al.
+2008, Kiko et al.
+2017).
+Comparing the summer and winder simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity.
+This condition would not be met if an aggregate particle class with sinking velocity of 100m/day were included.
+I suggest the inclusion of an additional "large aggregate" size class with appropriate sinking speed.}
+
+	\item \fixme{Finally, the analysis demonstrated in Figures 7 and 8 does not seem appropriate for gauging the contribution of small and large particles to export, and the role of remineralization.
+As far as I understand, the insets in these figures show the flux associated with each particle class at 25 days after the particle release, computed based on their abundance and velocity (advective plus sinking).
+But why is the flux at day 25 the important quantity?
+By this time, the large particles have had time to decay to a size where their sinking velocity is negligible, and therefore their contribution to the flux will be small.
+But, what about all of the large particles that settled across the export horizon (100m) earlier in the simulation, while their sinking velocity is still high?
+Really, we should be interested in how much of the initial biomass in each size category has "escaped" through the export horizon by the end of the simulation, i.e.
+their time-integrated contribution to export.
+For particles released at 80m, sinking at 5m/day and remineralizing at a rate of 0.13/day, it seems that at least 50\% of the inital biomass in the large size category must be exported through the 100m horizon, before remineralizing.
+In contrast, Figure 6 shows that only a very small fraction of the small particles reach 100m in winter, even when they are not remineralizing.
+It therefore seems that even in winter, large particles must dominate the integrated export flux in the simulation with remineralization, contradicting the second major conclusion of the study.
+I suggest the authors repeat their analysis, comparing time-integrated export through 100m in order to assess the contribution of large vs.
+small particles.}
+
+	\item \sout{Line 306: Is it three weeks, or 28 days (four weeks)?}
+
+	\item \sout{Figure 7+8: It would be useful to point out either in the caption or axis label that the x axes are the vertical velocity combining both sinking and advective components, and that the velocity in the legends is the initial sinking velocity.
+This confused me for a few minutes.}
+
+	\item \fixme{Acknowledgements: Will the model output be archived for public access?}
+}	
+	\end{itemize}
+	\pagebreak
+
+	\color{red}
+	\section*{Range of sinking speeds.}
+	The sinking speed examined by the authors are 0.025, 0.05, 1 and 5 m/d.
+All these values would be considered as "slow sinking rate" by the community.
+Yet, the manuscript concludes on the relative contribution of slow and fast sinking particles, which is misleading.
+It also means that the authors cannot really conclude about the relative role of particles that have sinking rates similar in magnitude or faster than submesoscale motions (i.e.
+50-300 m/d).
+
+	\begin{itemize}
+	\item Throughout the text, the authors should be very clear about what they call fast and slow sinking particles.
+They should also compare the values they use to existing observations of rates.
+I recommend to see Baker et al 2017 or Riley et al 2016 for example who present in-situ observations of sinking speed and define slow < 20 m/d and fast > 20 m/d.
+Also note that this nomenclature is consistent with the rates used in ocean biogeochemical models, which usually have a fast sinking rate of 50-200 m/d, and sometimes an additional pool with slow sinking rate of 1-5 m/d.
+
+	\item The authors need to justify their choice, discuss the implications of this choice and explain how it informs the current view of the community on POC export.
+The authors should justify the narrow range of vertical velocity they explore.
+Prior observation-based studies emphasize the importance of particles sinking at slow rates (< 10 m/d) but also those sinking at very fast rates similar in magnitude to submesoscale vertical motions (200-300 m/d) (e.g.
+Baker et al 2017, Riley et al 2016, Stuckel et al.
+2017b).
+What are the reasons to look at only very slow sinking particles?
+Is it because of limitations related to the Stokes Law?
+Is it because the model is not adapted to look at faster sinking rates.
+
+	\item By limiting their study to slow sinking particles, the authors target by design the particles that will be most sensitive to submesoscale dynamics (see Stukel et al) and exclude particles that sink with rates similar or faster than submesoscale motions and that can efficiently export at depth and participate to carbon sequestration.
+Indeed, submesoscale is largely trapped in the upper ocean and only have a limited impact on export at greater depth (see previous discussions of these effects in Stukel et al, Erikson et al and Resplandy et al).
+The authors should acknowledge these limitations and discuss their implications.
+
+	\item The author could introduce the study by acknowledging up front that slow sinking particles are the particles most impacted by submesoscale (as shown in previous papers) and this is why they are the focus of this paper that explores the sensitivity to size spectrum etc.
+	\end{itemize}
+
+	\section*{Remineralization and slower sinking particle contribution.}
+	The choice of some parameter appears arbitrary.
+I like the fact that the authors sweep the parameter space of the size spectrum ($\xi$ = 2, 3, 4).
+The choice of this parameteris however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).
+
+	\begin{itemize}
+	\item Could you please present the case where the biomass spectrum slope is positive? Same as Figure 8 but with ξ = 2 and contrast it with the case of $\xi$ = 4?
+
+	\item The authors briefly mention that slopes greater than 3 have been observed (L640).
+Could this discussion be augmented?
+What observational constraints do we have on the spectrum slope?
+Do we know if the biomass spectrum slope is positive or negative?
+Is it likely to change sign with season, biomes, looming conditions etc.?
+(not necessarily around station PAPA).
+Bridging your modeling results with available observations would greatly benefit the paper and facilitate the use of your conclusions by the community (please look into prior work to make these links).
+I strongly encourage you to discuss the implications of this result, what they mean for people measuring particles and export, what they should be looking for in the field?
+
+	\item The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague "under specific conditions ..." (L27).
+Please try to clarify what this means in Layman terms in the abstract.
+
+	\item How do your results depend on the remineralization (0.13 d-1) length-scale? 
+	\end{itemize}
+
+	\section*{Literature Survey and Discussion}
+	It is very concerning that the authors are missing key recent papers published on the subject, including observation-based papers that should be discussed with the author's modeling results.
+Please find below a list of relevant papers that should be included in introduction and/or discussion.
+This list is absolutely not exhaustive.
+
+	\section*{The introduction lacks some coherence. The different paragraphs are not clearly connected and the flow is rather tedious. It needs streamlining. }
+		\begin{itemize}
+	\item	The second paragraph presents detailed theoretical arguments about particle size spectrum and sinking velocities. 
+	\item	The third paragraph list some previous results suggesting a role of submesoscale vertical velocities in exporting carbon.
+Note that numerous recent papers, including observation-based studies, are missing from this list (see below).
+	\item	The fourth paragraph describe submesoscale frontogenesis.
+	\item	The fifth paragraph repeat the idea that submesoscale can export POC.
+	\item	The sixth paragraph add to the first paragraph on our knowledge about particle size and sinking speed.
+I would merge paragraphs 6 and 2.
+I would also strongly suggest to mention observations (paragraph 6) and what observed sinking speeds are (please add references for this.
+E.g.
+Baker et al 2017, Riley et al 2016 etc.).
+Then I would present the theoretical arguments (paragraph 2).
+	\item	Paragraphs 8 and 7 should be merged with paragraph 7.
+I suggest to present what the aim of the study is (some of paragraph 8) before mentioning the processes that your model does not resolve (e.g.
+surface wave in paragraph 7)
+		\end{itemize}
+
+	\section*{Abstract}
+	The abstract is long and technical but at the same time vague in presenting the key results to the reader.
+For example, the following sentences list raw modeling results without hinting at the mechanistic drivers of this response in the model.
+	"a steeper particle size spectrum increases the relative contribution of smaller slow-sinking particles." "Implementing a remineralization scheme generally decreases the total amount of biomass exported[...]", "Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles."
+
+	\section*{Section 2.2}
+	The method section is detailed and relatively clear except for section 2.2.3.
+To clarify this section, the author should give some contextual information about the different metrics (N, B etc.) and why they are presented to the reader.
+	\begin{itemize}
+			\item Link to observational constraints on the slope of the size spectrum (see comment \#2)?
+
+	\item Explain why you examine the dependence between these different metrics, e.g.
+something like "we explore the sensitivity of X and Y to the particle size spectrum .....
+We consider three distributions with slopes of Z, ZZ.." etc.
+		\end{itemize}
+
+	\section*{Minor comments:}
+	\begin{itemize}	
+	\item Can you specify if and how equation 9 differs from the traditional Martin curve?
+
+	\item L40: the last sentence of the first paragraph is vague and unnecessary. I would delete it.
+	\item \color{black}\sout{L 162: Problem with reference Laboratory, 2018?}\color{red}
+
+	\item Figures 7 and 8. Please label the size classes on the insert or at least mention the colors-size relationship in the caption.
+
+	\item The model data used in this study should be made available as requested by AGU standards.
+		\end{itemize}
+
+	References. 
+	Baker, C.A., Henson, S.A., Cavan, E.L., Giering, S.L.C., Yool, A., Gehlen, M., Belcher, A., Riley, J.S., Smith, H.E.K., Sanders, R., 2017.
+Slow-sinking particulate organic carbon in the Atlantic Ocean: Magnitude, flux, and potential controls.
+Global Biogeochemical Cycles 31, 1051-1065.
+https://doi.org/10.1002/2017GB005638\\
+	Boyd, P.W., Claustre, H., Levy, M., Siegel, D.A., Weber, T., 2019.
+Multi-faceted particle pumps drive carbon sequestration in the ocean.
+Nature 568, 327-335.
+https://doi.org/10.1038/s41586-019-1098-2\\
+	Erickson, Z.K., Thompson, A.F., 2018.
+The Seasonality of Physically Driven Export at Submesoscales in the Northeast Atlantic Ocean.
+Global Biogeochemical Cycles 32.
+https://doi.org/10.1029/2018GB005927\\
+	Llort, J., Langlais C., Matear R., Moreau S., Lenton A., Strutton Peter G., 2018.
+Evaluating Southern Ocean Carbon Eddy‐Pump From Biogeochemical‐Argo Floats.
+Journal of Geophysical Research: Oceans 123, 971-984.
+https://doi.org/10.1002/2017JC012861\\
+	Resplandy, L., Lévy, M., McGillicuddy, D.J., 2019. Effects of Eddy‐Driven Subduction on Ocean Biological Carbon Pump. Global Biogeochem. Cycles 2018GB006125. https://doi.org/10.1029/2018GB006125\\
+	Riley, J.S., Sanders, R., Marsay, C., Moigne, F.A.C.L., Achterberg, E.P., Poulton, A.J., 2012.
+The relative contribution of fast and slow sinking particles to ocean carbon export.
+Global Biogeochemical Cycles 26.
+https://doi.org/10.1029/2011GB004085\\
+	Stukel, M.R., Aluwihare, L.I., Barbeau, K.A., Chekalyuk, A.M., Goericke, R., Miller, A.J., Ohman, M.D., Ruacho, A., Song, H., Stephens, B.M., Landry, M.R., 2017a.
+Mesoscale ocean fronts enhance carbon export due to gravitational sinking and subduction.
+Proceedings of the National Academy of Sciences 114, 1252-1257.
+https://doi.org/10.1073/pnas.1609435114\\
+	Stukel, M.R., Ducklow, H.W., 2017.
+Stirring Up the Biological Pump: Vertical Mixing and Carbon Export in the Southern Ocean.
+Global Biogeochem.
+Cycles 31, 2017GB005652.
+https://doi.org/10.1002/2017GB005652\\
+	Stukel, M.R., Song, H., Goericke, R., Miller, A.J., 2017b.
+The role of subduction and gravitational sinking in particle export, carbon sequestration, and the remineralization length scale in the California Current Ecosystem: Subduction and sinking particle export in the CCE.
+Limnology and Oceanography 63, 363-383.
+https://doi.org/10.1002/lno.10636\\
+
+	\vfill
+
+	\pagebreak
+
+	\begin{itemize}
+	\item Regarding submesoscales during the summer -- it would be worth calculating the mixed layer deformation radius during summer.
+I suspect that it is at or less than your model resolution.
+This may mean that the real ocean could have a summertime advection of particles just at very small scales (and unlikely to penetrate too deep).
+Worth considering in your interpretation/discussion of results.
+
+	\item John Taylor has a nice paper (JPO 2018) where we looked at a similar problem with his LES and in some cases, buoyant particles. It might be worth citing.
+
+	\item I know computing time is always an issue, but it would be interesting to run these at higher (or lower) resolution to see how the fluxes change.
+I would be surprised if they were converging -- in fact, I am not sure you would ever expect convergence depending on the wavenumber spectrum of w.
+	\end{itemize}
+
+	\pagebreak
+	\color{black}
 	\section{Introduction}
@@
 Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity).
-Particles are tracked for three weeks (28 days).
+Particles are tracked for four weeks (28 days).
 Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles.
@@
 		\includegraphics[width = 1\linewidth]{Fig7.png}
-		\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
-Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class.
+		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity (sinking + advective) along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
 Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.}
@@
 		\includegraphics[width = 1\linewidth]{Fig8.png}
-		\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
-Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class.
+		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity (sinking + advective) along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
 Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}

### 2019-12-26 size_differentiated_export.tex
Deal with reviews
- Added a separate file for responses to reviews.
- included trackchanges in the main document
- included reviews and submitted manuscript

--- 2019-08-28 size_differentiated_export.tex
@@
 \usepackage{amsmath}
+\usepackage{ulem}
 
 % Trackchanges package
-%\usepackage{trackchanges}
+\usepackage{trackchanges}
 %% PLEASE USE THE FOLLOWING COMMANDS
@@
 	%% ------------------------------------------------------------------------ %%
+
 	\section{Introduction}
@@
 Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity).
-Particles are tracked for three weeks (28 days).
+Particles are tracked for \change{three}{four} weeks (28 days).
 Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles.
@@
 		\includegraphics[width = 1\linewidth]{Fig7.png}
-		\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
-Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class.
+		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity \add{(sinking + advective)} along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
 Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.}
@@
 		\includegraphics[width = 1\linewidth]{Fig8.png}
-		\caption{Probability Distribution Function (PDF) of relative biomass versus vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
-Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class.
+		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity \add{(sinking + advective)} along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
 Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}

### 2019-12-26 figures/code/Fig4.m

@@ -26,6 +26,21 @@ B0025_4 = B0*(0.025/wmax).^((3-slope)/2);
 B1_4 = B0*(1/wmax).^((3-slope)/2);
 B5_4 = B0*(5/wmax).^((3-slope)/2);
 
+% For Junge slope = 5
+slope = 5;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_5 = B0*(0.025/wmax).^((3-slope)/2);
+B1_5 = B0*(1/wmax).^((3-slope)/2);
+B5_5 = B0*(5/wmax).^((3-slope)/2);
+
+% For Junge slope = 6
+slope = 6;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_6 = B0*(0.025/wmax).^((3-slope)/2);
+B1_6 = B0*(1/wmax).^((3-slope)/2);
+B5_6 = B0*(5/wmax).^((3-slope)/2);
 %%
 
 % Set colors for each class
@@ -98,7 +113,7 @@ end
 set(gca,'xtick',Xtick,'xticklabel',xticklab)
 xlabel('Equivalent Stokes radius [\mum]')
 set(gcf,'color','w')
-export_fig -r300 Fig4a.png
+%export_fig -r300 Fig4a.png
 %%
 
 
@@ -190,4 +205,4 @@ end
 set(gca,'xtick',Xtick,'xticklabel',xticklab)
 xlabel('Equivalent Stokes radius [\mum]')
 set(gcf,'color','w')
-export_fig -r300 Fig4b.png
+%export_fig -r300 Fig4b.png

### 2019-12-26 response_to_reviewers.tex

\documentclass[12pt,letter]{article}
\usepackage{geometry}
\usepackage{fullpage}
\usepackage{float}
%\usepackage{cite}
\usepackage{amsmath}
\usepackage{color}
\usepackage{soul}
\usepackage{listings}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{natbib}

\singlespacing

% The FIXME macro
\newcommand{\fixme}[1]{\color{red}$<$\textbf{FIX ME: #1}$>$\color{black}}

% The NOTE macro
\newcommand{\note}[1]{\color{red}$<$\textbf{NOTE}: \textit{#1}$>$\color{black}}

% The postit macro
\newcommand{\postit}[1]{\color{blue}$<$\textbf{NOTE: #1}$>$\color{black}}

% The AUTHOR response macro
\newcommand{\rep}[1]{\color{blue}$<$\textbf{AUTHORS}: \textit{#1}$>$\color{black}\\}

\setlength\parindent{0pt}

% Change the subsection numbering style
\renewcommand\thesubsection{\alph{subsection}.}
% Change the font size of sections
\usepackage{sectsty}
\sectionfont{\normalsize}
\subsectionfont{\small}
\setlength\parindent{0pt}

%_____________________________________________
\begin{document}

% Article title and author
\begin{center}
\large
\textbf{
Response to reviewers\\}
\end{center}
\small

\section{Response to Editor's comments}

\section{Comments from Reviewer  \#1}
\small
\textit{First, it is not clear why the authors have chosen to release particles only at the base of the euphotic zone between 75-85, which is within 20m of the horizon defined as the export depth (100m). In fact, particles are produce throughout the entire euphotic zone, and the production rate (i.e. NPP) is generally highest within the first 10-20m where light is ample. Distributing the particles through the euphotic zone in this way would almost certainly diminish the contribution of small particles to export, as they would spend significantly longer remineralizing within the mixed layer before passing the export horizon. I suggest a new simulation with particles initially distributed between 0-80m, or a clearer reasoning for selecting 75-85m as the release depth.\\}

We carefully consider this question during our study. We deliberately  did not rely on a ``depth horizon" due to the facts that it is not consistently defined in the literature, and that recent work questions the validity of selecting a depth horizon as an ``export depth" , arguing for a dynamics-based definition \citep{Palevsky_2018}. This is one of the reasons why the conclusions focus on export fluxes, rather than export \textit{per se}, as the latter would require defining a possibly controversial export horizon.\\

Additionally, the base of the euphotic zone is preferred in our study for three main reasons: 
			\begin{enumerate}
				\item A series of non-trivia important transformations occur in the euphotic zone \citep[e.g., grazing, material packaging, and many others; see][for example]{Denman_1999} that are not captured in our idealized setup, and are far beyond the scope of our study. By seeding particles at the base of the euphotic layer, we focus on the particulate material available to export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than possibly advection. as demonstrated in this study). 
				\item The main results are expressed in terms of vertical fluxes. Vertical fluxes of particulate matter within the ML are not necessarily relevant to particle export, for the reasons detailed above. Including fluxes in the ML would introduce a bias into our results that is not relevant to our objectives.
				\item Seeding over 80 m instead of 10 m would require 8 times as many particles, as it is important to preserve particle density to adequately capture the physical dynamics as small scale (i.e., if particle seeding is too sparse, the presence of submesoscale dynamics would have little impact as no particles would be moving through these features). This would bring the total amount of particles tracked from $\sim$6 millions to $\sim$48 millions, largely limiting the number of experiments we could conduct in a reasonable time frame.
			\end{enumerate}

Finally, the small particles released at the base of the euphotic layer do not aim to represent small particles at the time of particle production. It can also represent larger particles at production that went through remineralization in the ML.

\note{Based on this comment, the text has been modified to better justify the choices outlined above. Cite where and how text has been modified.}  \\

\textit{Second, it is unclear why 5m/day is selected for the largest particle class. Studies using Underwater Vision Profilers reveal that a large portion of the particle flux is contributed by large aggregates of 0.1-5mm, which can have sinking speeds above 100m/day (see Guidi et al. 2008, Kiko et al. 2017). Comparing the summer and winder simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity. This condition would not be met if an aggregate particle class with sinking velocity of 100m/day were included. I suggest the inclusion of an additional "large aggregate" size class with appropriate sinking speed.\\}

\note{Hmm. this is a very good comment. This is true, for ``very large" particles, the biomass flux will be larger than for small particles. 2 things can nuance this: (1) While the flux of biomass is larger for 100 m/day particles, it requires an infinite reservoir of those large particles to be able to relate the larger flux to larger export. Are 100 m/day particles present all year, everywhere? If not, the biomass flux would be larger until the source is exhausted -- which is more likely to happen for 100 m/day particles than for smaller particles... (2) This is true, for $\xi$ up to 5 (based on Equation 8). Above that, the biomass flux spectrum would have a negative slope. This is not known to occur in the ocean though. But this value could change to smaller slopes if other relationships are used to relate $w_s$ and $B$ to $r$.
How to address this comment? Including a 100 m/day class will dilute the key conclusions of the study significantly, as the \% obtained in Fig 7 and 8 will be much smaller for small particles. It could be addressed by arguing that we focus on the transitional range of sinking velocities?\\}

 \textit{Finally, the analysis demonstrated in Figures 7 and 8 does not seem appropriate for gauging the contribution of small and large particles to export, and the role of remineralization. As far as I understand, the insets in these figures show the flux associated with each particle class at 25 days after the particle release, computed based on their abundance and velocity (advective plus sinking).\\}

 \rep{This is correct}

 \textit{But why is the flux at day 25 the important quantity? By this time, the large particles have had time to decay to a size where their sinking velocity is negligible, and therefore their contribution to the flux will be small. But, what about all of the large particles that settled across the export horizon (100m) earlier in the simulation, while their sinking velocity is still high? Really, we should be interested in how much of the initial biomass in each size category has "escaped" through the export horizon by the end of the simulation, i.e. their time-integrated contribution to export. For particles released at 80m, sinking at 5m/day and remineralizing at a rate of 0.13/day, it seems that at least 50\% of the inital biomass in the large size category must be exported through the 100m horizon, before remineralizing. In contrast, Figure 6 shows that only a very small fraction of the small particles reach 100m in winter, even when they are not remineralizing. It therefore seems that even in winter, large particles must dominate the integrated export flux in the simulation with remineralization, contradicting the second major conclusion of the study. I suggest the authors repeat their analysis, comparing time-integrated export through 100m in order to assess the contribution of large vs. small particles.}

\note{This is a good point. For Fig 7, the timestamp selected to display the results has little impact on the conclusions. A similar plot was produced for time-average biomass fluxes, and the results are only marginally different \textbf{(plots included in this document)}. The results are therefore displayed for day 25 for consistency, as this is the day used to display results in Fig 8.\linebreak For fig 8.}

\textit{Line 306: Is it three weeks, or 28 days (four weeks)?}\\
\rep{Text has been modified accordingly.}
\textit{Figure 7+8: It would be useful to point out either in the caption or axis label that the x axes are the vertical velocity combining both sinking and advective components, and that the velocity in the legends is the initial sinking velocity. This confused me for a few minutes.}\\
\rep{Text has been modified accordingly.}
\textit{Acknowledgments: Will the model output be archived for public access?}\\
\rep{Text has been modified accordingly.}

\section{Comments from Reviewer  \#2}

\section*{Range of sinking speeds.}
The sinking speed examined by the authors are 0.025, 0.05, 1 and 5 m/d. All these values would be considered as "slow sinking rate" by the community. Yet, the manuscript concludes on the relative contribution of slow and fast sinking particles, which is misleading. It also means that the authors cannot really conclude about the relative role of particles that have sinking rates similar in magnitude or faster than submesoscale motions (i.e. 50-300 m/d).

\begin{itemize}
	\item Throughout the text, the authors should be very clear about what they call fast and slow sinking particles. They should also compare the values they use to existing observations of rates. I recommend to see Baker et al 2017 or Riley et al 2016 for example who present in-situ observations of sinking speed and define slow < 20 m/d and fast > 20 m/d. Also note that this nomenclature is consistent with the rates used in ocean biogeochemical models, which usually have a fast sinking rate of 50-200 m/d, and sometimes an additional pool with slow sinking rate of 1-5 m/d.

	\item The authors need to justify their choice, discuss the implications of this choice and explain how it informs the current view of the community on POC export. The authors should justify the narrow range of vertical velocity they explore. Prior observation-based studies emphasize the importance of particles sinking at slow rates (< 10 m/d) but also those sinking at very fast rates similar in magnitude to submesoscale vertical motions (200-300 m/d) (e.g. Baker et al 2017, Riley et al 2016, Stuckel et al. 2017b). What are the reasons to look at only very slow sinking particles? Is it because of limitations related to the Stokes Law? Is it because the model is not adapted to look at faster sinking rates.

	\item By limiting their study to slow sinking particles, the authors target by design the particles that will be most sensitive to submesoscale dynamics (see Stukel et al) and exclude particles that sink with rates similar or faster than submesoscale motions and that can efficiently export at depth and participate to carbon sequestration. Indeed, submesoscale is largely trapped in the upper ocean and only have a limited impact on export at greater depth (see previous discussions of these effects in Stukel et al, Erikson et al and Resplandy et al). The authors should acknowledge these limitations and discuss their implications.

	\item The author could introduce the study by acknowledging up front that slow sinking particles are the particles most impacted by submesoscale (as shown in previous papers) and this is why they are the focus of this paper that explores the sensitivity to size spectrum etc. 
\end{itemize}

\section*{Remineralization and slower sinking particle contribution.}
The choice of some parameter appears arbitrary. I like the fact that the authors sweep the parameter space of the size spectrum ($\xi$ = 2, 3, 4). The choice of this parameteris however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).

\begin{itemize}
	\item Could you please present the case where the biomass spectrum slope is positive? Same as Figure 8 but with ξ = 2 and contrast it with the case of $\xi$ = 4?

	\item The authors briefly mention that slopes greater than 3 have been observed (L640). Could this discussion be augmented? What observational constraints do we have on the spectrum slope? Do we know if the biomass spectrum slope is positive or negative? Is it likely to change sign with season, biomes, looming conditions etc.? (not necessarily around station PAPA). Bridging your modeling results with available observations would greatly benefit the paper and facilitate the use of your conclusions by the community (please look into prior work to make these links). I strongly encourage you to discuss the implications of this result, what they mean for people measuring particles and export, what they should be looking for in the field?

	\item The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague "under specific conditions ..." (L27). Please try to clarify what this means in Layman terms in the abstract.

	\item How do your results depend on the remineralization (0.13 d-1) length-scale? 
\end{itemize}

\section*{Literature Survey and Discussion}
It is very concerning that the authors are missing key recent papers published on the subject, including observation-based papers that should be discussed with the author's modeling results. Please find below a list of relevant papers that should be included in introduction and/or discussion. This list is absolutely not exhaustive.

\section*{The introduction lacks some coherence. The different paragraphs are not clearly connected and the flow is rather tedious. It needs streamlining. }
\begin{itemize}
	\item	The second paragraph presents detailed theoretical arguments about particle size spectrum and sinking velocities. 
	\item	The third paragraph list some previous results suggesting a role of submesoscale vertical velocities in exporting carbon. Note that numerous recent papers, including observation-based studies, are missing from this list (see below).
	\item	The fourth paragraph describe submesoscale frontogenesis.
	\item	The fifth paragraph repeat the idea that submesoscale can export POC.
	\item	The sixth paragraph add to the first paragraph on our knowledge about particle size and sinking speed. I would merge paragraphs 6 and 2. I would also strongly suggest to mention observations (paragraph 6) and what observed sinking speeds are (please add references for this. E.g. Baker et al 2017, Riley et al 2016 etc.). Then I would present the theoretical arguments (paragraph 2). 
	\item	Paragraphs 8 and 7 should be merged with paragraph 7. I suggest to present what the aim of the study is (some of paragraph 8) before mentioning the processes that your model does not resolve (e.g. surface wave in paragraph 7)
\end{itemize}

\section*{Abstract}
The abstract is long and technical but at the same time vague in presenting the key results to the reader. For example, the following sentences list raw modeling results without hinting at the mechanistic drivers of this response in the model. 
"a steeper particle size spectrum increases the relative contribution of smaller slow-sinking particles." "Implementing a remineralization scheme generally decreases the total amount of biomass exported[...]", "Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles."

\section*{Section 2.2}
The method section is detailed and relatively clear except for section 2.2.3. To clarify this section, the author should give some contextual information about the different metrics (N, B etc.) and why they are presented to the reader. 
\begin{itemize}
	\item Link to observational constraints on the slope of the size spectrum (see comment \#2)?

	\item Explain why you examine the dependence between these different metrics, e.g. something like "we explore the sensitivity of X and Y to the particle size spectrum ..... We consider three distributions with slopes of Z, ZZ.." etc.
\end{itemize}

\section*{Minor comments:}
\begin{itemize}	
	\item Can you specify if and how equation 9 differs from the traditional Martin curve?

	\item L40: the last sentence of the first paragraph is vague and unnecessary. I would delete it.
	\item L 162: Problem with reference Laboratory, 2018?

	\item Figures 7 and 8. Please label the size classes on the insert or at least mention the colors-size relationship in the caption.

	\item The model data used in this study should be made available as requested by AGU standards.
\end{itemize}

References. 
Baker, C.A., Henson, S.A., Cavan, E.L., Giering, S.L.C., Yool, A., Gehlen, M., Belcher, A., Riley, J.S., Smith, H.E.K., Sanders, R., 2017. Slow-sinking particulate organic carbon in the Atlantic Ocean: Magnitude, flux, and potential controls. Global Biogeochemical Cycles 31, 1051-1065. https://doi.org/10.1002/2017GB005638\\
Boyd, P.W., Claustre, H., Levy, M., Siegel, D.A., Weber, T., 2019. Multi-faceted particle pumps drive carbon sequestration in the ocean. Nature 568, 327-335. https://doi.org/10.1038/s41586-019-1098-2\\
Erickson, Z.K., Thompson, A.F., 2018. The Seasonality of Physically Driven Export at Submesoscales in the Northeast Atlantic Ocean. Global Biogeochemical Cycles 32. https://doi.org/10.1029/2018GB005927\\
Llort, J., Langlais C., Matear R., Moreau S., Lenton A., Strutton Peter G., 2018. Evaluating Southern Ocean Carbon Eddy‐Pump From Biogeochemical‐Argo Floats. Journal of Geophysical Research: Oceans 123, 971-984. https://doi.org/10.1002/2017JC012861\\
Resplandy, L., Lévy, M., McGillicuddy, D.J., 2019. Effects of Eddy‐Driven Subduction on Ocean Biological Carbon Pump. Global Biogeochem. Cycles 2018GB006125. https://doi.org/10.1029/2018GB006125\\
Riley, J.S., Sanders, R., Marsay, C., Moigne, F.A.C.L., Achterberg, E.P., Poulton, A.J., 2012. The relative contribution of fast and slow sinking particles to ocean carbon export. Global Biogeochemical Cycles 26. https://doi.org/10.1029/2011GB004085\\
Stukel, M.R., Aluwihare, L.I., Barbeau, K.A., Chekalyuk, A.M., Goericke, R., Miller, A.J., Ohman, M.D., Ruacho, A., Song, H., Stephens, B.M., Landry, M.R., 2017a. Mesoscale ocean fronts enhance carbon export due to gravitational sinking and subduction. Proceedings of the National Academy of Sciences 114, 1252-1257. https://doi.org/10.1073/pnas.1609435114\\
Stukel, M.R., Ducklow, H.W., 2017. Stirring Up the Biological Pump: Vertical Mixing and Carbon Export in the Southern Ocean. Global Biogeochem. Cycles 31, 2017GB005652. https://doi.org/10.1002/2017GB005652\\
Stukel, M.R., Song, H., Goericke, R., Miller, A.J., 2017b. The role of subduction and gravitational sinking in particle export, carbon sequestration, and the remineralization length scale in the California Current Ecosystem: Subduction and sinking particle export in the CCE. Limnology and Oceanography 63, 363-383. https://doi.org/10.1002/lno.10636\\

\section{Comments from Andy Thompson}
\begin{itemize}
	\item Regarding submesoscales during the summer -- it would be worth calculating the mixed layer deformation radius during summer.  I suspect that it is at or less than your model resolution.  This may mean that the real ocean could have a summertime advection of particles just at very small scales (and unlikely to penetrate too deep).  Worth considering in your interpretation/discussion of results.

	\item John Taylor has a nice paper (JPO 2018) where we looked at a similar problem with his LES and in some cases, buoyant particles. It might be worth citing.

	\item I know computing time is always an issue, but it would be interesting to run these at higher (or lower) resolution to see how the fluxes change.  I would be surprised if they were converging -- in fact, I am not sure you would ever expect convergence depending on the wavenumber spectrum of w.
\end{itemize}

\bibliographystyle{plainnat}
\bibliography{reviews}

\end{document}

### 2020-01-02 Submission_and_reviews/response_to_reviewers.tex
Addressing reviews
Update Fig 7 and 8 based on reviews. Responsded to a few more comments

--- 2019-12-26 response_to_reviewers.tex
@@
 \textit{First, it is not clear why the authors have chosen to release particles only at the base of the euphotic zone between 75-85, which is within 20m of the horizon defined as the export depth (100m).
-In fact, particles are produce throughout the entire euphotic zone, and the production rate (i.e.
+In fact, particles are produced throughout the entire euphotic zone, and the production rate (i.e.
 NPP) is generally highest within the first 10-20m where light is ample.
@@
 
-We carefully consider this question during our study.
-We deliberately  did not rely on a ``depth horizon" due to the facts that it is not consistently defined in the literature, and that recent work questions the validity of selecting a depth horizon as an ``export depth" , arguing for a dynamics-based definition \citep{Palevsky_2018}.
-This is one of the reasons why the conclusions focus on export fluxes, rather than export \textit{per se}, as the latter would require defining a possibly controversial export horizon.\\
+We carefully considered this question during our study.
+We deliberately  did not rely on a ``export depth horizon" due to the facts that it is not consistently defined in the literature, and that recent work questions the validity of selecting a depth horizon as an ``export depth", arguing for a dynamics-based definition \citep{Palevsky_2018}.
+This is one of the reasons why the conclusions focus on export fluxes, rather than export, as the latter would require defining a possibly controversial export horizon.\\
 
@@
 				\item A series of non-trivia important transformations occur in the euphotic zone \citep[e.g., grazing, material packaging, and many others; see][for example]{Denman_1999} that are not captured in our idealized setup, and are far beyond the scope of our study.
-By seeding particles at the base of the euphotic layer, we focus on the particulate material available to export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than possibly advection.
-as demonstrated in this study).
+By seeding particles at the base of the euphotic layer, we focus on the particulate material available to export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than possibly advection, as demonstrated in this study).
 				\item The main results are expressed in terms of vertical fluxes.
@@
 Including fluxes in the ML would introduce a bias into our results that is not relevant to our objectives.
-				\item Seeding over 80 m instead of 10 m would require 8 times as many particles, as it is important to preserve particle density to adequately capture the physical dynamics as small scale (i.e., if particle seeding is too sparse, the presence of submesoscale dynamics would have little impact as no particles would be moving through these features).
+				\item Seeding over 80 m instead of 10 m would require 8 times as many particles, as it is important to preserve particle density to adequately capture the physical dynamics at small scale (i.e., if particle seeding is too sparse, the presence of submesoscale dynamics would have little impact as no particles would be advected through these features).
 This would bring the total amount of particles tracked from $\sim$6 millions to $\sim$48 millions, largely limiting the number of experiments we could conduct in a reasonable time frame.
@@
 
-\note{Based on this comment, the text has been modified to better justify the choices outlined above. Cite where and how text has been modified.}  \\
+Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above  \\
 
@@
 2017).
-Comparing the summer and winder simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity.
+Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity.
 This condition would not be met if an aggregate particle class with sinking velocity of 100m/day were included.
@@
 
-\note{Hmm.
-this is a very good comment.
-This is true, for ``very large" particles, the biomass flux will be larger than for small particles.
-2 things can nuance this: (1) While the flux of biomass is larger for 100 m/day particles, it requires an infinite reservoir of those large particles to be able to relate the larger flux to larger export.
-Are 100 m/day particles present all year, everywhere?
-If not, the biomass flux would be larger until the source is exhausted -- which is more likely to happen for 100 m/day particles than for smaller particles...
-(2) This is true, for $\xi$ up to 5 (based on Equation 8).
-Above that, the biomass flux spectrum would have a negative slope.
-This is not known to occur in the ocean though.
-But this value could change to smaller slopes if other relationships are used to relate $w_s$ and $B$ to $r$.
-How to address this comment?
-Including a 100 m/day class will dilute the key conclusions of the study significantly, as the \% obtained in Fig 7 and 8 will be much smaller for small particles.
-It could be addressed by arguing that we focus on the transitional range of sinking velocities?\\}
+This is a good, thought provoking, point about how does these results for sinking rates much larger than any advective vertical velocity?
+First, we would like to comment on \textit{``Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity."}; This is not necessarily exact in our case.
+At any given time, between 10 and 15\% of the vertical velocity over the model domain is larger than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles.
+
+However, your comment is very relevant: What do our findings mean for sinking rates far exceeding the maximum modeled vertical velocities?
+In that case, $w = w_s$, as the sinking rate largely dominate.
+We want to know if the ratio of fluxes of two large sinking velocity is greater and smaller than one (i.e., the slope of the biomass flux spectrum is positive or negative):
+
+\begin{equation}
+	\frac{B_2w_2}{B_1w_1} >1 \quad \text{with} \quad w_2 > w_1
+\end{equation}
+
+Using Equation 8 in the main text, we obtain:
+\begin{align}
+	\frac{B_0\left(\frac{w_1}{w_0}\right)^{\frac{3-\xi}{2}}w_1}{B_0\left(\frac{w_2}{w_0}\right)^{\frac{3-\xi}{2}}w_2} &> 1\\[.2cm]
+	\left(\frac{w_2}{w_1}\right)^{\frac{5-\xi}{2}} &>1
+\end{align}	
+which is only true for $w_2 > w_1$ if $\xi<$5.
+In other words, if the Junge slope is larger than 5, the slope of the particle size, biomass, AND biomass flux is negative.
+While large, a value of $\xi>5$ is not uneralistic, as it has been estimated from satellite-based algorithm in \cite{Kostadinov_2009}.
+
+To directly address your comment, it is true that for very large aggregates with sinking rates far exceeding the order of magnitude of vertical velocities, the contribution of slower sinking particles is not dominant.
+That has been established a while ago, and is the basis of the traditional 1-D model challenged in our work.
+Our study demonstrates the limitations of such a paradigm, as one considers slower-sinking particles classes.
+Furthermore, for the largest aggregate to constantly be driving the biomass flux, it would require an infinite reservoir of those large particles to be able to relate their larger flux to larger export.
+The biomass flux due to the aggregates would be larger until the source is exhausted -- which is likely to happen more quickly for 100 m/day particles than for smaller particles.
+Additionally, this paradigm is only true if the slope of the particle-size spectrum is smaller than $\sim$5 (based on our scaling).
+
+Including a ``large aggregate" size class sinking at 100m/day, for example, would not provide much more interesting information, in our opinion.
+In fact, the flux of such a size class can be computed theoretically (as $w \approx w_s$) and does not require any model simulations.
+This is, we agree, an important fact to consider.
+As a result, we have modified the text in section 4.2 to put our findings in perspective with aggregates sinking at much faster sinking rates.
 
@@
 A similar plot was produced for time-average biomass fluxes, and the results are only marginally different \textbf{(plots included in this document)}.
-The results are therefore displayed for day 25 for consistency, as this is the day used to display results in Fig 8.\linebreak For fig 8.}
+The results are therefore displayed for day 25 for consistency, as this is the day used to display results in Fig 8.\linebreak For fig 8...
+how to justify using doy 25?
+Should I make a Fig 9 with time series of \%...?}
 
@@
 This confused me for a few minutes.}\\
-\rep{Text has been modified accordingly.}
+\rep{Figure captions have been modified.}
 \textit{Acknowledgments: Will the model output be archived for public access?}\\
 \rep{Text has been modified accordingly.}
+\note{Create a subset dataset necessary to generate figures}
 
 \section{Comments from Reviewer  \#2}
+\rep{We would first like to thank this Reviewer for these very on-point and constructive reviews. They were very helpful to make the manuscript stronger!}
 
@@
 
+\note{The three sinking rates were defined based on having one class virtually non-sinking (0.025 m/day), one class within the range of $w$ measured in summer (1 m/day, which is the \#\# percentile of the PDF for $w$ showed in Fig 5), and one class with similar magnitude than $w$ observed at submesoscale in the winter case (1 m/day, which is the \#\# percentile of the PDF for $w$ showed in Fig 5).
+Selecting a sinking rate much faster than that would bring us back to the traditional 1D model, as the sinking rate would greatly dominate the vertical flux.
+The objective of the study is to capture that transitional part of the size spectrum.
+Station Papa remains a relatively calm region, so submesoscale $w$ are of the order of 50 m/day.
+Other regions with stronger vorticity would have $w$ of the order of magnitude you suggest ($\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.}
+
 \begin{itemize}
@@
 They should also compare the values they use to existing observations of rates.
-I recommend to see Baker et al 2017 or Riley et al 2016 for example who present in-situ observations of sinking speed and define slow < 20 m/d and fast > 20 m/d.
+I recommend to see Baker et al 2017 or Riley et al 2016 for example who present in-situ observations of sinking speed and define slow $<$ 20 m/d and fast $>$ 20 m/d.
 Also note that this nomenclature is consistent with the rates used in ocean biogeochemical models, which usually have a fast sinking rate of 50-200 m/d, and sometimes an additional pool with slow sinking rate of 1-5 m/d.
+
+	\note{We should be clearer in the text. This is partially (but poorly) done in section 2.2.2}
 
@@
 The authors should justify the narrow range of vertical velocity they explore.
-Prior observation-based studies emphasize the importance of particles sinking at slow rates (< 10 m/d) but also those sinking at very fast rates similar in magnitude to submesoscale vertical motions (200-300 m/d) (e.g.
+Prior observation-based studies emphasize the importance of particles sinking at slow rates ($<$ 10 m/d) but also those sinking at very fast rates similar in magnitude to submesoscale vertical motions (200-300 m/d) (e.g.
 Baker et al 2017, Riley et al 2016, Stuckel et al.
@@
 Is it because of limitations related to the Stokes Law?
-Is it because the model is not adapted to look at faster sinking rates.
+Is it because the model is not adapted to look at faster sinking rates?
+
+	\note{As outlined above, the choice of sinking rates is based on the dynamics of the region studied.
+Any other regions with stronger vertical motions at submesoscales could be explored with faster sinking particles.
+We believe the overarching conclusion would be the same: The 1D traditional paradigm fails to capture export for particles with sinking rates similar or smaller than the vertical velocity, especially when the spectrum slope is steeper.
+At Station Papa, this affects the range of particles sinking at $<$ 5 m/day, but in a place where relative vorticity is larger (e.g., gulf stream), and vertical velocities can reach the order of 100 m/day, then the range of particle size for which the 1D model fails would be greater.}
 
@@
 
+	\note{That is also a good point.
+$w$ are strogner in ML, but we have little particles in the ML, so our fluxes are mostly based on velocities below the ML.
+Submesoscale-driven subduction have been shown to leak below the ML (cite Sanjiv's paper, and the one from Ruiz and Pascual recently published?).
+}
+
 	\item The author could introduce the study by acknowledging up front that slow sinking particles are the particles most impacted by submesoscale (as shown in previous papers) and this is why they are the focus of this paper that explores the sensitivity to size spectrum etc.
+
+	\note{Yes, this should be done - I agree.}
 \end{itemize}
@@
 I like the fact that the authors sweep the parameter space of the size spectrum ($\xi$ = 2, 3, 4).
-The choice of this parameteris however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).
+The choice of this parameter is however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).
+
+\note{This parameter range is based on observational evidence cited in the text (L640), although not explicitly in section 2.2.3., where it would be most informative.
+We have modified the text in section 2.2.3 to better justify the range of $\xi$ used in this study.}
 
@@
 
+	\note{We have modified the text to discuss the implications of a steeper slope in a greater context.
+It now includes information about sources of observational evidence for steeper spectral slopes and the expected spatio-temporal variability }
+
 	\item The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague "under specific conditions ..." (L27).
 Please try to clarify what this means in Layman terms in the abstract.
+
+	\rep{Text has been modified to address this comment.}
 
@@
 
+\rep{The abstract has been modified to improve clarity of the study's result}
+
 \section*{Section 2.2}
@@
 https://doi.org/10.1002/2017GB005638\\
+
 Boyd, P.W., Claustre, H., Levy, M., Siegel, D.A., Weber, T., 2019.
@@
 https://doi.org/10.1038/s41586-019-1098-2\\
+
 Erickson, Z.K., Thompson, A.F., 2018.
@@
 https://doi.org/10.1029/2018GB005927\\
+
 Llort, J., Langlais C., Matear R., Moreau S., Lenton A., Strutton Peter G., 2018.
@@
 https://doi.org/10.1002/2017JC012861\\
+
 Resplandy, L., Lévy, M., McGillicuddy, D.J., 2019. Effects of Eddy‐Driven Subduction on Ocean Biological Carbon Pump. Global Biogeochem. Cycles 2018GB006125. https://doi.org/10.1029/2018GB006125\\
+
 Riley, J.S., Sanders, R., Marsay, C., Moigne, F.A.C.L., Achterberg, E.P., Poulton, A.J., 2012.
@@
 https://doi.org/10.1029/2011GB004085\\
+
 Stukel, M.R., Aluwihare, L.I., Barbeau, K.A., Chekalyuk, A.M., Goericke, R., Miller, A.J., Ohman, M.D., Ruacho, A., Song, H., Stephens, B.M., Landry, M.R., 2017a.
@@
 https://doi.org/10.1073/pnas.1609435114\\
+
 Stukel, M.R., Ducklow, H.W., 2017.
@@
 https://doi.org/10.1002/2017GB005652\\
+
 Stukel, M.R., Song, H., Goericke, R., Miller, A.J., 2017b.

### 2020-01-02 size_differentiated_export.tex
Updates from Overleaf
Addressing reviews
Update Fig 7 and 8 based on reviews. Responsded to a few more comments

@@
 \usepackage{trackchanges}
+\soulregister\ref7 % For references and citation to work within trackchanges
+\soulregister\cite7
 %% PLEASE USE THE FOLLOWING COMMANDS
@@
 The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important.
-The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export.
-A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles.
-Implementing a remineralization scheme generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven.
-Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export.
+The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export\change{.
+A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{, especially where the relative abundance of small particles is larger, as captured by a steeper particle size-spectrum slope}.
+\change{Implementing a r}{R}emineralization \remove{scheme} generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven.
+\change{Under specific conditions}{In an advectively-driven export regime}, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export.
 This study demonstrates that slow-sinking particles can be a significant contribution, and at times, even dominate the export flux.
@@
 This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined by the 1\% light level.
-The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Available Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}.
+\add{Particle seeding is located at the base of the euphotic layer where biological processes not captured by the particles (e.g., grazing, repackaging, aggregation, etc.) are not as active }\citep{Duclow_2001}.
+	The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically \change{Available}{Active} Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}.
 The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.
@@
 	In each particle-tracking experiment, four different classes of particles are released.
-Each particle class is characterized by a different sinking velocity: 0.025, 0.05, 1, and 5 m/day.
+Each particle class is characterized by a different sinking velocity: 0.025, \remove{0.05, }1, and 5 m/day.
 The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
@@
 		\centering
-		\includegraphics[width = 1\linewidth]{Fig7.png}
+		\includegraphics[width = 1\linewidth]{Fig7_revised.png}
 		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity \add{(sinking + advective)} along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
-Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
+\add{PDFs are computed from the whole 24-day particle tracking experiments.} Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
 Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.}
@@
 		\centering
-		\includegraphics[width = 1\linewidth]{Fig8.png}
-		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity \add{(sinking + advective)} along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
+		\includegraphics[width = 1\linewidth]{Fig8_revised.png}
+		\caption{\change{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
 Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
-Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}
+Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}
+		}	
 		\label{fig: biomass_export_remin}
@@
 	This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}). 
-This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \citep{Kostadinov_2009, White_2015}.
+	This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \add{: In-situ observations yield average spectral slopes varying between 3.5 and 4.5 }\citep[see Table 2 in ]{Kostadinov_2009}\add{, while spectral analysis of satellite data suggest global spectral slopes varying between 3 and 6.
+More recent observational work located in the Northeast Pacific, including Station Papa, found a spectral slope also greater than 3}\citep[][; Z.
+Xiaodong, personal communication]{White_2015}.
+    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \citep{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities (cite cite cite), and steeper during the wintertime, when communities are mostly composed of small particles (cite cite cite)}.
     The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content.
@@
 Thompson (Caltech) for his useful comments and suggestions, N.
-Pelland (NOAA) and Charlie Eriksen (University of Washington) for sharing the glider data collected at Ocean Station Papa, as well as Sebastian Essink for his assistance in developing the particle-tracking code.
+Pelland (NOAA) and C.
+Eriksen (University of Washington) for sharing the glider data collected at Ocean Station Papa, as well as S.
+Essink for his assistance in developing the particle-tracking code.
 All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website \citep[\url{https://www.pmel.noaa.gov/ocs/Papa};][]{PMEL_data} and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945} \citep{Gaillard_2015}.

### 2020-01-02 figures/code/Fig5_dynamic_signature_w_valid.m

@@ -2,7 +2,7 @@ clear
 close all
 
 %% Load gradients computed from glider data for comparison curve
-load('/Users/mathieudever/Documents/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
+load('dataset/Fig5_data.mat')
 glider.M2time = datevec(glider.M2time);
 clearvars -except glider cmap
 
@@ -267,5 +267,5 @@ text(1.82,6.1,'Papa\_winter','fontsize',30,'HorizontalAlignment','center','Units
 
 cd(thefolder)
 set(gcf,'color','w')
-export_fig -r200 Fig5_dynamic_signature_w_valid.png
-close
+%export_fig -r200 Fig5_dynamic_signature_w_valid.png
+%close

### 2020-01-02 figures/code/Fig7_revised.m

@@ -1,0 +1,260 @@
+clear
+
+%% This figure plots the histogram of the relative biomass vs vertical velocity at 
+% DOY 25 in Summer/Winter for xi = 2 and xi = 4
+
+%% Import w for each size class in winter and summer
+
+% Load data previously extracted from big database
+load dataset/Fig7_data.mat
+
+%% Set colors for each class
+color0025 = [215,48,39]/256;
+color1 = [39,100,25]/256;
+color5 = [49,54,149]/256;
+
+%% compute biomass per simulated particle
+
+% Set of marameters
+wmax = 5; wmin = 0.025;
+slope = 3; B0 = 1;
+% Compute total biomass based on the paramters
+Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+
+% For Junge slope = 2
+slope = 2;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_2 = B0*(0.025/wmax)^((3-slope)/2);
+B1_2 = B0*(1/wmax)^((3-slope)/2);
+B5_2 = B0*(5/wmax)^((3-slope)/2);
+
+% For Junge slope = 4
+slope = 4;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_4 = B0*(0.025/wmax)^((3-slope)/2);
+B1_4 = B0*(1/wmax)^((3-slope)/2);
+B5_4 = B0*(5/wmax)^((3-slope)/2);
+
+%%
+% Calculate total biomass to normalize by
+totalB = sum(N0025s.*B0025_2)+sum(N1s.*B1_2)+sum(N5s.*B5_2);
[…]

### 2020-01-02 figures/code/Fig8_revised.m

@@ -1,0 +1,256 @@
+clear
+
+%% This figure plots the histogram of the relative biomass vs vertical velocity at 
+% DOY 25 in Summer/Winter for xi = 2 and xi = 4
+
+%% Import w for each size class in winter and summer
+
+% Load data previously extracted from big database
+load dataset/Fig8_data.mat
+
+%% Set colors for each class
+color0025 = [215,48,39]/256;
+color1 = [39,100,25]/256;
+color5 = [49,54,149]/256;
+
+%% compute biomass per simulated particle
+
+% Set of marameters
+wmax = 5; wmin = 0.025;
+slope = 3; B0 = 1;
+% Compute total biomass based on the paramters
+Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+
+% For Junge slope = 2
+slope = 2;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_2 = B0*(0.025/wmax)^((3-slope)/2);
+B1_2 = B0*(1/wmax)^((3-slope)/2);
+B5_2 = B0*(5/wmax)^((3-slope)/2);
+
+% For Junge slope = 4
+slope = 4;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_4 = B0*(0.025/wmax)^((3-slope)/2);
+B1_4 = B0*(1/wmax)^((3-slope)/2);
+B5_4 = B0*(5/wmax)^((3-slope)/2);
+
+%%
+% Calculate total biomass to normalize by
+totalB = sum(N0025s.*B0025_2)+sum(N1s.*B1_2)+sum(N5s.*B5_2);
[…]

### 2020-01-02 figures/code/Fig7.m
minor directory modifications
Include pdf files to Git repo

@@ -4,15 +4,18 @@ clear
 % DOY 25 in Summer/Winter for xi = 2 and xi = 4
 
 %% Import w for each size class in winter and summer
-tt = 25;
-[~,~,wt0025s] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_summer.csv');
-[~,~,wt1s] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_summer.csv');
-[~,~,wt5s] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_summer.csv');
-
-[~,~,wt0025w] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_winter.csv');
-[~,~,wt1w] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_winter.csv');
-[~,~,wt5w] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_winter.csv');
-
+% tt = 25;
+% [~,~,wt0025s] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_summer.csv');
+% [~,~,wt1s] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_summer.csv');
+% [~,~,wt5s] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_summer.csv');
+% 
+% [~,~,wt0025w] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_winter.csv');
+% [~,~,wt1w] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_winter.csv');
+% [~,~,wt5w] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_winter.csv');
+% 
+% save Fig7_data.mat
+% error('stop')
+load Fig7_data.mat
 %% Set colors for each class
 color0025 = [215,48,39]/256;
 color1 = [39,100,25]/256;
@@ -92,7 +95,10 @@ ylim([1e-2 100])
 title('Summer','fontsize',50,'position',[-6 11e+01 0]);
 text(-9.5,6e1,'(a)   \xi = 2','fontweight','b','fontsize',40)
 HH = legend([h1 h2 h3],'0.025 m/day','1 m/day','5 m/day','location','southeast');
-set(HH,'fontsize',25)
[…]

### 2020-01-02 Submission_and_reviews/response_to_reviewers.tex
Addressing more reviews

@@
 \section{Comments from Reviewer  \#1}
+\subsection*{Major point \#1}
 \small
@@
 
-Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above  \\
+Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above.\\
 
+\subsection*{Major point \#2}
 \textit{Second, it is unclear why 5m/day is selected for the largest particle class.
@@
 
-This is a good, thought provoking, point about how does these results for sinking rates much larger than any advective vertical velocity?
-First, we would like to comment on \textit{``Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity."}; This is not necessarily exact in our case.
-At any given time, between 10 and 15\% of the vertical velocity over the model domain is larger than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles.
+\textit{``it is unclear why 5m/day is selected for the largest particle class."\\}
+The choice of 5m/day sinking rates as the ``face-sinking"  class is justified on lines 300-301 of the original manuscript.
+It is based on the PDFs of the advective vertical velocity.
+In our case, 5 m/day is faster than 85-90\% of the vertical velocity modeled in our domain at any given time.
+We have added some text in Section 2.2.2 to make the justification clearer to the reader.\\
+
+\textit{``Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity."\\}
+This is therefore not exact in this case.
+As mentioned, at any given time, between 10 and 15\% of the vertical velocity over the model domain is smaller than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles.
+If \textit{``vertical advective velocities exceed the large particle sinking velocity"}, it would be temporary and very rare.\\
 
 However, your comment is very relevant: What do our findings mean for sinking rates far exceeding the maximum modeled vertical velocities?
-In that case, $w = w_s$, as the sinking rate largely dominate.
+In that case, $w \approx w_s$, as the sinking rate largely dominate.
 We want to know if the ratio of fluxes of two large sinking velocity is greater and smaller than one (i.e., the slope of the biomass flux spectrum is positive or negative):
@@
 In other words, if the Junge slope is larger than 5, the slope of the particle size, biomass, AND biomass flux is negative.
-While large, a value of $\xi>5$ is not uneralistic, as it has been estimated from satellite-based algorithm in \cite{Kostadinov_2009}.
+While large, a value of $\xi>5$ is not unrealistic, as it falls within the range of $\xi$ obtained from satellite-based estimates \citep{Kostadinov_2009}.
 
 To directly address your comment, it is true that for very large aggregates with sinking rates far exceeding the order of magnitude of vertical velocities, the contribution of slower sinking particles is not dominant.
-That has been established a while ago, and is the basis of the traditional 1-D model challenged in our work.
-Our study demonstrates the limitations of such a paradigm, as one considers slower-sinking particles classes.
+We believe it to be well-established, and is the basis of the traditional 1-D model commonly used.
+Our study demonstrates the limitations of this paradigm, as one considers slower-sinking particles classes.
 Furthermore, for the largest aggregate to constantly be driving the biomass flux, it would require an infinite reservoir of those large particles to be able to relate their larger flux to larger export.
 The biomass flux due to the aggregates would be larger until the source is exhausted -- which is likely to happen more quickly for 100 m/day particles than for smaller particles.
+In fact, export from very fast sinking particles (e.g., 100 m /day) tend to occur as events \citep{Kiko_2017}.
 Additionally, this paradigm is only true if the slope of the particle-size spectrum is smaller than $\sim$5 (based on our scaling).
@@
 Including a ``large aggregate" size class sinking at 100m/day, for example, would not provide much more interesting information, in our opinion.
-In fact, the flux of such a size class can be computed theoretically (as $w \approx w_s$) and does not require any model simulations.
-This is, we agree, an important fact to consider.
-As a result, we have modified the text in section 4.2 to put our findings in perspective with aggregates sinking at much faster sinking rates.
+In fact, the flux of such a size class can be computed theoretically (using $w \approx w_s$) and does not require any model simulations.
+We agree, however, that this is an important fact to consider.
+As a result, we have added a paragraph in section 4.2 to put our findings in perspective with aggregates sinking at much faster sinking rates.
 
+\subsection*{Major point \#3}
  \textit{Finally, the analysis demonstrated in Figures 7 and 8 does not seem appropriate for gauging the contribution of small and large particles to export, and the role of remineralization.

### 2020-01-02 size_differentiated_export.tex
Addressing more reviews

@@
 	%% ------------------------------------------------------------------------ %%
-
 	\section{Introduction}
@@
 The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
-The fastest-sinking velocity is chosen as an end-member velocity class of particle that will be exported in its entirety over the course of our experiment.
-%The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.
+The fastest-sinking velocity is chosen as an end-member velocity class of particle\change{ that will be exported in its entirety over the course of our experiment.
+}{, based on the PDF of vertical velocities in the model.
+At any given time, at least 85\% of the model vertical velocity is weaker than 5 m/day.
+The results presented for the 5 m/day sinking class can therefore be theoretically extrapolated to any class with a higher sinking velocity.}
 
@@
 Xiaodong, personal communication]{White_2015}.
-    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \citep{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities (cite cite cite), and steeper during the wintertime, when communities are mostly composed of small particles (cite cite cite)}.
+    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \citep{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities, and steeper during the wintertime, when communities are mostly composed of small particles}.
     The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content.
@@
 Their export timescale is barely affected by remineralization processes as it only depends on local ocean dynamics.
+
+	\add{These results are robust to the range of sinking rates explored.
+If one considers a particle class with a sinking rate far exceeding the vertical advective velocity }\citep[e.g., 100 m/day; ][]{Turner_2015}\add{, then the associated biomass flux can be estimated by relying on the traditional 1-D paradigm, assuming $w_{tot}\approx w_s$.
+Combining this approximation with Equation \ref{eq: biomassjungeslope} shows that the slope of the biomass flux spectrum is positive for $\xi<5$, in which case very fast-sinking particles would dominate  vertical biomass fluxes.
+However, for $\xi>5$, the slope of the biomass flux spectrum become negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime.
+While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates} \citep{Kostadinov_2009}.
 

### 2020-01-02 Submission_and_reviews/response_to_reviewers.tex
More revisions

@@
 
- \rep{This is correct}
+This is correct.\\
 
  \textit{But why is the flux at day 25 the important quantity?
-By this time, the large particles have had time to decay to a size where their sinking velocity is negligible, and therefore their contribution to the flux will be small.
-But, what about all of the large particles that settled across the export horizon (100m) earlier in the simulation, while their sinking velocity is still high?
+By this time, the large particles have had time to decay to a size where their sinking velocity is negligible, and therefore their contribution to the flux will be small.}
+
+ This is a good point that is now addressed in the revised manuscript.
+Fig 7 and 8 are now displaying the PDF of biomass fluxes integrating over the entire particle tracking experiment (i.e.
+28 days), to avoid confusion.
+Our conclusions are robust to whether the PDFs are displayed for a specific day, or for the entire simulation.
+The respective contributions of the different size classes vary little over the course of a simulation.
+We opted to show day 25 of simulation to simplify the interpretation of the PDFs; in fact, the impact of remineralization on the PDFs is not as clear in the time-integrated PDFs.
+We added some text along the new version of figures 7 and 8 to facilitate plot interpretation.
+
+ \textit{ But, what about all of the large particles that settled across the export horizon (100m) earlier in the simulation, while their sinking velocity is still high?
 Really, we should be interested in how much of the initial biomass in each size category has "escaped" through the export horizon by the end of the simulation, i.e.
-their time-integrated contribution to export.
+their time-integrated contribution to export.\\}
+
   For particles released at 80m, sinking at 5m/day and remineralizing at a rate of 0.13/day, it seems that at least 50\% of the inital biomass in the large size category must be exported through the 100m horizon, before remineralizing.
@@
 I suggest the authors repeat their analysis, comparing time-integrated export through 100m in order to assess the contribution of large vs.
-small particles.}
+small particles.\\}
+
+As mentioned above, we aimed to not rely on a depth-horizon to present our results, mainly due to the subjectivity it involves (see \textbf{Major Point \#1}).
+%There is also another major operational complication when using a depth-horizon: In our study, particles are seeded once,
+
+Addressing the first part of this comment, related to why Day 25 is used,
 

### 2020-01-03 Submission_and_reviews/response_to_reviewers.tex
Reviewer1
Addressed all comments by reviewer #1

@@
 
+Comments provided vby reviewer \#1 were very constructive and relevant.
+They lead to major changes in the manuscript, namely figure 7 and 8.
+It also led us to clarify some of the aspects of the manuscript, as the scientific reasoning behind some of the choices made (e.g., particle seeding depth).
+Most of the concerns rose by the reviewer were however related to the definition of an export horizon to quantify export.
+We argue, based on both our work and recent studies \citep{Palevsky_2018}, that the definition of an export horizon is not adequate and introduces subjectivity and biases in the results.
+
 \section{Comments from Reviewer  \#1}
@@
 This is therefore not exact in this case.
-As mentioned, at any given time, between 10 and 15\% of the vertical velocity over the model domain is smaller than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles.
-If \textit{``vertical advective velocities exceed the large particle sinking velocity"}, it would be temporary and very rare.\\
+As mentioned, at any given time, between 10 and 15\% of the vertical velocity over the model domain is larger than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles.
+If \textit{``vertical advective velocities exceed the large particle sinking velocity"}, it is temporary and very rare.\\
 
@@
 which is only true for $w_2 > w_1$ if $\xi<$5.
-In other words, if the Junge slope is larger than 5, the slope of the particle size, biomass, AND biomass flux is negative.
+In other words, if the Junge slope is larger than 5, the slopes of the particle size, biomass, AND biomass flux spectra are negative.
 While large, a value of $\xi>5$ is not unrealistic, as it falls within the range of $\xi$ obtained from satellite-based estimates \citep{Kostadinov_2009}.
@@
 The biomass flux due to the aggregates would be larger until the source is exhausted -- which is likely to happen more quickly for 100 m/day particles than for smaller particles.
-In fact, export from very fast sinking particles (e.g., 100 m /day) tend to occur as events \citep{Kiko_2017}.
+In fact, export from very fast sinking particles (e.g., 100 m /day) tend to occur as events and are not sustained in time \citep{Kiko_2017}.
 Additionally, this paradigm is only true if the slope of the particle-size spectrum is smaller than $\sim$5 (based on our scaling).
@@
 In fact, the flux of such a size class can be computed theoretically (using $w \approx w_s$) and does not require any model simulations.
-We agree, however, that this is an important fact to consider.
+We agree, however, that this is an important fact to consider and discuss in the manuscript.
 As a result, we have added a paragraph in section 4.2 to put our findings in perspective with aggregates sinking at much faster sinking rates.
@@
  This is a good point that is now addressed in the revised manuscript.
-Fig 7 and 8 are now displaying the PDF of biomass fluxes integrating over the entire particle tracking experiment (i.e.
+Fig 7 and 8 are now displaying the PDF of biomass fluxes integrated over the entire particle tracking experiment (i.e.
 28 days), to avoid confusion.
@@
 We opted to show day 25 of simulation to simplify the interpretation of the PDFs; in fact, the impact of remineralization on the PDFs is not as clear in the time-integrated PDFs.
-We added some text along the new version of figures 7 and 8 to facilitate plot interpretation.
+We added some text along the new version of figures 7 and 8 to facilitate plot interpretation.\\
 
- \textit{ But, what about all of the large particles that settled across the export horizon (100m) earlier in the simulation, while their sinking velocity is still high?
+ \textit{But, what about all of the large particles that settled across the export horizon (100m) earlier in the simulation, while their sinking velocity is still high?
 Really, we should be interested in how much of the initial biomass in each size category has "escaped" through the export horizon by the end of the simulation, i.e.
@@
 
-  For particles released at 80m, sinking at 5m/day and remineralizing at a rate of 0.13/day, it seems that at least 50\% of the inital biomass in the large size category must be exported through the 100m horizon, before remineralizing.
+ As previously mentioned, the study focuses on export fluxes rather than export, to avoid introducing subjectivity in defining an export horizon.\\
+
+\textit{For particles released at 80m, sinking at 5m/day and remineralizing at a rate of 0.13/day, it seems that at least 50\% of the inital biomass in the large size category must be exported through the 100m horizon, before remineralizing.
 In contrast, Figure 6 shows that only a very small fraction of the small particles reach 100m in winter, even when they are not remineralizing.
-It therefore seems that even in winter, large particles must dominate the integrated export flux in the simulation with remineralization, contradicting the second major conclusion of the study.
-I suggest the authors repeat their analysis, comparing time-integrated export through 100m in order to assess the contribution of large vs.
-small particles.\\}
+It therefore seems that even in winter, large particles must dominate the integrated export flux in the simulation with remineralization, contradicting the second major conclusion of the study.\\}
 
-As mentioned above, we aimed to not rely on a depth-horizon to present our results, mainly due to the subjectivity it involves (see \textbf{Major Point \#1}).
-%There is also another major operational complication when using a depth-horizon: In our study, particles are seeded once,
+This is a good example of how defining an arbitrary export horizon can skew the results.
+If the export horizon was set to 90 m, then almost all of the 1m/day particles would be "exported", and they would therefore dominate export for $\xi=4$.
+If 100 m is used as an export horizon, this is no longer the case and the 5m/day class would dominate export.
+if 300 m was used, then there would be no export.
+A large flux of biomass, even over a limited vertical scale, has the potential to lead to a large export.
+This is why we focus on biomass fluxes as opposed to integrated biomass.
+Along with other reasons mentioned above (seeding strategy, operational limitations, etc).\\
 
-Addressing the first part of this comment, related to why Day 25 is used,
+\textit{I suggest the authors repeat their analysis, comparing time-integrated export through 100m in order to assess the contribution of large vs. small particles.\\}
 
-\note{This is a good point.
-For Fig 7, the timestamp selected to display the results has little impact on the conclusions.
-A similar plot was produced for time-average biomass fluxes, and the results are only marginally different \textbf{(plots included in this document)}.
-The results are therefore displayed for day 25 for consistency, as this is the day used to display results in Fig 8.\linebreak For fig 8...
-how to justify using doy 25?
-Should I make a Fig 9 with time series of \%...?}
+This was the original direction that we took for this study.
+However, we came to realize that looking at time-integrated export introduces large complications, the main ones being: (1) It requires defining an export depth, and (2) The one-time particle seeding strategy becomes inappropriate.
+Constant reseeding becomes necessary, which is operationally constraining, (3) the timescales integrated over drives the result.
+If particles are tracked for an infinitely long time, they will eventually all be exported, and the dominant particle class is only a function of the Junge slope.
+If particles are tracked for long enough for one class to cross the export horizon, but not other classses (as it would be the case for a horizon defined a t100 m), then the export would artificially be driven by the fast sinking particles.
 
+\subsection*{Minor comments}
 \textit{Line 306: Is it three weeks, or 28 days (four weeks)?}\\
@@
 \textit{Acknowledgments: Will the model output be archived for public access?}\\
-\rep{Text has been modified accordingly.}
-\note{Create a subset dataset necessary to generate figures}
+\rep{Due to the very large amount of data necessary for this study, a subset of the data, equired to produce the figures, is publicly available (link is now included in acknowledgments).
+Full dataset is available on request.}
 

### 2020-01-03 size_differentiated_export.tex
Updates from Overleaf
Reviewer1
Addressed all comments by reviewer #1

@@
 As the Junge slope increases, the spectrum of biomass steepens, and the relative contribution of slower-sinking particles to the downward biomass flux significantly increases (Figure \ref{fig: biomass_export}c).
-In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.1\% to 10\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$.
+In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.2\% to \change20\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$.
 While significant, the impact of a change in the Junge slope in summer conditions does not challenge the dominant role played by faster-sinking particles.
@@
 	In the winter, PDFs of relative biomass as a function of vertical velocities present a much larger spread, with velocity magnitudes exceeding 50 m/day.
-For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.1\% in the summer to about 4\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes (Figure \ref{fig: biomass_export}b).
+For $\xi = 2$, the relative contribution of slower-sinking particles to the downward flux significantly increases from 0.2\% in the summer to about 3\% in the winter, demonstrating the impact advective velocities alone can have on vertical fluxes (Figure \ref{fig: biomass_export}b).
 Nevertheless, slower-sinking particles remain a relatively small contributor to the total downward flux of biomass.
 When winter ocean dynamics are coupled with a steeper Junge slope, however, slower-sinking particles largely dominate the downward biomass flux.
-In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 80\% of the biomass flux (Figure \ref{fig: biomass_export}d).
+In our winter simulations with $\xi = 4$, we find that the slowest-sinking particle class is responsible for about 79\% of the biomass flux (Figure \ref{fig: biomass_export}d).
 
@@
 
-	Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 4$ with and without the remineralization scheme.
-As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization.
+	Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for \add{$\xi = 2$ and} $\xi = 4$ \change{with and without }{including} the remineralization scheme.
+As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization \add{(see Figure} \ref{fig: biomass_export}).
 This is due to the fact that the flux of biomass $\left<w_{tot}B\right> = \left<w_sB\right> + \left<wB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content per particle.
@@
 Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize.
-This effect can be seen in Figure \ref{fig: biomass_export_remin}c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation (\ref{eq: sinking_velocity_remin}).
-As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}).
+This effect can \add{particularly} be seen in Figure \ref{fig: biomass_export_remin}\add{a and} c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation (\ref{eq: sinking_velocity_remin}).
+\remove{As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}).}
 
@@
 	\end{figure}
-	In a advectively-driven system where $\left<w_sB\right> < \left<wB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
-This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}c): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (60\%; see Figure \ref{fig: biomass_export_remin}a).
-When remineralization processes are considered, slower-sinking particles become the dominant contributor to biomass fluxes (see inset in Figure \ref{fig: biomass_export_remin}c).
+	In a advectively-driven system where $\left<w_sB\right> \sim \left<wB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
+This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}\remove{c}): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (\change{60}{53}\%; see Figure \ref{fig: biomass_export}c).
+When remineralization processes are considered, slower-sinking particles \change{become the dominant contributor}{contribute more} to biomass fluxes (see inset in Figure \ref{fig: biomass_export_remin}c).
 As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics.
-Biomass fluxes are dominated by the slower-sinking particles, representing 82\% of the downward biomass flux (Figure \ref{fig: biomass_export_remin}b).
-Even after implementing our remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (87\%; see Figure \ref{fig: biomass_export_remin}d).
+Biomass fluxes are dominated by the slower-sinking particles \add{when $\xi =4$}, representing 79\% of the downward biomass flux (Figure \ref{fig: biomass_export}d).
+Even after implementing the remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (82\%; see Figure \ref{fig: biomass_export_remin}d).
 
@@
 It also demonstrates that, contrarily to the traditional paradigm, remineralization processes enhance the role played by slower-sinking particles in biomass fluxes, in cases where the biomass spectrum slope is negative.
-
-	The timescales over which the system transitioned from an gravitationally-driven to an advectively-driven system depends on the remineralization model used.
+%The timescales over which the system transitioned from an gravitationally-driven to an advectively-driven system depends on the remineralization model used.
 
@@
 Combining this approximation with Equation \ref{eq: biomassjungeslope} shows that the slope of the biomass flux spectrum is positive for $\xi<5$, in which case very fast-sinking particles would dominate  vertical biomass fluxes.
-However, for $\xi>5$, the slope of the biomass flux spectrum become negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime.
+However, for $\xi>5$, the slope of the biomass flux spectrum becomes negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime.
 While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates} \citep{Kostadinov_2009}.

### 2020-03-15 Submission_and_reviews/response_to_reviewers.tex
update revised manuscript
Not final version

@@
 
-Comments provided vby reviewer \#1 were very constructive and relevant.
+Comments provided by reviewer \#1 are constructive and relevant.
 They lead to major changes in the manuscript, namely figure 7 and 8.
 It also led us to clarify some of the aspects of the manuscript, as the scientific reasoning behind some of the choices made (e.g., particle seeding depth).
-Most of the concerns rose by the reviewer were however related to the definition of an export horizon to quantify export.
+Most of the concerns rose by the reviewer were, however, related to the definition of an export horizon to quantify export.
 We argue, based on both our work and recent studies \citep{Palevsky_2018}, that the definition of an export horizon is not adequate and introduces subjectivity and biases in the results.
@@
 \textit{``it is unclear why 5m/day is selected for the largest particle class."\\}
-The choice of 5m/day sinking rates as the ``face-sinking"  class is justified on lines 300-301 of the original manuscript.
+The choice of 5m/day sinking rates as the ``fast-sinking"  class is justified on lines 300-301 of the original manuscript.
 It is based on the PDFs of the advective vertical velocity.
@@
 If particles are tracked for an infinitely long time, they will eventually all be exported, and the dominant particle class is only a function of the Junge slope.
-If particles are tracked for long enough for one class to cross the export horizon, but not other classses (as it would be the case for a horizon defined a t100 m), then the export would artificially be driven by the fast sinking particles.
+If particles are tracked for long enough for one class to cross the export horizon, but not other classes (as it would be the case for a horizon defined a t100 m), then the export would artificially be driven by the fast sinking particles.
 
@@
 \section*{Range of sinking speeds.}
-The sinking speed examined by the authors are 0.025, 0.05, 1 and 5 m/d.
+\textit{The sinking speed examined by the authors are 0.025, 0.05, 1 and 5 m/d.
 All these values would be considered as "slow sinking rate" by the community.
@@
 It also means that the authors cannot really conclude about the relative role of particles that have sinking rates similar in magnitude or faster than submesoscale motions (i.e.
-50-300 m/d).
+50-300 m/d).\\}
 
-\note{The three sinking rates were defined based on having one class virtually non-sinking (0.025 m/day), one class within the range of $w$ measured in summer (1 m/day, which is the \#\# percentile of the PDF for $w$ showed in Fig 5), and one class with similar magnitude than $w$ observed at submesoscale in the winter case (1 m/day, which is the \#\# percentile of the PDF for $w$ showed in Fig 5).
+The three sinking rates were defined based on having one class virtually non-sinking (0.025 m/day), one class within the range of $w$ modeled (1 m/day), and one class larger than $w$ modeled at submesoscale in the winter case (5 m/day).
+In fact, at any given time, at least 85\% of the modeled vertical velocity is smaller than 5 m/day -- our fastest sinking rate -- and an even larger percentage is sampled by the Lagrangian particles.
+For all intents and purposes, a 5 m/day sinking particle is ``fast" compared to the dynamical flow of the simulations.
+Any particle class with a faster sinking rate would behave in a predictable way, as vertical velocity is dominated by sinking.
+We modified the text in Section 2.2.2 to clarify this (Line 304 - 307)
+
+, which is the 90percentile of the PDF for $w$ showed in Fig 5).
 Selecting a sinking rate much faster than that would bring us back to the traditional 1D model, as the sinking rate would greatly dominate the vertical flux.
@@
 Station Papa remains a relatively calm region, so submesoscale $w$ are of the order of 50 m/day.
-Other regions with stronger vorticity would have $w$ of the order of magnitude you suggest ($\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.}
+Other regions with stronger vorticity would have $w$ of the order of magnitude you suggest ($\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.
 

### 2020-03-15 size_differentiated_export.tex
update revised manuscript
Not final version

@@
 \usepackage{trackchanges}
-\soulregister\ref7 % For references and citation to work within trackchanges
+\soulregister\ref7
 \soulregister\cite7
@@
 Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
-Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}
-		}	
+Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}}
 		\label{fig: biomass_export_remin}

### 2020-03-15 figures/code/Fig1_model_domain.m

@@ -3,56 +3,61 @@ clear
 %% This code plot the model domain with the wind profile and the het flux 
 % meridoinal anomaly in 3 panels
 %%
-ii = 0;
-x = ncread(['/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/full_',num2str(ii,'%05d'),'.cdf'],'xc')*1000;
-y = ncread(['/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/full_',num2str(ii,'%05d'),'.cdf'],'yc')*1000;
-Z = ncread(['/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/full_',num2str(ii,'%05d'),'.cdf'],'zc');
-z = squeeze(Z(1,1,:));
-rho = ncread(['/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/full_',num2str(ii,'%05d'),'.cdf'],'rho');
-rho(1,:,:) = NaN; rho(end,:,:) = NaN;
-
-% Import the scale factor for restauration time scale
-filename = '/Volumes/garuda/Mathieu/output_Papa_Dx=500_from_1km/K1/scalefactor.out';
-delimiter = ','; startRow = 2; formatSpec = '%*s%s%[^\n\r]';
-fileID = fopen(filename,'r');
-dataArray = textscan(fileID, formatSpec, 'Delimiter', delimiter, 'TextType', 'string', 'HeaderLines' ,startRow-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
-fclose(fileID);
-raw = repmat({''},length(dataArray{1}),length(dataArray)-1);
-for col=1:length(dataArray)-1
-    raw(1:length(dataArray{col}),col) = mat2cell(dataArray{col}, ones(length(dataArray{col}), 1));
-end
-numericData = NaN(size(dataArray{1},1),size(dataArray,2));
-rawData = dataArray{1};
-for row=1:size(rawData, 1)
-    % Create a regular expression to detect and remove non-numeric prefixes and
-    % suffixes.
-    regexstr = '(?<prefix>.*?)(?<numbers>([-]*(\d+[\,]*)+[\.]{0,1}\d*[eEdD]{0,1}[-+]*\d*[i]{0,1})|([-]*(\d+[\,]*)*[\.]{1,1}\d+[eEdD]{0,1}[-+]*\d*[i]{0,1}))(?<suffix>.*)';
-    try
[…]

### 2020-03-15 figures/code/Fig4.m

@@ -52,8 +52,8 @@ figure(2)
 thew = [0.025 1 5];
 h1 = loglog(thew,[B0025_3 B1_3 B5_3]./sum([B0025_3 B1_3 B5_3])*100,'-k','linewidth',2);
 hold on
-h2 = loglog(thew,[B0025_2 B1_2 B5_2]./sum([B0025_2 B1_2 B5_2])*100,'--k','linewidth',2);
-h3 = loglog(thew,[B0025_4 B1_4 B5_4]./sum([B0025_4 B1_4 B5_4])*100,':k','linewidth',2);
+h2 = loglog(thew,[B0025_2 B1_2 B5_2]./sum([B0025_2 B1_2 B5_2])*100,':k','linewidth',2);
+h3 = loglog(thew,[B0025_4 B1_4 B5_4]./sum([B0025_4 B1_4 B5_4])*100,'--k','linewidth',2);
 
 
 scatter(thew,[B0025_3 B1_3 B5_3]./sum([B0025_3 B1_3 B5_3])*100,100,cat(1,color0025,color1,color5),'s','filled');

### 2020-03-18 Submission_and_reviews/response_to_reviewers.tex
Update response_to_reviewers.tex

@@
 It also led us to clarify some of the aspects of the manuscript, as the scientific reasoning behind some of the choices made (e.g., particle seeding depth).
-Most of the concerns rose by the reviewer were, however, related to the definition of an export horizon to quantify export.
-We argue, based on both our work and recent studies \citep{Palevsky_2018}, that the definition of an export horizon is not adequate and introduces subjectivity and biases in the results.
+Most of the concerns risen by the reviewer were, however, related to the definition of an export horizon to quantify export.
+We argue below that, based on both our work and recent studies \citep{Palevsky_2018}, the definition of an export horizon is not adequate and introduces subjectivity and biases in the results.
 
@@
 As mentioned, at any given time, between 10 and 15\% of the vertical velocity over the model domain is larger than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles.
-If \textit{``vertical advective velocities exceed the large particle sinking velocity"}, it is temporary and very rare.\\
+If \textit{``vertical advective velocities exceed the large particle sinking velocity"}, it is rare and short-lived.\\
 
@@
 However, we came to realize that looking at time-integrated export introduces large complications, the main ones being: (1) It requires defining an export depth, and (2) The one-time particle seeding strategy becomes inappropriate.
-Constant reseeding becomes necessary, which is operationally constraining, (3) the timescales integrated over drives the result.
+Constant reseeding becomes necessary, which is operationally constraining, (3) the timescales integrated over drive the results.
 If particles are tracked for an infinitely long time, they will eventually all be exported, and the dominant particle class is only a function of the Junge slope.
-If particles are tracked for long enough for one class to cross the export horizon, but not other classes (as it would be the case for a horizon defined a t100 m), then the export would artificially be driven by the fast sinking particles.
+If particles are tracked for long enough for one class to cross the export horizon, but not other classes (as it would be the case for a horizon defined at 100 m), then the export would artificially be driven by the fast sinking particles.
 
@@
 Any particle class with a faster sinking rate would behave in a predictable way, as vertical velocity is dominated by sinking.
-We modified the text in Section 2.2.2 to clarify this (Line 304 - 307)
+We modified the text in Section 2.2.2 to clarify this (Line 304 - 307).\\
 
-, which is the 90percentile of the PDF for $w$ showed in Fig 5).
-Selecting a sinking rate much faster than that would bring us back to the traditional 1D model, as the sinking rate would greatly dominate the vertical flux.
+Considering a sinking rate much faster than 5 m/day would bring us back to the traditional 1D model, as the sinking rate would greatly dominate the vertical flux.
 The objective of the study is to capture that transitional part of the size spectrum.
-Station Papa remains a relatively calm region, so submesoscale $w$ are of the order of 50 m/day.
-Other regions with stronger vorticity would have $w$ of the order of magnitude you suggest ($\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.
+Station Papa remains a relatively calm region, so submesoscale $w$ are of the order of 10 m/day at most.
+Other regions with stronger vorticity would have $w$ of the order of magnitude you suggest ($\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.\\
 
-\begin{itemize}
-	\item Throughout the text, the authors should be very clear about what they call fast and slow sinking particles.
+\textit{Throughout the text, the authors should be very clear about what they call fast and slow sinking particles.
 They should also compare the values they use to existing observations of rates.
 I recommend to see Baker et al 2017 or Riley et al 2016 for example who present in-situ observations of sinking speed and define slow $<$ 20 m/d and fast $>$ 20 m/d.
-Also note that this nomenclature is consistent with the rates used in ocean biogeochemical models, which usually have a fast sinking rate of 50-200 m/d, and sometimes an additional pool with slow sinking rate of 1-5 m/d.
+Also note that this nomenclature is consistent with the rates used in ocean biogeochemical models, which usually have a fast sinking rate of 50-200 m/d, and sometimes an additional pool with slow sinking rate of 1-5 m/d.\\}
 
-	\note{We should be clearer in the text. This is partially (but poorly) done in section 2.2.2}
+\note{We should be clearer in the text. This is partially (but poorly) done in section 2.2.2}\\
 
-	\item The authors need to justify their choice, discuss the implications of this choice and explain how it informs the current view of the community on POC export.
+\textit{The authors need to justify their choice, discuss the implications of this choice and explain how it informs the current view of the community on POC export.
 The authors should justify the narrow range of vertical velocity they explore.
@@
 Is it because of limitations related to the Stokes Law?
-Is it because the model is not adapted to look at faster sinking rates?
+Is it because the model is not adapted to look at faster sinking rates?\\}
 
@@
 We believe the overarching conclusion would be the same: The 1D traditional paradigm fails to capture export for particles with sinking rates similar or smaller than the vertical velocity, especially when the spectrum slope is steeper.
-At Station Papa, this affects the range of particles sinking at $<$ 5 m/day, but in a place where relative vorticity is larger (e.g., gulf stream), and vertical velocities can reach the order of 100 m/day, then the range of particle size for which the 1D model fails would be greater.}
+At Station Papa, this affects the range of particles sinking at $<$ 5 m/day, but in a place where relative vorticity is larger (e.g., gulf stream), and vertical velocities can reach the order of 100 m/day, then the range of particle size for which the 1D model fails would be greater.}\\
 
-	\item By limiting their study to slow sinking particles, the authors target by design the particles that will be most sensitive to submesoscale dynamics (see Stukel et al) and exclude particles that sink with rates similar or faster than submesoscale motions and that can efficiently export at depth and participate to carbon sequestration.
+\textit{By limiting their study to slow sinking particles, the authors target by design the particles that will be most sensitive to submesoscale dynamics (see Stukel et al) and exclude particles that sink with rates similar or faster than submesoscale motions and that can efficiently export at depth and participate to carbon sequestration.
 Indeed, submesoscale is largely trapped in the upper ocean and only have a limited impact on export at greater depth (see previous discussions of these effects in Stukel et al, Erikson et al and Resplandy et al).
-The authors should acknowledge these limitations and discuss their implications.
+The authors should acknowledge these limitations and discuss their implications.\\}
 
@@
 Submesoscale-driven subduction have been shown to leak below the ML (cite Sanjiv's paper, and the one from Ruiz and Pascual recently published?).
-}
+}\\
 
-	\item The author could introduce the study by acknowledging up front that slow sinking particles are the particles most impacted by submesoscale (as shown in previous papers) and this is why they are the focus of this paper that explores the sensitivity to size spectrum etc.
+\textit{The author could introduce the study by acknowledging up front that slow sinking particles are the particles most impacted by submesoscale (as shown in previous papers) and this is why they are the focus of this paper that explores the sensitivity to size spectrum etc.\\}
 
 \note{Yes, this should be done - I agree.}
-\end{itemize}
 
 \section*{Remineralization and slower sinking particle contribution.}
-The choice of some parameter appears arbitrary.
+\textit{The choice of some parameter appears arbitrary.
 I like the fact that the authors sweep the parameter space of the size spectrum ($\xi$ = 2, 3, 4).
-The choice of this parameter is however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).
+The choice of this parameter is however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).\\}
 

### 2020-04-03 Submission_and_reviews/response_to_reviewers.tex
progress on response to reviewers

@@
 
+To ensure that this is clearer in the manuscript, the text has been modified in the introduction and in the second paragraph of section 2.2.2.\\
+
 \textit{Throughout the text, the authors should be very clear about what they call fast and slow sinking particles.
@@
 
-\note{We should be clearer in the text. This is partially (but poorly) done in section 2.2.2}\\
+We trust that this is now clearer in the manuscript, with the characterization into "slow" and "fast" not being based on the absolute value of the sinking rates, but rather on the ratio with the vertical currents present in the the study region.
+The text has been modified to improve clarity in both the introduction and section 2.2.2.\\
 
@@
 
-\note{As outlined above, the choice of sinking rates is based on the dynamics of the region studied.
+There are no analytic limitations in exploring the faster-sinking part of the particle sinking velocity spectrum.
+As outlined above, the choice of sinking rates is based on the dynamics of the region studied.
 Any other regions with stronger vertical motions at submesoscales could be explored with faster sinking particles.
 We believe the overarching conclusion would be the same: The 1D traditional paradigm fails to capture export for particles with sinking rates similar or smaller than the vertical velocity, especially when the spectrum slope is steeper.
-At Station Papa, this affects the range of particles sinking at $<$ 5 m/day, but in a place where relative vorticity is larger (e.g., gulf stream), and vertical velocities can reach the order of 100 m/day, then the range of particle size for which the 1D model fails would be greater.}\\
+At Station Papa, this affects the range of particles sinking at $<$ 5 m/day, but in a place where relative vorticity is larger (e.g., gulf stream), and vertical velocities can reach the order of 100 m/day, then the range of particle size for which the 1D model fails would be greater.
+All of our results are put in perspective of the ratio between advective and sinking rates, which makes them applicable to other regions of the ocean.
+We have addressed this point even further in our response to another comment above (Major point \#2 of reviewer \#1).\\
 

### 2020-04-03 size_differentiated_export.tex
progress on response to reviewers

@@
 	The dynamical model is coupled with a particle-tracking module to model the advection of particles by fluid flow, while neglecting the effects of particle inertia and drag on their advection.
-In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$).
+In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$) \add{scaled from the range of vertical currents modeled in this region.
+We aim to address the transitional regime of the particle sinking velocity spectrum, where both advection and sinking speeds have similar order of magnitudes.
+This transitional regime will thus vary depending on the local dynamics: in strong frontal regions such as western boundary current, vertical currents can $\mathcal{O}$(100 m/day).}
 
@@
 Each particle class is characterized by a different sinking velocity: 0.025, \remove{0.05, }1, and 5 m/day.
-The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
+\add{In this study, these particle classes are refered to as slow- intermediate-, and fast-sinking particles.
+This characterization is not based on the absolute value of the sinking rate, but rather on the ratio with vertical currents in the study region.} While 5 m/day remains a relatively slow sinking rate, } The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
 The fastest-sinking velocity is chosen as an end-member velocity class of particle\change{ that will be exported in its entirety over the course of our experiment.

### 2020-04-03 Submission_and_reviews/response_to_reviewers.tex
more review responses

@@
 All of our results are put in perspective of the ratio between advective and sinking rates, which makes them applicable to other regions of the ocean.
-We have addressed this point even further in our response to another comment above (Major point \#2 of reviewer \#1).\\
+We have addressed this point even further in our response to another comment above (Major point \#2 of reviewer \#1), which led to additional text in the discussion section.\\
 
@@
 Submesoscale-driven subduction have been shown to leak below the ML (cite Sanjiv's paper, and the one from Ruiz and Pascual recently published?).
-}\\
+BTW: Resplandy and al does not resolve submesoscale.
+They say it explicitely in the paper that the spectrum of vertical velocity suggest they resolve scales at 10 km and larger.
+Same for Stukel and Erikson - scales are O(10 km), not subkilometer.}\\
 
@@
 
-\note{Yes, this should be done - I agree.}
+This is a good point. We trust that the modifications made to the introduction now reflect this key aspect of the paper. The point is reiterated in Section 2.2.2 as well.
 
@@
 
-\note{This parameter range is based on observational evidence cited in the text (L640), although not explicitly in section 2.2.3., where it would be most informative.
-We have modified the text in section 2.2.3 to better justify the range of $\xi$ used in this study.}
+This parameter range is based on observational evidence cited in the text (L640), although not explicitly in section 2.2.3., where it would be most informative.
+We have modified the text in section 2.2.3 to better justify the range of $\xi$ used in this study.
+there is also a few sentences in Section 4.2 putting these values of the slope into perspective, explaining that the exact value is a result of our approximations, but that the conclusion of the importance of constraining that slope remains valid, as the threshold is likely within the range of observed values for $\xi$.\\
 
-\begin{itemize}
-	\item Could you please present the case where the biomass spectrum slope is positive? Same as Figure 8 but with ξ = 2 and contrast it with the case of $\xi$ = 4?
+\textit{Could you please present the case where the biomass spectrum slope is positive? Same as Figure 8 but with ξ = 2 and contrast it with the case of $\xi$ = 4?\\}
 
-	\item The authors briefly mention that slopes greater than 3 have been observed (L640).
+\note{How to address that? not much to gain from putting those results in...\\}
+
+\textit{The authors briefly mention that slopes greater than 3 have been observed (L640).
 Could this discussion be augmented?
@@
 Bridging your modeling results with available observations would greatly benefit the paper and facilitate the use of your conclusions by the community (please look into prior work to make these links).
-I strongly encourage you to discuss the implications of this result, what they mean for people measuring particles and export, what they should be looking for in the field?
+I strongly encourage you to discuss the implications of this result, what they mean for people measuring particles and export, what they should be looking for in the field?\\}
 
 	\note{We have modified the text to discuss the implications of a steeper slope in a greater context.
-It now includes information about sources of observational evidence for steeper spectral slopes and the expected spatio-temporal variability }
+It now includes information about sources of observational evidence for steeper spectral slopes and the expected spatio-temporal variability \\}
 
-	\item The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague "under specific conditions ..." (L27).
-Please try to clarify what this means in Layman terms in the abstract.
+\textit{The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague "under specific conditions ..." (L27).
+Please try to clarify what this means in Layman terms in the abstract.\\
+}
+\rep{Text has been modified to address this comment.\\}
 
-	\rep{Text has been modified to address this comment.}
-
-	\item How do your results depend on the remineralization (0.13 d-1) length-scale? 
-\end{itemize}
+\textit{How do your results depend on the remineralization (0.13 d-1) length-scale? \\}
 

### 2020-04-03 Submission_and_reviews/response_to_reviewers.tex
and some more

@@
 
-	\note{We have modified the text to discuss the implications of a steeper slope in a greater context.
-It now includes information about sources of observational evidence for steeper spectral slopes and the expected spatio-temporal variability \\}
+We have modified the text in the discussion section to discuss the implications of a steeper slope in a greater context.
+It now includes information about sources of observational evidence for steeper spectral slopes and the expected spatio-temporal variability.\\
 
@@
 \textit{How do your results depend on the remineralization (0.13 d-1) length-scale? \\}
+
+\note{hmm...}
 

### 2020-04-10 Submission_and_reviews/response_to_reviewers.tex
more revisions

--- 2020-04-03 Submission_and_reviews/response_to_reviewers.tex
@@
 \usepackage{natbib}
+\usepackage{hyperref}
 
@@
 
-Comments provided by reviewer \#1 are constructive and relevant.
-They lead to major changes in the manuscript, namely figure 7 and 8.
-It also led us to clarify some of the aspects of the manuscript, as the scientific reasoning behind some of the choices made (e.g., particle seeding depth).
-Most of the concerns risen by the reviewer were, however, related to the definition of an export horizon to quantify export.
-We argue below that, based on both our work and recent studies \citep{Palevsky_2018}, the definition of an export horizon is not adequate and introduces subjectivity and biases in the results.
+Comments provided by both reviewers are constructive, relevant, and thus greatly appreciated.
+We are grateful to those two reviewers for providing helpful comments that improved the clarity of the study.\\
+
+Their comments led to major changes in the manuscript, namely figure 7 and 8.
+It also led us to clarify some of the aspects of the manuscript, such as the scientific reasoning behind some of the choices made (e.g., particle seeding depth).
+Most of the concerns risen by the reviewer were, however, related to either the definition of an export horizon to quantify export, or the range of sinking speeds selected for the study.
+We argue below that (1) based on both our work and recent studies \citep{Palevsky_2018}, the definition of an export horizon is not adequate and introduces subjectivity and biases in the results, and (2) the relevant range of sinking rates is scaled to the dynamics of the region.
+The absolute values are not so much what is important, but rather the relative importance to vertical currents.
+In a more energetic region than the northeast Pacific, the range of particle sinking speeds would be wider and reach sinking rates of O(100 m/day), but would lead to similar results than the ones detailed in this study.\\
+
+These two important points were clarified in several part of the revised manuscript.
 
@@
 
-We carefully considered this question during our study.
-We deliberately  did not rely on a ``export depth horizon" due to the facts that it is not consistently defined in the literature, and that recent work questions the validity of selecting a depth horizon as an ``export depth", arguing for a dynamics-based definition \citep{Palevsky_2018}.
-This is one of the reasons why the conclusions focus on export fluxes, rather than export, as the latter would require defining a possibly controversial export horizon.\\
-
-Additionally, the base of the euphotic zone is preferred in our study for three main reasons: 
+{\color{blue}
+We carefully considered this question during our study. The base of the euphotic zone is preferred in our study for three main reasons: 
 			\begin{enumerate}
@@
 By seeding particles at the base of the euphotic layer, we focus on the particulate material available to export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than possibly advection, as demonstrated in this study).
+				\item Seeding over 80 m instead of 10 m would require 8 times as many particles, as it is important to preserve particle density to adequately capture the physical dynamics at small scale (i.e., if particle seeding is too sparse, the presence of submesoscale dynamics would have little impact as no particles would be advected through these features).
+This would bring the total amount of particles tracked from $\sim$6 millions to $\sim$48 millions, largely limiting the number of experiments we could conduct in a reasonable time frame, but more importantly would not provide any more insights to the study (see point \#1).
 				\item The main results are expressed in terms of vertical fluxes.
@@
 Including fluxes in the ML would introduce a bias into our results that is not relevant to our objectives.
-				\item Seeding over 80 m instead of 10 m would require 8 times as many particles, as it is important to preserve particle density to adequately capture the physical dynamics at small scale (i.e., if particle seeding is too sparse, the presence of submesoscale dynamics would have little impact as no particles would be advected through these features).
-This would bring the total amount of particles tracked from $\sim$6 millions to $\sim$48 millions, largely limiting the number of experiments we could conduct in a reasonable time frame.
 			\end{enumerate}
+
+Additionally, we deliberately did not rely on a ``export depth horizon" due to the facts that it is not consistently defined in the literature, and that recent work questions the validity of selecting a depth horizon as an ``export depth", arguing for a dynamics-based definition \citep{Palevsky_2018}.
+This is one of the reasons why the conclusions focus on export fluxes, rather than export, as the latter would require defining a possibly controversial export horizon.\\
 
@@
 
-Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above.\\
+Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above.\\}
 
@@
 \textit{``it is unclear why 5m/day is selected for the largest particle class."\\}
+{\color{blue}
 	The choice of 5m/day sinking rates as the ``fast-sinking"  class is justified on lines 300-301 of the original manuscript.
@@
 In our case, 5 m/day is faster than 85-90\% of the vertical velocity modeled in our domain at any given time.
-We have added some text in Section 2.2.2 to make the justification clearer to the reader.\\
+We have added some text in Section 2.2.2 to make the justification clearer to the reader.\\}
 
 \textit{``Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity."\\}
+{\color{blue}
 	This is therefore not exact in this case.
 As mentioned, at any given time, between 10 and 15\% of the vertical velocity over the model domain is larger than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles.
-If \textit{``vertical advective velocities exceed the large particle sinking velocity"}, it is rare and short-lived.\\
+If  }\textit{``vertical advective velocities exceed the large particle sinking velocity"}{\color{blue}, it is rare and short-lived.\\}
 
+{\color{blue}
 	However, your comment is very relevant: What do our findings mean for sinking rates far exceeding the maximum modeled vertical velocities?
@@
 We agree, however, that this is an important fact to consider and discuss in the manuscript.
-As a result, we have added a paragraph in section 4.2 to put our findings in perspective with aggregates sinking at much faster sinking rates.
+As a result, we have added a paragraph in section 4.2 to put our findings in perspective with aggregates sinking at much faster sinking rates.}
 
@@
 
-This is correct.\\
+ {\color{red}
+This is correct.\\}
 
@@
 
- This is a good point that is now addressed in the revised manuscript.
+ {\color{blue}
+ This is a good point, that is now addressed in the revised manuscript.
 Fig 7 and 8 are now displaying the PDF of biomass fluxes integrated over the entire particle tracking experiment (i.e.
@@
 We opted to show day 25 of simulation to simplify the interpretation of the PDFs; in fact, the impact of remineralization on the PDFs is not as clear in the time-integrated PDFs.
-We added some text along the new version of figures 7 and 8 to facilitate plot interpretation.\\
+We added some text along the new version of figures 7 and 8 to facilitate plot interpretation.\\}
 
@@
 Really, we should be interested in how much of the initial biomass in each size category has "escaped" through the export horizon by the end of the simulation, i.e.
-their time-integrated contribution to export.\\}
+their time-integrated contribution to export.}
 
- As previously mentioned, the study focuses on export fluxes rather than export, to avoid introducing subjectivity in defining an export horizon.\\
+ {\color{blue}
+ As previously mentioned, the study focuses on export fluxes rather than export, to avoid introducing subjectivity in defining an export horizon.\\}
 
@@
 In contrast, Figure 6 shows that only a very small fraction of the small particles reach 100m in winter, even when they are not remineralizing.
-It therefore seems that even in winter, large particles must dominate the integrated export flux in the simulation with remineralization, contradicting the second major conclusion of the study.\\}
+It therefore seems that even in winter, large particles must dominate the integrated export flux in the simulation with remineralization, contradicting the second major conclusion of the study.}
 
+{\color{blue}
 	This is a good example of how defining an arbitrary export horizon can skew the results.
@@
 This is why we focus on biomass fluxes as opposed to integrated biomass.
-Along with other reasons mentioned above (seeding strategy, operational limitations, etc).\\
+Along with other reasons mentioned above (seeding strategy, operational limitations, etc).\\}
 
-\textit{I suggest the authors repeat their analysis, comparing time-integrated export through 100m in order to assess the contribution of large vs. small particles.\\}
+\textit{I suggest the authors repeat their analysis, comparing time-integrated export through 100m in order to assess the contribution of large vs. small particles.}
 
+{\color{blue}
 This was the original direction that we took for this study.
@@
 If particles are tracked for an infinitely long time, they will eventually all be exported, and the dominant particle class is only a function of the Junge slope.
-If particles are tracked for long enough for one class to cross the export horizon, but not other classes (as it would be the case for a horizon defined at 100 m), then the export would artificially be driven by the fast sinking particles.
+If particles are tracked for long enough for one class to cross the export horizon, but not other classes (as it would be the case for a horizon defined at 100 m), then the export would artificially be driven by the fast sinking particles.}
 
 \subsection*{Minor comments}
-\textit{Line 306: Is it three weeks, or 28 days (four weeks)?}\\
-\rep{Text has been modified accordingly.}
+\textit{Line 306: Is it three weeks, or 28 days (four weeks)?}
+
+{\color{blue}Text has been modified accordingly.\\}
+
 \textit{Figure 7+8: It would be useful to point out either in the caption or axis label that the x axes are the vertical velocity combining both sinking and advective components, and that the velocity in the legends is the initial sinking velocity.
-This confused me for a few minutes.}\\
-\rep{Figure captions have been modified.}
+This confused me for a few minutes.}
+
+{\color{blue}Figure captions have been modified.\\}
+
 \textit{Acknowledgments: Will the model output be archived for public access?}\\
-\rep{Due to the very large amount of data necessary for this study, a subset of the data, equired to produce the figures, is publicly available (link is now included in acknowledgments).
-Full dataset is available on request.}
+{\color{red}Due to the very large amount of data necessary for this study ($>$ 1 TB), it is not possible to store the data online.
+To remediate this issue, the source code used to conduct the physical model simulation is made publicly available on GitHub (\url{https://github.com/PSOM/V1.0/tree/master/code/NP_summer} and \url{https://github.com/PSOM/V1.0/tree/master/code/NP_winter}).
+	The source code for particle tracking experiments is also available online \url{https://github.com/matdever/offline_particle_tracking}.
+Finally, the routines used to extract the relevant data and produce the figures is available HERE.
+This information is provided in the ACKNOWLEDGMENTS}
 
 \section{Comments from Reviewer  \#2}
-\rep{We would first like to thank this Reviewer for these very on-point and constructive reviews. They were very helpful to make the manuscript stronger!}
 
@@
 It also means that the authors cannot really conclude about the relative role of particles that have sinking rates similar in magnitude or faster than submesoscale motions (i.e.
-50-300 m/d).\\}
+50-300 m/d).}
 
+{\color{blue}
 	The three sinking rates were defined based on having one class virtually non-sinking (0.025 m/day), one class within the range of $w$ modeled (1 m/day), and one class larger than $w$ modeled at submesoscale in the winter case (5 m/day).
@@
 
-To ensure that this is clearer in the manuscript, the text has been modified in the introduction and in the second paragraph of section 2.2.2.\\
+To ensure that this is clearer in the manuscript, the text has been modified in the introduction and in the second paragraph of section 2.2.2.\\}
 
@@
 I recommend to see Baker et al 2017 or Riley et al 2016 for example who present in-situ observations of sinking speed and define slow $<$ 20 m/d and fast $>$ 20 m/d.
-Also note that this nomenclature is consistent with the rates used in ocean biogeochemical models, which usually have a fast sinking rate of 50-200 m/d, and sometimes an additional pool with slow sinking rate of 1-5 m/d.\\}
+Also note that this nomenclature is consistent with the rates used in ocean biogeochemical models, which usually have a fast sinking rate of 50-200 m/d, and sometimes an additional pool with slow sinking rate of 1-5 m/d.}
 
-We trust that this is now clearer in the manuscript, with the characterization into "slow" and "fast" not being based on the absolute value of the sinking rates, but rather on the ratio with the vertical currents present in the the study region.
-The text has been modified to improve clarity in both the introduction and section 2.2.2.\\
+{\color{blue}
+	We trust that this is now clearer in the manuscript, with the characterization into "slow" and "fast" not being based on the absolute value of the sinking rates, but rather on the ratio with the vertical currents present in the the study region (see comments above).
+The text has been modified to improve clarity in both the introduction and section 2.2.2.\\}
 
@@
 Is it because of limitations related to the Stokes Law?
-Is it because the model is not adapted to look at faster sinking rates?\\}
+Is it because the model is not adapted to look at faster sinking rates?}
 
+{\color{blue}
 	There are no analytic limitations in exploring the faster-sinking part of the particle sinking velocity spectrum.
@@
 All of our results are put in perspective of the ratio between advective and sinking rates, which makes them applicable to other regions of the ocean.
-We have addressed this point even further in our response to another comment above (Major point \#2 of reviewer \#1), which led to additional text in the discussion section.\\
+We have addressed this point even further in our response to another comment above (Major point \#2 of reviewer \#1), which led to additional text in the discussion section.\\}
 
@@
 
-\textit{The author could introduce the study by acknowledging up front that slow sinking particles are the particles most impacted by submesoscale (as shown in previous papers) and this is why they are the focus of this paper that explores the sensitivity to size spectrum etc.\\}
+\textit{The author could introduce the study by acknowledging up front that slow sinking particles are the particles most impacted by submesoscale (as shown in previous papers) and this is why they are the focus of this paper that explores the sensitivity to size spectrum etc.}
 
-This is a good point. We trust that the modifications made to the introduction now reflect this key aspect of the paper. The point is reiterated in Section 2.2.2 as well.
+{\color{blue}
+	This is a good point. We trust that the modifications made to the introduction now reflect this key aspect of the paper. The point is reiterated in Section 2.2.2 as well.}
 
@@
 I like the fact that the authors sweep the parameter space of the size spectrum ($\xi$ = 2, 3, 4).
-The choice of this parameter is however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).\\}
+The choice of this parameter is however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).}
 
+{\color{blue}
 	This parameter range is based on observational evidence cited in the text (L640), although not explicitly in section 2.2.3., where it would be most informative.
 We have modified the text in section 2.2.3 to better justify the range of $\xi$ used in this study.
-there is also a few sentences in Section 4.2 putting these values of the slope into perspective, explaining that the exact value is a result of our approximations, but that the conclusion of the importance of constraining that slope remains valid, as the threshold is likely within the range of observed values for $\xi$.\\
+there is also a few sentences in Section 4.2 putting these values of the slope into perspective, explaining that the exact value is a result of our approximations, but that the conclusion of the importance of constraining that slope remains valid, as the threshold is likely within the range of observed values for $\xi$.\\}
 
-\textit{Could you please present the case where the biomass spectrum slope is positive? Same as Figure 8 but with ξ = 2 and contrast it with the case of $\xi$ = 4?\\}
+\textit{Could you please present the case where the biomass spectrum slope is positive? Same as Figure 8 but with $\xi$ = 2 and contrast it with the case of $\xi$ = 4?\\}
 
-\note{How to address that? not much to gain from putting those results in...\\}
+\note{Include the figure for the reviewer}
 
@@
 Bridging your modeling results with available observations would greatly benefit the paper and facilitate the use of your conclusions by the community (please look into prior work to make these links).
-I strongly encourage you to discuss the implications of this result, what they mean for people measuring particles and export, what they should be looking for in the field?\\}
+I strongly encourage you to discuss the implications of this result, what they mean for people measuring particles and export, what they should be looking for in the field?}
 
-	\note{We have modified the text to discuss the implications of a steeper slope in a greater context.
-It now includes information about sources of observational evidence for steeper spectral slopes and the expected spatio-temporal variability \\}
+{\color{blue}
+	We have modified the text in the discussion section to discuss the implications of a steeper slope in a greater context.
+It now includes information about sources of observational evidence for steeper spectral slopes and the expected spatio-temporal variability.\\}
 
 \textit{The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague "under specific conditions ..." (L27).
-Please try to clarify what this means in Layman terms in the abstract.\\
-}
-\rep{Text has been modified to address this comment.\\}
+Please try to clarify what this means in Layman terms in the abstract.}
+
+{\color{blue}Text has been modified to address this comment.\\}
 
 \textit{How do your results depend on the remineralization (0.13 d-1) length-scale? \\}
+
+\note{hmm...}
 
@@
 This list is absolutely not exhaustive.
+
+{\color{red} Thank you for pointing out some of the studies we missed... }
 
@@
 
+{\color{red} Amala will tackle this part.}
+
 \section*{Abstract}
@@
 
-\rep{The abstract has been modified to improve clarity of the study's result}
+{\color{blue}The abstract has been modified to improve clarity of the study's result}
 
@@
 \end{itemize}
+
+{\color{red} TBD}
 

### 2020-04-10 Submission_and_reviews/response_to_reviewers.tex
Updates from Overleaf

--- 2020-04-03 Submission_and_reviews/response_to_reviewers.tex
@@
 It also led us to clarify some of the aspects of the manuscript, as the scientific reasoning behind some of the choices made (e.g., particle seeding depth).
-Most of the concerns risen by the reviewer were, however, related to the definition of an export horizon to quantify export.
+Most of the concerns raised by the reviewer were, however, related to the definition of an export horizon to quantify export.
 We argue below that, based on both our work and recent studies \citep{Palevsky_2018}, the definition of an export horizon is not adequate and introduces subjectivity and biases in the results.
@@
 			\begin{enumerate}
-				\item A series of non-trivia important transformations occur in the euphotic zone \citep[e.g., grazing, material packaging, and many others; see][for example]{Denman_1999} that are not captured in our idealized setup, and are far beyond the scope of our study.
+				\item A series of non-trivial important transformations occur in the euphotic zone \citep[e.g., grazing, material packaging, and many others; see][for example]{Denman_1999} that are not captured in our idealized setup, and are far beyond the scope of our study.
 By seeding particles at the base of the euphotic layer, we focus on the particulate material available to export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than possibly advection, as demonstrated in this study).

### 2020-04-20 Submission_and_reviews/response_to_reviewers.tex
Amala's edits

--- 2020-04-10 Submission_and_reviews/response_to_reviewers.tex
@@
 
-\section{Response to Editor's comments}
+%\section{Response to Editor's comments}
 
-Comments provided by both reviewers are constructive, relevant, and thus greatly appreciated.
+%Comments provided by both reviewers are constructive, relevant, and thus greatly appreciated.
 We are grateful to those two reviewers for providing helpful comments that improved the clarity of the study.\\
+We thank the reviewers for their constructive comments, which we have used to improve the manuscript in several ways. 
+\begin{itemize}
+    \item Figures 7 and 8 are revised 
+    \item We have clarified the scientific reasoning behind some of the choices we made (e.g., particle seeding depth)
+    \item We clarify that the range of sinking speeds selected for the study are comparable to the vertical velocities of the flow.
+It is the relative speed (between particle sinking and advection) that matters.
+Particles that sink faster are less affected by the flow.
+    \item We argue that the export horizon can introduce bias and subjectivity \citep{Palevsky_2018, buesseler2020metrics} and keep our results in terms of the flux.
+\end{itemize}
 
-Their comments led to major changes in the manuscript, namely figure 7 and 8.
+%Their comments led to major changes in the manuscript, namely figure 7 and 8.
 It also led us to clarify some of the aspects of the manuscript, such as the scientific reasoning behind some of the choices made (e.g., particle seeding depth).
@@
 
-These two important points were clarified in several part of the revised manuscript.
+The latter two important points were clarified in several part of the revised manuscript. In addition, we respond to each of the reviewers' points (in blue).
 
@@
 {\color{blue}
-We carefully considered this question during our study. The base of the euphotic zone is preferred in our study for three main reasons: 
+This study deals with the fate of sinking organic matter after it leaves the base of the euphotic zone.
+Accounting for physical processes (waves, Langmuir circulations, wind and buoyancy forced turbulence) within the surface mixed layer and the biological transformations within the euphotic layer are beyond the scope of this study.
+There are several reasons for considering only the region beneath the base of the euphotic layer (or beneath the base of the mixed layer, if the mixed layer were deeper than the euphotic layer).
+%We carefully considered this question during our study.
+The base of the euphotic zone is preferred in our study for three main reasons:
 			\begin{enumerate}
-				\item A series of non-trivia important transformations occur in the euphotic zone \citep[e.g., grazing, material packaging, and many others; see][for example]{Denman_1999} that are not captured in our idealized setup, and are far beyond the scope of our study.
-By seeding particles at the base of the euphotic layer, we focus on the particulate material available to export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than possibly advection, as demonstrated in this study).
+				\item A series of non-trivial important transformations occur in the euphotic zone \citep[e.g., grazing, materal packaging, aggregation, disaggregation, etc.; see][for example]{Denman_1999} that are not captured in our idealized setup, and are far beyond the scope of our study.
+By seeding particles at the base of the euphotic layer, we focus on the particulate material available for export, where remineralization and sinking are the dominant processes driving vertical fluxes (other than possibly advection, as demonstrated in this study).
 				\item Seeding over 80 m instead of 10 m would require 8 times as many particles, as it is important to preserve particle density to adequately capture the physical dynamics at small scale (i.e., if particle seeding is too sparse, the presence of submesoscale dynamics would have little impact as no particles would be advected through these features).
-This would bring the total amount of particles tracked from $\sim$6 millions to $\sim$48 millions, largely limiting the number of experiments we could conduct in a reasonable time frame, but more importantly would not provide any more insights to the study (see point \#1).
+This would bring the total amount of particles tracked from $\sim$6 million to $\sim$48 million, largely limiting the number of experiments we could conduct in a reasonable time frame, but more importantly would not provide any more insights to the study (see point \#1).
 				\item The main results are expressed in terms of vertical fluxes.
-Vertical fluxes of particulate matter within the ML are not necessarily relevant to particle export, for the reasons detailed above.
+Vertical fluxes of particulate matter within the ML are not necessarily relevant to particle export for the reasons detailed above.
 Including fluxes in the ML would introduce a bias into our results that is not relevant to our objectives.
@@
 
-Additionally, we deliberately did not rely on a ``export depth horizon" due to the facts that it is not consistently defined in the literature, and that recent work questions the validity of selecting a depth horizon as an ``export depth", arguing for a dynamics-based definition \citep{Palevsky_2018}.
+Additionally, we deliberately did not rely on an ``export depth horizon" due to the facts that it is not consistently defined in the literature.
+Recent work questions the validity of selecting a depth horizon as an ``export depth", arguing for a dynamics-based definition \citep{Palevsky_2018, buesseler2020metrics}.
 This is one of the reasons why the conclusions focus on export fluxes, rather than export, as the latter would require defining a possibly controversial export horizon.\\
 
-Finally, the small particles released at the base of the euphotic layer do not aim to represent small particles at the time of particle production.
-It can also represent larger particles at production that went through remineralization in the ML.
+Finally, the small particles released at the base of the euphotic layer do not necessarily represent small particles at the time of particle production.
+They can also represent larger particles at production that went through remineralization in the ML.\\
 
-Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above.\\}
+Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above.}
 
@@
 
+{\color{blue}Thank you for this comment.
+We have now clarified that we refer to particles as ``fast (or slow)'' sinking if their sinking speed is fast (or slow) compared to the vertical velocities in the flow.} \\
+
 \textit{``it is unclear why 5m/day is selected for the largest particle class."\\}
 {\color{blue}
-	The choice of 5m/day sinking rates as the ``fast-sinking"  class is justified on lines 300-301 of the original manuscript.
-It is based on the PDFs of the advective vertical velocity.
+	The choice of 5m/day sinking rates as the ``fast-sinking"  class (lines 300-301 of the original manuscript) is based on the PDFs of the advective vertical velocity.
 In our case, 5 m/day is faster than 85-90\% of the vertical velocity modeled in our domain at any given time.
-We have added some text in Section 2.2.2 to make the justification clearer to the reader.\\}
+We have added text in Section 2.2.2 to make this clearer to the reader.
+It is worth noting that the region we model here has low eddy kinetic energy and weaker vertical velocities compared to frontal regions, or regions with deep mixed layers, such as the North Atlantic subpolar gyre.\\}
 
@@
 {\color{blue}
-	This is therefore not exact in this case.
-As mentioned, at any given time, between 10 and 15\% of the vertical velocity over the model domain is larger than 5 m/day -- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles.
+ At any given time, between 10 and 15\% of the vertical velocities of the flow are larger than 5 m/day. 
+ %-- our fastest sinking rate -- and an even smaller percentage is sampled by the Lagrangian particles. 
  If  }\textit{``vertical advective velocities exceed the large particle sinking velocity"}{\color{blue}, it is rare and short-lived.\\}
@@
 {\color{blue}
-	However, your comment is very relevant: What do our findings mean for sinking rates far exceeding the maximum modeled vertical velocities?
-In that case, $w \approx w_s$, as the sinking rate largely dominate.
-We want to know if the ratio of fluxes of two large sinking velocity is greater and smaller than one (i.e., the slope of the biomass flux spectrum is positive or negative):
+	However, this comment is very relevant: What do our findings mean for particle sinking rates that exceed the maximum modeled vertical velocities? 
+	%In that case, $w \approx w_s$, as the sinking rate largely dominate. 
+	We want to know if the ratio of sinking fluxes of two ``fast'' sinking particle classes (with sinking speeds $w_1, w_2$) is greater and smaller than one (i.e., if the slope of the biomass flux spectrum is positive or negative):
 
@@
 
-To directly address your comment, it is true that for very large aggregates with sinking rates far exceeding the order of magnitude of vertical velocities, the contribution of slower sinking particles is not dominant.
-We believe it to be well-established, and is the basis of the traditional 1-D model commonly used.
-Our study demonstrates the limitations of this paradigm, as one considers slower-sinking particles classes.
-Furthermore, for the largest aggregate to constantly be driving the biomass flux, it would require an infinite reservoir of those large particles to be able to relate their larger flux to larger export.
-The biomass flux due to the aggregates would be larger until the source is exhausted -- which is likely to happen more quickly for 100 m/day particles than for smaller particles.
-In fact, export from very fast sinking particles (e.g., 100 m /day) tend to occur as events and are not sustained in time \citep{Kiko_2017}.
-Additionally, this paradigm is only true if the slope of the particle-size spectrum is smaller than $\sim$5 (based on our scaling).
+It is generally true that for very large aggregates with sinking rates far exceeding the vertical velocities in the flow, the contribution of slower sinking particles is not dominant.
+Our study demonstrates the limitations of this paradigm as one considers slower-sinking particles classes.
+Furthermore, for the largest aggregate to constantly be driving the biomass flux, it would require a sustained production of those large particles.
+The biomass flux due to the aggregates would be larger, but the production of large aggregate particles is less sustained than small particles.
+In fact, export from very fast sinking particles (e.g., 100 m /day) tends to occur as events and  not sustained in time \citep{Kiko_2017}.
+Additionally, this paradigm is only true if the slope of the particle-size spectrum is smaller than 5 (based on our scaling).
 
-Including a ``large aggregate" size class sinking at 100m/day, for example, would not provide much more interesting information, in our opinion.
-In fact, the flux of such a size class can be computed theoretically (using $w \approx w_s$) and does not require any model simulations.
-We agree, however, that this is an important fact to consider and discuss in the manuscript.
-As a result, we have added a paragraph in section 4.2 to put our findings in perspective with aggregates sinking at much faster sinking rates.}
+e to a large, fast-sinking (e.g.
+100m/day) class of particles can be computed theoretically (using $w \approx w_s$) and does not require any model simulations.
+We agree that this is important to consider and discuss in the manuscript.
+We have added a paragraph in section 4.2 to address the contribution of aggregates sinking much faster  than 5 m/day.}
 
@@
 
- {\color{red}
-This is correct.\\}
+% {\color{red}
+%This is correct.\\}
 
@@
  {\color{blue}
- This is a good point, that is now addressed in the revised manuscript.
-Fig 7 and 8 are now displaying the PDF of biomass fluxes integrated over the entire particle tracking experiment (i.e.
-28 days), to avoid confusion.
-Our conclusions are robust to whether the PDFs are displayed for a specific day, or for the entire simulation.
-The respective contributions of the different size classes vary little over the course of a simulation.
-We opted to show day 25 of simulation to simplify the interpretation of the PDFs; in fact, the impact of remineralization on the PDFs is not as clear in the time-integrated PDFs.
-We added some text along the new version of figures 7 and 8 to facilitate plot interpretation.\\}
+ This is a good point.
+We have revised Fig 7 and 8 to now display the PDF of biomass fluxes integrated over the entire particle tracking experiment (i.e.
+28 days).
+Our conclusions are not sensitive to whether the PDFs are for a specific day or for the entire simulation, because the respective contributions of the different size classes does not vary significantly over the course of the simulation.
+Showing day 25 of the simulation simplified the interpretation of the PDFs; in fact, the impact of remineralization on the PDFs is not as clear in the time-integrated PDFs.
+However, based on the reviewer's comment we have now replaced the figures with the time-integrated PDFs and  added an explanation.\\}
 
@@
  {\color{blue}
- As previously mentioned, the study focuses on export fluxes rather than export, to avoid introducing subjectivity in defining an export horizon.\\}
+Our study focuses on export fluxes rather than export through a horizon to avoid introducing subjectivity in defining an export horizon.\\}
 
@@
 	This is a good example of how defining an arbitrary export horizon can skew the results.
-If the export horizon was set to 90 m, then almost all of the 1m/day particles would be "exported", and they would therefore dominate export for $\xi=4$.
-If 100 m is used as an export horizon, this is no longer the case and the 5m/day class would dominate export.
+If the export horizon was set to 90 m, then almost all of the 1m/day particles would be ``exported", and they would therefore dominate export for $\xi=4$.
+If 100 m was used as an export horizon, this is no longer the case and the 5m/day class would dominate export.
 if 300 m was used, then there would be no export.
@@
 
-{\color{blue}Text has been modified accordingly.\\}
+{\color{blue}The text has been modified accordingly.\\}
 
@@
 \textit{Acknowledgments: Will the model output be archived for public access?}\\
-{\color{red}Due to the very large amount of data necessary for this study ($>$ 1 TB), it is not possible to store the data online.
-To remediate this issue, the source code used to conduct the physical model simulation is made publicly available on GitHub (\url{https://github.com/PSOM/V1.0/tree/master/code/NP_summer} and \url{https://github.com/PSOM/V1.0/tree/master/code/NP_winter}).
+{\color{red}Due to the very large amount of model data necessary for this study ($>$ 1 TB), it is not possible to provide the data online.
+Instead, the source code used to conduct the physical model simulations is made publicly available on GitHub (\url{https://github.com/PSOM/V1.0/tree/master/code/NP_summer} and \url{https://github.com/PSOM/V1.0/tree/master/code/NP_winter}).
 	The source code for particle tracking experiments is also available online \url{https://github.com/matdever/offline_particle_tracking}.
@@
 
+{\color{blue}Thank you for this comment.
+We have now clarified that we refer to particles as ``fast (or slow)'' sinking if their sinking speed is fast (or slow) compared to the vertical velocities in the flow.} \\
+
 {\color{blue}
 	The three sinking rates were defined based on having one class virtually non-sinking (0.025 m/day), one class within the range of $w$ modeled (1 m/day), and one class larger than $w$ modeled at submesoscale in the winter case (5 m/day).
-In fact, at any given time, at least 85\% of the modeled vertical velocity is smaller than 5 m/day -- our fastest sinking rate -- and an even larger percentage is sampled by the Lagrangian particles.
-For all intents and purposes, a 5 m/day sinking particle is ``fast" compared to the dynamical flow of the simulations.
-Any particle class with a faster sinking rate would behave in a predictable way, as vertical velocity is dominated by sinking.
-We modified the text in Section 2.2.2 to clarify this (Line 304 - 307).\\
+In fact, at any given time, at least 85\% of the modeled vertical velocity is smaller than 5 m/day -- our fastest sinking rate.
+	%and an even larger percentage is sampled by the Lagrangian particles. For all intents and purposes, a 5 m/day sinking particle is ``fast" compared to the dynamical flow of the simulations. 
+	Particles with sinking speeds that greatly exceed the flow velocities would behave in a predictable way; their flux would be dominated by sinking.
+The objective of the study is to capture that transitional part of the size spectrum.
+Station Papa is a relatively calm region, so submesoscale vertical velocities $w$ are of the order of 10 m/day at most.
+Other regions with stronger fronts would have $w\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.\\
 
-	Considering a sinking rate much faster than 5 m/day would bring us back to the traditional 1D model, as the sinking rate would greatly dominate the vertical flux.
-The objective of the study is to capture that transitional part of the size spectrum.
-Station Papa remains a relatively calm region, so submesoscale $w$ are of the order of 10 m/day at most.
-Other regions with stronger vorticity would have $w$ of the order of magnitude you suggest ($\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.\\
-
-To ensure that this is clearer in the manuscript, the text has been modified in the introduction and in the second paragraph of section 2.2.2.\\}
+To ensure that this is clearer in the manuscript, we have modified the Introduction and the second paragraph of section 2.2.2.\\}
 
@@
 {\color{blue}
-	We trust that this is now clearer in the manuscript, with the characterization into "slow" and "fast" not being based on the absolute value of the sinking rates, but rather on the ratio with the vertical currents present in the the study region (see comments above).
-The text has been modified to improve clarity in both the introduction and section 2.2.2.\\}
+	It has been clarified in the manuscript (Introduction and Section 2.2.2) that our  characterization of ``slow" and ``fast" is not based on the absolute sinking rates, but on the ratio of the sinking speed to the vertical currents present in the the study region (see comments above).\\}
 
@@
 We have modified the text in section 2.2.3 to better justify the range of $\xi$ used in this study.
-there is also a few sentences in Section 4.2 putting these values of the slope into perspective, explaining that the exact value is a result of our approximations, but that the conclusion of the importance of constraining that slope remains valid, as the threshold is likely within the range of observed values for $\xi$.\\}
+there is also a few sentences in Section 4.2 putting these values of the slope into perspective.
+\\} %, explaining that the exact value is a result of our approximations, but that the conclusion of the importance of constraining that slope remains valid, as the threshold is likely within the range of observed values for $\xi$.\\}
 
@@
 
-{\color{red} Thank you for pointing out some of the studies we missed... }
+{\color{red} Thank you for pointing out these studies, which have now been cited in the manuscript. }
 

### 2020-04-20 size_differentiated_export.tex
Amala's edits

@@
 Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux.
-However, this need not be the case in a dynamic oceanic flow field, where the ocean velocity can influence the descent rate of particles.
-Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
-The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important.
+However, this need not be the case \change{in a dynamic oceanic flow field,}{for particles whose sinking speeds are comparable to the vertical velocities of a dynamic oceanic flow field} \change{where the ocean velocity}{that} can influence the descent rate of particles.
+Particles with different settling speeds \change{}{that can be affected by the flow} are released in two process-oriented model simulations of an upper ocean eddying flow \change{}{in the Northeast Pacific near Station Papa} to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
+The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more \change{important}{active in the region}.
 The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export\change{.
-A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{, especially where the relative abundance of small particles is larger, as captured by a steeper particle size-spectrum slope}.
+A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{, especially where the relative abundance of small particles is large, as represented by a steep particle size-spectrum slope}.
 \change{Implementing a r}{R}emineralization \remove{scheme} generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven.
@@
 Each particle class is characterized by a different sinking velocity: 0.025, \remove{0.05, }1, and 5 m/day.
-\add{In this study, these particle classes are refered to as slow- intermediate-, and fast-sinking particles.
-This characterization is not based on the absolute value of the sinking rate, but rather on the ratio with vertical currents in the study region.} While 5 m/day remains a relatively slow sinking rate, } The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
+\add{In this study, these particle classes are referred to as slow- intermediate-, and fast-sinking particles.
+This characterization is not based on the absolute value of the sinking rate, but rather on the ratio with vertical currents in the study region.
+While 5 m/day remains a relatively slow sinking rate, } the slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
 The fastest-sinking velocity is chosen as an end-member velocity class of particle\change{ that will be exported in its entirety over the course of our experiment.

### 2020-06-26 Submission_and_reviews/response_to_reviewers.tex
Another round of corrections appliued to the manuscript.
Addresses all remaining comments except for the suggested citations.

@@
 We are grateful to those two reviewers for providing helpful comments that improved the clarity of the study.\\
-We thank the reviewers for their constructive comments, which we have used to improve the manuscript in several ways. 
+We thank the reviewers for their constructive comments, which we have used to improve the manuscript in several ways. Most notable changes include:
 \begin{itemize}
@@
     \item We clarify that the range of sinking speeds selected for the study are comparable to the vertical velocities of the flow.
-It is the relative speed (between particle sinking and advection) that matters.
+It is the relative speed (between particle sinking and advection) that is important, as opposed to the absolute value of the sinking speed.
 Particles that sink faster are less affected by the flow.
-    \item We argue that the export horizon can introduce bias and subjectivity \citep{Palevsky_2018, buesseler2020metrics} and keep our results in terms of the flux.
+    \item We argue that the export horizon can introduce bias and subjectivity \citep{Palevsky_2018, buesseler2020metrics} and thus keep our results in terms of fluxes.
 \end{itemize}
@@
 
-The latter two important points were clarified in several part of the revised manuscript. In addition, we respond to each of the reviewers' points (in blue).
+The last two points were clarified in several parts of the revised manuscript. In addition, we respond to each of the reviewers' points (in blue).
 
@@
 
-Additionally, we deliberately did not rely on an ``export depth horizon" due to the facts that it is not consistently defined in the literature.
+Additionally, we deliberately did not rely on an ``export depth horizon" due to the fact that it is not consistently defined in the literature.
 Recent work questions the validity of selecting a depth horizon as an ``export depth", arguing for a dynamics-based definition \citep{Palevsky_2018, buesseler2020metrics}.
@@
 {\color{blue}
-	The choice of 5m/day sinking rates as the ``fast-sinking"  class (lines 300-301 of the original manuscript) is based on the PDFs of the advective vertical velocity.
+	The choice of 5 m/day sinking rates as the ``fast-sinking"  class (lines 300-301 of the original manuscript) is based on the PDFs of the advective vertical velocity.
 In our case, 5 m/day is faster than 85-90\% of the vertical velocity modeled in our domain at any given time.
@@
 
-e to a large, fast-sinking (e.g.
-100m/day) class of particles can be computed theoretically (using $w \approx w_s$) and does not require any model simulations.
-We agree that this is important to consider and discuss in the manuscript.
+Furthermore, the contribution of a fast-sinking (e.g.
+100 m/day) class of particles to export fluxes can be computed theoretically (using $w \approx w_s$) and does not require any model simulations.
+We agree that this is important to consider and it is now discussed in the manuscript.
 We have added a paragraph in section 4.2 to address the contribution of aggregates sinking much faster than 5 m/day.}
@@
 Showing day 25 of the simulation simplified the interpretation of the PDFs; in fact, the impact of remineralization on the PDFs is not as clear in the time-integrated PDFs.
-However, based on the reviewer's comment we have now replaced the figures with the time-integrated PDFs and  added an explanation.\\}
+However, based on the reviewer's comment we have now replaced the figures with the time-integrated PDFs and  added an explanation in the text.\\}
 
@@
  {\color{blue}
-Our study focuses on export fluxes rather than export through a horizon to avoid introducing subjectivity in defining an export horizon.\\}
+Our study focuses on export fluxes rather than export through a horizon to avoid introducing subjectivity in defining an export horizon (see comment above).\\}
 
@@
 \textit{Acknowledgments: Will the model output be archived for public access?}\\
-{\color{red}Due to the very large amount of model data necessary for this study ($>$ 1 TB), it is not possible to provide the data online.
+{\color{blue} Due to the very large amount of model data necessary for this study ($>$ 1 TB), it is not possible to provide the data online.
 Instead, the source code used to conduct the physical model simulations is made publicly available on GitHub (\url{https://github.com/PSOM/V1.0/tree/master/code/NP_summer} and \url{https://github.com/PSOM/V1.0/tree/master/code/NP_winter}).
-	The source code for particle tracking experiments is also available online \url{https://github.com/matdever/offline_particle_tracking}.
-Finally, the routines used to extract the relevant data and produce the figures is available HERE.
-This information is provided in the ACKNOWLEDGMENTS}
+The source code for particle tracking experiments is also available online \url{https://github.com/PSOM/offline_particle_tracking}.
+Finally, the routines used to extract the relevant data and produce the figures is available \url{https://github.com/matdever/Size-differentiated_Export_GBC/tree/master/figures/code}.
+This information is provided in the acknowledgements, with a citeable DOI.}
 
@@
 
+Please read the response to reviewer \#1 section for an even more in-depth justification of the range of sinking speeds.
 To ensure that this is clearer in the manuscript, we have modified the Introduction and the second paragraph of section 2.2.2.\\}
@@
 
-\textit{By limiting their study to slow sinking particles, the authors target by design the particles that will be most sensitive to submesoscale dynamics (see Stukel et al) and exclude particles that sink with rates similar or faster than submesoscale motions and that can efficiently export at depth and participate to carbon sequestration.
-Indeed, submesoscale is largely trapped in the upper ocean and only have a limited impact on export at greater depth (see previous discussions of these effects in Stukel et al, Erikson et al and Resplandy et al).
+\textit{By limiting their study to slow sinking particles, the authors target by design the particles that will be most sensitive to submesoscale dynamics (see Stukel et al) and exclude particles that sink with rates similar or faster than submesoscale motions and that can efficiently export at depth and participate to carbon sequestration.}
+
+{\color{blue}
+	As mentioned above, the range of sinking velocity is scaled to the environment, and is meant to encompass the range of velocities observed in that region.
+Sinking velocity far exceeding water vertical velocity can be simply computed using a 1D approximation.
+See above for more in-depth discussion\\}
+
+ \textit{Indeed, submesoscale is largely trapped in the upper ocean and only have a limited impact on export at greater depth (see previous discussions of these effects in Stukel et al, Erikson et al and Resplandy et al).
 The authors should acknowledge these limitations and discuss their implications.\\}
 
-\note{That is also a good point.
-$w$ are strogner in ML, but we have little particles in the ML, so our fluxes are mostly based on velocities below the ML.
-Submesoscale-driven subduction have been shown to leak below the ML (cite Sanjiv's paper, and the one from Ruiz and Pascual recently published?).
-BTW: Resplandy and al does not resolve submesoscale.
-They say it explicitely in the paper that the spectrum of vertical velocity suggest they resolve scales at 10 km and larger.
-Same for Stukel and Erikson - scales are O(10 km), not subkilometer.}\\
+{\color{blue} While submesoscale dynamics are strongest in the mixed layer, they have been proven to leak into the ocean interior, especially when coupled to a mesoscale circulation (see Ramachandran et al.
+2014 in JGR and Ruiz et al.
+2019 in JGR).
+Resplandy et al.
+2019 explicitely mentions the fact that submesoscales dynamics are not resolved in the model used, and that the asymmetry associated with vertical velocityies at submesoscales  (i.e.
+the main mechanism leading to our conclusions) is not resolved (see Section 4.2 "Caveats and Limitations" in Resplandy et al.).
+A similar comment can be made for Erickson and Thompson 2018 (horizontal resolution is 2-4 km, so realistically not resolving processes at less than 10 km scales), and Stukel and Ducklow 2017 (stations are at most 10 km apart).
+We do not believe that the study is biased by design, as the fastest sinking particle class (5 m/day) virtually follows the 1D gravitational model that would also apply to all faster-sinkin particle classes, and are therefore insensitive to the presence of submesoscale dynamics (as demonstrated in the study).\\}
 
@@
 We have modified the text in section 2.2.3 to better justify the range of $\xi$ used in this study.
-there is also a few sentences in Section 4.2 putting these values of the slope into perspective.
+there is also a few sentences in Section 4.2 putting these values for the slope into perspective.
 \\} %, explaining that the exact value is a result of our approximations, but that the conclusion of the importance of constraining that slope remains valid, as the threshold is likely within the range of observed values for $\xi$.\\}
@@
 
-\note{Include the figure for the reviewer}
+{\color{blue}
+Figure 8 has been modified to include both $\xi$ = 2 and $\xi$ = 4 cases in the presence of remineraliztion.\\}
 
@@
 
-\note{hmm...}
+{\color{blue} We can only offer a hypothesis to answer that question, as the impacts of remineralization are non-linear and even counter-intuitive in the dynamically active submesoscale flows, and accumulate through time at an exponential rate (see Equation 9 and 10).
+In the absence of submesoscale dynamics, a back-of-the-envelope calculation that assumes $w_{tot} = w_{s}$ tells us that a  1\% change in the remineralization rate leads to a 0.2\% per day change in the vertical flux.
+The corresponding sensitivity in the presence of submesoscale dynamics is impossible to confidently predict without a thorough investigation involving a significant number of additional simulations.\\}
 
@@
 
-{\color{red} Thank you for pointing out these studies, which have now been cited in the manuscript. }
+{\color{blue} Thank you for pointing out these studies, some of which are now cited in the manuscript.
+Some of those studies focus on, we believe, ocean dynamics at a different scale (and regime) and are not necessarily directly relevant.
+While useful for context, those were intentionally left out of the bibliography.\\}
 
@@
 
-{\color{blue}The abstract has been modified to improve clarity of the study's result}
+{\color{blue}The abstract has been modified to improve clarity of the study's result.\\}
 
@@
 \begin{itemize}
-	\item Link to observational constraints on the slope of the size spectrum (see comment \#2)?
+	\item Link to observational constraints on the slope of the size spectrum (see comment \#2)?\\
+	{\color{blue} Range of typical values, along with the references, have been added to Section 2.2.3.\\}
 
@@
 We consider three distributions with slopes of Z, ZZ.." etc.
+		{\color{blue} An introductory sentence was added in ection 2.2.3 to clarify the link between the method and the study's objective.\\}
 \end{itemize}
-
-{\color{red} TBD}
 
@@
 	\item Can you specify if and how equation 9 differs from the traditional Martin curve?
+	{\color{blue} A good reference for this would be Cael and Bisson (2018) in \textit{frontiers in Marine Science}.
+The model used here is an exponential model, as opposed to the "Martin Curve" that relies on a power-law model.
+The Martin curve implicitely includes a decrease of the remineralization rate with time that is not considered in the exponential model.\\}
 
 	\item L40: the last sentence of the first paragraph is vague and unnecessary. I would delete it.
+	{\color{blue} text was modified\\}
 	\item L 162: Problem with reference Laboratory, 2018?
-
+	{\color{blue} Reference was fixed\\}
 	\item Figures 7 and 8. Please label the size classes on the insert or at least mention the colors-size relationship in the caption.
+	{\color{blue} To avoid overcrowing the figures, the color coding is included in the caption for figures 6-8.\\}
 
 	\item The model data used in this study should be made available as requested by AGU standards.
+	{\color{blue} The size of the data files exceed a few Terabytes due to the high-resolution simulation,  the very large number of particles tracked, and the number of experiments conducted.
+We were not able to identify a platform that would host such a large volume of data in a sustained way, and guaranteeing public access, and not for a lack of trying.
+We would happily consider any suggestions on that issue, as this is a re-occuring challenge in high-resolution modelling.\\}
 \end{itemize}

### 2020-06-26 size_differentiated_export.tex
Another round of corrections appliued to the manuscript.
Addresses all remaining comments except for the suggested citations.

@@
 	%% ------------------------------------------------------------------------ %%
-	\title{Size-differentiated Export in Different Dynamical Regimes in the Ocean}
+	\title{Size-differentiated Export \add{Flux} in Different Dynamical Regimes in the Ocean}
 
@@
 The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export\change{.
-A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{, especially where the relative abundance of small particles is large, as represented by a steep particle size-spectrum slope}.
+A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{by a factor ranging from 3 to 10, especially where the relative abundance of small particles is large, as represented by a steep particle size-spectrum slope}.
 \change{Implementing a r}{R}emineralization \remove{scheme} generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven.
@@
 The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.
-Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.
+%Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.
 
@@
 	\label{sec: equations_biomass}
-	The slope $\xi$ of the size spectrum of particles \citep[also know as the Junge slope;][]{White_2015} is the slope of the log-log curve of particle number $N$ vs. particle radius $r$, where
+
+	\add{To quantify vertical export fluxes, both the distribution of the number of particles and the associated biomass can be modeled based on two main variables: the particles' radii and the rate at which the number of particles changes with respect to the size.
+The particle number is modeled using a power-law function as a function of size that is driven by the paramater $\xi$.} This slope $\xi$ of the size spectrum of particles \citep[also know as the Junge slope;][]{White_2015} is the slope of the log-log curve of particle number $N$ vs.
+particle radius $r$, where
 	\begin{equation}
@@
 	Here, $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily.
+\add{Typical values for $\xi$ derived from both in-situ observations and satellite data have been reported to range from 3 to 6} \citep[][Z.
+Xiaodong, personal communication]{Kostadinov_2009, White_2015}.
 For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically.
@@
 
-	Assuming a Stokes-like relationship, we can construct a particle sinking velocity spectrum $N(w_s)$ based on (\ref{eq: powerlaw_radius}), as
+	Assuming a Stokes-like relationship, we can construct based on (\ref{eq: powerlaw_radius}) a particle sinking velocity spectrum $N(w_s)$, as \add{a function of the Junge slope $\xi$:}
 	\begin{equation}
@@
 Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\times t$.
-[right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class.
+[right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class \add{(red = 0.025 m/day; green = 1 m/day; blue = 5 m/day)}.
 The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions.
@@
 		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity \add{(sinking + advective)} along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
-\add{PDFs are computed from the whole 24-day particle tracking experiments.} Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
+\add{PDFs are computed from the whole 24-day particle tracking experiments.} Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity \add{(red = 0.025 m/day; green = 1 m/day; blue = 5 m/day)}.
 Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.}
@@
 		\caption{\change{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
-Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity.
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity \add{(red = 0.025 m/day; green = 1 m/day; blue = 5 m/day)}.
 Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}}
@@
 Xiaodong, personal communication]{White_2015}.
-    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \citep{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities, and steeper during the wintertime, when communities are mostly composed of small particles}.
+    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \citep{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities, and steeper during the wintertime, when communities are mostly composed of small particles} \citep{Parsons_1988, Dale_1999, Behrenfeld_2010}.
     The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content.
@@
 Glider data is archived at the University of Washington's Library \citep[\url{http://hdl.handle.net/1773/41656};][]{Pelland_2018_data}.
-%Model outputs, and particle trajectories are available on request.
-% Finally, we are grateful to the two anonymous reviewers for their valuable comments and suggestions.
+Code to reproduce analysis and figures are publicly available at \url{https://github.com/matdever/Size-differentiated_Export_GBC} \citep{Dever_dataset}.
+Due to the very large filesize, model outputs and particle trajectories are available on request.
+%Finally, we are grateful to the two anonymous reviewers for their valuable comments and suggestions.
 

### 2020-06-26 figures/code/Fig8_revised.m

@@ -181,8 +181,8 @@ ylim([1e-2 100])
 title('Relative Downward Flux','FontSize',28,'position',[2 200 0])
 
 set(gcf,'color','w')
-export_fig -r300 Fig8_revised.png
-close
+%export_fig -r300 Fig8_revised.png
+%close
 %%
 
 % Calculate total biomass to normalize by

### 2020-06-26 figures/code/dataset/Fig7_data.m

@@ -1,0 +1,96 @@
+clear
+%% This code extracts all the necessary data from the SQLite database to
+% produce Fig7 of the GBC manuscript.
+% This figure plots the histogram of the relative biomass vs vertical
+% velocity at DOY 25 in Summer/Winter for xi = 2 and xi = 4
+
+% Add the local path with the importw function
+addpath('/vortexfs1/home/mdever/Fig7')  
+
+%% Import w for each size class in winter and summer
+
+counter = 1;
+for tt = 1:0.125:25
+    disp(['Day ',num2str(tt),' out of 25 (',num2str(counter/193*100),'%)'])
+    if mod(59.5+tt,1)==0
+        summernum = num2str(59.5+tt,'%2.1f');
+    else
+        summernum = num2str(59.5+tt);
+    end
+    [wt0025s(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_summer/w0025mday_summer_doy',summernum,'.csv']);
+    [wt1s(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_summer/w1mday_summer_doy',summernum,'.csv']);
+    [wt5s(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_summer/w5mday_summer_doy',summernum,'.csv']);
+    
+    if mod(39+tt,1)==0
+        winternum = num2str(39+tt,'%2.1f');
+    else
+        winternum = num2str(39+tt);
+    end    
+    [wt0025w(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_winter/w0025mday_winter_doy',winternum,'.csv']);
+    [wt1w(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_winter/w1mday_winter_doy',winternum,'.csv']);
[…]

### 2020-06-26 figures/code/dataset/Fig7_datav2.m

@@ -1,0 +1,220 @@
+clear
+
+%% This figure plots the histogram of the relative biomass vs vertical velocity at
+% DOY 25 in Summer/Winter for xi = 2 and xi = 4
+addpath('/vortexfs1/home/mdever/Fig7')
+
+%% Set colors for each class
+color0025 = [215,48,39]/256;
+color1 = [39,100,25]/256;
+color5 = [49,54,149]/256;
+
+%% compute biomass per simulated particle
+
+% Set of marameters
+wmax = 5; wmin = 0.025;
+slope = 3; B0 = 1;
+% Compute total biomass based on the paramters
+Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+
+% For Junge slope = 2
+slope = 2;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_2 = B0*(0.025/wmax)^((3-slope)/2);
+B1_2 = B0*(1/wmax)^((3-slope)/2);
+B5_2 = B0*(5/wmax)^((3-slope)/2);
+
+% For Junge slope = 4
+slope = 4;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_4 = B0*(0.025/wmax)^((3-slope)/2);
+B1_4 = B0*(1/wmax)^((3-slope)/2);
+B5_4 = B0*(5/wmax)^((3-slope)/2);
+
+%% Import w for each size class in winter and summer
+counter = 1;
+wt0025s = zeros(1971717,1);
+wt1s = zeros(1971717,1);
+wt5s = zeros(1971717,1);
+
+wt0025w = zeros(1971717,1);
+wt1w = zeros(1971717,1);
+wt5w = zeros(1971717,1);
+
+for tt = 1:0.125:25
+    disp(['Day ',num2str(tt),' out of 25 (',num2str(counter/193*100),'%)'])
[…]

### 2020-06-26 figures/code/dataset/Fig8_data.m

@@ -1,0 +1,96 @@
+clear
+%% This code extracts all the necessary data from the SQLite database to
+% produce Fig7 of the GBC manuscript.
+% This figure plots the histogram of the relative biomass vs vertical
+% velocity at DOY 25 in Summer/Winter for xi = 2 and xi = 4
+
+% Add the local path with the importw function
+addpath('/vortexfs1/home/mdever/Fig7')  
+
+%% Import w for each size class in winter and summer
+
+counter = 1;
+for tt = 1:0.125:25
+    disp(['Day ',num2str(tt),' out of 25 (',num2str(counter/193*100),'%)'])
+    if mod(59.5+tt,1)==0
+        summernum = num2str(59.5+tt,'%2.1f');
+    else
+        summernum = num2str(59.5+tt);
+    end
+    [wt0025s(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_summer/w0025mday_remin_summer_doy',summernum,'.csv']);
+    [wt1s(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_summer/w1mday_remin_summer_doy',summernum,'.csv']);
+    [wt5s(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_summer/w5mday_remin_summer_doy',summernum,'.csv']);
+    
+    if mod(39+tt,1)==0
+        winternum = num2str(39+tt,'%2.1f');
+    else
+        winternum = num2str(39+tt);
+    end    
+    [wt0025w(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_winter/w0025mday_remin_winter_doy',winternum,'.csv']);
+    [wt1w(:,counter)] = importw(['/vortexfs1/share/mahadevanlab/mathieudever/particle_backup/particlespeed/Papa_winter/w1mday_remin_winter_doy',winternum,'.csv']);
[…]

### 2020-06-26 figures/code/dataset/importw.m

@@ -1,0 +1,23 @@
+function wtotal = importw(filename)
+
+%% Initialize variables.
+delimiter = ',';
+startRow = 1;
+endRow = inf;
+
+%% Format for each line of text:
+formatSpec = '%f%[^\n\r]';
+
+%% Open the text file.
+fileID = fopen(filename,'r');
+
+%% Read columns of data according to the format.
+dataArray = textscan(fileID, formatSpec, endRow(1)-startRow(1)+1, 'Delimiter', delimiter, 'TextType', 'string', 'EmptyValue', NaN, 'HeaderLines', startRow(1)-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
+
+
+%% Close the text file.
+fclose(fileID);
+
+%% Allocate imported array to column variable names
+wtotal = dataArray{:, 1};
+end

### 2020-07-06 Submission_and_reviews/response_to_reviewers.tex
Amala's modifications

@@
 It is the relative speed (between particle sinking and advection) that is important, as opposed to the absolute value of the sinking speed.
-Particles that sink faster are less affected by the flow.
+Particles that sink faster than the vertical velocities in the flow field are less affected by the flow.
     \item We argue that the export horizon can introduce bias and subjectivity \citep{Palevsky_2018, buesseler2020metrics} and thus keep our results in terms of fluxes.
@@
 
-The last two points were clarified in several parts of the revised manuscript. In addition, we respond to each of the reviewers' points (in blue).
+The last two points are clarified in several parts of the revised manuscript. In addition, we respond to each of the reviewers' points (in blue).
 
@@
 {\color{blue}
-	As mentioned above, the range of sinking velocity is scaled to the environment, and is meant to encompass the range of velocities observed in that region.
-Sinking velocity far exceeding water vertical velocity can be simply computed using a 1D approximation.
-See above for more in-depth discussion\\}
+	As mentioned above, the range of particle sinking velocities chosen in this study is based on the vertical 
+	%is scaled to the environment, and is meant to encompass the range of
+	velocities of the flow in that region.
+The sinking flux of particles with Sinking velocity far exceeding water vertical velocity can be computed using a 1D sinking flux model (e.g.
+Omand et al., 2020).
+See above for a more in-depth discussion\\}
 
@@
 Resplandy et al.
-2019 explicitely mentions the fact that submesoscales dynamics are not resolved in the model used, and that the asymmetry associated with vertical velocityies at submesoscales  (i.e.
-the main mechanism leading to our conclusions) is not resolved (see Section 4.2 "Caveats and Limitations" in Resplandy et al.).
-A similar comment can be made for Erickson and Thompson 2018 (horizontal resolution is 2-4 km, so realistically not resolving processes at less than 10 km scales), and Stukel and Ducklow 2017 (stations are at most 10 km apart).
-We do not believe that the study is biased by design, as the fastest sinking particle class (5 m/day) virtually follows the 1D gravitational model that would also apply to all faster-sinkin particle classes, and are therefore insensitive to the presence of submesoscale dynamics (as demonstrated in the study).\\}
+2019 explicitly state that submesoscale dynamics are not resolved in their model and that the asymmetry associated with vertical velocities at submesoscales  (an important mechanism leading to our conclusions) is not resolved by them (see Section 4.2 ``Caveats and Limitations" in Resplandy et al.).
+A similar comment can be made for Erickson and Thompson 2018 (horizontal resolution is 2-4 km, so realistically not resolving processes at scales less than 10 km), and Stukel and Ducklow 2017 (stations are at most 10 km apart).
+We do not believe that the study is biased by design, as the fastest sinking particle class (5 m/day) virtually follows the 1D gravitational model that would also apply to all faster-sinking particle classes, and is therefore insensitive to the presence of submesoscale dynamics (as demonstrated in the study).\\}
 
@@
 {\color{blue}
-	This is a good point. We trust that the modifications made to the introduction now reflect this key aspect of the paper. The point is reiterated in Section 2.2.2 as well.}
+	This is a good point. We trust that the modifications made to the Introduction now reflect this key aspect of the paper. The point is reiterated in Section 2.2.2 as well.}
 
@@
 We have modified the text in section 2.2.3 to better justify the range of $\xi$ used in this study.
-there is also a few sentences in Section 4.2 putting these values for the slope into perspective.
+There are also a few sentences in Section 4.2 that provide perspective for these values of the Junge slope.
 \\} %, explaining that the exact value is a result of our approximations, but that the conclusion of the importance of constraining that slope remains valid, as the threshold is likely within the range of observed values for $\xi$.\\}
@@
 Bridging your modeling results with available observations would greatly benefit the paper and facilitate the use of your conclusions by the community (please look into prior work to make these links).
-I strongly encourage you to discuss the implications of this result, what they mean for people measuring particles and export, what they should be looking for in the field?}
+I strongly encourage you to discuss the implications of this result, what they mean for people measuring particles and export, what they should be looking for in the field?}\\
 
 {\color{blue}
-	We have modified the text in the discussion section to discuss the implications of a steeper slope in a greater context.
-It now includes information about sources of observational evidence for steeper spectral slopes and the expected spatio-temporal variability.\\}
+	We have modified the Discussion section to address the implications of a steeper slope, the expected spatio-temporal variability and  observational evidence for steeper spectral slopes.\\}
 
-\textit{The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague "under specific conditions ..." (L27).
-Please try to clarify what this means in Layman terms in the abstract.}
+\textit{The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague ``under specific conditions ..." (L27).
+Please try to clarify what this means in layman terms in the abstract.}\\
 
@@
 
-\textit{How do your results depend on the remineralization (0.13 d-1) length-scale? \\}
+\textit{How do your results depend on the remineralization (0.13 d$^{-1}$) length-scale? \\}
 
@@
 Please find below a list of relevant papers that should be included in introduction and/or discussion.
-This list is absolutely not exhaustive.
+This list is absolutely not exhaustive.\\
 
@@
 
-{\color{red} Amala will tackle this part.}
+{\color{blue} The Introduction has been modified taking these comments into consideration and several references have been added.}
 
@@
 For example, the following sentences list raw modeling results without hinting at the mechanistic drivers of this response in the model.
-"a steeper particle size spectrum increases the relative contribution of smaller slow-sinking particles." "Implementing a remineralization scheme generally decreases the total amount of biomass exported[...]", "Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles."
+"a steeper particle size spectrum increases the relative contribution of smaller slow-sinking particles." "Implementing a remineralization scheme generally decreases the total amount of biomass exported[...]", "Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles."\\
 
-{\color{blue}The abstract has been modified to improve clarity of the study's result.\\}
+{\color{blue}The abstract has been modified to more clearly highlight the study's result.\\}
 
@@
 	\item Link to observational constraints on the slope of the size spectrum (see comment \#2)?\\
-	{\color{blue} Range of typical values, along with the references, have been added to Section 2.2.3.\\}
+	{\color{blue} Range of typical values, along with the references, has been added to Section 2.2.3.\\}
 
 	\item Explain why you examine the dependence between these different metrics, e.g.
-something like "we explore the sensitivity of X and Y to the particle size spectrum .....
+something like ``we explore the sensitivity of X and Y to the particle size spectrum .....
 We consider three distributions with slopes of Z, ZZ.." etc.
-		{\color{blue} An introductory sentence was added in ection 2.2.3 to clarify the link between the method and the study's objective.\\}
+
+		{\color{blue} An introductory sentence was added in Section 2.2.3 to clarify the link between the method and the study's objective.\\}
 \end{itemize}
@@
 \begin{itemize}
-	\item Can you specify if and how equation 9 differs from the traditional Martin curve?
-	{\color{blue} A good reference for this would be Cael and Bisson (2018) in \textit{frontiers in Marine Science}.
-The model used here is an exponential model, as opposed to the "Martin Curve" that relies on a power-law model.
-The Martin curve implicitely includes a decrease of the remineralization rate with time that is not considered in the exponential model.\\}
+	\item Can you specify if and how equation 9 differs from the traditional Martin curve?\\
+	{\color{blue} A good reference for this would be Cael and Bisson (2018) in \textit{Frontiers in Marine Science}.
+The flux profile here is exponential, as opposed to a power-law that is used to explain the ``Martin Curve".}
 
-	\item L40: the last sentence of the first paragraph is vague and unnecessary. I would delete it.
-	{\color{blue} text was modified\\}
+	%The Martin curve implicitely includes a decrease of the remineralization rate with time that is not considered in the exponential model.\\}
+
+	\item L40: the last sentence of the first paragraph is vague and unnecessary. I would delete it.\\
+	{\color{blue} The text was modified\\}
 	\item L 162: Problem with reference Laboratory, 2018?
 	{\color{blue} Reference was fixed\\}
-	\item Figures 7 and 8. Please label the size classes on the insert or at least mention the colors-size relationship in the caption.
-	{\color{blue} To avoid overcrowing the figures, the color coding is included in the caption for figures 6-8.\\}
+	\item Figures 7 and 8. Please label the size classes on the insert or at least mention the colors-size relationship in the caption.\\
+	{\color{blue} To avoid overcrowding the figures, the color coding is included in the caption for figures 6-8.\\}
 
@@
 	{\color{blue} The size of the data files exceed a few Terabytes due to the high-resolution simulation,  the very large number of particles tracked, and the number of experiments conducted.
-We were not able to identify a platform that would host such a large volume of data in a sustained way, and guaranteeing public access, and not for a lack of trying.
-We would happily consider any suggestions on that issue, as this is a re-occuring challenge in high-resolution modelling.\\}
+We were not able to identify a platform that would host such a large volume of data in a sustained way, while guaranteeing public access.
+We have therefore provided a link to the model code on Github.\\}
+	%We would happily consider any suggestions on this issue, as it is a re-occurring challenge in high-resolution modelling.\\}
 \end{itemize}
 
-References.
+{\bf References}\\
+
 Baker, C.A., Henson, S.A., Cavan, E.L., Giering, S.L.C., Yool, A., Gehlen, M., Belcher, A., Riley, J.S., Smith, H.E.K., Sanders, R., 2017.

### 2020-07-06 size_differentiated_export.tex
Amala's modifications

@@
 %Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.
+	\add{Despite progress on sampling and viewing particles in the ocean, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density} \citep{McDonnell_2010,Mcdonnell2012}.
 
-	Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth.
-Particles produced through primary and secondary production in the surface layer that are relatively large and fast-sinking, tend to sink out of the upper surface layer on timescales shorter than the timescale on which the particles get remineralized.
+	Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth \citep{Jackson1997,Armstrong2001,DeVries2014,omand2020sinking}.
+Particles produced through primary and secondary production in the surface layer that are relatively large and fast sinking tend to sink out of the upper surface layer on timescales shorter than the timescale on which the particles get remineralized.
 It is reasonable to treat POC export as sinking-dominated if the vertical advective velocities in the ocean are weaker than the velocities associated with gravitational sinking.
-However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type, that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day.
-The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, for which the abundance of small particles is $\mathcal{O}(10^4 - 10^8)$ greater than large particles.
+However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type, that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day \citep{riley2012relative,baker2017slow}.
+The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, for which the abundance of small particles is $\mathcal{O}(10^4 - 10^8)$ greater than large particles \citep{McCave1984,Petrik2013}.
 The biomass size spectrum, which indicates the distribution of biomass vs.
 particle size, tends to be flatter and variable in shape \citep{Sheldon_1972} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and typically varies between 2 and 3 depending on shape and porosity).
-Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction.
+Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction \citep{RichardsonJackson2007}.
 Even though the sinking velocity $w_s$ of particles does not perfectly relate to particle size $l$, it is fair to assume  that  $w_s \sim l^n$ (with $n=2$ according to Stokes law, and $1<n<2$ for complex particle shapes).
@@
 	Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior.
-For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \citep{vanHaren_2006, Waite_2016}.
+For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \citep{vanHaren_2006, Waite_2016} and in mesoscale features in the California current \citep{stukel2017mesoscale}.
 	\cite{Omand_2015}  found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic.
@@
 On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front.
-The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}.
-Enhanced vertical velocities can generate a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2000,Levy_2001}, or can significantly increase the export of POC to the ocean interior through downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.
-
-	The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
+The distribution of relative vorticity \change{across a front is asymmetric and skewed toward cyclonic vorticity}{associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity} \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \citep{Mahadevan_2006}.
+Enhanced vertical velocities can aid the supply
+	%generate a local bloom by supplying 
+	nutrients to the sunlit layer of the ocean for primary production \citep{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through \add{localized} downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.
+	\add{	The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
+If the fraction of  biomass associated with such slow sinking velocities is significant, submesoscale dynamics can significantly impact the export of POC.}
+	%The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
 Through this mechanism, smaller particles can be exported on timescales shorter than their remineralization timescales, despite their slower sinking velocities.
@@
 
-	In this study, we account for a range of particle sinking velocities in a dynamic flow field.
+	%In this study, we account for a range of particle sinking velocities in a dynamic flow field.
 Despite progress on sampling and viewing particles in the ocean \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density.
@@
 	We  rely on a submesoscale-resolving, non-hydrostatic  ocean model to simulate the dynamics in the upper few hundred meters of the ocean. 
-The model does not represent surface waves or boundary layer turbulence, but rather, examines the fate of particulate organic matter beneath the turbulent surface boundary layer.
 	The dynamical model is coupled with a particle-tracking module to model the advection of particles by fluid flow, while neglecting the effects of particle inertia and drag on their advection.
-In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$) \add{scaled from the range of vertical currents modeled in this region.
+In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$) \add{that is based on the range of vertical currents modeled in this region.
 We aim to address the transitional regime of the particle sinking velocity spectrum, where both advection and sinking speeds have similar order of magnitudes.
-This transitional regime will thus vary depending on the local dynamics: in strong frontal regions such as western boundary current, vertical currents can $\mathcal{O}$(100 m/day).}
+A similar study with sinking tracers  showed the influence of the flow \citep{taylor2020influence}, but the use of particles enables a characterization of export associated with each sinking  class of particles.
+}
+%	This transitional regime will vary depending on the local dynamics; in strong frontal regions such as western boundary currents, vertical currents can $\mathcal{O}$(100 m/day), but the region modeled in this study has weak submesoscale activity and vertical velocities, particularly in summer.}
 
@@
 Similar PSOM configurations were successfully used in previous studies \citep{Mahadevan_2012,Omand_2015}.
+\add{The model does not simulate surface waves or boundary layer turbulence, but rather, examines the fate of particulate organic matter beneath the turbulent surface boundary layer.}
 
 	Two main experiments are conducted using the same configuration of PSOM, where only initial conditions and surface forcings are varied: \textit{Papa\_summer} aims at generating ocean dynamics representing conditions in the Northeast Pacific in the summertime.
-Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($\ll$1).
+Summer ocean dynamics are characterized by a flow generally in geostrophic balance, with relatively weak density gradients and low Rossby numbers ($Ro\ll$1).
 \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region.
-A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \citep{Mensa_2013,Callies_2015,Thompson_2016}.
-The individual characteristics of each of \linebreak \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.
+A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $Ro=\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \citep{Mensa_2013,Callies_2015,Thompson_2016}.
+The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.
 

### 2020-07-06 size_differentiated_export.tex
Updates from Overleaf

@@
 We aim to address the transitional regime of the particle sinking velocity spectrum, where both advection and sinking speeds have similar order of magnitudes.
-A similar study with sinking tracers  showed the influence of the flow \citep{taylor2020influence}, but the use of particles enables a characterization of export associated with each sinking  class of particles.
+A similar study with sinking tracers  showed the influence of the flow }\citep{taylor2020influence}\add{, but the use of particles enables a characterization of export associated with each sinking  class of particles.
 }

### 2020-07-06 Submission_and_reviews/response_to_reviewers.tex

@@
 	velocities of the flow in that region.
-The sinking flux of particles with Sinking velocity far exceeding water vertical velocity can be computed using a 1D sinking flux model (e.g.
-Omand et al., 2020).
+The sinking flux of particles with Sinking velocity far exceeding water vertical velocity can be computed using a 1D sinking flux model \citep[e.g., ][]{Omand_2020}.
 See above for a more in-depth discussion\\}
@@
 Some of those studies focus on, we believe, ocean dynamics at a different scale (and regime) and are not necessarily directly relevant.
-While useful for context, those were intentionally left out of the bibliography.\\}
+While useful for context, those specific studies were intentionally left out of the bibliography.\\}
 
@@
 
-\bibliographystyle{plainnat}
+\bibliographystyle{apalike}
 \bibliography{reviews}

### 2020-07-06 size_differentiated_export.tex

--- 2020-07-06 size_differentiated_export.tex
@@
 The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.
-%Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.
-	\add{Despite progress on sampling and viewing particles in the ocean, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density} \citep{McDonnell_2010,Mcdonnell2012}.
+\add{Despite progress on sampling and viewing particles in the ocean, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density} \citep{McDonnell_2010,Mcdonnell_2012}.
 
-	Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth \citep{Jackson1997,Armstrong2001,DeVries2014,omand2020sinking}.
+	Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth \citep{Jackson_1997,Armstrong_2001,DeVries_2014,Omand_2020}.
 Particles produced through primary and secondary production in the surface layer that are relatively large and fast sinking tend to sink out of the upper surface layer on timescales shorter than the timescale on which the particles get remineralized.
 It is reasonable to treat POC export as sinking-dominated if the vertical advective velocities in the ocean are weaker than the velocities associated with gravitational sinking.
-However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type, that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day \citep{riley2012relative,baker2017slow}.
-The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, for which the abundance of small particles is $\mathcal{O}(10^4 - 10^8)$ greater than large particles \citep{McCave1984,Petrik2013}.
+However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type, that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day \citep{Riley_2012,Baker_2017}.
+The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, for which the abundance of small particles is $\mathcal{O}(10^4 - 10^8)$ greater than large particles \citep{McCave_1984,Petrik_2013}.
 The biomass size spectrum, which indicates the distribution of biomass vs.
 particle size, tends to be flatter and variable in shape \citep{Sheldon_1972} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and typically varies between 2 and 3 depending on shape and porosity).
-Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction \citep{RichardsonJackson2007}.
+Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction \citep{Richardson_2007}.
 Even though the sinking velocity $w_s$ of particles does not perfectly relate to particle size $l$, it is fair to assume  that  $w_s \sim l^n$ (with $n=2$ according to Stokes law, and $1<n<2$ for complex particle shapes).
@@
 	Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior.
-For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \citep{vanHaren_2006, Waite_2016} and in mesoscale features in the California current \citep{stukel2017mesoscale}.
+For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \citep{vanHaren_2006, Waite_2016} \add{and in mesoscale features in the California current }\citep{Stukel_2017}.
 \cite{Omand_2015}  found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic.
@@
 But, these estimates did not account for a range of sinking particle velocities.
-Typically, particulate organic matter (POM) has a wide spectrum of sinking velocities and in order to understand its fate and export, we need to consider the biomass distribution as a function of the particle sinking velocity spectrum and its interaction with the dynamics of the flow field in the ocean.
+Typically, POM has a wide spectrum of sinking velocities and in order to understand its fate and export, we need to consider the biomass distribution as a function of the particle sinking velocity spectrum and its interaction with the dynamics of the flow field in the ocean.
 
-	A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012,Mahadevan_2016}.
+	A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012, Mahadevan_2016}.
 Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2013b,Klein_2009,McWilliams_2016}.
@@
 The distribution of relative vorticity \change{across a front is asymmetric and skewed toward cyclonic vorticity}{associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity} \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \citep{Mahadevan_2006}.
-Enhanced vertical velocities can aid the supply
-	%generate a local bloom by supplying 
-	nutrients to the sunlit layer of the ocean for primary production \citep{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through \add{localized} downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.
-	\add{	The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
-If the fraction of  biomass associated with such slow sinking velocities is significant, submesoscale dynamics can significantly impact the export of POC.}
-	%The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum.
-Through this mechanism, smaller particles can be exported on timescales shorter than their remineralization timescales, despite their slower sinking velocities.
-Depending on the fraction of  biomass in smaller particles (i.e., with slow sinking velocities), the impact of submesoscale dynamics on the export of POC is potentially significant.
-
-	%In this study, we account for a range of particle sinking velocities in a dynamic flow field.
-Despite progress on sampling and viewing particles in the ocean \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density.
-Though we acknowledge a large variability in these relationships, we assume a relationship between particle size, biomass, and particle sinking velocity in order to assess the impact of the flow dynamics and particle size spectrum on the export flux.
+Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \citep{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through \add{localized} downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.\add{	The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
+If the fraction of  biomass associated with such slow sinking velocities is significant, submesoscale dynamics can potentially impact the export of POC.}
 
@@
 We aim to address the transitional regime of the particle sinking velocity spectrum, where both advection and sinking speeds have similar order of magnitudes.
-A similar study with sinking tracers  showed the influence of the flow \citep{taylor2020influence}, but the use of particles enables a characterization of export associated with each sinking  class of particles.
-}
-%	This transitional regime will vary depending on the local dynamics; in strong frontal regions such as western boundary currents, vertical currents can $\mathcal{O}$(100 m/day), but the region modeled in this study has weak submesoscale activity and vertical velocities, particularly in summer.}
+A similar study with sinking tracers  showed the influence of the flow} \citep{Taylor_2020}\add{, but the use of particles enables a characterization of export associated with each sinking class of particles.}
 
@@
 
-	In each particle-tracking experiment, four different classes of particles are released.
+	In each particle-tracking experiment, three different classes of particles are released.
 Each particle class is characterized by a different sinking velocity: 0.025, \remove{0.05, }1, and 5 m/day.
 \add{In this study, these particle classes are referred to as slow- intermediate-, and fast-sinking particles.
-This characterization is not based on the absolute value of the sinking rate, but rather on the ratio with vertical currents in the study region.
-While 5 m/day remains a relatively slow sinking rate, } the slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
-The fastest-sinking velocity is chosen as an end-member velocity class of particle\change{ that will be exported in its entirety over the course of our experiment.
+This characterization is not based on the absolute value of the sinking rate, but rather on the ratio with vertical currents in the study region.} The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 400 days to sink 10 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
+\add{While 5 m/day remains a relatively slow sinking rate, this} ``fastest-sinking" velocity is chosen as an end-member velocity class of particle\change{ that will be exported in its entirety over the course of our experiment.
 }{, based on the PDF of vertical velocities in the model.
@@
 For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represents 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}).
+
 	The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$ can be estimated if the biomass is assumed to scale with the particle's volume.
@@
 		\caption{\change{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
-Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity \add{(red = 0.025 m/day; green = 1 m/day; blue = 5 m/day)}.
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity (red = 0.025 m/day; green = 1 m/day; blue = 5 m/day).
 Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}}

### 2020-07-29 Submission_and_reviews/response_to_reviewers.tex
pre-submission changes

@@
 
-{\bf References}\\
+{\bf Suggested References}\\
 
@@
 
-\section{Comments from Andy Thompson}
-\begin{itemize}
-	\item Regarding submesoscales during the summer -- it would be worth calculating the mixed layer deformation radius during summer.
+%\section{Comments from Andy Thompson}
+%\begin{itemize}
+	%\item Regarding submesoscales during the summer -- it would be worth calculating the mixed layer deformation radius during summer.
 I suspect that it is at or less than your model resolution.
@@
 
-	\item John Taylor has a nice paper (JPO 2018) where we looked at a similar problem with his LES and in some cases, buoyant particles. It might be worth citing.
+	%\item John Taylor has a nice paper (JPO 2018) where we looked at a similar problem with his LES and in some cases, buoyant particles. It might be worth citing.
 
-	\item I know computing time is always an issue, but it would be interesting to run these at higher (or lower) resolution to see how the fluxes change.
+	%\item I know computing time is always an issue, but it would be interesting to run these at higher (or lower) resolution to see how the fluxes change.
 I would be surprised if they were converging -- in fact, I am not sure you would ever expect convergence depending on the wavenumber spectrum of w.
-\end{itemize}
+%\end{itemize}
 

### 2020-07-29 size_differentiated_export.tex
pre-submission changes

@@
-\documentclass[article,linenumbers]{agujournal2018}
-\usepackage{apacite}
+\documentclass[article,linenumbers]{agujournal2019}
 \usepackage{url} %this package should fix any errors with URLs in refs.
-\usepackage{amsmath}
-\usepackage{ulem}
+\usepackage{lineno}
+\usepackage[finalnew]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage{soul}
+\linenumbers
 
-% Trackchanges package
-\usepackage{trackchanges}
 \soulregister\ref7
@@
 
-% The FIXME macro
-\newcommand{\fixme}[1]{\color{red}$<$\textbf{#1}$>$\color{black}}
-% The AUTHOR response macro
-\newcommand{\rep}[1]{\color{blue}$<$\textbf{AUTHORS}: \textit{#1}$>$\color{black}\\}
+\usepackage{amsmath}
+\usepackage{ulem}
 
-%\draftfalse
+\draftfalse
 
@@
 Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux.
-However, this need not be the case \change{in a dynamic oceanic flow field,}{for particles whose sinking speeds are comparable to the vertical velocities of a dynamic oceanic flow field} \change{where the ocean velocity}{that} can influence the descent rate of particles.
-Particles with different settling speeds \change{}{that can be affected by the flow} are released in two process-oriented model simulations of an upper ocean eddying flow \change{}{in the Northeast Pacific near Station Papa} to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
+However, this need not be the case \change{in a dynamic oceanic flow field,}{for particles whose sinking speeds are comparable to the vertical velocities of a dynamic flow field} \change{where the ocean velocity}{that} can influence the descent rate of particles.
+Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow \change{}{in the Northeast Pacific} to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
 The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more \change{important}{active in the region}.
-The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export\change{.
-A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{by a factor ranging from 3 to 10, especially where the relative abundance of small particles is large, as represented by a steep particle size-spectrum slope}.
+The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export flux\change{.
+A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{by a factor ranging from 3 to 10, especially where the relative abundance of small particles is large, (i.e., steep particle size-spectrum slope)}.
 \change{Implementing a r}{R}emineralization \remove{scheme} generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven.
@@
 	Photosynthesis in the sunlit upper ocean and the production of Particulate Organic Carbon (POC) takes up dissolved inorganic carbon and facilitates the uptake of CO$_2$ from the atmosphere.
-The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.
-\add{Despite progress on sampling and viewing particles in the ocean, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density} \citep{McDonnell_2010,Mcdonnell_2012}.
+The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \cite{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.
+\add{Despite progress on sampling and viewing particles in the ocean, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density} \cite{McDonnell_2010,Mcdonnell_2012}.
 
-	Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth \citep{Jackson_1997,Armstrong_2001,DeVries_2014,Omand_2020}.
+	Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth \cite{Jackson_1997,Armstrong_2001,DeVries_2014,Omand_2020}.
 Particles produced through primary and secondary production in the surface layer that are relatively large and fast sinking tend to sink out of the upper surface layer on timescales shorter than the timescale on which the particles get remineralized.
 It is reasonable to treat POC export as sinking-dominated if the vertical advective velocities in the ocean are weaker than the velocities associated with gravitational sinking.
-However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type, that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day \citep{Riley_2012,Baker_2017}.
-The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, for which the abundance of small particles is $\mathcal{O}(10^4 - 10^8)$ greater than large particles \citep{McCave_1984,Petrik_2013}.
+However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type, that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day \cite{Riley_2012,Baker_2017}.
+The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, for which the abundance of small particles is $\mathcal{O}(10^4 - 10^8)$ greater than large particles \cite{McCave_1984,Petrik_2013}.
 The biomass size spectrum, which indicates the distribution of biomass vs.
-particle size, tends to be flatter and variable in shape \citep{Sheldon_1972} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and typically varies between 2 and 3 depending on shape and porosity).
-Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction \citep{Richardson_2007}.
+particle size, tends to be flatter and variable in shape \cite{Sheldon_1972} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and typically varies between 2 and 3 depending on shape and porosity).
+Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction \cite{Richardson_2007}.
 Even though the sinking velocity $w_s$ of particles does not perfectly relate to particle size $l$, it is fair to assume  that  $w_s \sim l^n$ (with $n=2$ according to Stokes law, and $1<n<2$ for complex particle shapes).
@@
 	Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior.
-For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \citep{vanHaren_2006, Waite_2016} \add{and in mesoscale features in the California current }\citep{Stukel_2017}.
-\cite{Omand_2015}  found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic.
-Advectively subducting plumes or filaments of high oxygen, chlorophyll and small POC (evidenced through backscatter) were detected from a suite of gliders during the North Atlantic Bloom experiment \citep{Alkire_2012}.
-Using model simulations to capture the process of eddy-driven subduction, \cite{Omand_2015} estimated the downward advective flux of non-sinking POC and parameterized it.
-\cite{Briggs_2011} quantified the flux of fast-sinking particles consisting largely of diatoms from observations of optical backscatter.
+For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \cite{vanHaren_2006, Waite_2016} \add{and in mesoscale features in the California current }\cite{Stukel_2017}.
+\citeA{Omand_2015}  found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic.
+Advectively subducting plumes or filaments of high oxygen, chlorophyll and small POC (evidenced through backscatter) were detected from a suite of gliders during the North Atlantic Bloom experiment \cite{Alkire_2012}.
+Using model simulations to capture the process of eddy-driven subduction, \citeA{Omand_2015} estimated the downward advective flux of non-sinking POC and parameterized it.
+\citeA{Briggs_2011} quantified the flux of fast-sinking particles consisting largely of diatoms from observations of optical backscatter.
 But, these estimates did not account for a range of sinking particle velocities.
@@
 
-	A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012, Mahadevan_2016}.
-Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2013b,Klein_2009,McWilliams_2016}.
-In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}.
+	A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \cite{Levy_2012, Mahadevan_2016}.
+Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \cite{Thomas_2013b,Klein_2009,McWilliams_2016}.
+In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \cite{FoxKemper_2008,Mahadevan_2016}.
 On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front.
-The distribution of relative vorticity \change{across a front is asymmetric and skewed toward cyclonic vorticity}{associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity} \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \citep{Mahadevan_2006}.
-Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \citep{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through \add{localized} downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.\add{	The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
+The distribution of relative vorticity \change{across a front is asymmetric and skewed toward cyclonic vorticity}{associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity} \cite{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \cite{Mahadevan_2006}.
+Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through \add{localized} downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.\add{	The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
 If the fraction of  biomass associated with such slow sinking velocities is significant, submesoscale dynamics can potentially impact the export of POC.}
@@
 We aim to address the transitional regime of the particle sinking velocity spectrum, where both advection and sinking speeds have similar order of magnitudes.
-A similar study with sinking tracers  showed the influence of the flow} \citep{Taylor_2020}\add{, but the use of particles enables a characterization of export associated with each sinking class of particles.}
+A similar study with sinking tracers  showed the influence of the flow} \cite{Taylor_2020}\add{, but the use of particles enables a characterization of export associated with each sinking class of particles.}
 
@@
 
-	This study uses a non-hydrostatic, three-dimensional, Process Study Ocean Model \citep[PSOM;][]{Mahadevan_1996a,Mahadevan_1996b} to simulate an eddy field that is representative of the Northeast Pacific Ocean.
+	This study uses a non-hydrostatic, three-dimensional, Process Study Ocean Model \cite<PSOM;>[]{Mahadevan_1996a,Mahadevan_1996b} to simulate an eddy field that is representative of the Northeast Pacific Ocean.
 The model is set in a channel configuration with periodic east-west boundaries, and solid boundaries in the south and north.
@@
 	Time-varying wind stress and heat flux are prescribed at the surface boundary.
-Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory \citep{PMEL_data}.
+Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory \cite{PMEL_data}.
 Daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long climatology.
@@
 While net surface heat fluxes are homogeneous in the zonal direction, a meridional gradient is maintained throughout the simulation.
-The meridional gradient was determined from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}, and set to 1/24 W/m$^2$/km (Figure \ref{fig: model_domain}c).
+The meridional gradient was determined from the North American Regional Reanalysis (NARR) product \cite{Mesinger_2006}, and set to 1/24 W/m$^2$/km (Figure \ref{fig: model_domain}c).
 
-	Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from Argo floats \citep{Gaillard_2015,Gaillard_2016}.
+	Initial hydrographic conditions are determined from a three-dimensional gridded field of temperature and salinity from Argo floats \cite{Gaillard_2015,Gaillard_2016}.
 Argo data is averaged monthly over the period 2002-2012 and two different months are used to initialize the two main numerical experiments for this study: Climatological conditions in April are used to initialize the \textit{Papa\_summer} experiment, while January climatological conditions are used to initialize the \textit{Papa\_winter} experiment (Table \ref{tab: meso_vs_submeso}).
 The north-south background density gradient is then intensified into three fronts located at $y = 75$, $y = 150$, and $y = 225$ km (Figure \ref{fig: model_domain}).
-The amplitude of the density gradient associated with the three fronts is determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \citep{Pelland_2016,Pelland_2018_data}.
+The amplitude of the density gradient associated with the three fronts is determined from the probability distribution function (PDF) of the density gradients measured by underwater gliders deployed around Station Papa over the period 2008-2010 \cite{Pelland_2016,Pelland_2018_data}.
 To reduce model spin-up time, density fronts are perturbed by a sinusoidal wave with a wavelength close to the 1st baroclinic deformation radius ($\lambda = $ 66 km).
-Similar PSOM configurations were successfully used in previous studies \citep{Mahadevan_2012,Omand_2015}.
+Similar PSOM configurations were successfully used in previous studies \cite{Mahadevan_2012,Omand_2015}.
 \add{The model does not simulate surface waves or boundary layer turbulence, but rather, examines the fate of particulate organic matter beneath the turbulent surface boundary layer.}
@@
 \textit{Papa\_winter} aims at capturing wintertime ocean conditions in the region.
-A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $Ro=\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \citep{Mensa_2013,Callies_2015,Thompson_2016}.
+A different dynamical regime is expected to dominate during wintertime when mixed layers are deeper and lateral density gradients enhanced, with sharper density fronts, filament-like features and localized Rossby number $Ro=\mathcal{O}$(1) over spatial scales $\mathcal{O}$(1 km) \cite{Mensa_2013,Callies_2015,Thompson_2016}.
 The individual characteristics of each of \textit{Papa\_summer} and \textit{Papa\_winter} are detailed below.
@@
 
-	To ensure that PSOM simulations yielded realistic conditions for both \textit{Papa\_summer} and \textit{Papa\_winter}, distributions of horizontal ($M^2$) and vertical ($N^2$) buoyancy gradients are compared with glider observations collected over the period 2008-2009 \citep{Pelland_2016}.
+	To ensure that PSOM simulations yielded realistic conditions for both \textit{Papa\_summer} and \textit{Papa\_winter}, distributions of horizontal ($M^2$) and vertical ($N^2$) buoyancy gradients are compared with glider observations collected over the period 2008-2009 \cite{Pelland_2016}.
 	During this period, underwater gliders sampled in a ``bow-tie" pattern centered on Station Papa.
@@
 	\subsubsection{Particle Advective Scheme}
-	To quantify the impact of submesoscale dynamics on the export of Particulate Organic Matter (POC), Lagrangian particle trajectories are computed using the same scheme as in ``TRACMASS'' \citep{Doos_2013} with the flow fields from the two experiments described above.
+	To quantify the impact of submesoscale dynamics on the export of Particulate Organic Matter (POC), Lagrangian particle trajectories are computed using the same scheme as in ``TRACMASS'' \cite{Doos_2013} with the flow fields from the two experiments described above.
 The three-dimensional, non-divergent velocity components from the faces of each ``C" grid cell are linearly interpolated onto the particle's position within the grid cell.
@@
 	\end{equation}
-	where $\beta = (u_{i}-u_{i-1})/\Delta x$ and $\delta = -u_{i-1} - \beta x_{i-1}$ \citep{Doos_2013}. This differential equation can be solved analytically for $\beta \neq 0$ as
+	where $\beta = (u_{i}-u_{i-1})/\Delta x$ and $\delta = -u_{i-1} - \beta x_{i-1}$ \cite{Doos_2013}. This differential equation can be solved analytically for $\beta \neq 0$ as
 	\begin{equation}
@@
 This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined by the 1\% light level.
-\add{Particle seeding is located at the base of the euphotic layer where biological processes not captured by the particles (e.g., grazing, repackaging, aggregation, etc.) are not as active }\citep{Duclow_2001}.
+\add{Particle seeding is located at the base of the euphotic layer where biological processes not captured by the particles (e.g., grazing, repackaging, aggregation, etc.) are not as active }\cite{Duclow_2001}.
 	The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically \change{Available}{Active} Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}.
-The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.
+The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \cite{Sherry_1999,Harrison_2004}.
 
@@
 Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles.
-Particles located deeper than the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.
+Particles located deeper than the maximum winter mixed layer \cite<i.e., 100 m;>[]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.
 
@@
 	\add{To quantify vertical export fluxes, both the distribution of the number of particles and the associated biomass can be modeled based on two main variables: the particles' radii and the rate at which the number of particles changes with respect to the size.
-The particle number is modeled using a power-law function as a function of size that is driven by the paramater $\xi$.} This slope $\xi$ of the size spectrum of particles \citep[also know as the Junge slope;][]{White_2015} is the slope of the log-log curve of particle number $N$ vs.
+The particle number is modeled using a power-law function as a function of size that is driven by the paramater $\xi$.} This slope $\xi$ of the size spectrum of particles \cit<ealso know as the Junge slope;>[]{White_2015} is the slope of the log-log curve of particle number $N$ vs.
 particle radius $r$, where
@@
 	Here, $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily.
-\add{Typical values for $\xi$ derived from both in-situ observations and satellite data have been reported to range from 3 to 6} \citep[][Z.
-Xiaodong, personal communication]{Kostadinov_2009, White_2015}.
+\add{Typical values for $\xi$ derived from both in-situ observations and satellite data have been reported to range from 3 to 6} \cite{Kostadinov_2009, White_2015}.
 For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically.
-Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \citep{Bach_2012}.
+Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \cite{Bach_2012}.
 
@@
 		\centering
-		\includegraphics[width = .49\linewidth]{Fig4b.png}
-		\includegraphics[width = .49\linewidth]{Fig4a.png}
+		\includegraphics[width = \linewidth]{Fig4.png}
 		\caption{Relative number of particles (left) and biomass (right) as a function of sinking velocity $w_s$.
@@
 In the absence of a consensus on a general functional form of particle remineralization, we rely on an idealized relationship which assumes that the biomass content of a particle decreases in time proportionally to the particle volume.
-Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \citep{Iversen_2010, Iversen_2013}
+Remineralization is thus modeled as an exponential decrease of biomass with time at a rate $k$ \cite{Iversen_2010, Iversen_2013}
 	\begin{equation}
@@
 	\end{equation}
-	where $B^0$ denotes the biomass content at $t = 0$ days, and the remineralization rate is taken to be $k = 0.13$ day$^{-1}$ in this study \citep{Iversen_2010}.
-This remineralization rate is independent of particle sinking velocity, and seems to lie within the range of other estimates \citep{Ploug_2008, Iversen_2010, Iversen_2013}.
+	where $B^0$ denotes the biomass content at $t = 0$ days, and the remineralization rate is taken to be $k = 0.13$ day$^{-1}$ in this study \cite{Iversen_2010}.
+This remineralization rate is independent of particle sinking velocity, and seems to lie within the range of other estimates \cite{Ploug_2008, Iversen_2010, Iversen_2013}.
 The change in biomass with time is in turn expected to affect the sinking velocity of the particle.
@@
 	Lateral buoyancy gradients in the summer are relatively weak $\mathcal{O}$(10$^{-8}$ s$^{-2}$) and result in low Rossby numbers $\mathcal{O}$(0.1), with positive relative vorticity on the denser (north) side of the front and negative relative vorticity on the lighter (south) side of the front.
-Corresponding vertical velocities are consistently weaker than 1 m/day ($<$10$^{-5}$ m/s) and are characterized by regions of weak upwelling and downwelling on 10 km scales, associated with the meandering of the front \citep{Bower_1989}.
+Corresponding vertical velocities are consistently weaker than 1 m/day ($<$10$^{-5}$ m/s) and are characterized by regions of weak upwelling and downwelling on 10 km scales, associated with the meandering of the front \cite{Bower_1989}.
 Alternating bands of upwelling and downwelling at $\mathcal{O}$(1 km) spatial scale are superimposed, and likely caused by propagating internal waves.
 Coherent vertical velocities structures extend to depths much greater than the mixed layer depth ($\sim$25 m; Figure \ref{fig: dynamics}).
-The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \citep{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ s$^{-1}$ (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ s$^{-1}$, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s, or $\sim 10^{-1}$ m/day.
+The amplitude of the vertical velocity field coincides with the expected order of magnitude given by the scaling $w \propto RofU/N$ \cite{Mahadevan_2016}: using $Ro\sim0.1$ (Figure \ref{fig: dynamics}), $N\sim10^{-2}$ s$^{-1}$ (Figure \ref{fig: Papa_summer}), $f\sim10^{-5}$ s$^{-1}$, and $U\sim0.01$ m/s, we obtain $w\sim 10^{-6}$ m/s, or $\sim 10^{-1}$ m/day.
 
-	\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \citep{Pelland_2016}.
-At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m \citep[Figure \ref{fig: Papa_winter}][]{Pelland_2016}.
+	\textit{Papa\_winter} is, on the other hand, initialized in the winter (doy 0) to capture a time period where the mixed layer depth is deeper ($\sim$ 100 m) and density gradients more pronounced \cite{Pelland_2016}.
+At this time of year, the water column in this region is characterized by the presence of a deep halocline between 100 and 150 m \cite<Figure \ref{fig: Papa_winter}>[]{Pelland_2016}.
 After spin-up, the vertical stratification remains consistent throughout the model run, and compares well with the vertical profile obtained from glider observations for the month of March ($r = 0.95$; see Figure \ref{fig: Papa_winter}).
@@
 The PDF of relative vorticity reveals a positively-skewed distribution ($s = 0.68$).
-This is in agreement with the fact that the relative vorticity is more likely to be cyclonic than anticyclonic, based on conservation of potential vorticity \citep{Hoskins_1972}.
+This is in agreement with the fact that the relative vorticity is more likely to be cyclonic than anticyclonic, based on conservation of potential vorticity \cite{Hoskins_1972}.
 Regions with  high Rossby number are localized and located in the mixed layer exclusively.
@@
 Contrary to the PDF of relative vorticity, the distribution of vertical velocities demonstrate a negative skewness ($s =$ -0.25).
-This is in agreement with the theory: In fact, positive relative vorticity is associated with the dense side of a density front, where vertical velocities are negative \citep{Mahadevan_2016}.
+This is in agreement with the theory: In fact, positive relative vorticity is associated with the dense side of a density front, where vertical velocities are negative \cite{Mahadevan_2016}.
 Once again, the amplitude of these vertical velocity hot spots is coherent with the scaling $w \propto RofU/N$: using $Ro\sim1$, $N\sim10^{-2}$ 1/s, $f\sim10^{-5}$ 1/s, and $U\sim0.1$ m/s, we obtain $w\sim 10^{-4}$ m/s, or $\sim 10^{1}$ m/day.
@@
 
-	Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \citep{Dasaro_2011, Thomas_2013}, or the edge of mesoscale features \citep{vanHaren_2006,Waite_2016}.
-The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \citep{Thompson_2016, Buckingham_2016}.
-Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \citep{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2013b,Rudnick_2001, Buckingham_2016}.
+	Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \cite{Dasaro_2011, Thomas_2013}, or the edge of mesoscale features \cite{vanHaren_2006,Waite_2016}.
+The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \cite{Thompson_2016, Buckingham_2016}.
+Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \cite{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2013b,Rudnick_2001, Buckingham_2016}.
 
@@
 The vertical currents in \textit{Papa\_winter}, however, tend to be much patchier than the weaker vertical currents observed in \textit{Papa\_summer}.
-Because both particle production and downward vertical velocities present a high degree of patchiness, it requires a certain level of covariance between the two fields for the export to effectively be enhanced \citep{Mahadevan_2012}.
+Because both particle production and downward vertical velocities present a high degree of patchiness, it requires a certain level of covariance between the two fields for the export to effectively be enhanced \cite{Mahadevan_2012}.
 A more realistic seeding strategy for Lagrangian particles, such as one guided by biological tracers, would likely provide important information towards a better understanding of the effects of patchiness on POC export at submeso-scales
@@
 The wintertime intensification in submesoscale activity has the potential to indeed enhance export (see discussion in Section \ref{sec: discussion_particle}).
-However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \citep{Plant_2016}.
+However, the seasonal cycle in submesoscale activity is out of phase with the one in net community productivity, which peaks in the spring and summertime when the mixed layer is shallower \cite{Plant_2016}.
 Two mechanisms are therefore present to potentially sustain a year-long POC export flux: In the winter, less particulate material is present in the mixed layer, but active submesoscale dynamics tend to enhance the POC export flux by advecting the more numerous slower-sinking particles into the ocean interior.
@@
 In the winter, submesoscale dynamics are intensified, and sharp fronts and filaments develop in the mixed layer.
-This seasonal change in dynamics is consistent with recent observations \citep{Thompson_2016, Buckingham_2016}, and models \citep{Brannigan_2015, Callies_2015, Rocha_2016} characterizing the seasonal cycle of submesoscale dynamics.
+This seasonal change in dynamics is consistent with recent observations \cite{Thompson_2016, Buckingham_2016}, and models \cite{Brannigan_2015, Callies_2015, Rocha_2016} characterizing the seasonal cycle of submesoscale dynamics.
 The winter intensification in submesoscale dynamics was proven to have an important impact on the downward flux of all sinking-velocity classes modeled in this experiment.
@@
 	This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}).
-	This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \add{: In-situ observations yield average spectral slopes varying between 3.5 and 4.5 }\citep[see Table 2 in ]{Kostadinov_2009}\add{, while spectral analysis of satellite data suggest global spectral slopes varying between 3 and 6.
-More recent observational work located in the Northeast Pacific, including Station Papa, found a spectral slope also greater than 3}\citep[][; Z.
-Xiaodong, personal communication]{White_2015}.
-    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \citep{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities, and steeper during the wintertime, when communities are mostly composed of small particles} \citep{Parsons_1988, Dale_1999, Behrenfeld_2010}.
+	This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \add{: In-situ observations yield average spectral slopes varying between 3.5 and 4.5 }\cite<see Table 2 in >{Kostadinov_2009}\add{, while spectral analysis of satellite data suggest global spectral slopes varying between 3 and 6.
+More recent observational work located in the Northeast Pacific, including Station Papa, found a spectral slope also greater than 3}\cite{White_2015}.
+    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \cite{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities, and steeper during the wintertime, when communities are mostly composed of small particles} \cite{Parsons_1988, Dale_1999, Behrenfeld_2010}.
     The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content.
@@
 	\add{These results are robust to the range of sinking rates explored.
-If one considers a particle class with a sinking rate far exceeding the vertical advective velocity }\citep[e.g., 100 m/day; ][]{Turner_2015}\add{, then the associated biomass flux can be estimated by relying on the traditional 1-D paradigm, assuming $w_{tot}\approx w_s$.
+If one considers a particle class with a sinking rate far exceeding the vertical advective velocity }\cite<e.g., 100 m/day;>[]{Turner_2015}\add{, then the associated biomass flux can be estimated by relying on the traditional 1-D paradigm, assuming $w_{tot}\approx w_s$.
 Combining this approximation with Equation \ref{eq: biomassjungeslope} shows that the slope of the biomass flux spectrum is positive for $\xi<5$, in which case very fast-sinking particles would dominate  vertical biomass fluxes.
 However, for $\xi>5$, the slope of the biomass flux spectrum becomes negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime.
-While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates} \citep{Kostadinov_2009}.
+While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates} \cite{Kostadinov_2009}.
 
@@
 Essink for his assistance in developing the particle-tracking code.
-All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website \citep[\url{https://www.pmel.noaa.gov/ocs/Papa};][]{PMEL_data} and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945} \citep{Gaillard_2015}.
-Glider data is archived at the University of Washington's Library \citep[\url{http://hdl.handle.net/1773/41656};][]{Pelland_2018_data}.
-Code to reproduce analysis and figures are publicly available at \url{https://github.com/matdever/Size-differentiated_Export_GBC} \citep{Dever_dataset}.
+All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website \cite[\url{https://www.pmel.noaa.gov/ocs/Papa};][]{PMEL_data} and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945} \cite{Gaillard_2015}.
+Glider data is archived at the University of Washington's Library \cite[\url{http://hdl.handle.net/1773/41656};][]{Pelland_2018_data}.
+Code to reproduce analysis and figures are publicly available at \url{https://github.com/matdever/Size-differentiated_Export_GBC} \cite{Dever_dataset}.
 Due to the very large filesize, model outputs and particle trajectories are available on request.

### 2020-07-29 size_differentiated_export.tex
Updates from Overleaf

@@
 The month of April is chosen for initialization so the experiment would capture the onset of positive net heat fluxes, and the summer restratification that ensues in July-August (Figure \ref{fig: Papa_summer}).
-In this region, the summer stratification is associated with large primary productivity, particle production, and POC export \citep[e.g., fecal pellets, dead phytoplankter; ][]{Plant_2016}.
+In this region, the summer stratification is associated with large primary productivity, particle production, and POC export \cite<e.g., fecal pellets, dead phytoplankter; >[]{Plant_2016}.
 
@@
 	\add{To quantify vertical export fluxes, both the distribution of the number of particles and the associated biomass can be modeled based on two main variables: the particles' radii and the rate at which the number of particles changes with respect to the size.
-The particle number is modeled using a power-law function as a function of size that is driven by the paramater $\xi$.} This slope $\xi$ of the size spectrum of particles \cit<ealso know as the Junge slope;>[]{White_2015} is the slope of the log-log curve of particle number $N$ vs.
+The particle number is modeled using a power-law function as a function of size that is driven by the paramater $\xi$.} This slope $\xi$ of the size spectrum of particles \cite<also know as the Junge slope;>[]{White_2015} is the slope of the log-log curve of particle number $N$ vs.
 particle radius $r$, where
@@
 The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \cite{Thompson_2016, Buckingham_2016}.
-Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \cite{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \citep[see Figure \ref{fig: dynamics};][]{Thomas_2013b,Rudnick_2001, Buckingham_2016}.
+Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \cite{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \cite<see Figure \ref{fig: dynamics};>[]{Thomas_2013b,Rudnick_2001, Buckingham_2016}.
 
@@
 Essink for his assistance in developing the particle-tracking code.
-All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website \cite[\url{https://www.pmel.noaa.gov/ocs/Papa};][]{PMEL_data} and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945} \cite{Gaillard_2015}.
-Glider data is archived at the University of Washington's Library \cite[\url{http://hdl.handle.net/1773/41656};][]{Pelland_2018_data}.
+All data used in this manuscript are publicly available: Ocean Station Papa data is available on PMEL's website \cite<\url{https://www.pmel.noaa.gov/ocs/Papa};>[]{PMEL_data} and gridded Argo products can be downloaded at \url{http://www.seanoe.org/data/00348/45945} \cite{Gaillard_2015}.
+Glider data is archived at the University of Washington's Library \cite<\url{http://hdl.handle.net/1773/41656};>[]{Pelland_2018_data}.
 Code to reproduce analysis and figures are publicly available at \url{https://github.com/matdever/Size-differentiated_Export_GBC} \cite{Dever_dataset}.

### 2020-12-04 size_differentiated_export.tex
cleanup
only keeps what is need for final version

@@
 \usepackage{lineno}
-\usepackage[finalnew]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage[]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
 \usepackage{soul}
@@
 	%% ------------------------------------------------------------------------ %%
-	\title{Size-differentiated Export \add{Flux} in Different Dynamical Regimes in the Ocean}
+	\title{Size-differentiated Export Flux in Different Dynamical Regimes in the Ocean}
 
@@
 Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux.
-However, this need not be the case \change{in a dynamic oceanic flow field,}{for particles whose sinking speeds are comparable to the vertical velocities of a dynamic flow field} \change{where the ocean velocity}{that} can influence the descent rate of particles.
-Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow \change{}{in the Northeast Pacific} to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
-The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more \change{important}{active in the region}.
-The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export flux\change{.
-A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{by a factor ranging from 3 to 10, especially where the relative abundance of small particles is large, (i.e., steep particle size-spectrum slope)}.
-\change{Implementing a r}{R}emineralization \remove{scheme} generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven.
-\change{Under specific conditions}{In an advectively-driven export regime}, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export.
+However, this need not be the case for particles whose sinking speeds are comparable to the vertical velocities of a dynamic flow field that can influence the descent rate of particles.
+Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow in the Northeast Pacific to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope.
+The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more active in the region.
+The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export flux by a factor ranging from 3 to 10, especially where the relative abundance of small particles is large, (i.e., steep particle size-spectrum slope).
+Remineralization generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven.
+In an advectively-driven export regime, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export.
 This study demonstrates that slow-sinking particles can be a significant contribution, and at times, even dominate the export flux.
@@
 The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \cite{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.
-\add{Despite progress on sampling and viewing particles in the ocean, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density} \cite{McDonnell_2010,Mcdonnell_2012}.
+Despite progress on sampling and viewing particles in the ocean, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density \cite{McDonnell_2010,Mcdonnell_2012}.
 
@@
 	Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior.
-For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \cite{vanHaren_2006, Waite_2016} \add{and in mesoscale features in the California current }\cite{Stukel_2017}.
+For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \cite{vanHaren_2006, Waite_2016} and in mesoscale features in the California current \cite{Stukel_2017}.
 \citeA{Omand_2015} found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic.
@@
 On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front.
-The distribution of relative vorticity \change{across a front is asymmetric and skewed toward cyclonic vorticity}{associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity} \cite{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \cite{Mahadevan_2006}.
-Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through \add{localized} downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.\add{	The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
-If the fraction of  biomass associated with such slow sinking velocities is significant, submesoscale dynamics can potentially impact the export of POC.}
+The distribution of relative vorticity associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity \cite{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \cite{Mahadevan_2006}.
+Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through localized downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.
+The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
+If the fraction of  biomass associated with such slow sinking velocities is significant, submesoscale dynamics can potentially impact the export of POC.
 
@@
 The dynamical model is coupled with a particle-tracking module to model the advection of particles by fluid flow, while neglecting the effects of particle inertia and drag on their advection.
-In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$) \add{that is based on the range of vertical currents modeled in this region.
+In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$) that is based on the range of vertical currents modeled in this region.
 We aim to address the transitional regime of the particle sinking velocity spectrum, where both advection and sinking speeds have similar order of magnitudes.
-A similar study with sinking tracers  showed the influence of the flow} \cite{Taylor_2020}\add{, but the use of particles enables a characterization of export associated with each sinking class of particles.}
+A similar study with sinking tracers  showed the influence of the flow \cite{Taylor_2020}, but the use of particles enables a characterization of export associated with each sinking class of particles.
 
@@
 		\centering
-		\includegraphics[width = .6\linewidth]{Fig1_model_domain}
+		\includegraphics[width = .6\linewidth]{Fig1}
 		\caption{PSOM model setup.
@@
 Similar PSOM configurations were successfully used in previous studies \cite{Mahadevan_2012,Omand_2015}.
-\add{The model does not simulate surface waves or boundary layer turbulence, but rather, examines the fate of particulate organic matter beneath the turbulent surface boundary layer.}
+The model does not simulate surface waves or boundary layer turbulence, but rather, examines the fate of particulate organic matter beneath the turbulent surface boundary layer.
 
@@
 	\begin{figure}[t]
-		\includegraphics[width = 1\linewidth]{Fig2_Papa500_summer}
+		\includegraphics[width = 1\linewidth]{Fig2}
 		\caption{PSOM configuration for \textit{Papa\_summer}.
@@
 	\begin{figure}[ht]
-		\includegraphics[width = 1\linewidth]{Fig3_Papa500_winter}
+		\includegraphics[width = 1\linewidth]{Fig3}
 		\caption{PSOM configuration for \textit{Papa\_winter}.
@@
 This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined by the 1\% light level.
-\add{Particle seeding is located at the base of the euphotic layer where biological processes not captured by the particles (e.g., grazing, repackaging, aggregation, etc.) are not as active }\cite{Duclow_2001}.
-	The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically \change{Available}{Active} Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}.
+Particle seeding is located at the base of the euphotic layer where biological processes not captured by the particles (e.g., grazing, repackaging, aggregation, etc.) are not as active \cite{Duclow_2001}.
+	The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Active Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}.
 The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \cite{Sherry_1999,Harrison_2004}.
@@
 	In each particle-tracking experiment, three different classes of particles are released.
-Each particle class is characterized by a different sinking velocity: 0.025, \remove{0.05, }1, and 5 m/day.
-\add{In this study, these particle classes are referred to as slow- intermediate-, and fast-sinking particles.
-This characterization is not based on the absolute value of the sinking rate, but rather on the ratio with vertical currents in the study region.} The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 400 days to sink 10 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
-\add{While 5 m/day remains a relatively slow sinking rate, this} ``fastest-sinking" velocity is chosen as an end-member velocity class of particle\change{ that will be exported in its entirety over the course of our experiment.
-}{, based on the PDF of vertical velocities in the model.
+Each particle class is characterized by a different sinking velocity: 0.025, 1, and 5 m/day.
+In this study, these particle classes are referred to as slow- intermediate-, and fast-sinking particles.
+This characterization is not based on the absolute value of the sinking rate, but rather on the ratio with vertical currents in the study region.
+The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 400 days to sink 10 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales.
+While 5 m/day remains a relatively slow sinking rate, this ``fastest-sinking" velocity is chosen as an end-member velocity class of particle, based on the PDF of vertical velocities in the model.
 At any given time, at least 85\% of the model vertical velocity is weaker than 5 m/day.
-The results presented for the 5 m/day sinking class can therefore be theoretically extrapolated to any class with a higher sinking velocity.}
+The results presented for the 5 m/day sinking class can therefore be theoretically extrapolated to any class with a higher sinking velocity.
 
@@
 Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity).
-Particles are tracked for \change{three}{four} weeks (28 days).
+Particles are tracked for four weeks (28 days).
 Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles.
@@
 
-	\add{To quantify vertical export fluxes, both the distribution of the number of particles and the associated biomass can be modeled based on two main variables: the particles' radii and the rate at which the number of particles changes with respect to the size.
-The particle number is modeled using a power-law function as a function of size that is driven by the paramater $\xi$.} This slope $\xi$ of the size spectrum of particles \cite<also know as the Junge slope;>[]{White_2015} is the slope of the log-log curve of particle number $N$ vs.
+	To quantify vertical export fluxes, both the distribution of the number of particles and the associated biomass can be modeled based on two main variables: the particles' radii and the rate at which the number of particles changes with respect to the size.
+The particle number is modeled using a power-law function as a function of size that is driven by the paramater $\xi$.
+This slope $\xi$ of the size spectrum of particles \cite<also know as the Junge slope;>[]{White_2015} is the slope of the log-log curve of particle number $N$ vs.
 particle radius $r$, where
@@
 	Here, $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily.
-\add{Typical values for $\xi$ derived from both in-situ observations and satellite data have been reported to range from 3 to 6} \cite{Kostadinov_2009, White_2015}.
+Typical values for $\xi$ derived from both in-situ observations and satellite data have been reported to range from 3 to 6 \cite{Kostadinov_2009, White_2015}.
 For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically.
@@
 
-	Assuming a Stokes-like relationship, we can construct based on (\ref{eq: powerlaw_radius}) a particle sinking velocity spectrum $N(w_s)$, as \add{a function of the Junge slope $\xi$:}
+	Assuming a Stokes-like relationship, we can construct based on (\ref{eq: powerlaw_radius}) a particle sinking velocity spectrum $N(w_s)$, as a function of the Junge slope $\xi$:
 	\begin{equation}
@@
 		\centering
-		\includegraphics[width = 1\linewidth]{Fig5_dynamic_signature_w_valid}
+		\includegraphics[width = 1\linewidth]{Fig5}
 		\caption{Snapshots of $M^2$ (top), $\zeta /f$ (middle), and $w$ (bottom) half-way through the particle tracking experiment for \textit{Papa\_summer} (left) and \textit{Papa\_winter} (right), with the Mixed Layer Depth indicated by the solid black line.
@@
 Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\times t$.
-[right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class \add{(red = 0.025 m/day; green = 1 m/day; blue = 5 m/day)}.
+[right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class (red = 0.025 m/day; green = 1 m/day; blue = 5 m/day).
 The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions.
@@
 As the Junge slope increases, the spectrum of biomass steepens, and the relative contribution of slower-sinking particles to the downward biomass flux significantly increases (Figure \ref{fig: biomass_export}c).
-In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.2\% to \change20\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$.
+In fact, the contribution of slower-sinking particles to the summer downward flux increases by a factor 100 (from 0.2\% to 20\%) when the Junge slope varies from $\xi =2$ to $\xi = 4$.
 While significant, the impact of a change in the Junge slope in summer conditions does not challenge the dominant role played by faster-sinking particles.
@@
 		\centering
-		\includegraphics[width = 1\linewidth]{Fig7_revised.png}
-		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity \add{(sinking + advective)} along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
-\add{PDFs are computed from the whole 24-day particle tracking experiments.} Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity \add{(red = 0.025 m/day; green = 1 m/day; blue = 5 m/day)}.
+		\includegraphics[width = 1\linewidth]{Fig7.png}
+		\caption{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity (sinking + advective) along particle trajectories in the summer case [left] and winter case [right], with a Junge slope of 2 [top] and 4 [bottom].
+PDFs are computed from the whole 24-day particle tracking experiments.
+Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity (red = 0.025 m/day; green = 1 m/day; blue = 5 m/day).
 Both winter dynamics and steeper Junge slopes tend to increase the relative contribution of slower-sinking particles.}
@@
 
-	Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for \add{$\xi = 2$ and} $\xi = 4$ \change{with and without }{including} the remineralization scheme.
-As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization \add{(see Figure} \ref{fig: biomass_export}).
+	Figure \ref{fig: biomass_export_remin} compares the relative biomass and downward biomass fluxes associated with each of the modeled particle classes for $\xi = 2$ and $\xi = 4$ including the remineralization scheme.
+As previously detailed, downward fluxes of biomass are dominated by faster-sinking particles during summertime and in the absence of remineralization (see Figure \ref{fig: biomass_export}).
 This is due to the fact that the flux of biomass $\left<w_{tot}B\right> = \left<w_sB\right> + \left<wB\right>$ is driven by $\left<w_sB\right>$, despite a smaller relative biomass content per particle.
@@
 Implementing remineralization processes, however, directly affects the particle settling velocity which slows down as particles remineralize.
-This effect can \add{particularly} be seen in Figure \ref{fig: biomass_export_remin}\add{a and} c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation (\ref{eq: sinking_velocity_remin}).
-\remove{As a result, the gravitationally-driven term $\left<w_sB\right>$ decreases with time, and the downward flux of biomass becomes generally advectively-driven by day 25 (Figure \ref{fig: biomass_export_remin}).}
+This effect can particularly be seen in Figure \ref{fig: biomass_export_remin}a and c, where PDFs of relative biomass per particle class are shifted towards weaker vertical velocities than in the absence of remineralization, as predicted by Equation (\ref{eq: sinking_velocity_remin}).
 
@@
 		\centering
-		\includegraphics[width = 1\linewidth]{Fig8_revised.png}
-		\caption{\change{Probability Distribution Function (PDF) of relative biomass versus total vertical velocity along particle trajectories in the summer case [left] and winter case [right], ignoring [top] and including [bottom] particle remineralization, for $\xi$ = 4 and 25 days after particle release.
-Inserts show the integrated relative downward biomass flux associated with each sinking-velocity class, categorized according to their initial sinking velocity (red = 0.025 m/day; green = 1 m/day; blue = 5 m/day).
-Remineralization processes have the greatest impact on fast-sinking particles, especially in summer dynamics.}{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}}
+		\includegraphics[width = 1\linewidth]{Fig8.png}
+		\caption{Same as Figure \ref{fig: biomass_export}, but including particle remineralization (see Equation \ref{eq: sinking_velocity_remin}).}
 		\label{fig: biomass_export_remin}
@@
 	In a advectively-driven system where $\left<w_sB\right> \sim \left<wB\right>$, the relative amount of biomass content in a particle class becomes important and dictates the respective contribution of each particle class to the total downward biomass fluxes.
-This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}\remove{c}): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (\change{60}{53}\%; see Figure \ref{fig: biomass_export}c).
-When remineralization processes are considered, slower-sinking particles \change{become the dominant contributor}{contribute more} to biomass fluxes (see inset in Figure \ref{fig: biomass_export_remin}c).
+This shift from a gravitationally-driven to an advectively-driven system is observed when implementing particle remineralization in the summer (Figure \ref{fig: biomass_export_remin}): in the absence of remineralization, faster-sinking particles dominate the downward biomass fluxes (53\%; see Figure \ref{fig: biomass_export}c).
+When remineralization processes are considered, slower-sinking particles contribute more to biomass fluxes (see inset in Figure \ref{fig: biomass_export_remin}c).
 As shown in Figure \ref{fig: biomass_export}, downward biomass fluxes in the wintertime are generally advectively-driven, due to the larger vertical velocities associated with wintertime ocean dynamics.
-Biomass fluxes are dominated by the slower-sinking particles \add{when $\xi =4$}, representing 79\% of the downward biomass flux (Figure \ref{fig: biomass_export}d).
+Biomass fluxes are dominated by the slower-sinking particles when $\xi =4$, representing 79\% of the downward biomass flux (Figure \ref{fig: biomass_export}d).
 Even after implementing the remineralization scheme, slower-sinking particles remain the largest contributor to downward biomass fluxes (82\%; see Figure \ref{fig: biomass_export_remin}d).
@@
 	This is only when both of these conditions are combined, however, that slower-sinking particles dominate the downward flux of biomass (Figure \ref{fig: biomass_export}).
-	This is a significant result, as Junge slopes greater than 3 have been observed in the ocean \add{: In-situ observations yield average spectral slopes varying between 3.5 and 4.5 }\cite<see Table 2 in >{Kostadinov_2009}\add{, while spectral analysis of satellite data suggest global spectral slopes varying between 3 and 6.
-More recent observational work located in the Northeast Pacific, including Station Papa, found a spectral slope also greater than 3}\cite{White_2015}.
-    \add{Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically} \cite{Kostadinov_2009, White_2015}\add{, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities, and steeper during the wintertime, when communities are mostly composed of small particles} \cite{Parsons_1988, Dale_1999, Behrenfeld_2010}.
+	This is a significant result, as Junge slopes greater than 3 have been observed in the ocean: In-situ observations yield average spectral slopes varying between 3.5 and 4.5 \cite<see Table 2 in >{Kostadinov_2009}, while spectral analysis of satellite data suggest global spectral slopes varying between 3 and 6.
+More recent observational work located in the Northeast Pacific, including Station Papa, found a spectral slope also greater than 3 \cite{White_2015, Cram_2018}.
+    Junge slopes are expected to vary in space, depending on the community composition, both lateraly and vertically \cite{Kostadinov_2009, White_2015}, as well as in time; spectrum slopes tend to be flatter during a spring bloom event, where larger particles (e.g., diatoms) are produced in large quantities, and steeper during the wintertime, when communities are mostly composed of small particles \cite{Parsons_1988, Dale_1999, Behrenfeld_2010}.
     The threshold value of $\xi =3$ for a change in the biomass spectral slope (see Figure \ref{fig: sinking_velocity_spectrum}b) is of course a consequence of first-order approximations used in this study describing the relationships between particle size, sinking velocity, and biomass content.
@@
 	Introducing remineralization processes significantly decreases the biomass flux.
-Counter-intuitively, however, the implementation of a remineralization scheme further strengthens the contribution of slower-sinking particles to the biomass flux (Figure \ref{fig: biomass_export_remin}).
+Counter-intuitively, however, the implementation of a remineralization scheme further strengthens the contribution of slower-sinking particles to the biomass flux\add{, once particles have left the euphotic layer} (Figure \ref{fig: biomass_export_remin}).
 This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as these particles decelerate as they remineralize.
@@
 Their export timescale is barely affected by remineralization processes as it only depends on local ocean dynamics.
+\add{Changing the remineralization timescale would therefore only affect the results in a gravitationally-driven flux: increasing the timescales (i.e.
+slower remineralization) would give more weight to the smaller classes, while decreasing the timescales (i.e.
+faster remineralization) would favor faster sinking particles to drive the downward flux.
+In an advectively-driven flux, however, all particles classes are equally affected by remineralization (i.e.
+lose 12\% of their biomass per day).
+While this affects the total amount of biomass flux, it does not impact the respective contributions of the different particle classes to the downward biomass flux.}
 
-	\add{These results are robust to the range of sinking rates explored.
-If one considers a particle class with a sinking rate far exceeding the vertical advective velocity }\cite<e.g., 100 m/day;>[]{Turner_2015}\add{, then the associated biomass flux can be estimated by relying on the traditional 1-D paradigm, assuming $w_{tot}\approx w_s$.
+These results are robust to the range of sinking rates explored.
+If one considers a particle class with a sinking rate far exceeding the vertical advective velocity \cite<e.g., 100 m/day;>[]{Turner_2015}, then the associated biomass flux can be estimated by relying on the traditional 1-D paradigm, assuming $w_{tot}\approx w_s$.
 Combining this approximation with Equation \ref{eq: biomassjungeslope} shows that the slope of the biomass flux spectrum is positive for $\xi<5$, in which case very fast-sinking particles would dominate  vertical biomass fluxes.
 However, for $\xi>5$, the slope of the biomass flux spectrum becomes negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime.
-While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates} \cite{Kostadinov_2009}.
+\change{While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates}{While values of $\xi > 5$ have been estimated by} \citeA{Kostadinov_2009} \add{using satellite data, in-situ estimated values of $\xi$ tend to range between 2 and 4.5}\cite{White_2015, Cram_2018}.
 
@@
 		\end{enumerate}
-		\item Remineralization processes logically reduce the amount of biomass flux.
+		\item Remineralization processes \add{below the euphotic depth} logically reduce the amount of biomass flux.
 However, it unexpectedly enhances the role of slower-sinking particles, which are are advectively transported.
-The impact of remineralization is greater on faster-sinking particles since it affects both the biomass content and their sinking velocity.
+The impact of remineralization \add{below the euphotic depth} is greater on faster-sinking particles since it affects both the biomass content and their sinking velocity.
 	\end{enumerate}

### 2020-12-04 figures/code/Fig1.m

@@ -1,0 +1,102 @@
+clear
+
+%% This code plot the model domain with the wind profile and the het flux 
+% meridoinal anomaly in 3 panels
+%%
+% ii = 0;
+% x = ncread(['/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/full_',num2str(ii,'%05d'),'.cdf'],'xc')*1000;
+% y = ncread(['/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/full_',num2str(ii,'%05d'),'.cdf'],'yc')*1000;
+% Z = ncread(['/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/full_',num2str(ii,'%05d'),'.cdf'],'zc');
+% z = squeeze(Z(1,1,:));
+% rho = ncread(['/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/full_',num2str(ii,'%05d'),'.cdf'],'rho');
+% rho(1,:,:) = NaN; rho(end,:,:) = NaN;
+% clear ii
+% 
+% % Import the scale factor for restauration time scale
+% filename = '/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/scalefactor.out';
+% delimiter = ','; startRow = 2; formatSpec = '%*s%s%[^\n\r]';
+% fileID = fopen(filename,'r');
+% dataArray = textscan(fileID, formatSpec, 'Delimiter', delimiter, 'TextType', 'string', 'HeaderLines' ,startRow-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
+% fclose(fileID);
+% raw = repmat({''},length(dataArray{1}),length(dataArray)-1);
+% for col=1:length(dataArray)-1
+%     raw(1:length(dataArray{col}),col) = mat2cell(dataArray{col}, ones(length(dataArray{col}), 1));
+% end
+% numericData = NaN(size(dataArray{1},1),size(dataArray,2));
+% rawData = dataArray{1};
+% for row=1:size(rawData, 1)
+%     % Create a regular expression to detect and remove non-numeric prefixes and
+%     % suffixes.
[…]

### 2020-12-04 figures/code/Fig1_model_domain.m

@@ -1,102 +1,0 @@
-clear
-
-%% This code plot the model domain with the wind profile and the het flux 
-% meridoinal anomaly in 3 panels
-%%
-% ii = 0;
-% x = ncread(['/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/full_',num2str(ii,'%05d'),'.cdf'],'xc')*1000;
-% y = ncread(['/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/full_',num2str(ii,'%05d'),'.cdf'],'yc')*1000;
-% Z = ncread(['/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/full_',num2str(ii,'%05d'),'.cdf'],'zc');
-% z = squeeze(Z(1,1,:));
-% rho = ncread(['/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/full_',num2str(ii,'%05d'),'.cdf'],'rho');
-% rho(1,:,:) = NaN; rho(end,:,:) = NaN;
-% clear ii
-% 
-% % Import the scale factor for restauration time scale
-% filename = '/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/scalefactor.out';
-% delimiter = ','; startRow = 2; formatSpec = '%*s%s%[^\n\r]';
-% fileID = fopen(filename,'r');
-% dataArray = textscan(fileID, formatSpec, 'Delimiter', delimiter, 'TextType', 'string', 'HeaderLines' ,startRow-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
-% fclose(fileID);
-% raw = repmat({''},length(dataArray{1}),length(dataArray)-1);
-% for col=1:length(dataArray)-1
-%     raw(1:length(dataArray{col}),col) = mat2cell(dataArray{col}, ones(length(dataArray{col}), 1));
-% end
-% numericData = NaN(size(dataArray{1},1),size(dataArray,2));
-% rawData = dataArray{1};
-% for row=1:size(rawData, 1)
-%     % Create a regular expression to detect and remove non-numeric prefixes and
-%     % suffixes.
[…]

### 2020-12-04 figures/code/Fig2.m

@@ -1,0 +1,200 @@
+clear
+
+% Create a blue-to-red colorbar for line plot
+cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(12,:);cmap(16,:)];
+
+%% this code creates the figures that synthetize the forcing and density
+% field for the Papa500 xperiment
+
+% Load glider data
+%load('/Users/mathieudever/Documents/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
+load('/Volumes/mdever/1-Projects/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
+glider.N2 = 9.81./nanmean(glider.density(:))*(glider.density(3:end,:)-glider.density(1:end-2,:))./(glider.depth(3:end,:)-glider.depth(1:end-2,:));
+glider.time = datevec(nanmean(glider.time));
+clearvars -except glider cmap
+
+%% STEP 1 - Compute the TKE vs time. cannot use the full resolution, as it is domain integrated
+thefolder = pwd;
+cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/
+% Surface view
+depth = 50; % depth to plot in m
+lat = 50;   % Latitude of mid-domain (for f)
+f = gsw_f(lat);
+g = 9.81;
+
+jstart = 201;
+jfinish = 402;
+
+%% Step 2 - load the forcing time series
+
+% Heat Fluxes
+fileID = fopen('/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_configuration/Papa_summer/ini_heatfluxes.in','r');
+dataArray = textscan(fileID, '%f%[^\n\r]');
+fclose(fileID);
+HF = dataArray{:, 1};
+clearvars fileID dataArray ans;
+
+% Windstress
+fileID = fopen('/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_configuration/Papa_summer/ini_windstress.in','r');
+dataArray = textscan(fileID, '%f%f%[^\n\r]','delimiter',',');
+fclose(fileID);
+WS = [dataArray{1:end-1}];
+clearvars fileID dataArray ans;
+
+% Applies the scaling imposed in the model
+HF(1:5*86400/216) = 0;
+for ii = 5*86400/216:10*86400/216
[…]

### 2020-12-04 figures/code/Fig2_Papa500_summer.m

@@ -1,197 +1,0 @@
-clear
-
-% Create a blue-to-red colorbar for line plot
-cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(12,:);cmap(16,:)];
-
-%% this code creates the figures that synthetize the forcing and density
-% field for the Papa500 xperiment
-
-% Load glider data
-load('/Users/mathieudever/Documents/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
-glider.N2 = 9.81./nanmean(glider.density(:))*(glider.density(3:end,:)-glider.density(1:end-2,:))./(glider.depth(3:end,:)-glider.depth(1:end-2,:));
-glider.time = datevec(nanmean(glider.time));
-clearvars -except glider cmap
-
-%% STEP 1 - Compute the TKE vs time. cannot use the full resolution, as it is domain integrated
-thefolder = pwd;
-cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/
-% Surface view
-depth = 50; % depth to plot in m
-lat = 50;   % Latitude of mid-domain (for f)
-f = gsw_f(lat);
-g = 9.81;
-
-jstart = 201;
-jfinish = 402;
-
-%% Step 2 - load the forcing time series
-
-% Heat Fluxes
-fileID = fopen('/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_configuration/Papa_summer/ini_heatfluxes.in','r');
-dataArray = textscan(fileID, '%f%[^\n\r]');
-fclose(fileID);
-HF = dataArray{:, 1};
-clearvars fileID dataArray ans;
-
-% Windstress
-fileID = fopen('/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_configuration/Papa_summer/ini_windstress.in','r');
-dataArray = textscan(fileID, '%f%f%[^\n\r]','delimiter',',');
-fclose(fileID);
-WS = [dataArray{1:end-1}];
-clearvars fileID dataArray ans;
-
-% Applies the scaling imposed in the model
-HF(1:5*86400/216) = 0;
-for ii = 5*86400/216:10*86400/216
-    HF(ii) = HF(ii)*(ii-(5*86400/216))/(5*86400/216);
-end
-WS(1:5*86400/216,:) = 0;
[…]

### 2020-12-04 figures/code/Fig3.m

@@ -1,0 +1,204 @@
+clear
+% Create a blue-to-red colorbar for line plot
+cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(12,:);cmap(16,:)];
+
+%% this code creates the figures that synthetize the forcing and density
+% field for the Papa500 xperiment
+
+% Load glider data
+%load('/Users/mathieudever/Documents/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
+load('/Volumes/mdever/1-Projects/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
+glider.N2 = 9.81./nanmean(glider.density(:))*(glider.density(3:end,:)-glider.density(1:end-2,:))./(glider.depth(3:end,:)-glider.depth(1:end-2,:));
+glider.time = datevec(nanmean(glider.time));
+clearvars -except glider cmap
+
+
+%% STEP 1 - Compute the TKE vs time. cannot use the full resolution, as it is domain integrated
+thefolder = pwd;
+
+cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_winter
+% Surface view
+depth = 50; % depth to plot in m
+lat = 50;   % Latitude of mid-domain (for f)
+f = gsw_f(lat);
+g = 9.81;
+
+jstart = 201;
+jfinish = 402;
+
+%% Step 2 - load the forcing time series
+
+% Heat Fluxes
+fileID = fopen('/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_configuration/Papa_winter/ini_heatfluxes_108s.in','r');
+dataArray = textscan(fileID, '%f%[^\n\r]');
+fclose(fileID);
+HF = dataArray{:, 1};
+clearvars fileID dataArray ans;
+
+% Windstress
+fileID = fopen('/Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_configuration/Papa_winter/ini_windstress_108s.in','r');
+dataArray = textscan(fileID, '%f%f%[^\n\r]','delimiter',',');
+fclose(fileID);
+WS = [dataArray{1:end-1}];
+clearvars fileID dataArray ans;
+
+% Applies the scaling imposed in the model
+HF(1:5*86400/216) = 0;
+for ii = 5*86400/216:10*86400/216
[…]

### 2020-12-04 figures/code/Fig3_Papa500_winter.m

@@ -1,201 +1,0 @@
-clear
-% Create a blue-to-red colorbar for line plot
-cmap = jet(16); cmap = [cmap(1,:);cmap(5,:);cmap(12,:);cmap(16,:)];
-
-%% this code creates the figures that synthetize the forcing and density
-% field for the Papa500 xperiment
-
-% Load glider data
-load('/Users/mathieudever/Documents/EXPORTS/Data/station_Papa_glider/glider_non_gridded.mat')
-glider.N2 = 9.81./nanmean(glider.density(:))*(glider.density(3:end,:)-glider.density(1:end-2,:))./(glider.depth(3:end,:)-glider.depth(1:end-2,:));
-glider.time = datevec(nanmean(glider.time));
-clearvars -except glider cmap
-
-
-%% STEP 1 - Compute the TKE vs time. cannot use the full resolution, as it is domain integrated
-thefolder = pwd;
-
-cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_winter
-% Surface view
-depth = 50; % depth to plot in m
-lat = 50;   % Latitude of mid-domain (for f)
-f = gsw_f(lat);
-g = 9.81;
-
-jstart = 201;
-jfinish = 402;
-
-%% Step 2 - load the forcing time series
-
-% Heat Fluxes
-fileID = fopen('/Users/mathieudever/Google Drive/Publications/size_differentiated_sinking/figures/code/Papa500_winter/ini_heatfluxes.in','r');
-dataArray = textscan(fileID, '%f%[^\n\r]');
-fclose(fileID);
-HF = dataArray{:, 1};
-clearvars fileID dataArray ans;
-
-% Windstress
-fileID = fopen('/Users/mathieudever/Google Drive/Publications/size_differentiated_sinking/figures/code/Papa500_winter/ini_windstress.in','r');
-dataArray = textscan(fileID, '%f%f%[^\n\r]','delimiter',',');
-fclose(fileID);
-WS = [dataArray{1:end-1}];
-clearvars fileID dataArray ans;
-
-% Applies the scaling imposed in the model
-HF(1:5*86400/216) = 0;
-for ii = 5*86400/216:10*86400/216
-    HF(ii) = HF(ii)*(ii-(5*86400/216))/(5*86400/216);
-end
[…]

### 2020-12-04 figures/code/Fig4_particle_PDF.m

@@ -1,138 +1,0 @@
-clear
-
-%% This code plots the distribution of Particle, given a spectral slope and the number of LARGEST particle
-
-counter = 1;
-for spectral_slope = [2 3 4]
-    
-    % compute for the sinking velocity actually modeled
-    ws = [0.025 0.5 1 5];
-    N0 = 1971717;
-    N = (ws/max(ws)).^-(spectral_slope/2)*N0;
-    B = (ws/max(ws)).^((3-spectral_slope)/2);
-    
-    % Create the theoretical curve
-    thexaxis = [min(ws):0.001:max(ws)];
-    theyaxis = (thexaxis/thexaxis(4976)).^-(spectral_slope/2);
-    theyaxisB = (thexaxis/thexaxis(4976)).^((3-spectral_slope)/2);
-    
-    %%
-    
-    figure(1)
-    % theoretical curve
-    if spectral_slope>3
-        color = 'r';
-    elseif spectral_slope == 3
-        color = 'k';
-    elseif spectral_slope <3
-        color = 'b';
-    end
-
-    % Plot N/N0
-    h(1) = plot(thexaxis,theyaxis,'--','color',color,'linewidth',2);
-    hold on
-    scatter(ws,N./N0,100,'s','markeredgecolor',color,'markerfacecolor',color)
-    
-    % Plot B/B0
-    h(2) = plot(thexaxis,theyaxisB,'-','color',color,'linewidth',2);
-    g(counter) = h(2);
-    scatter(ws,B,100,'s','markeredgecolor',color,'markerfacecolor',color)
-    
-    set(gca,'yscale','log','xscale','log','fontsize',16)
-    grid on; axis tight;    
-    
-    xlabel('Sinking velocity [m/day]')
-    %ylabel('Number of particles')
-    xlim([0.01 10])
-    counter = counter +1;
-end
-H = legend([h(1) h(2)],'N/N_0','B/B_0','location','east');
-set(H,'Position',[0.7554 0.56 0.1321 0.1250])
-
-
-% get the figure smaller to accomodate the 2nd x-axis later
-POS = get(gca,'position');
-set(gca,'position',[POS(1) POS(2) POS(3) POS(4)-0.05])
-
-% create 2 x-axis
-axes('position',get(gca,'position'),...
-    'xlim',get(gca,'xlim'),...
-    'xscale','log',...
[…]

### 2020-12-04 figures/code/Fig5.m

@@ -1,0 +1,271 @@
+clear
+close all
+
+%% Load gradients computed from glider data for comparison curve
+load('dataset/Fig5_data.mat')
+glider.M2time = datevec(glider.M2time);
+clearvars -except glider cmap
+
+
+lat = 50;   % Latitude of mid-domain (for f)
+f = gsw_f(lat);
+g = 9.81;
+
+istart = 200;
+ifinish = 400;
+
+%fullfigure
+
+%%
+thefolder = pwd;
+fullfigure
+for plt = 1:2
+    if plt == 1
+        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/highrez
+        timesteps = 30500;%[0 24000 30000 36000];
+    elseif plt == 2
+        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_winter
+        timesteps = 44000;%[0 32000 44000 56000];
+    end
+    counter = 0;
+    for tt = timesteps
+        counter = counter +1;
+        
+        rho = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'rho');
+        rho(1,:,:) = NaN; rho(end,:,:) = NaN;
+        u = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'u');
+        u(1,:,:) = NaN; u(end,:,:) = NaN;
+        v = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'v');
+        v(1,:,:) = NaN; v(end,:,:) = NaN;
+        w = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'w');
+        w(1,:,:) = NaN; w(end,:,:) = NaN;
+        % vor = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'vor');
+        % vor(1,:,:) = NaN; vor(end,:,:) = NaN;
+        
+        x = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'xc')*1000;
+        y = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'yc')*1000;
+        Z2 = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'zc');
+        z = squeeze(Z2(1,1,:));
+        [X,Y] = meshgrid(x,y);
+        [X2,Y2,Z2] = meshgrid(x,y,squeeze(Z2(1,1,:)));
[…]

### 2020-12-04 figures/code/Fig5_dynamic_signature_w_valid.m

@@ -1,271 +1,0 @@
-clear
-close all
-
-%% Load gradients computed from glider data for comparison curve
-load('dataset/Fig5_data.mat')
-glider.M2time = datevec(glider.M2time);
-clearvars -except glider cmap
-
-
-lat = 50;   % Latitude of mid-domain (for f)
-f = gsw_f(lat);
-g = 9.81;
-
-istart = 200;
-ifinish = 400;
-
-%fullfigure
-
-%%
-thefolder = pwd;
-fullfigure
-for plt = 1:2
-    if plt == 1
-        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/highrez
-        timesteps = 30500;%[0 24000 30000 36000];
-    elseif plt == 2
-        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_winter
-        timesteps = 44000;%[0 32000 44000 56000];
-    end
-    counter = 0;
-    for tt = timesteps
-        counter = counter +1;
-        
-        rho = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'rho');
-        rho(1,:,:) = NaN; rho(end,:,:) = NaN;
-        u = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'u');
-        u(1,:,:) = NaN; u(end,:,:) = NaN;
-        v = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'v');
-        v(1,:,:) = NaN; v(end,:,:) = NaN;
-        w = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'w');
-        w(1,:,:) = NaN; w(end,:,:) = NaN;
-        % vor = ncread(['full_',num2str(ii,'%05d'),'.cdf'],'vor');
-        % vor(1,:,:) = NaN; vor(end,:,:) = NaN;
-        
-        x = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'xc')*1000;
-        y = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'yc')*1000;
-        Z2 = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'zc');
-        z = squeeze(Z2(1,1,:));
-        [X,Y] = meshgrid(x,y);
-        [X2,Y2,Z2] = meshgrid(x,y,squeeze(Z2(1,1,:)));
[…]

### 2020-12-04 figures/code/Fig6.m

@@ -1,0 +1,164 @@
+clear
+
+%% Import (x,y,z) for each size class in winter and summer
+[x0025s,y0025s,z0025s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal0025mday_summer.csv');
+[x1s,y1s,z1s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal1mday_summer.csv');
+[x5s,y5s,z5s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal5mday_summer.csv');
+
+[x0025,y0025,z0025] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal0025mday_winter.csv');
+[x1,y1,z1] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal1mday_winter.csv');
+[x5,y5,z5] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal5mday_winter.csv');
+
+color0025 = [215,48,39]/256;
+color1 = [39,100,25]/256;
+color5 = [49,54,149]/256;
+
+%% Bin the data into 1x1 km and compute the median vertical displacement
+% with respect to the gravitational model
+thedoy = 25;
+countx = 1;
+rez = 1;
+for x = 0:rez:111
+    county = 1;
+    for y = 100:rez:200
+        
+        %% 0025 m/day
+        ind = find(x0025>=x & x0025<=x+rez & y0025>=y & y0025<=y+rez);
+        if isempty(ind)
+            medi0025(countx,county) = NaN;
+        else
+            medi0025(countx,county) = median(z0025(ind)-(80+0.025*thedoy));
+        end
+        
+        %% 1 m/day
+        ind = find(x1>=x & x1<=x+rez & y1>=y & y1<=y+rez);
+        if isempty(ind)
+            medi1(countx,county) = NaN;
+        else
+            medi1(countx,county) = median(z1(ind)-(80+1*thedoy));
+        end
+        
+        %% 5 m/day
+        ind = find(x5>=x & x5<=x+rez & y5>=y & y5<=y+rez);
+        if isempty(ind)
+            medi5(countx,county) = NaN;
+        else
+            medi5(countx,county) = median(z5(ind)-(80+5*thedoy));
+        end
+        county = county + 1;
[…]

### 2020-12-04 figures/code/Fig6_particle_export.m

@@ -1,203 +1,0 @@
-clear
-
-% this code import the number of simulated particles located below 100 m in
-% Papa_meso and Papa_submeso
-
-%% Start with Papa_meso
-
-path = '/Volumes/garuda/Mathieu/particle_tracking/MATLAB/Papa500_';
-for ii = 1:5
-    if ii ==1
-        filename = [path,'0mday/exportTS0mday.txt'];
-    elseif ii == 2
-        filename = [path,'0025mday/exportTS0025mday.txt'];
-    elseif ii == 3
-        filename = [path,'05mday/exportTS05mday.txt'];
-    elseif ii == 4
-        filename = [path,'1mday/exportTS1mday.txt'];
-    elseif ii == 5
-        filename = [path,'5mday/exportTS5mday.txt'];
-    end
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filename,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    
-    export_meso(:,ii) = dataArray{:, 1};
-    
-    clearvars filename delimiter formatSpec fileID dataArray ans
-end; clear ii path
-
-%% Compute export anomaly based on expected export computed from sinking
-% velocity and distance from 100m horizon
-
-N0 = 1971717;
-t0 = 60.5;
-%ws = 5;
-
-time_meso = 60.5:0.125:88.375;
-Nmeso = zeros(size(export_meso));
-
-wscounter = 1;
-for ws = [0 0.025 0.5 1 5]
-    counter = 1;
-    for zz = 15:25
-        if zz == 15
-            Nmeso(time_meso<t0+zz/ws,wscounter) = 0;
-        end
-        if zz == 25
-            Nmeso(time_meso>t0+zz/ws,wscounter) = 1;
-        end
-        Nmeso(time_meso>=t0+zz/ws & time_meso<t0+(zz+1)/ws,wscounter) = counter/11;
-        counter = counter+1;
-    end
-    wscounter = wscounter +1;
-end; clear ws t0 counter wscounter zz
-
-
-%
-%
-% figure(2)
-% plot(time,(data./Ntot-N)*100,'--','LineWidth',2)
[…]

### 2020-12-04 figures/code/Fig6_particle_export_flux.m

@@ -1,223 +1,0 @@
-clear
-
-% this code import the number of simulated particles located below 100 m in
-% Papa_meso and Papa_submeso
-
-%% Start with Papa_summer
-
-% total number of particles
-N0 = 1971717;
-% start day
-t0 = 60.5;
-% Time vector.
-time_meso = 60.5:0.125:88.375;
-
-path = '/Volumes/mahadevanlab/mathieudever/particle_backup/Papa_summer/';
-for ii = 1:5
-    if ii ==1
-        continue
-    elseif ii == 2
-        continue
-    elseif ii == 3
-        filenamedown = [path,'05mday/exportTS05mdaydown.txt'];
-        filenameup = [path,'05mday/exportTS05mdayup.txt'];
-    elseif ii == 4
-        filenamedown = [path,'1mday/exportTS1mdaydown.txt'];
-        filenameup = [path,'1mday/exportTS1mdayup.txt'];
-    elseif ii == 5
-        filenamedown = [path,'5mday/exportTS5mdaydown.txt'];
-        filenameup = [path,'5mday/exportTS5mdayup.txt'];
-    end
-    
-    % Get downward flux
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filenamedown,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    flux_meso_down(:,ii) = dataArray{:, 1};
-    clearvars filenamedown delimiter formatSpec fileID dataArray ans
-    
-    % Get upward flux
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filenameup,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    flux_meso_up(:,ii) = dataArray{:, 1};
-    
-    clearvars filenameup delimiter formatSpec fileID dataArray ans
-end; clear ii path
-
-
-%% Compute export anomaly based on expected export computed from sinking
-% velocity and distance from 100m horizon
-
-grav_flux_meso = zeros(size(flux_meso_up));
-wscounter = 2;
-for ws = [0.025 0.5 1 5]
[…]

### 2020-12-04 figures/code/Fig6_v3.m

@@ -1,88 +1,0 @@
-clear
-close all
-
-istart = 200;
-ifinish = 400;
-
-%fullfigure
-
-%%
-thefolder = pwd;
-for plt = 2:-1:1
-    if plt == 1
-        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/highrez
-        timesteps = 24000:1000:36000;
-    elseif plt == 2
-        cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_winter/highrez
-        timesteps = 32000:1000:56000;
-    end
-    counter = 0;
-    thew = [];
-    for tt = timesteps
-        counter = counter +1;
-        
-        
-        w = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'w');
-        w(1,:,:) = NaN; w(end,:,:) = NaN;
-        
-        x = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'xc')*1000;
-        y = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'yc')*1000;
-        Z2 = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'zc');
-        z = squeeze(Z2(1,1,:));
-        [X,Y] = meshgrid(x,y);
-        [X2,Y2,Z2] = meshgrid(x,y,squeeze(Z2(1,1,:)));
-        X2 = permute(X2,[2 1 3]);
-        Y2 = permute(Y2,[2 1 3]);
-        Z2 = permute(Z2,[2 1 3]);
-        
-        w = permute(w,[2 1 3]);
-        
-        %% PLOT HISTOGRAMS
-        
-        blop = w(istart:ifinish,:,16:end)*86400;
-        thew = cat(1,thew,blop(:));
-        if tt == 36000 && plt == 1
-            %histogram(thew,-10:.5:10,'Normalization','probability')
-            yyaxis right
-            [N,EDGES] = histcounts(thew,-10:.1:10,'Normalization','probability');
-            h2 = plot((EDGES(2:end)+EDGES(1:end-1))/2,N*100,'color',[0.8500    0.3250    0.0980],'linewidth',3);
-            set(gca,'ycolor',[0.8500    0.3250    0.0980])
-            ylabel('PDF [%]')
-        elseif tt == 56000 && plt == 2
-            fullfigure
[…]

### 2020-12-04 figures/code/Fig6_v4.m

@@ -1,238 +1,0 @@
-clear
-
-%speed = {'0025','05','1','5'};
-speed = {'0025','1','5'};
-fullfigure
-for ii = 1:length(speed)
-    subplot(2,1,1)
-    
-    %% SUMMER
-    % Get data
-    filename = ['/Volumes/home/mdever/allparticles/wtotal',num2str(speed{ii}),'mday_summer.csv'];
-    M = csvread(filename);
-    %M(M(:,2)==max(M(:,2)),2) = NaN;
-    
-    % Plots data
-    plot(M(:,1)*86400,M(:,2)./sum(M(:,2))*100,'r')
-    hold on
-    set(gca,'fontsize',18)
-    xlabel('Vertical velocity [m/day]')
-    ylabel('Particles PDF [%]')
-    
-    % computes stats
-    mu = sum(M(:,1).*M(:,2))/sum(M(:,2));
-    std = sqrt(sum(M(:,2).*(M(:,1)-mu).^2)/(sum(M(:,2))-1));
-    s = (sum(M(:,2).*(M(:,1)-mu).^3)/sum(M(:,2)))/(std^3);
-    k = (sum(M(:,2).*(M(:,1)-mu).^4)/sum(M(:,2)))/(std^4) - 3;
-    
-    xlim([-20 20])
-    %ylim([0 60])
-    
-    % display stats
-    %YLIM = get(gca,'ylim');
-    %text(-28,0.85*(YLIM(2)-YLIM(1))+YLIM(1),{['\mu = ',num2str(mu*86400,'%2.2f')],...
-    %    ['\sigma = ',num2str(std*86400,'%2.2f')],...
-    %    ['s = ',num2str(s*86400,'%2.2e')],...
-    %    ['\kappa = ',num2str(k*86400,'%2.2e')]},...
-    %    'fontsize',21,'color','r')
-    
-    
-end
-
-%% GET MODEL PDF
-istart = 200;
-ifinish = 400;
-
-thefolder = pwd;
-cd /Volumes/mahadevanlab/mathieudever/PSOM_backup/PSOM_outputs/Papa_summer/highrez
-timesteps = 24000:1000:36000;
-counter = 0;
-thew = [];
-for tt = timesteps
-    counter = counter +1;
-    
-    w = ncread(['full_',num2str(tt,'%05d'),'.cdf'],'w');
-    w(1,:,:) = NaN; w(end,:,:) = NaN;
-    
[…]

### 2020-12-04 figures/code/Fig6_v5.m

@@ -1,162 +1,0 @@
-clear
-
-%% Import (x,y,z) for each size class in winter and summer
-[x0025s,y0025s,z0025s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal0025mday_summer.csv');
-[x1s,y1s,z1s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal1mday_summer.csv');
-[x5s,y5s,z5s] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal5mday_summer.csv');
-
-[x0025,y0025,z0025] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal0025mday_winter.csv');
-[x1,y1,z1] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal1mday_winter.csv');
-[x5,y5,z5] = importxyz('/Volumes/mdever/particleposition/doy25/wtotal5mday_winter.csv');
-
-color0025 = [215,48,39]/256;
-color1 = [39,100,25]/256;
-color5 = [49,54,149]/256;
-
-%% Bin the data into 1x1 km and compute the median vertical displacement
-% with respect to the gravitational model
-thedoy = 25;
-countx = 1;
-rez = 1;
-for x = 0:rez:111
-    county = 1;
-    for y = 100:rez:200
-        
-        %% 0025 m/day
-        ind = find(x0025>=x & x0025<=x+rez & y0025>=y & y0025<=y+rez);
-        if isempty(ind)
-            medi0025(countx,county) = NaN;
-        else
-            medi0025(countx,county) = median(z0025(ind)-(80+0.025*thedoy));
-        end
-        
-        %% 1 m/day
-        ind = find(x1>=x & x1<=x+rez & y1>=y & y1<=y+rez);
-        if isempty(ind)
-            medi1(countx,county) = NaN;
-        else
-            medi1(countx,county) = median(z1(ind)-(80+1*thedoy));
-        end
-        
-        %% 5 m/day
-        ind = find(x5>=x & x5<=x+rez & y5>=y & y5<=y+rez);
-        if isempty(ind)
-            medi5(countx,county) = NaN;
-        else
-            medi5(countx,county) = median(z5(ind)-(80+5*thedoy));
-        end
-        county = county + 1;
[…]

### 2020-12-04 figures/code/Fig7.m

@@ -4,18 +4,10 @@ clear
 % DOY 25 in Summer/Winter for xi = 2 and xi = 4
 
 %% Import w for each size class in winter and summer
-% tt = 25;
-% [~,~,wt0025s] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_summer.csv');
-% [~,~,wt1s] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_summer.csv');
-% [~,~,wt5s] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_summer.csv');
-% 
-% [~,~,wt0025w] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_winter.csv');
-% [~,~,wt1w] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_winter.csv');
-% [~,~,wt5w] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_winter.csv');
-% 
-% save Fig7_data.mat
-% error('stop')
-load Fig7_data.mat
+
+% Load data previously extracted from big database
+load dataset/Fig7_data.mat
+
 %% Set colors for each class
 color0025 = [215,48,39]/256;
 color1 = [39,100,25]/256;
@@ -45,25 +37,6 @@ B0025_4 = B0*(0.025/wmax)^((3-slope)/2);
 B1_4 = B0*(1/wmax)^((3-slope)/2);
 B5_4 = B0*(5/wmax)^((3-slope)/2);
 
-% Compute histograms in summer
-[N0025s,E] = histcounts(wt0025s*86400,-10.05:.1:10.05);
-[N1s,~] = histcounts(wt1s*86400,-10.05:.1:10.05);
-[N5s,~] = histcounts(wt5s*86400,-10.05:.1:10.05);
-E = (E(1:end-1)+E(2:end))/2;
-
-N0025s(N0025s==0) = 1e-2; % to lok better in log plots
-N1s(N1s==0) = 1e-2;
-N5s(N5s==0) = 1e-2;
-
-% Compute histograms in winter
-[N0025w,Ew] = histcounts(wt0025w*86400,-155:10:155);
-[N1w,~] = histcounts(wt1w*86400,-155:10:155);
-[N5w,~] = histcounts(wt5w*86400,-155:10:155);
[…]

### 2020-12-04 figures/code/Fig7_biomass_export_flux.m

@@ -1,347 +1,0 @@
-clear
-
-% this code import the number of simulated particles located below 100 m in
-% Papa_meso and Papa_submeso
-
-%% Start with Papa_summer
-
-% arbitrary biomass unit
-B0 = 1;
-% Sinking-velocity classes
-ws = [0 0.025 0.5 1 5];
-% Reference sinking-velocity
-ws0 = max(ws);
-
-% total number of particles
-N0 = 1971717;
-% start day
-t0 = 60.5;
-% Time vector.
-time_meso = 60.5:0.125:88.375;
-
-path = '/Volumes/mahadevanlab/mathieudever/particle_backup/Papa_summer/';
-for ii = 1:5
-    if ii ==1
-        continue
-    elseif ii == 2
-        continue
-    elseif ii == 3
-        filenamedown = [path,'05mday/exportTS05mdaydown.txt'];
-        filenameup = [path,'05mday/exportTS05mdayup.txt'];
-    elseif ii == 4
-        filenamedown = [path,'1mday/exportTS1mdaydown.txt'];
-        filenameup = [path,'1mday/exportTS1mdayup.txt'];
-    elseif ii == 5
-        filenamedown = [path,'5mday/exportTS5mdaydown.txt'];
-        filenameup = [path,'5mday/exportTS5mdayup.txt'];
-    end
-    
-    % Get downward flux
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filenamedown,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    flux_meso_down(:,ii) = dataArray{:, 1};
-    clearvars filenamedown delimiter formatSpec fileID dataArray ans
-    
-    % Get upward flux
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filenameup,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    flux_meso_up(:,ii) = dataArray{:, 1};
-    
-    clearvars filenameup delimiter formatSpec fileID dataArray ans
-end; clear ii
-
-for ii = 1:5
-    if ii ==1
-        continue
-    elseif ii == 2
-        continue
-    elseif ii == 3
-        continue
[…]

### 2020-12-04 figures/code/Fig7_biomass_spectra.m

@@ -1,133 +1,0 @@
-clear
-
-cmap = get(gca,'ColorOrder');
-%close all
-
-%speed = {'0025','05','1','5'};
-speed = {'0025','1','5'};
-%numspeed = [0.025,0.5,1,5];
-numspeed = [0.025,1,5];
-fullfigure
-for ii = 1:length(speed)
-    subplot(2,1,1)
-    
-    %% SUMMER
-    % Get data
-    filename = ['/Volumes/home/mdever/sousML/wtotal',num2str(speed{ii}),'mday_summer.csv'];
-    M = csvread(filename);
-    %M(M(:,2)==max(M(:,2)),2) = NaN;
-    
-    % convert Particles to biomass
-    wmax = 5; wmin = 0.025;
-    slope = 3; B0 = 1;
-    Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-
-    slope = 2;
-    B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-    B2 = B0*(numspeed(ii)/wmax)^((3-slope)/2);
-    
-    slope = 3;
-    B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-    B3 = B0*(numspeed(ii)/wmax)^((3-slope)/2);
-    
-    slope = 4;
-    B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-    B4 = B0*(numspeed(ii)/wmax)^((3-slope)/2);
-    
-    % Plots data
-    h1(ii)=plot(M(:,1)*86400,M(:,2)*B2,'-','linewidth',2,'color',cmap(ii,:));
-    disp(['Total biomass for speed ',speed{ii},'is ',num2str(sum(M(:,2)*B2)),' and xi = 2'])
-    disp(['Total biomass for speed ',speed{ii},'is ',num2str(sum(M(:,2)*B4)),' and xi = 4'])
-    hold on
[…]

### 2020-12-04 figures/code/Fig7_biomass_spectra_remin.m

@@ -1,92 +1,0 @@
-clear
-
-cmap = get(gca,'ColorOrder');
-close all
-
-%speed = {'0025','05','1','5'};
-speed = {'0025','1','5'};
-%numspeed = [0.025,0.5,1,5];
-numspeed = [0.025,1,5];
-styles = {'-',':'};
-fullfigure
-for ii = 2:length(speed)
-    subplot(2,1,1)
-    
-    for xi = [2 4]
-        %% SUMMER
-        % Get data
-        filename = ['/Volumes/home/mdever/sousML/wtotal',speed{ii},'mday_remin_summer_xi',num2str(xi),'.csv'];
-        M = csvread(filename);
-        %M(M(:,2)==max(M(:,2)),2) = NaN;
-        
-        % Plots data
-        h1(xi/2)=plot(M(:,1)*86400,M(:,2),styles{xi/2},'linewidth',2,'color',cmap(ii,:));
-        hold on
-        set(gca,'fontsize',18,'yscale','log')
-        xlabel('Vertical velocity [m/day]')
-        ylabel('Biomass [arbitrary unit]')
-        grid on
-        
-        % computes stats
-        mu = sum(M(:,1).*M(:,2))/sum(M(:,2));
-        std = sqrt(sum(M(:,2).*(M(:,1)-mu).^2)/(sum(M(:,2))-1));
-        s = (sum(M(:,2).*(M(:,1)-mu).^3)/sum(M(:,2)))/(std^3);
-        k = (sum(M(:,2).*(M(:,1)-mu).^4)/sum(M(:,2)))/(std^4) - 3;
-    end
-    xlim([-20 20])
-    %ylim([0 60])
-    
-    % display stats
-    %YLIM = get(gca,'ylim');
-    %text(-28,0.85*(YLIM(2)-YLIM(1))+YLIM(1),{['\mu = ',num2str(mu*86400,'%2.2f')],...
-    %    ['\sigma = ',num2str(std*86400,'%2.2f')],...
-    %    ['s = ',num2str(s*86400,'%2.2e')],...
-    %    ['\kappa = ',num2str(k*86400,'%2.2e')]},...
-    %    'fontsize',21,'color','r')
-end
-title('Summer','fontsize',21)
-legend([h1],'\xi = 2','\xi = 4')
-
-%% WINTER
-for ii = 1:length(speed)
-    subplot(2,1,2)
-    
-    for xi = [2 4]
-        
-        %% SUMMER
[…]

### 2020-12-04 figures/code/Fig7_revised.m

@@ -1,260 +1,0 @@
-clear
-
-%% This figure plots the histogram of the relative biomass vs vertical velocity at 
-% DOY 25 in Summer/Winter for xi = 2 and xi = 4
-
-%% Import w for each size class in winter and summer
-
-% Load data previously extracted from big database
-load dataset/Fig7_data.mat
-
-%% Set colors for each class
-color0025 = [215,48,39]/256;
-color1 = [39,100,25]/256;
-color5 = [49,54,149]/256;
-
-%% compute biomass per simulated particle
-
-% Set of marameters
-wmax = 5; wmin = 0.025;
-slope = 3; B0 = 1;
-% Compute total biomass based on the paramters
-Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-
-% For Junge slope = 2
-slope = 2;
-% Compute biomass of 1 largest particle necessary to keep total biomass constant
-B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-B0025_2 = B0*(0.025/wmax)^((3-slope)/2);
-B1_2 = B0*(1/wmax)^((3-slope)/2);
-B5_2 = B0*(5/wmax)^((3-slope)/2);
-
-% For Junge slope = 4
-slope = 4;
-% Compute biomass of 1 largest particle necessary to keep total biomass constant
-B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-B0025_4 = B0*(0.025/wmax)^((3-slope)/2);
-B1_4 = B0*(1/wmax)^((3-slope)/2);
-B5_4 = B0*(5/wmax)^((3-slope)/2);
-
-%%
-% Calculate total biomass to normalize by
-totalB = sum(N0025s.*B0025_2)+sum(N1s.*B1_2)+sum(N5s.*B5_2);
[…]

### 2020-12-04 figures/code/Fig8.m

@@ -1,17 +1,12 @@
 clear
 
-%% This figure plots the histogram of the biomass vs vertical velocity at 
-% DOY 25 in Summer/Winter with and without remineralization for slope = 4
+%% This figure plots the histogram of the relative biomass vs vertical velocity at 
+% DOY 25 in Summer/Winter for xi = 2 and xi = 4
 
 %% Import w for each size class in winter and summer
-tt = 25;
-[~,~,wt0025s] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_summer.csv');
-[~,~,wt1s] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_summer.csv');
-[~,~,wt5s] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_summer.csv');
 
-[~,~,wt0025w] = importw('/Volumes/mdever/particlespeed/doy25/w0025mday_winter.csv');
-[~,~,wt1w] = importw('/Volumes/mdever/particlespeed/doy25/w1mday_winter.csv');
-[~,~,wt5w] = importw('/Volumes/mdever/particlespeed/doy25/w5mday_winter.csv');
+% Load data previously extracted from big database
+load dataset/Fig8_data.mat
 
 %% Set colors for each class
 color0025 = [215,48,39]/256;
@@ -26,6 +21,14 @@ slope = 3; B0 = 1;
 % Compute total biomass based on the paramters
 Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
 
+% For Junge slope = 2
+slope = 2;
+% Compute biomass of 1 largest particle necessary to keep total biomass constant
+B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
+B0025_2 = B0*(0.025/wmax)^((3-slope)/2);
+B1_2 = B0*(1/wmax)^((3-slope)/2);
[…]

### 2020-12-04 figures/code/Fig8_biomass_export_flux_remin.m

@@ -1,342 +1,0 @@
-clear
-
-% this code import the number of simulated particles located below 100 m in
-% Papa_meso and Papa_submeso
-
-%% Start with Papa_summer
-
-% arbitrary biomass unit
-B0 = 1;
-% Sinking-velocity classes
-ws = [0 0.025 0.5 1 5];
-% Reference sinking-velocity
-ws0 = max(ws);
-
-% total number of particles
-N0 = 1971717;
-% start day
-t0 = 60.5;
-% Time vector.
-time_meso = 60.5:0.125:88.375;
-
-path = '/Volumes/mahadevanlab/mathieudever/particle_backup/Papa_summer/';
-for ii = 1:5
-    if ii ==1
-        continue
-    elseif ii == 2
-        continue
-    elseif ii == 3
-        filenamedown = [path,'05mday/exportTS05mdaydown.txt'];
-        filenameup = [path,'05mday/exportTS05mdayup.txt'];
-    elseif ii == 4
-        filenamedown = [path,'1mday/exportTS1mdaydown.txt'];
-        filenameup = [path,'1mday/exportTS1mdayup.txt'];
-    elseif ii == 5
-        filenamedown = [path,'5mday/exportTS5mdaydown.txt'];
-        filenameup = [path,'5mday/exportTS5mdayup.txt'];
-    end
-    
-    % Get downward flux
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filenamedown,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    flux_meso_down(:,ii) = dataArray{:, 1};
-    clearvars filenamedown delimiter formatSpec fileID dataArray ans
-    
-    % Get upward flux
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filenameup,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    flux_meso_up(:,ii) = dataArray{:, 1};
-    
-    clearvars filenameup delimiter formatSpec fileID dataArray ans
-end; clear ii
-
-for ii = 1:5
-    if ii ==1
-        continue
-    elseif ii == 2
-        continue
-    elseif ii == 3
[…]

### 2020-12-04 figures/code/Fig8_revised.m

@@ -1,256 +1,0 @@
-clear
-
-%% This figure plots the histogram of the relative biomass vs vertical velocity at 
-% DOY 25 in Summer/Winter for xi = 2 and xi = 4
-
-%% Import w for each size class in winter and summer
-
-% Load data previously extracted from big database
-load dataset/Fig8_data.mat
-
-%% Set colors for each class
-color0025 = [215,48,39]/256;
-color1 = [39,100,25]/256;
-color5 = [49,54,149]/256;
-
-%% compute biomass per simulated particle
-
-% Set of marameters
-wmax = 5; wmin = 0.025;
-slope = 3; B0 = 1;
-% Compute total biomass based on the paramters
-Btot = B0/(wmax.^((3-slope)/2))*(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-
-% For Junge slope = 2
-slope = 2;
-% Compute biomass of 1 largest particle necessary to keep total biomass constant
-B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-B0025_2 = B0*(0.025/wmax)^((3-slope)/2);
-B1_2 = B0*(1/wmax)^((3-slope)/2);
-B5_2 = B0*(5/wmax)^((3-slope)/2);
-
-% For Junge slope = 4
-slope = 4;
-% Compute biomass of 1 largest particle necessary to keep total biomass constant
-B0 = Btot*(wmax.^((3-slope)/2))/(2/(5-slope)*wmax.^((5-slope)/2) - 2/(5-slope)*wmin.^((5-slope)/2));
-B0025_4 = B0*(0.025/wmax)^((3-slope)/2);
-B1_4 = B0*(1/wmax)^((3-slope)/2);
-B5_4 = B0*(5/wmax)^((3-slope)/2);
-
-%%
-% Calculate total biomass to normalize by
-totalB = sum(N0025s.*B0025_2)+sum(N1s.*B1_2)+sum(N5s.*B5_2);
[…]

### 2020-12-04 figures/code/old_Fig7_biomass_export_old.m

@@ -1,217 +1,0 @@
-clear
-
-% this code import the number of simulated particles located below 100 m in
-% Papa_meso and Papa_submeso
-
-%% Start with Papa_meso
-
-time_meso = 60.5:0.125:88.375;
-
-path = '/Volumes/mathieudever/particle_backup/Papa500/';
-for ii = 3:5
-    if ii ==1
-        filename = [path,'0mday/exportTS0mday.txt'];
-    elseif ii == 2
-        filename = [path,'0025mday_remin/exportTS0025mday_remin.txt'];
-    elseif ii == 3
-        filename = [path,'05mday_remin/exportTS05mday_remin.txt'];
-    elseif ii == 4
-        filename = [path,'1mday_remin/exportTS1mday_remin.txt'];
-    elseif ii == 5
-        filename = [path,'5mday_remin/exportTS5mday_remin.txt'];
-    end
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filename,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    
-    export_meso_remin(:,ii) = dataArray{:, 1};
-    
-    clearvars filename delimiter formatSpec fileID dataArray ans
-end; clear ii path
-
-time_meso = 60.5:0.125:88.375;
-
-path = '/Volumes/mathieudever/particle_backup/Papa500/';
-for ii = 3:5
-    if ii ==1
-        filename = [path,'0mday/exportTS0mday.txt'];
-    elseif ii == 2
-        filename = [path,'0025mday/exportTS0025mday.txt'];
-    elseif ii == 3
-        filename = [path,'05mday/exportTS05mday.txt'];
-    elseif ii == 4
-        filename = [path,'1mday/exportTS1mday.txt'];
-    elseif ii == 5
-        filename = [path,'5mday/exportTS5mday.txt'];
-    end
-    formatSpec = '%f%[^\n\r]';
-    fileID = fopen(filename,'r');
-    dataArray = textscan(fileID, formatSpec, 'Delimiter', '', 'TextType', 'string',  'ReturnOnError', false);
-    fclose(fileID);
-    
-    export_meso(:,ii) = dataArray{:, 1};
-    
-    clearvars filename delimiter formatSpec fileID dataArray ans
[…]

### 2020-12-04 size_differentiated_export.tex
Updates from Overleaf
final adjusmtents
hopefully.

@@
 \usepackage{lineno}
-\usepackage[]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage[finalnew]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
 \usepackage{soul}
@@
 \usepackage{amsmath}
-\usepackage{ulem}
+%\usepackage{ulem}
 
@@
 	Photosynthesis in the sunlit upper ocean and the production of Particulate Organic Carbon (POC) takes up dissolved inorganic carbon and facilitates the uptake of CO$_2$ from the atmosphere.
-The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \cite{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.
+The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \cite{Falkowski_1998, Boyd_2019} on timescales ranging from days to years depending on the sinking depth and  circulation.
 Despite progress on sampling and viewing particles in the ocean, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density \cite{McDonnell_2010,Mcdonnell_2012}.
@@
 
-	Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior.
+	Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior \cite{Stukel_2017b,Stukel_2018,Llort_2018}.
 For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \cite{vanHaren_2006, Waite_2016} and in mesoscale features in the California current \cite{Stukel_2017}.
@@
 The distribution of relative vorticity associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity \cite{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \cite{Mahadevan_2006}.
-Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through localized downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.
+Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through localized downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}, \add{a process that might not be captured if submesoscales O(1 km) are not fully resolved} \cite{Resplandy_2019}.
 The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
@@
 	Studies investigating submesoscale dynamics traditionally focused on regions where the presence of submesoscale fronts and filaments are established, such as western boundary currents with strong gradients \cite{Dasaro_2011, Thomas_2013}, or the edge of mesoscale features \cite{vanHaren_2006,Waite_2016}.
-The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \cite{Thompson_2016, Buckingham_2016}.
+The seasonality in submesoscale dynamics captured in the glider dataset at Station Papa and reflected in the model experiments, echoes the behavior seen from recent observational studies conducted at a similar latitude in the Atlantic Ocean, which demonstrate the intensification of submesoscale dynamics in the wintertime \cite{Thompson_2016, Buckingham_2016, Erickson_2018}.
 Despite being sometimes qualified as an ``eddy desert" with low kinetic energy \cite{Chelton_2011}, ocean characteristics in the eastern part of the Pacific subpolar gyre suggest the presence of submesoscale features in the wintertime: strong density gradients, localized Rossby numbers of order 1, a balanced Richardson number $Ri_b = \frac{f^2N^2}{M^4}$ smaller than 1, a positively skewed distribution in vorticity, and a negatively skewed distribution of vertical velocities \cite<see Figure \ref{fig: dynamics};>[]{Thomas_2013b,Rudnick_2001, Buckingham_2016}.
@@
 Glider data is archived at the University of Washington's Library \cite<\url{http://hdl.handle.net/1773/41656};>[]{Pelland_2018_data}.
-Code to reproduce analysis and figures are publicly available at \url{https://github.com/matdever/Size-differentiated_Export_GBC} \cite{Dever_dataset}.
-Due to the very large filesize, model outputs and particle trajectories are available on request.
-%Finally, we are grateful to the two anonymous reviewers for their valuable comments and suggestions.
+Both the code and dataset necessary to reproduce analysis and figures are publicly available\cite{Dever_dataset, Dever_dataset2}.
+Finally, we are grateful to the two anonymous reviewers for their valuable comments and suggestions.
 

### 2021-01-27 size_differentiated_export.tex
Adresses editor's comments
Lengthen the discussion section

@@
 The distribution of relative vorticity associated with submesoscale dynamics near the surface exhibits an asymmetry with higher values of positive vorticity than negative vorticity \cite{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger scale upwelling regions \cite{Mahadevan_2006}.
-Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through localized downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}, \add{a process that might not be captured if submesoscales O(1 km) are not fully resolved} \cite{Resplandy_2019}.
+Enhanced vertical velocities can aid the supply nutrients to the sunlit layer of the ocean for primary production \cite{Mahadevan_2000,Levy_2001} or can significantly increase the export of POC to the ocean interior through localized downwelling \cite{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}, a process that might not be captured if submesoscales O(1 km) are not fully resolved \cite{Resplandy_2019}.
 The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism for exporting slow sinking or neutrally buoyant particles on timescales shorter than their remineralization timescales.
@@
 Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles.
-Particles located deeper than the maximum winter mixed layer \cite<i.e., 100 m;>[]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.
+%Particles located deeper than the maximum winter mixed layer \cite<i.e., 100 m;>[]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.
 
@@
 	Introducing remineralization processes significantly decreases the biomass flux.
-Counter-intuitively, however, the implementation of a remineralization scheme further strengthens the contribution of slower-sinking particles to the biomass flux\add{, once particles have left the euphotic layer} (Figure \ref{fig: biomass_export_remin}).
+Counter-intuitively, however, the implementation of a remineralization scheme further strengthens the contribution of slower-sinking particles to the biomass flux, once particles have left the euphotic layer (Figure \ref{fig: biomass_export_remin}).
 This can be explained by the fact that remineralization processes have a greater impact on sinking-velocity classes that rely on gravitational sinking to be exported, as these particles decelerate as they remineralize.
@@
 Their export timescale is barely affected by remineralization processes as it only depends on local ocean dynamics.
-\add{Changing the remineralization timescale would therefore only affect the results in a gravitationally-driven flux: increasing the timescales (i.e.
+Changing the remineralization timescale would therefore only affect the results in a gravitationally-driven flux: increasing the timescales (i.e.
 slower remineralization) would give more weight to the smaller classes, while decreasing the timescales (i.e.
@@
 lose 12\% of their biomass per day).
-While this affects the total amount of biomass flux, it does not impact the respective contributions of the different particle classes to the downward biomass flux.}
+While this affects the total amount of biomass flux, it does not impact the respective contributions of the different particle classes to the downward biomass flux.
 
@@
 However, for $\xi>5$, the slope of the biomass flux spectrum becomes negative as well, meaning that the biomass flux is always dominated by the slow-sinking particle classes, regardless of the ocean dynamical regime.
-\change{While considered large, values of $\xi > 5$ remain realistic and fall within the range obtained from satellite-based estimates}{While values of $\xi > 5$ have been estimated by} \citeA{Kostadinov_2009} \add{using satellite data, in-situ estimated values of $\xi$ tend to range between 2 and 4.5}\cite{White_2015, Cram_2018}.
+While values of $\xi > 5$ have been estimated by \citeA{Kostadinov_2009} using satellite data, in-situ estimated values of $\xi$ tend to range between 2 and 4.5 \cite{White_2015, Cram_2018}.
 
-	The results of this study suggest that slow- and non-sinking particles must be considered when studying the downward flux of particulate matter in the upper ocean.
-The patchiness associated with both particle production and submesoscale features poses a real observational challenge to properly resolve vertical fluxes.
-Based on our findings, subsequent studies should focus on testing the impact of patchiness on vertical fluxes.
+\add{Our findings add to a rapidly growing body of literature supporting the key role of an export pathway from the upper ocean to the interior driven by vertical ocean dynamic, and directly affecting particulate carbon.
+This pathway is often referred to as the  ''particle-injection pump" }\cite{Boyd_2019}\add{, or "subduction hot spots" }\cite{Levy_2013, Omand_2015, Resplandy_2019}, \add{ and is consistently identified as an important mechanism to POC export} \cite{Siegel_2016, Stukel_2017, Stukel_2018, Llort_2018}.
+\add{Vertical mixing at submesocales, in fact, was found to be equally important for the subduction of tracers from the mixed layer to the interior, and the obduction of tracers having a subsurface maximum (e.g., nutrients)} \cite{Taylor_2020, Mahadevan_2016}.
+\add{The importance of the seasonality in submesoscales dynamics highlighted in our process-oriented study supports recent findings obtained from high-resolution observations: both }\citeA{Erickson_2018} and \citeA{Bol_2018}\add{ studied glider data to conclude that the winter intensification of submesoscale dynamics can generate a large downward export of POC.
+The third key component to our results, additionally to the roles of submesocale dynamics and seasonality, is the contribution of smaller, slower-sinking POC to the export flux.
+The results presented in this work directly align with studies providing evidence that smaller particles contribute significantly to the POC flux} \cite{Baker_2017, Riley_2012, Bol_2018, Taylor_2020}.\add{ The magnitude of the downward flux driven by slow-sinking particles, however, is still uncertain and was sometimes estimated to be largely compensated by an upward flux} \cite{Resplandy_2019}, \add{indicating a possible dependence on data resolution.
+In our study, we piece together three key components to POC vertical fluxes to characterize limit cases where ocean conditions favor either a gravitationally- or advectively-driven POC flux.
+We reached the conclusion}
+\remove{The results of this study suggest} that slow- and non-sinking particles \add{, compared to the magnitude of vertical currents,} should be considered when studying the downward flux of particulate matter in the upper ocean.
+\add{Furthermore,} the patchiness associated with both particle production and submesoscale features poses a real observational challenge to properly resolve vertical fluxes.
+Based on our findings, subsequent studies could focus on testing the impact of patchiness on vertical fluxes.
 In the wintertime, when size spectral slope is steep and submesoscale dynamics most active, vertical fluxes could be grossly underestimated depending on the level of co-occurrence between particle production and stronger vertical currents.
@@
 		\end{enumerate}
-		\item Remineralization processes \add{below the euphotic depth} logically reduce the amount of biomass flux.
+		\item Remineralization processes below the euphotic depth logically reduce the amount of biomass flux.
 However, it unexpectedly enhances the role of slower-sinking particles, which are are advectively transported.
-The impact of remineralization \add{below the euphotic depth} is greater on faster-sinking particles since it affects both the biomass content and their sinking velocity.
+The impact of remineralization below the euphotic depth is greater on faster-sinking particles since it affects both the biomass content and their sinking velocity.
 	\end{enumerate}
